### 2016-07-14 Manuscript.tex
Initial ShareLaTeX Import

\documentclass[final,twocolumn,5p]{elsarticle}
\usepackage{tikz}
  \def\firstcircle{(90:1.75cm) circle (2.5cm)}
  \def\secondcircle{(210:1.75cm) circle (2.5cm)}
  \def\thirdcircle{(330:1.75cm) circle (2.5cm)} 
\usepackage{comment}
\usepackage{framed,graphicx}
\usepackage{multirow}
\usepackage{rotating}
\usepackage{amsmath}
\usepackage{bigstrut}
\usepackage{color}
\usepackage{graphics} 
\usepackage{eqparbox}
\usepackage{graphics}
\usepackage{colortbl} 
%\usepackage{times}
 \usepackage{mathptmx} \usepackage[scaled=.90]{helvet} \usepackage{courier}
\usepackage{balance}
\usepackage{picture}
\usepackage{algorithm}
\usepackage{algorithmicx}
\usepackage{algpseudocode}
\usepackage[export]{adjustbox}
\renewcommand{\footnotesize}{\scriptsize}
\definecolor{lightgray}{gray}{0.8}
\definecolor{darkgray}{gray}{0.6}
\definecolor{lavenderpink}{rgb}{0.98, 0.68, 0.82}
\definecolor{celadon}{rgb}{0.67, 0.88, 0.69}
\renewcommand{\algorithmicrequire}{\textbf{Input:}}
\renewcommand{\algorithmicensure}{\textbf{Output:}}
%%% graph
\newcommand{\crule}[3][darkgray]{\textcolor{#1}{\rule{#2}{#3}}}

\newcommand{\quart}[4]{\begin{picture}(80,4)%1
{\color{black}\put(#3,2){\circle*{4}}\put(#1,2){\line(1,0){#2}}}\end{picture}}

\definecolor{Gray}{gray}{0.95}
\definecolor{LightGray}{gray}{0.975}

\newcommand{\wei}[1]{\textcolor{red}{Wei: #1}} 
\newcommand{\Menzies}[1]{\textcolor{red}{Dr.Menzies: #1}}

%% timm tricks
\newcommand{\bi}{\begin{itemize}[leftmargin=0.4cm]}
\newcommand{\ei}{\end{itemize}}
\newcommand{\be}{\begin{enumerate}}
\newcommand{\ee}{\end{enumerate}}
\newcommand{\tion}[1]{\S\ref{sect:#1}}
\newcommand{\fig}[1]{Figure~\ref{fig:#1}}
\newcommand{\tab}[1]{Table~\ref{tab:#1}}
\newcommand{\eq}[1]{Equation~\ref{eq:#1}}

\usepackage[shortlabels]{enumitem}  
\usepackage{url}

\usepackage{tikz}
\usepackage{xcolor}
   \usepackage[framed]{ntheorem}
\usepackage{framed}
\usetikzlibrary{shadows}
%\newtheorem{Lesson}{Lesson}
\theoremclass{Lesson}
\theoremstyle{break}

% inner sep=10pt,
\tikzstyle{thmbox} = [rectangle, rounded corners, draw=black,
  fill=Gray!20,  drop shadow={fill=black, opacity=1}]
\newcommand\thmbox[1]{%
  \noindent\begin{tikzpicture}%
  \node [thmbox] (box){%
\begin{minipage}{.94\textwidth}%    
      \vspace{-3mm}#1\vspace{-3mm}%
    \end{minipage}%
  };%
  \end{tikzpicture}}

\let\theoremframecommand\thmbox
\newshadedtheorem{lesson}{Research answer}

\begin{document}

\begin{frontmatter}

\title{Which ``Bad Smells'' Can Be Ignored?}

\author{Rahul Krishna\corref{cor1}\textsuperscript{a,}}
\ead{rkrish11@ncsu.edu}
\author{Tim Menzies\corref{cor1}\textsuperscript{a,}}
\ead{tim.menzies@gmail.com}
\author{Lucas Layman\textsuperscript{b}}
\ead{ llayman@cese.fraunhofer.org }
\cortext[cor1]{Corresponding author: Tel:+1-919-396-4143(Rahul)}
\address{\textsuperscript{a}Department of Computer Science, North Carolina State University, Raleigh, NC, USA\\
\textsuperscript{b}Fraunhofer CESE, College Park, USA}

\begin{abstract} 
{\bf Context: }The literature lists many bad smells that may be detrimental to a software system. But which are relevant to the current project and which can be ignored?
Developers, text books, and tools disagree on which bad smells are important. 
Further, it is unclear at what threshold values smell-related metrics
should trigger code improvement or preventative maintenance. Most studies do not offer {\em both} measurable metrics {\em and} a threshold for their proposed bad smells.

\noindent 
{\bf Objective: }We seek to propose a tool to prioritize  bad  smells.

\noindent
{\bf Method: } We introduce XTREE, a tool which, given a historical log of defects seen previously in the code, deprioritizes bad smells that have no prior association with defects.

\noindent
{\bf Evaluation: } We evaluate XTREE's recommendations for bad smell improvement against recommendations from previous work (Shatnawi, Alves, and Borges) using multiple data sets of code metrics and defect counts.

\noindent
{\bf Results: }Code modules that are changed in response to XTREE's recommendations contain significantly fewer defects than recommendations in previous studies. Further, XTREE endorses changes to far fewer code metrics, and that bad smell recommendations (learned from previous studies) are not universal to software projects.

\noindent
{\bf Conclusion: }It is important to  prioritize the importance of specific bad smells in the context of each project since not all bad smells are relevant to the current project. Based on these results, we endorse using bad smells to guiding refactoring.

\end{abstract}
\end{frontmatter}
\pagenumbering{arabic} %XXX delete before submission

\vspace{1mm}
\noindent
{\bf Keywords:} Bad smells,
performance prediction,  decision trees

\section{Introduction}

\noindent
According to   Fowler ~\cite{fowler99}, bad smells (a.k.a. code smells)
are ``a surface indication that usually corresponds to a deeper problem''.
Fowler strongly recommends   removing   code smells   by
\begin{quote}
``...applying a series of small behavior-preserving transformations, each 
of which seem ``too small to be worth doing''. 
The  effect of   these transformations is quite significant. By doing them in small steps you {\em reduce the risk of introducing errors}'' (our italics).
\end{quote}
The literature is divided on the merits of bad smells.
Much research endorses them to guide
code improvement (e.g., refactoring or preventative maintenance). A recent literature review by Tufano et al.~\cite{Tufano2015}  
lists dozens of papers on smell detection and repair tools.

Other papers cast doubt on the value of bad smells
as triggers for code improvement~\cite{Mantyla2004,Yamashita2013,Sjoberg2013}. 
As we show in this paper,  
 tools, text books, and developers disagree on what bad smells
are important enough to hunt down and eliminate. Our findings
are consistent with other research suggesting that universal bad
smells that ignore project context are not useful to guide refactoring~\cite{Mantyla2004,Yamashita2013,Sjoberg2013}.

Bad smells are a widely used technique for evaluating code. As of  early 2016, ACM Digital Library reports 
the Fowler text has 6434 references. A search  on {\em ``bad smell''programming} 
where {\em proceedings=ICSE} finds 1,748 papers since 2006.
Hence it is important to understand the value of
this popular topic.  
Valuable development resources may be wasted on bad smells that are ``bad''; i.e. 
 irrelevant or misleading
for some particular project.

To address this problem, we propose the XTREE
tool that uses: 
     \begin{itemize}
         \item A historical log of defects seen previously in the code;
         \item  Bad smells expressed in terms of the 
          metrics   in that log;
         \item Some proposed refactorings justified using those bad smells.
     \end{itemize}
Given that,  XTREE can determine which
  proposed refactorings are to be ignored
since they are not justifiable  
with respect to the history of the project. XTREE addresses four problems that  make it hard to  learn useful
bad smells for a particular project.

{\em PROBLEM \#1:} As discussed in the next section, programmer
  cognitive biases result in different
developers declaring that
bad smell X or Y is most important. 
 XTREE offers a way to assess the value of competing recommendations to address smell X vs. Y.

{\em PROBLEM \#2:} Not all bad smells can be fixed. 
When new code must
be combined with code from a third party, 
sometimes the constraints of that code 
lead unavoidably to bad smells violations (e.g.
developers might need to passed as a single closure a  very long method
to  a third-party GUI toolkit).   In this case,
a refactoring proposed to reduce that bad smell
may be irrelevant since it cannot be applied to this code base.

To address this problem, XTREE {\em reasons optimistically} to find the set
$R_0$ of refactorings that \textit{might} be useful (see \tion{rq} on optimistic reasoning).
The space of \textit{actually usable} refactorings is 
the subset $R_1 \subseteq R_0$.
If a developer's proposed refactoring $R_2$ is
not in $R_0$, then it cannot be in the usable
set $R_1$.  We show experimentally that XTREE
often recommends small subsets of
code metrics as useful guides for refactoring. Thus, we
can rule out some proposed refactorings
since many of those proposals fall outside of the space
useful refactorings ($R_0$) suggested by XTREE.

{\em PROBLEM \#3:}  
Shantnawi~\cite{Shatnawi10} warns most  studies do not offer
{\em both} a metric and a threshold for proposed bad smells. For example,  Darcy and Kemerer~\cite{darcy05}
discuss object-oriented (OO) design metrics that might defect bad smells (e.g. an excessive
depth of inheritance tree), but they do not define thresholds
for when the code starts to smell bad.  
Shatnawi~\cite{Shatnawi10}
and  Alves et al.~\cite{Alves2010} are rare cases where both metrics and thresholds are defined (see \tion{bst}).
However, their approaches do not explore the interconnections between sets of code metrics. This is important if sets of
code metrics have to be changed at the same time.
For example, it is not possible to refactor a
long method if several smaller ones without increasing
the coupling metrics of a class. 
More generally, we say that bad smell thresholds should be
{\em conjunctions} of metric+threshold pairs that need to be changed {\em together}.
Shatnawi~\cite{Shatnawi10}
and Alves et al. report {\em disjunctions} of multiple metrics+thresholds~\cite{Shatnawi10,Alves2010} without indicating how changes to these metrics are related.

To address this third problem, 
XTREE   generates {\em conjunctions} of   thresholds
than should  be considered at the same time.

{\em PROBLEM \#4:} It is hard to judge the  effects of removing bad smells.
Refactored code cannot be assessed just by a rerun of the the test
suite (since refactorings are supposed to preserve behavior), and otherwise one must wait for new defect reports to evaluate the effect of refactoring changes on code.  
% waiting to observe 
% code refactorings is meant to
% preserve the behavior of the system (i.e. the same tests
% should pass before and after the refactoring). 
% Also, it many not be practical
%  to assessing refactorings by making the
% refactorings,  then seeing what happens to that code for the rest
% of the project. In a test-driven agile project, as
% SCRUM meetings change what stories are implemented next,
% the operational profile that lead to defects in the old
% code may not be repeated in future executions. 
To resolve this  problem, SE researchers such as 
Cheng et al.~\cite{Cheng10}, O'Keefe et al.~\cite{OKeeffe08,OKeeffe07},
Moghadam~\cite{Moghadam2011} and Mkaouer et al.~\cite{Mkaouer14}
use a pair of systems: 
\begin{enumerate}
    \item One system to propose changes;
\item A separate system to assess
how defective is the code before and after some
refactoring.
\end{enumerate}
For the second system,
 Cheng, O'Keefe, Moghadam and  Mkaouer et al. use the QMOOD hierarchical
quality model~\cite{Bansiya02}.
A shortcoming of QMOOD
is that quality models learned from other projects
may perform poorly when applied to new projects~\cite{localvsglobal}.

To solve this fourth problem, this study  eschews
older quality models like QMOOD, we use
Random Forests~\cite{Breiman2001} to learn defect predictors
from OO code metrics.
Note that, unlilke QMOOD, such measurements 
  are specific to the project, and the measurements can be reconstructed and the predictors rebuilt for other projects.

The rest of this paper is structured as follows. 
The next section
discusses the cognitive
biases that make developers disagree on the relevance of those bad smells to
their particular projects
(that discussion is our motivation for developing 
tools like XTREE). This is followed by a discussion
on various methods to learn thresholds for bad smells.
After evaluating those methods, we discuss various threats to
validity that threaten our conclusions.

Before  that, we offer one following note on a
core assumption of XTREE.
XTREE   is focused on Fowler's bad smells
as contributors to software defects. Some researchers 
 suggest that discussing bad smells is useful for more just reducing defects. For example, Bosu and Carver~\cite{bosu13} report that
debates about code smells and refactorings can (a)~introduce new comers to the code base or (b)~share knowledge on a team
about interactions within the code. In that view, 
the concept of refactoring can be useful
even if it does not address issues of defects.

\subsection{Contributions of this Paper }
The XTREE learner has not been reported
previously. 
The comparative analysis of XTREE
    versus previously published approaches to learning
    bad smell detectors shows
    that XTREE   rarely perfoms
      worse that the other approaches~\cite{Shatnawi10,Alves2010}
      and often is it   much better at proposing
      changes that reduce the expected
      number of of the defects. Further, the number
    of code metrics mentioned by XTREE is far
    fewer than other approaches, making it easier to validate refactorings proposed by
    developers. 
We
show here that XTREE is less verbose and offers better recommendations than the CD tool   developed previously with Borges~\cite{me12c}.
 The experimental rig
 used to comparatively assess
    XTREE is another novel contribution\footnote{tiny.cc/XTREE}. Using the design
    of that rig,
    other researchers could confirm/improve/refute
    the conclusions of this paper.

\section{Motivation}\label{sect:prelim}

Why build tools like XTREE to  critique proposed developer actions?
Are not those developers the best guide to what is important or irrelevant
to their code? Developer {\em cognitive biases} can mislead them to
assert that some things are important and relevant when they are not.
This section discusses those biases-- firstly in the general sense
across all SE beliefs; then secondly in the   context of code smells.

A widespread malaise in software engineering is that
beliefs about software are rarely revised and hence may be
  inaccurate and 
misleading~\cite{passos11,jorgensen09,mei15,me16phase,prem16}. Software developers may have strong views on many issues, including bad smells, but those views may be wrong for the current
project.
Software engineering is not the only field with this problem.
  For example, the medical profession applies many practices based on studies that have been disproved (a recent article in the Mayo Clinic Proceedings~\cite{prasad13} found 146 medical practices based on studies in year i, but which were reversed by subsequent trials within years i + 10). Even when the evidence for or against a treatment or intervention is clear, medical providers and patients may not accept it~\cite{aschwanden10}. Aschwanden warns that {\em cognitive biases} such as confirmation bias (the tendency to look for evidence that supports what you already know and to ignore the rest) influence how we process information~\cite{aschwanden15}.

As in medicine, so too in software engineering.
According to Passos et al.~\cite{passos11},  developers often  assume that the lessons they learn from a few past projects are general to all their future projects. They comment ``past experiences were taken into account without much consideration for their context''~\cite{passos11}.  J{\o}rgensen \& Gruschke~\cite{jorgensen09} offer a similar warning. They report that the supposed software engineering ``gurus'' rarely use lessons from past projects to improve their future reasoning and that such poor past advice can be detrimental to new projects.~\cite{jorgensen09}. Other studies have shown some widely-held views are   now questionable given new evidence:

\begin{enumerate} 
% COMMENT FROM LL: This bullet is weak. Maybe goto isn't used in an unrestricted manner because of Djikstra's warning.
% \item
% Nagappan et al. analyzed~\cite{mei15} 
% how   {\tt goto}  was used  in 11,000 Github repositories. 
% They found that developers
% rarely used {\tt goto} in the unrestricted manner that alarmed Dijkstra in his  1968
% memo ``Go to statement considered harmful''~\cite{Dijkstra68}.
\item
In other work~\cite{me16phase} with the Software Engineering Institute (SEI), we have revisited
the ``phase delay'' truism that {\em the cost of fixing an error dramatically increases the longer it is in the system}. 
We found no evidence for such large   phase delay effect in modern
software (in 171 software projects shepherded
by the SEI, 2006-2014) possibly since it has been  heavily mitigated by $21^{st}$ century software development languages, tools and development practices. 
Whatever the reason, the main point  is that phase delay is a widely
held belief, despite little recent evidence to support it.
\item
Devanbu et al.  examined responses from 564 Microsoft software developers from around
the world, they found that  ``(a)~programmers do indeed have very
strong beliefs on certain topics; (b)~their beliefs are primarily formed
based on personal experience, rather than on findings in empirical
research; (c)~beliefs can vary with each project, but do not necessarily
correspond with actual evidence in that project''~\cite{prem16}.
\end{enumerate}
Devanbu et al. further  comment that ``programmers give personal experience
as the strongest influence in forming their opinions''. This is a troubling
result, especially given the above comments from Passos and  J{\o}rgensen et al.~\cite{passos11,jorgensen09} about how quickly practitioners form, freeze, and rarely revist those opinions.

\input{tex/refactor}

If the above remarks hold true for bad smells, then we would expect
to see much disagreement on which bad smells are important and relevant
to  a particular project. This is indeed the case.
The first column of \fig{smells} 
lists  commonly mentioned bad smells and comes from Fowler's 1999 text~\cite{fowler99} and a subsequent 2005 text by Kerievsky that is widely cited~\cite{Kerievsky2005}.
The other
columns show data from other studies on which bad smells matter most.
The columns marked as Lanza'06 and Yamashita'13 are from peer reviewed literature. The column maked SonarQube is a popular open source
code assessment tool that includes detectors for six of the bad smells
in column one. 
The {\em developer survey}   (in the right-hand-side column),
  this shows the results of an hour-long whiteboard sessions with a group of 12 developers from a Washington
    D.C. web tools development company. Participants
    worked in a round robin manner to rank the bad smells they thought were
    important (and any disagreements were discussed with the whole group).
     Amongst the group, there was  some
    consensus on  the priority of which bad smells to fix
    (see the annotations VH=very high,
    H=high, L=low, VL=very low, and ``?''= no consensus).

\input{tex/jur_char}

A  blank cell in \fig{smells}
indicates where   other work has chosen to ignore
one the   bad smells in column one. 
Note that most of the cells are blank, and that the studies ignore the majority of the Fowler bad smells.
SonarQube has no detectors for many of the column one bad smells.
Also, nearly half the Yamashita list of bad smells
    does not appear in the Fowler and Kerievsky list. The eight numbers
    in the  Yamashita'13 column show the rankings for the bad smells 
    that overlap with Fowler and Kerievsky; Yamashita also discussed other smells not covered in Fowler'99.

Two of the studies in \fig{smells} offers some comments on the relative importance
of the different bad smells in the Yamashita'13 study and the developer study. Three of the bad smells listed in the top half of the Yamashita'13 rankings also score very high in the developer survey. Those three were {\em duplicated code, large class}, 
        and {\em long method}. 
 Note that this agreement also means that the
  Yamashita'13 study and the developer survey   
  believe
        that very few  code smells are   high priority issues
        requiring refactoring.

In summary, just because one developer strongly believes in the importance of a bad smells does not mean that belief transfers to other developers or projects.
Developers can be clever, but their thinking can also be distorted
by cognitive biases.
Hence, as shown in \fig{smells}, developers, text books, and tools 
can disagree on which bad smells are important.
Special tools are needed to assess their beliefs, for example, their beliefs in
bad smells.

\section{Learning Bad Smell Thresholds}\label{sect:bst}
Research studies and tools (e.g., SonarQube~\cite{sq15}) leverage OO metrics as representatives for code smells, as we do in this study. In this section, we focus on determining thresholds for interpreting these metrics as ``bad smells'' or not.

The SE literature offers  two ways to 
learning bad smell thresholds.
One approach relies on 
{\em outlier statistics}~\cite{erni96,bender99}. This approach
has been used   by Shatnawi~\cite{Shatnawi10}, Alvenes et al.~\cite{Alves2010}
    and Hermans et al.~\cite{hermans15}.
    Another approach is 
    based on {\em cluster deltas} that we developed
    for   Centroid Deltas~\cite{me12c} and 
    use here for XTREE. 
    These two approaches are discussed below.
\subsection{  Outlier Statistics}\label{sect:p}

The outlier approach assume that unusually large measurements indicate risk-prone code.
Hence, they generate one bad smell threshold for any metric
with such an ``unusually large'' measurements. 
The literature lists several ways to define ``unusually large''.

\subsubsection{Enri \& Lewerentz}
Given classes described with the  code metrics of \fig{ck},
Enri and Lewerentzz~\cite{erni96} found the   mean $\mu$ and the standard deviation $\sigma$
of each
code metrics. Their definition of problematic outlier was any code
metric with a measurement greater than $\mu+\sigma$.
Shatnawi and Alves et al.~\cite{Shatnawi10,Alves2010} depreciate
using $\mu+\sigma$ since it does not consider the fault-proneness of classes when the thresholds are computed. Also, the method lacks  empirical validation.

\subsubsection{ Shatnawi}
Shatnawi~\cite{Shatnawi10}'s preferred alternative to $\mu+\sigma$
is to use the VARL method (Value of Acceptable Risk Level) proposed by Bender~\cite{bender99} in his epidemiology studies.  This approach uses two
thresholds which, following Shatnawi's guidance, we set to
$p_0=p_1=0.05$.

VARL encodes the defect count
for each class as 0 (no defects known in class) or 1 (defects known in class).
Univariate binary logistic regression is applied to learn three coefficients:  
 $\alpha$ is the intercept constant;
    $\beta$ is the coefficient for maximizing log-likelihood;
  and $p_0$  
    measures   how well this   model predicts for   defects.
Any code metric with $p_0>0.05$ is  rejected as being a poor defect predictor. Thresholds are then learned from the surviving metrics $M_c$ using
an equation proposed by Bender:
\begin{equation}
 \mathit{bad\; smell\; if\;} M_c > \frac{1}{\beta }\left( {\log \left( {\frac{{{p_1}}}{{1 - {p_1}}}} \right) - \alpha } \right) 
\end{equation}

\subsubsection{ Alves et al.}
Alves et al.~\cite{Alves2010} propose another approach
to finding thresholds that  utilizes the underlying statistical distribution and scale of the metrics. 
Metric values for each class are weighted according to the source lines of code (SLOC) of the class. All the weighted metrics are then normalized by the sum of all weights of for the system. 
The normalized metric values are ordered in an ascending fashion (this is equivalent to computing a density function, in which the x-axis represents the weight ratio (0-100\%), and the y-axis the metric scale).
Alves et al. then select a percentage value (they suggest 90\%) which represents the ``normal'' values for metrics. The metric threshold, then, is the metric value for which 90\% of the classes fall below. The intuition  is that the worst code has outliers beyond 90\% of the normal code measurements. Hermans et al.~\cite{hermans15} used the
Alves et al. method in their  2015 paper on
exploring bad smells.

For consistency
with Shatnawi, we explore the correlation between
the code metrics and the defect counts and   reject code metrics that are poor predictors of defects (i.e.   those  with $p > 0.05$).

\begin{figure*}[!t]
~\hrule~
\begin{minipage}{.53\linewidth}
\small
 \begin{tabular}{p{0.95\linewidth}} 
 On the right-hand-side is a tree
 generated by iterative dichomization. 
 This tree can be read like a nested if-then-else statement; e.g.
 \begin{itemize}
     \item Lines 3 and 8 show two branches for lines of code (denoted here as {\em `\$loc}) below 698 and above 698.
     \item Any line with a colon ":" character shows  a  leaf  of  this  nesting.   For  example,  if  some  new  code module is passed down this tree and falls to the line marked in \textcolor{orange}{{\bf orange}},  the colon on that line indicates a prediction that this module has a 100\% chance of being defective. 
     \end{itemize}
Using this tree,
 XTREE looks for a nearby branch that has a lower chance of being defective. Finding the \textcolor{green}{{\bf green}} desired  branch,  XTREE reports a bad smell threshold for that module that is the delta between the \textcolor{orange}{{\bf orange}}  current branch  and   \textcolor{green}{{\bf green}} designed branch. 
 In this case, that threshold relates to:
 \begin{itemize}
     \item Lines of code and comments ({\em lcom}) 
     \item The cohesion between classes ({\em cam}) which measures similarity of parameter lists to assess the relatedness amongst class   methods.
     \end{itemize}\\ 
 \end{tabular}
 \end{minipage}~~~~
 \begin{minipage}{.45\linewidth}
\includegraphics[width=\linewidth]{figs/XTREE_samp.png}
\end{minipage}
~\hrule~
 \caption{A brief tutorial on XTREE.} \label{fig:xtree_samp}
\end{figure*}

\subsubsection{Discussion }\label{sect:disc}
The advantage of the outlier-based
approaches is that they are simple to implement, but the approaches have   two  major disadvantages. 
First, they are {\em verbose}. A threshold can be calculated for every metric -- so, which one should the developers focus on changing? Without a means for prioritizing the  thresholds and metrics against one another, developers may have numerous or conflicting recommendations on what to improve. Second, the outlier approaches suffers from
the {\em disjunction} problem.
That is, while
 they propose thresholds for many code metrics
individually, they make no comment on what
metrics need to be changed at the same time.

\subsection{Cluster Deltas}

Cluster deltas are a general method
for learning {\em conjunctions} of changes
that need to be applied at the same time. 
This approach works as follows:
\begin{itemize}
    \item Cluster the data. 
    \item Find
neighboring clusters $C_+,C_-$ where $C_+$ has more examples of defective
modules than $C_-$;
\item Compute the  delta   in code metrics between the clusters using \mbox{$\Delta = C_+ - C_-$}, i.e.
{\em towards} the cluster with lower defects;
\item $\Delta$ are changes needed in defective modules of $C_+$ to
      make them more like the less-defective modules of $C_-$
\end{itemize}
Note that $\Delta$ is a conjunction of  recommendations.
Since it is computed
from neighboring clusters, the examples contain similar distributions and $\Delta$ respects the naturally occurring constraints in the data. For example,
given a bad smell pertaining to large methods,   $\Delta$   will not  suggest lowering lines of code
without also increasing a coupling measure. 
Cluster deltas are used in CD~\cite{me12c} and XTREE.

\subsubsection{CD}
Borges and Menzies first proposed the CD centroid delta approach to
generate {\em conjunctions} of code metrics
that need to be changes at the same time
in order to reduce defects~\cite{me12c}.
CD used the WHERE clustering algorithm developed by the
authors for a prior application~\cite{localvsglobal}.
Each cluster was then replaced by its centroid
and $\Delta$ was calculated directly from the difference
between code metrics values between one centroid
and its nearest neighbor.

As shown below, one drawback with with CD is that it is {\em verbose}
since
CD   recommended changes to all code
metrics with different values in those two centroids. 
This makes it hard to use CD to   critique and prune away bad smells. Further, CD will be shown to be
not as effective
in proposing changes to reduce defects as XTREE.

\subsubsection{XTREE: Overview}

  XTREE  is a cluster delta algorithm
  that avoids the problem of verbose $\Delta$s.
  Instead of reasoning over cluster centroids,
  XTREE utilizes a decision tree learning approach
  to find the fewest differences between clusters of examples.

 XTREE uses an iterative dichotomizer that
first converts the values for each code
metrics into a small number of ranges.
Consider a code metric is split into $r$ ranges and each range is of
  size
    $n_r$ is
  associated with a set of defect counts $x$ with standard deviation
  $\sigma_r$.
  The best split for that range is
  the one that minimizes the expected value of the
  defect variance, after the split; i.e.
  $\sum_r\frac{n_r}{n}\sigma_x$ (where $n=\sum_r n_r$).
  This discretizer then recurses on each part of the split
  to find other splits.

  When discretization finishes, each code metric $M$ has a 
  final expected value $M_v$ for the defect standard deviation 
  across all the discretized ranges of that metric.
  Iterative dichomization sorts the metrics by $M_c$
  to find the best ``splitter'' for the data
  (the code metric with smallest $M_v$). The data
  is then split on the ranges of the splitter and
  iterative dichomization recurses on each range.  In this way,
  each split is the root of a sub-tree.

  While not usually labelled as such, iterative dichomization can
  be viewed as a clustering algorithm that groups together code modules
  with similar defect counts and some shared ranges of code metrics.
  For our purposes, we score each cluster found in this way according
  to the percent of classes with known defects. For example,
  the last line of \fig{xtree_samp} shows a tree lead with 75\%
  defective modules.

 \fig{xtree_samp} offers
  a small example of how XTREE builds
    $\Delta$ by comparing branches that lead to leaf clusters
  with different defect percentages. In this example, assume a project with a table of code metrics data describing its classes in the form of \fig{ck}. After code inspections and running test cases or operational
      tests, each such class is augmented with a defect count.
      Iterative dichomization takes that table of data and, 
        generates the tree of \fig{xtree_samp}.

     Once the tree is built, a class with code metric data is passed into the tree and evaluated down the tree to a leaf node (see the \textcolor{orange}{{\bf orange}} line in \fig{xtree_samp}).
      XTREE then looks for a nearby leaf node with a lower defect
      count (see the \textcolor{green}{{\bf green}} line in \fig{xtree_samp}). For that evaluated class, XTREE proposes a bad smell
      thresholds that is  the difference between 
      \textcolor{green}{{\bf green}} and \textcolor{orange}{{\bf orange}}.

\subsubsection{XTREE:   Details}

Using the training data,  XTREE uses  
iterative dichomization to
  divide  $N$ code modules  into  clusters of
size $\sqrt{N}$.

Next, for each test code module, 
	  find $C_+$ as follows take each test , run it down to a leaf in the decision tree.  
After that,	  find $C_-$ as follows:
		\begin{itemize}
		\item Starting at the  $C_+$ leaf, ascend   $lvl\in \{0,1,2...\}$ tree levels;
		\item Identify {\em sibling} leaves; i.e. leaf clusters that can be reached from level $lvl$ that are not same as {\em current }
		\item Find the {\em better} siblings; i.e. those 50\% (or less)
		fewer defects than $C_+$.
		   If none found, then repeat for $lvl += 1$. Also,
		    return nil  if the new $lvl$ is above the root. 
		\item  Set $C_-$ to the  {\em closest} better sibling where distance is measured between the mean centroids of that sibling and {\em current}
		\ei
	 Now find $\Delta = C_+ - C_-$  by reflecting
	 on the set difference between  conditions in the decision tree branch to $C_-$ and $C_+$. To find that delta,
	 for discrete attributes, the delta is the value from {\em desired};
	    for numerics  expressed as ranges, the delta is a random number selected from the low and high boundaries of the that range.

\input{tex/prediction_stats.tex}      
\section{Evaluation}
\subsection{Research Questions}
% To define our experiments, we  review some details
% about XTREE.

 XTREE proposes
conjunctions of changes that might perform better than
the disjunctions proposed by Shatnawi and Alves et al.
Unlike CD, XTREE should be less verbose since
it only reports the deltas in the code
metrics rather than values for all metrics.
To evaluate XTREE,
we propose four research questions.

\subsubsection{ RQ1: Effectiveness} \label{sect:rq}

{\em In a comparison of   outlier and cluster delta
methods, which one most reduces the expected number
of defects?}

To find an answer to this question, we will assume that developers
refactor their code until the bad smell thresholds is not violated.
This refactoring will start with some {\em initial} code
base that is changed to a {\em new} code base. 
For example, if the bad smell is \mbox{{\em loc $>100$}} and a 
code module has 500 lines of code, we reason
optimistically that we can change that code metric
to 100.  
Using a defect
predictor learned via Random Forest, we then predict the
number of defects in $d_+,d_-$ in {\em initial} and {\em new}. We evaluate the performance of XTREE, CD, Shatnawi, and Alves methods in setting bad smell thresholds.
The best bad smell threshold method is the one that maximizes
\begin{equation}\label{eq:diff}
\mathit{improvement} = 100* \left(1 - \frac{ d_- }{ d_+}\right)
\end{equation}

\subsubsection{RQ2: Verbosity}

{\em In a comparison of    outlier and cluster delta
methods, which one proposes the fewest thresholds?}

Note that this is important since our goal is to critique and, possibly,
reject irrelevant bad smell detectors. As mentioned above,
  verbosity makes it hard   to critique and prune bad smells
since any bad smell mentioned by a developer has some support
somewhere amongst all those proposed thresholds.

To measure verbosity, we will compare the counts of how often
different approaches assign thresholds to code metrics
(and the one that makes the least assignments is the least verbose).

\subsubsection{RQ3: Optimality}

{\em How consistent are the leaves of XTREE?}

Before using XTREE to critique bad smell detectors, it is important to analyze the quality XTREE. Such analysis allows users to determine the credibility of the critiques offered.

To measure the optimality we measure the discriminatory power of the tree as suggested by ~\cite{osei04}. (Note: this is done in addition to the most commonly used performance criterion (i.e.
correct classification rate). For XTREE (with binary target variables) we present the probability of false alarm (PF) and the probability of detection (pf) in \fig{j}.)

\subsubsection{RQ4: Understanding Co-changes}

{\em In a comparison of outlier and cluster delta
methods, which one is aware of the existing associations between software metrics?}

Our goal is to critique and, possibly, reject irrelevant bad smell detectors. However, with low verbosity there exists the risk of ignoring underlying associations that exist between software metrics. Failure to respect this challenges the validity of the critiques.

To measure if our methods respect these co-changes in metrics, we will compare the medians of each of the metrics. Statistically significant changes in all co-varying metrics will indicate our method's efficacy in respecting these underlying associations.

\subsection{Test Data}\label{sect:tesd}

To explore these research questions,
we used data from
Jureczko et al.'s collection of object-oriented Java systems~\cite{jureczko10}. To access that data, go to   git.io/vGYxc.
The Jureczko data records the number of known defects for each class using a post-release bug tracking system. The classes are described in terms of nearly two dozen metrics included in the Chidamber and Kemerer metric suite, such as number of children (noc), lines of code (loc), etc. For details on the Jureczko code
metrics, see  \fig{ck}. For details on the rows and versions
of that data, see the left-hand-side columns of \fig{j}.

\subsection{Assessment Oracles}
\label{sect:eval}
We must be able to assess how defective the code is before and after a proposed refactoring. Since we do not have actual  examples of defect counts post-refactoring, we   approximate   defect counts after the   changes   (as changes to the code metrics).

Prior work~\cite{Cheng10,OKeeffe08,OKeeffe07,Moghadam2011,Mkaouer14} 
used the QMOOD   quality model ~\cite{Bansiya02} to assess the results of their refactorings
Since the QMOOD method based on old (2002) project data, we use Random Forests~\cite{Breiman2001} to build
the assessment methods.
  Random Forests are a decision tree learning method but
  instead of building one tree, hundreds are built using
  randomly selected subsets of the data. The final predictions
  come from averaging the predictions over all the trees.
  Recent studies endorsed the use
  of  Random Forests for  defect prediction~\cite{lessmann}.

\fig{j} shows   studies with Random Forests and
the Jureczko data. Given   $V$ released versions, we test on version $V$ and train on the available data from $V-1$ earlier releases (as shown in \fig{j}. Note the   \colorbox{lavenderpink}{three bottom rows}   marked with $\times$: these contain predominately defective classes (two-thirds, or more).  In such data, it is hard to distinguish good examples (due to all the bad examples).

In order to identify the presence (or absence) of defects, we can   use Boolean classes in the  Jureczko data ( \texttt{True} if defects \textgreater 0; \texttt{False} if defects = 0). For such data, the quality of the predictor can be measured using (1) the  probability of detection (a.k.a. ``pd'' or recall):  the percent of faulty classes in the test data detected by the {\em predictor}; and (2) the  probability of false alarm (a.k.a. ``pf''): the percent of non-fault classes that are {\em predicted} to be defective.

The ``untuned'' columns of \fig{j}
show a preliminary study. This study used
Random Forest with its ``off-the-shelf'' tunings (i.e.  
100 trees per forest).  
The forests were built from training data and applied to test data
not seen during training.  In this
study, we called a data set ``usable'' if   Random Forest was able to classify the instances with a performance threshold of $\mathit{pd}\ge 60 \wedge \mathit{pf} \le 30$\% (determined from standard results in other publications~\cite{me07b}). Note that no  data set meet
that criteria.

The ``tuned'' columns of \fig{j} show that we can salvage some of the data sets. We applied both the SMOTE algorithm and differential evolution to improve the performance of the classifier. Pelayo and Dick~\cite{pelayo07} report that defect prediction is improved by SMOTE~\cite{Chawla2002}; i.e. an over-sampling of minority-class examples and an under-sampling of majority-class examples. Fu et al.~\cite{fu:ase15} report that parameter tuning with differential evolution~\cite{storn97} can quickly explore the tuning options of Random Forest to find better settings for the (e.g.) size of the forest, the termination criteria
for tree generation, etc. We note that SMOTE-ing and
parameter tunings were applied to the training data only and not to the test data.

The rows \colorbox{celadon}{marked with a $\star$} in \fig{j} show data sets whose performance was improved remarkably by these techniques. For example, in {\em poi}, the recall increased by 4\% while the false alarm rate dropped by 21\%. However, as might have been expected, we could not salvage the data sets in the  three bottom rows.

We eliminate the data sets for which we could not build an adequately performing Random Forest classifier with $\mathit{pd}\ge 60 \wedge \mathit{pf} \le 30$\%. Thus, our analysis uses the {\em jedit, ivy, ant, lucene} and {\em poi} for evaluating recommended changes.

\subsection{Statistics}

We use 40 repeated runs, each with different random number seeds (we use 40 since that is  more than the 30 samples  needed to satisfy the central limit theorem). Each run collects the \eq{diff} values.
We use multiple runs since two of our methods use some random choices: CD uses the  stochastic WHERE clustering algorithm~\cite{localvsglobal}
while XTREE non-deterministically picks thresholds randomly from
the high and low boundary of a range. 
 Hence, to compare all
four methods, we must run the analysis many times.

\input{tex/results_jur.tex}

To rank these 40 numbers collected from CD, XTREE, Shatnawi, and Alves et al., we use the Scott-Knott test recommended by Mittas and Angelis~\cite{mittas13}. 
Scott-Knott is a top-down clustering approach used to rank different
treatments. If that clustering finds an interesting division of the data, then
some statistical test is applied to the two divisions to check if they
are statistically significant different. If so, Scott-Knott recurses
into both halves.

To  apply Scott-Knott,
  we
sorted a list of  $l=40$ values of \eq{diff} values found in  $ls=4$ different methods. 
Then, we split $l$ into sub-lists $m,n$ in order to maximize the expected value of differences in the observed performances before and after divisions. E.g. for lists $l,m,n$ of size $ls,ms,ns$ where $l=m\cup n$: \[E(\Delta)=\frac{ms}{ls}abs(m.\mu - l.\mu)^2 + \frac{ns}{ls}abs(n.\mu - l.\mu)^2\]
We then apply a apply a statistical hypothesis test $H$ to check
if $m,n$ are significantly different  (in our case, the conjunction of A12 and bootstrapping). If so, Scott-Knott recurses on the splits. In other words, we divide the data if \textit{both} bootstrap sampling and effect size test agree that a division is statistically significant (with a confidence of 99\%) and not a small effect ($A12 \ge 0.6$).
For a justification of the use of non-parametric bootstrapping, see Efron \& Tibshirani~\cite[p220-223]{efron93}. For a justification of the use of effect size tests see Shepperd\&MacDonell~\cite{shepperd12a}; Kampenes~\cite{kampenes07}; and Kocaguenli et al.~\cite{Kocaguneli2013:ep}. These researchers warn that even if a hypothesis test declares two populations to be ``significantly'' different, then that result is misleading if the ``effect size'' is very small. Hence, to assess the performance differences we first must rule out small effects using A12, a test   recently endorsed by Arcuri and Briand at ICSE'11~\cite{arcuri11}.

The Scott-Knott  results are presented in the form of line diagrams like those shown on the right-hand-side of \fig{jur}.
The black dot shows the median \eq{diff} values and the horizontal lines stretch 
from the 25th percentile to the 75th percentile (the inter-quartile range, IQR).
As an example of how to read this table, consider the {\em Ant}
results. Those rows are  sorted on the median values of each method. Note that all the methods have \eq{diff} \textgreater $ 0\%$; i.e. all these methods reduced the expected value of the performance score in that experiment while XTREE achieved the greatest reduction (of 56\% from the original value).
These results table has a  left-hand-side  {\bf Rank} column, computed using the
Scott-Knott test described above. In the {\em Ant}
results, XTREE is ranked the best, while CD is  ranked   worst.

\input{tex/rq2.tex}
\subsection{Results}

\begin{figure*}[!t]
\centering
\includegraphics[width=\linewidth]{figs/changes01.png}
\caption{Results  from XTREE.
While \fig{counts} are the {\em number} of times a code metric was changed,
this  figure shows {\em how far} each code metric was changed. Each vertical bar
marks the 27,50,75th percentile change seen in 40 repeats.
All numbers are ratios of initial to final values.
All bar regions marked in gray show {\em increases}.
The interesting feature of these results are that many
of the changes proposed by XTREE require {\em increases}
(this puzzling observation is explained in the text).}
\label{fig:changes}
\end{figure*}

\subsubsection{RQ1: Effectiveness}

\begin{lesson}
In terms of the expected number of defects
  after refactoring,
XTREE is marginally better than Alves. CD and Shatnawi.
on the other hand, usually perform worst.
\end{lesson}

{\em In a comparison of   outlier and cluster delta
methods, which one most reduces the expected number
of defects?}

\fig{jur} shows the comparison results.  The Alves and Shatnawi
entries show the net effects of applying (separately) all the disjuncts
proposed by those methods. In this part of the  analysis,
we applied Scott-Knott to all the \eq{diff} values
seen when code metrics were changed
according to the  Alves and Shatnawi

Two data sets are very responsive to defect reduction suggestions:
 Ant, and Ivy (both of which show best case improvements over 50\%).
 The  expected value of defects  
 is changed less in Jedit. This data sets' results
 surprisingly uniform; i.e.   all methods
 find the same ways to reduce the expected number of
defects.   For an explanation of the Jedit uniformity, see \tion{inc}.

Two data sets are not very responsive to defect reduction:
Poi and Lucene. The reason for this can be see in \fig{j}:
both these data sets contain more than 50\% defective modules.
In that space, all our  methods lack a large sample of
defect-free examples.

Also consider the relative
rank of the different approaches,
 CD and Shatnawi usually  perform comparatively worse while  XTREE gets top ranked position the most
number of times. That said, Alves sometimes beats XTREE (see Ivy)
while sometimes it ties (see Jedit).

Another interesting feature of the XTREE results of
\fig{jur} was that the used code metrics vary
from data set to data set. While changing lines of
code {\em loc} was important in all data sets, 
the other code metrics used were often different.

 \subsubsection{RQ2: Verbosity}

{\em In a comparison of outlier and cluster delta methods, which one proposes the fewest thresholds?}

\fig{counts} shows the frequency with which the methods
recommend changes to specific code methods.
Note that XTREE proposes thresholds to
few code metrics compared to the other approaches.

% COMMENT From LL: This is such a strange way of putting this lesson, and you haven't actually evaluated this.
%

When combining  \fig{jur} with \fig{counts}, we   see that
even though XTREE proposes changes to far fewer code metrics, those few
code metrics are usually just as effective (or
more effective) than the multiple
thresholds
proposed by CD, Shatnawi or Alves.  That is, XTREE proposes
{\em fewer} and better thresholds than the other approaches studied here.

\begin{lesson}
XTREE finds finds far fewer recommended changes to code metrics, and yet performs as good as or better than other methods in recommending changes that results in fewer defects.
\end{lesson}

\input{tex/all_changes.tex}

\subsubsection{RQ3: Stability of Decision Trees}
\input{tex/rq3.tex}

\fig{rq3} shows the measure of ambiguity of the leaves of XTREE. As proposed by ~\cite{osei04}, this measure is used to determine the discriminatory power of the decision tree. Trees with leaf nodes that have low ambiguity with regards to the class variable is more desirable.

To measure the ambiguity we compute the weighted average of the entropy of the leaf nodes. Leaf nodes with lower ambiguity tend to have much lower entropy.

We note that in all cases, the weighted average of entropy is close zero with very low variance. Therefore,

\begin{lesson}
In terms of stability, XTREE produces trees with consistently low ambiguity. This mitigates the risk of learning from less than optimum tree.
\end{lesson}

\subsubsection{RQ4: Understanding Co-changes}

{\em In a comparison of outlier and cluster delta
methods, which one is aware of the existing associations between software metrics?}

In \fig{changes} we identify the magnitude of changes proposed by the plans offered by XTREE.
At first glance, \fig{changes} seems strange since it 
shows many metrics need to be {\em increased} in order
to reduce defects. Note that such increases  to reduce
defects would never be proposed by the outlier methods
of Shatnawi or Alves since their core assumption is that bad
smells arise from unusually large code metrics.

The increases proposed by 
\fig{changes} arise from the interdependancies between
code metrics. For example, consider the {\em Poi} results
from \fig{counts} that recommends decreasing {\em loc}
but making large increases to {\em cbo} (coupling between
objects). Here, XTREE is advising us to break up
large classes class by into services
in other classes. Note that such a refactoring will, by
definition, increase the coupling between objects.

Figure ~\ref{fig:multcomp} highlights all possible changes proposed by XTREE, upon close inspection it becomes apparent that XTREE suggests that it is perhaps better to reduce only certain forms of coupling. Refactoring operations that reduce one form of coupling at the cost of increasing another can sometimes be beneficial. This is most noticeable in Ivy, where one of the better approaches is to reduce coupling between objects (cbo) (efferent coupling) while increasing the afferent coupling (CA), again implying a redistribution of responsibilities. Using thresholds may not always appreciate the existence of these co-changes between metrics, and as a result many refactoring operations are usually left unexplored.

Note that we prefer XTREE to Shatnawi and the Alves
method since those other methods
do not reason
2about decreases {\em and} increases of multiple 
code metrics, at the same time.

As a final comment, we note
that  \fig{changes} enables us to explain the uniformity
of the results seen with Jedit in \fig{jur}.
Observe how in \fig{changes} the only change ever
found is a reduction to {\em rfc}. Clearly, in this
data set, there is very little that can be usefully changed.

\fig{multcomp} shows the frequency with which the methods
recommend changes to specific code methods.
Note that XTREE proposes thresholds to
few code metrics compared to the other approaches.

When combining  \fig{jur}, \fig{counts}, and \fig{multcomp}, we   see that
even though XTREE proposes changes to far fewer code metrics, those few
code metrics are usually just as effective (or
more effective) than the multiple
thresholds
proposed by CD, Shatnawi or Alves.  That is, XTREE proposes
{\em fewer} and better thresholds than the other approaches studied here.

\begin{lesson}
In addition to recommending useful changes, XTREE recommends changes to all co-varying software metrics.
\end{lesson}

\section{Threats to Validity}\label{sect:valid}

As with any empirical study, several issues can affect the final results. Therefore, any
conclusions made from this work must be offered with the following
caveats.

\subsection{External Validity}
Based on the experimental results above,
as well as the discussion in \tion{prelim},
we believe that bad smell indicators (e.g. \mbox{{\em loc}$>$ 100})
have limited external validity beyond the projects from which they are derived. 
While specific models are externally valid,
there may still be general methods like XTREE for finding the good local models.

Our definition of bad smells is limited to those represented by OO code metrics (a premise often used in related work).   
XTREE, Shatnawi, Alves et al. can  only comment
on bad smells   expressed as code metrics 
  in the historical log of a project.

If developers want to justify their refactorings
via bad smells expressed in other terminology,
then the  analysis of this paper must:
\begin{itemize}
    \item Either wait till 
data about those new
terms has been collected. 
\item Or, apply cutting edge transfer learning
methods~\cite{Nam15,Jing15} to map data from other projects
into the current one.
\end{itemize}
Note that the transfer learning approach would
be highly experimental and require more study
before it can be safely recommended.

Sampling bias threatens any data mining experiment; i.e., what matters
there may not be true here. For example, the data sets used here comes from Jureczko et al. and any biases in their selection procedures
threaten the validity of these results. 
That said,
the best we can do is define our methods and publicize our data and code so that other researchers can
try to repeat our results and, perhaps, point out a previously unknown bias
in our analysis. Hopefully, other researchers will emulate our methods in
order to repeat, refute, or improve our results.

% Data mining is a large and active field and any single study can only use a small subset of the known classification algorithms.  
% That said, we have taken care to document in this paper the decisions made by engineering
% judgement that could effect our conclusions.

% \subsection{Trusting the Changes}\label{sect:trust}
%   XTREE is evaluated by  comparing
% predicted performance scores before and after a planner makes changes to the feature values of an example:
% After making those
% changes, we may have a new example that has never been seen before. Therefore, it must be asked
% {\em ``can we trust the predictions made on such new examples?''}

% To answer this question, we note
% that data miners explore two  ``clouds'' of data: (1) the cloud of training examples and (2) the  cloud   of test examples
% (for a visualization of these clouds, see \fig{howxy}).
% \begin{figure}[!t]
%   \includegraphics[width=\linewidth]{figs/2d.eps} 
%  % \includegraphics[width=1\linewidth]{figs/BDBC.eps}
% \caption{Gray, red, green show (1) training examples, (2) test examples and 
%   (3) tests that have been altered by planners.
%   This figure uses axes generated from the first two components of a PCA analysis of all points. 
% }\label{fig:howxy}
% \end{figure}
% We should mistrust the predictions made by a  model   if it is being applied to examples  that are
% too far away from the
% training cloud.
% To test for ``too far'', we can run a data mining experiment that tests how well
% a model learned from the training data applies to the test data. Such experiments return some performance value.

% Note that predictions  about changes that  fall within the space of the training+test data, will be at least
% as accurate as the predictions of the original test data. With this, we assert that the predictions for changes that move examples towards/away from the training data can be trusted more/less (respectively).

% Accordingly, we need {\em trust-increasing} planners to generate new examples {\em closer} to the
% training examples.  To see how this works, 
%  \fig{howxy} is from the {\em ivy} data
% set (one of the Jureczko data sets used in this paper). It shows: (1)~the training examples in gray, (2)~the test examples in red, and (3)~the
% changed  examples displaced after applying a plan (in green).
%  Note that the  the   changed examples
% cases  (shown in green)  fall closer to the training cases (shown in gray) than
% the test cases (shown in red).

% In that green region of changed examples, our belief in the value of predictions
% will be just as much as, if not more than, our belief in the value of the predictions in the red region (that
% contains the original test data).
% This pattern of \fig{howxy} (where the new examples are found closer to  the training cases than the test cases) has been observed in all the other data sets studied in this
% paper. Hence,  we can assert that
% predictors learned from these training examples have some authority in the regions
% containing the changes examples.

% That said, the above comes with some important caveats:
% \bi
% \item 
% The quality of the prediction depends on the nature of the training data. Thus, we strongly recommend that both the data set and the predictor be assessed prior to planning. This ensures that the predictor's performance is adequate for a data set. We tackle this issue in detail in \tion{tesd}.
% \item
% Planners should be designed to be {\em trust increasing}. We list four such planning methods in \tion{planners}.
% \item
% Where possible, planners should be assessed via some external
% oracle that can accurately assess new examples. For an example of that kind of analysis,
% see  \tion{coc}.
% \ei

\subsection{  Internal Validity}\label{sect:coc}

% The main internal validity threat   in this study was the use of
% optimistic reasoning when generating the changed code modules.
We assumed in \tion{rq}
that any code module can be changed in order
to stop triggering a bad smell detector. This is not necessarily
true, as noted in {\em PROBLEM \#2} in this paper's introduction.
To mitigate this issue:
\begin{itemize}
    \item We do not propose using XTREE as a bad
smell generator;
\item Rather, we offer it as  a critique agent for bad smells
proposed by some other oracle (e.g. a human developer).
\end{itemize}
We showed about that XTREE's recommendations are not verbose.
That is, even if XTREE recommends the superset of possibly important bad smells,
that superset is not so large as to  overlap with many
 bad smell proposed at random 
by   developers.

XTREE does not require a working defect predictor to generate
its bad smell thresholds. However, to {\em certify}
that those thresholds are satisfactory, some
second quality predictor must be applied. A data set containing defect counts before and after refactoring activities would enable an accurate assessment of the performance of the threshold-setting and recommender methods, however, such a data set is not available at this time.

 Historically,
SE researchers~\cite{Cheng10,OKeeffe08,OKeeffe07,Moghadam2011,Mkaouer14} have used the QMOOD hierarchical quality model~\cite{Bansiya02}.
Since such quality models may be very project specific~\cite{localvsglobal}, we prefer building local 
defect predictors using Random Forests. We chose this approach,  based on its reputation for having the better  performance of 21 other learners for defect prediction~\cite{lessmann}.  
Our results show that when a defect log contains too few
non-defective examples then defector predictors
perform poorly (see the data sets in the last few lines of \fig{j})
as do their associated bad smell threshold generators
(recall the performance of Lucene and Poi in~\fig{jur}). It should be noted that this is not a limitation of XTREE-- rather
it seems fundamental to the problem of certifying bad smells.
As evidence of this, recall that {\em all} the bad smell threshold generators of~\fig{jur}
had issues with the defect data sets with  many defects
(Lucene and Poi).

% \subsection{ Learner Bias}
% This study used two kinds of learners: (1) methods for suggesting
% changes to code like Shatnawi, Alves et al., CD and XTREE;
% (2) methods for assessing the changes proposed by these learners.
% Prior studies implemented (2) using  the QMOOD hierarchical quality model
% which is so old, that we suspect it may no longer be current. Hence,
% we used Random Forests to build the assessment oracles that were specific
% to the data sets used in this study. We chose this approach,  based on its reputation for having the better  performance of 21 other learners for defect prediction~\cite{lessmann}.

% \subsection{  Sampling bias} 
% Sampling bias threatens any data mining experiment; i.e., what matters
% there may not be true here. For example, the data sets used here comes from two  Jureczko et al. and any biases in their selection procedures
% threaten the validity of these results. 
% That said,
% the best we can do is define our methods and publicize our data and code so that other researchers can
% try to repeat our results and, perhaps, point out a previously unknown bias
% in our analysis. Hopefully, other researchers will emulate our methods in
% order to repeat, refute, or improve our results.

% \input{tex/results_models.tex}

\section{Conclusions}
Which  bad smells can  be ignored? 
We say: ignore those not supported by the historical log of data from
the current project.

When that data is not available (e.g. early
in the project) then developers could use the general list of
bad smells shown in \fig{smells}. However, 
our results
show that  bad smell detectors are most
effective when they are based
on a small handful of code metrics (as done by XTREE).
Hence, using all the bad smells of \fig{smells} may not be optimal.

XTREE improves on prior methods for generating bad smells:
\begin{itemize}
    \item As described in \tion{prelim}, bad smells generated by humans may not be applicable to the current project. On the other hand, XTREE can automatically learn specific thresholds
    for bad smells for the current project.
    \item Prior methods used an old quality predictor (QMOOD) which we replace with defect predictors learned via Random Forests
    from   current project data.
    \item As described in in \tion{bst}, 
    XTREE generates conjunctions of code metric thresholds
    that need to be satisfied at the same time.
    Older methods, such as those proposed by  Shatnawi and Alves
    offer only disjunctions that might be inappropriately applied
    to yield impossible refactorings (e.g. reducing lines of code
    and coupling at the same time).

    \item XTREE's conjunctions proved to be arguably as effective
    as those of Alves (see \fig{jur}) but far less verbose (see \fig{counts}) thus making XTREE a better tool for critiquing and rejecting
    more bad smells proposed by developers.
\end{itemize}
In summary, this paper offers a baseline result
that XTREE can be used as a {\em diagnostic tool}
for identifying which bad smells can be ignored.
But can it be used as a {\em prescriptive tool}
to recommend new refactorings?

As discussed in {\em PROBLEM \#2}
(from the introduction), XTREE might propose
changes to code metrics that are
not feasible  (due to the local domain constraints
of the code). To repair this, XTREE needs to be extended
with architectural knowledge of the code it is studying.
Elsewhere, we have had some   success
with reasoning about such architectural knowledge
(expressed as software product lines~\cite{sayyad13a,sayyad13b}). In future
work, we will explore extending XTREE 
with  
architectural knowledge such that it can
become a tool which perscribes
feasible refactorings.

\section*{Acknowledgements}
The work is partially funded by NSF  awards \#1506586 and \#1302169.

% \bibliographystyle{plain}
\balance
\bibliographystyle{unsrt}
\bibliography{References}
\end{document}

### 2016-07-14 tex/all_changes.tex
Initial ShareLaTeX Import

% Please add the following required packages to your document preamble:
% \usepackage{graphicx}
\begin{figure*}[htbp!]
\centering
\resizebox{\textwidth}{!}{%
\begin{tabular}{l|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c}
         & wmc & dit & noc & cbo & rfc & lcom & ca & ce & npm & lcom3 & loc & dam & moa & mfa & cam & ic & cbm & amc & max\_cc & avg\_cc \bigstrut\\ \hline
Ant      &  & & & $-$ &$-$&  & &$+$& & &$-$& & &$-$& & &  &$+$&     &$+$\bigstrut\\ \hline

Ivy      &$-$& & &$-$&$+$&$-$&$+$& &$-$&$-$&$-$& & & &$+$& & & &     &      \bigstrut\\ \hline

Poi      & & & &$+$&$-$& & & & & &$-$& & & &$-$& & & & & \bigstrut\\ \hline

Lucene   &$-$& & &$+$&$+$& &$+$& & &$-$&$-$& & & &$-$& & &$-$& &$-$\bigstrut\\ \hline

Jedit    & & & & &$-$& & & & & & & & & & & & & & &     \bigstrut\\

\end{tabular}}

\caption{Results of Wilcoxon Signed Ranked Test studying the statistical significance of co-varying changes proposed by XTREE. Each dataset contains 20 Static Code Metrics (for a description of each of these metrics, please refer to~\cite{me12d}). The rows contain the datasets, and the columns denote the metrics. A ``$+$'' symbol represents a recommendation that requires a significant statistical increase (with a p-value$\le$0.05), and likewise, a ``$-$'' represents a significant statistical decrease.} 
\label{fig:multcomp}
\end{figure*}

### 2016-07-14 tex/jur_char.tex
Initial ShareLaTeX Import

\begin{figure*}[t!]
	\renewcommand{\baselinestretch}{0.8}\begin{center}
		{\scriptsize
			\begin{tabular}{c|l|p{4.7in}}
				amc & average method complexity & e.g. number of JAVA byte codes\\\hline
				avg\, cc & average McCabe & average McCabe's cyclomatic complexity seen
				in class\\\hline
				ca & afferent couplings & how many other classes use the specific
				class. \\\hline
				class. \\\hline
				cam & cohesion amongst classes & summation of number of different
				types of method parameters in every method divided by a multiplication
				of number of different method parameter types in whole class and
				number of methods. \\\hline
				cbm &coupling between methods &  total number of new/redefined methods
				to which all the inherited methods are coupled\\\hline
				cbo & coupling between objects & increased when the methods of one
				class access services of another.\\\hline
				ce & efferent couplings & how many other classes is used by the
				specific class. \\\hline
				dam & data access & ratio of the number of private (protected)
				attributes to the total number of attributes\\\hline
				dit & depth of inheritance tree &\\\hline
				ic & inheritance coupling &  number of parent classes to which a given
				class is coupled (includes counts of methods and variables inherited)
				\\\hline
				lcom & lack of cohesion in methods &number of pairs of methods that do
				not share a reference to an case variable.\\\hline
				locm3 & another lack of cohesion measure & if $m,a$ are  the number of
				$methods,attributes$
				in a class number and $\mu(a)$  is the number of methods accessing an
				attribute, 
				then
				$lcom3=((\frac{1}{a} \sum, j^a \mu(a, j)) - m)/ (1-m)$.
				\\\hline
				loc & lines of code &\\\hline
				max\, cc & maximum McCabe & maximum McCabe's cyclomatic complexity seen
				in class\\\hline
				mfa & functional abstraction & number of methods inherited by a class
				plus number of methods accessible by member methods of the
				class\\\hline
				moa &  aggregation &  count of the number of data declarations (class
				fields) whose types are user defined classes\\\hline
				noc &  number of children &\\\hline
				npm & number of public methods & \\\hline
				rfc & response for a class &number of  methods invoked in response to
				a message to the object.\\\hline
				wmc & weighted methods per class &\\\hline
				\rowcolor{lightgray}
				nDefects & raw defect counts & Numeric: number of defects found in post-release bug-tracking systems.\\
				\rowcolor{lightgray}
				defect & defects present? & Boolean: if {\em nDefects} $>0$ then {\em true} else {\em false}
			\end{tabular}
		}
	\end{center}
	\caption{OO code metrics used for all studies in this paper.
	   Last lines, shown in \textcolor{gray} denote the dependent variables.}\label{fig:ck}
\end{figure*}

### 2016-07-14 tex/prediction_stats.tex
Initial ShareLaTeX Import

\begin{figure*}[!t]
	\small
	\begin{center}
		\begin{minipage}{.46\linewidth}
			\begin{tabular}{r@{~}|l@{~}|r@{~}|l@{~}|r@{~}|r@{~}|} \cline{2-6}

				& \multicolumn{5}{c|}{ Data set  properties}\\

				& \multicolumn{2}{c|}{training}   & \multicolumn{3}{c|}{testing}      \\ \cline{2-6}
				data set      & versions           & cases & versions     & cases    & \% defective             \\ \hline
				jedit    & 3.2, 4.0, 4.1, 4.2 & 1257      & 4.3          & 492          & 2 \\
				ivy      & 1.1, 1.4           & 352       & 2.0          & 352          & 11 \\
				camel    & 1.0, 1.2, 1.4      & 1819      & 1.6          & 965          & 19 \\
				ant      & 1.3, 1.4, 1.5, 1.6 & 947       & 1.7          & 745          & 22 \\
				synapse  & 1.0, 1.1           & 379       & 1.2          & 256          & 34 \\
				velocity & 1.4, 1.5           & 410       & 1.6          & 229          & 34 \\
				lucene   & 2.0, 2.2           & 442       & 2.4          & 340          & 59 \\
				poi      & 1.5, 2, 2.5        & 936       & 3.0          & 442          & 64 \\
			 xerces   & 1.0, 1.2, 1.3      & 1055      & 1.4          & 588          & 74  \\ 
			 log4j    & 1.0, 1.1           & 244       & 1.2          & 205          & 92   \\
			 xalan    & 2.4, 2.5, 2.6      & 2411      & 2.7          & 909          & 99  \\\hline

			\end{tabular}\end{minipage}~~~~~~\begin{minipage}{.4\linewidth}
			\begin{tabular}{|rrr|rrr|rr|l} \cline{1-8}

				\multicolumn{8}{|c|}{  Results from learning}\\

				\multicolumn{3}{|c|}{untuned} & \multicolumn{3}{c|}{tuned} & \multicolumn{2}{c|}{change}\\
				\cline{1-8}

				pd & pf & good? & pd & pf & good? & pd & pf\\\cline{1-8}
				\rowcolor{celadon}55 & 29 &   & 64 & 29 & y & 9 & 0&$\star$\\
				\rowcolor{celadon}	65 & 35 & y & 65 & 28 & y & 0 & -7&$\star$\\
				49 & 31 &   & 56 & 37 &   & 5 & 6\\
				\rowcolor{celadon}	49 & 13 & y & 63 & 16 & y & 14 & 3&$\star$\\
				45 & 19 &   & 47 & 15 &   & 2 & -4\\
				78 & 60 &   & 76 & 60 &   & -2 & 0\\
				56 & 25 &   & 60 & 25 & y & 4 & 0\\
				\rowcolor{celadon}	56 & 31 &   & 60 & 10 & y & 4 & -21&$\star$\\
			\rowcolor{lavenderpink}	30 & 31 &   & 40 & 29 &   & 10 & -2&$\times$\\
				\rowcolor{lavenderpink}32 & 6 &   & 30 & 6 &   & -2 & 0&$\times$\\
				\rowcolor{lavenderpink}38 & 9 &   & 47 & 9 &   & 9 & 0&$\times$\\
				\hline 
			\end{tabular}

		\end{minipage}
	\end{center}

	\caption{Training and test {\em data set properties} for  Jureczko data ,
		sorted by \% defective examples.
		On the right-hand-side, we show the {\em results from learning}.
		Data is usable if it has a recall of 60\% or more and false alarm of 30\% or less (and note that, after tuning, there are more usable data sets than before). Results  	\colorbox{celadon}{ marked with ``$\star$''} show large improvements in performance, after tuning
		(lower {\em pf} or higher {\em pd}).
		Data in  the  \colorbox{lavenderpink}{three bottom rows}, marked with ``$\times$'', are  performing
		poorly-- that data so many defective examples  that it  is hard for
		our learners to distinguish between classes.
	}\label{fig:j}
\end{figure*}

### 2016-07-14 tex/results_models.tex
Initial ShareLaTeX Import

\begin{figure}[!t]
%\noindent\begin{minipage}{0.5\textwidth} 
{\small 
\begin{tabular}{llrrc}
\arrayrulecolor{lightgray}
\rowcolor{lightgray}\textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\\hline
  1 &        XTREE &   59   &  9 & \quart{75}{4}{78}{99} \\
2 &      CD &    -9  &  77 & \quart{21}{41}{42}{99} \\
\hline \end{tabular}}
\caption{Planners applied to some ground-truth data (in this case, the POM3 model).
Values collected from  40 repeated runs of each method with different random seeds.
Results show the efficacy of XTREE in reducing the total overall cost in the original test data, when CD fail to do so.}
\label{fig:coc}
\end{figure}

### 2016-07-14 tex/rq2.tex
Initial ShareLaTeX Import

% Please add the following required packages to your document preamble:
% \usepackage{multirow}
% \usepackage[table,xcdraw]{xcolor}
% If you use beamer only pass "xcolor=table" option, i.e. \documentclass[xcolor=table]{beamer}
\newcommand{\ZZ}{.}
\begin{figure*}
\renewcommand{\baselinestretch}{0.8} 
\scriptsize  
\centering

\label{my-label}

\begin{tabular}{c|rrrr|rrrr|rrrr|rrrr|rrrr}
\multicolumn{1}{c}{\cellcolor[HTML]{EFEFEF}{\color[HTML]{000000} }} & \multicolumn{4}{c}{\cellcolor[HTML]{EFEFEF}{\color[HTML]{000000} Ant}} & \multicolumn{4}{c}{\cellcolor[HTML]{EFEFEF}{\color[HTML]{000000} Ivy}} & \multicolumn{4}{c}{\cellcolor[HTML]{EFEFEF}{\color[HTML]{000000} Lucene}} & \multicolumn{4}{c}{\cellcolor[HTML]{EFEFEF}{\color[HTML]{000000} Jedit}} & \multicolumn{4}{c}{\cellcolor[HTML]{EFEFEF}{\color[HTML]{000000} Poi}} \\
\multicolumn{1}{c@{}}{\multirow{-2}{*}{\cellcolor[HTML]{EFEFEF}{\color[HTML]{000000} Features}}} & \multicolumn{1}{c@{}}{\cellcolor[HTML]{EFEFEF}{\color[HTML]{000000} XTREE}} & \multicolumn{1}{c@{}}{\cellcolor[HTML]{EFEFEF}{\color[HTML]{000000} CD}} & \multicolumn{1}{c@{}}{\cellcolor[HTML]{EFEFEF}{\color[HTML]{000000} Alves}} & \multicolumn{1}{c@{}}{\cellcolor[HTML]{EFEFEF}{\color[HTML]{000000} Shatn}} & \multicolumn{1}{c@{}}{\cellcolor[HTML]{EFEFEF}{\color[HTML]{000000} XTREE}} & \multicolumn{1}{c@{}}{\cellcolor[HTML]{EFEFEF}{\color[HTML]{000000} CD}} & \multicolumn{1}{c@{}}{\cellcolor[HTML]{EFEFEF}{\color[HTML]{000000} Alves}} & \multicolumn{1}{c@{}}{\cellcolor[HTML]{EFEFEF}{\color[HTML]{000000} Shatn}} & \multicolumn{1}{c@{}}{\cellcolor[HTML]{EFEFEF}{\color[HTML]{000000} XTREE}} & \multicolumn{1}{c@{}}{\cellcolor[HTML]{EFEFEF}{\color[HTML]{000000} CD}} & \multicolumn{1}{c@{}}{\cellcolor[HTML]{EFEFEF}{\color[HTML]{000000} Alves}} & \multicolumn{1}{c@{}}{\cellcolor[HTML]{EFEFEF}{\color[HTML]{000000} Shatn}} & \multicolumn{1}{c@{}}{\cellcolor[HTML]{EFEFEF}{\color[HTML]{000000} XTREE}} & \multicolumn{1}{c@{}}{\cellcolor[HTML]{EFEFEF}{\color[HTML]{000000} CD}} & \multicolumn{1}{c@{}}{\cellcolor[HTML]{EFEFEF}{\color[HTML]{000000} Alves}} & \multicolumn{1}{c@{}}{\cellcolor[HTML]{EFEFEF}{\color[HTML]{000000} Shatn}} & \multicolumn{1}{c@{}}{\cellcolor[HTML]{EFEFEF}{\color[HTML]{000000} XTREE}} & \multicolumn{1}{c@{}}{\cellcolor[HTML]{EFEFEF}{\color[HTML]{000000} CD}} & \multicolumn{1}{c@{}}{\cellcolor[HTML]{EFEFEF}{\color[HTML]{000000} Alves}} & \multicolumn{1}{c@{}}{\cellcolor[HTML]{EFEFEF}{\color[HTML]{000000} Shatn}} \\
wmc & \ZZ & 92 & 100 & 100 & 18 & 95 & 100 & 100 & 89 & 95 & 100 & \ZZ &\ZZ& 63 & \ZZ &\ZZ& \ZZ & 100 & 100 &\ZZ\\
dit & \ZZ & 77 & 100 & \ZZ & \ZZ & 87 & 100 & \ZZ & \ZZ & 80 & 100 & \ZZ &\ZZ& 72 & 100 & 100 & \ZZ & 46 & 100 &\ZZ\\
noc & \ZZ & 20 & 100 & \ZZ & \ZZ & \ZZ & 100 & \ZZ & \ZZ & 26 & \ZZ &\ZZ& \ZZ &\ZZ& \ZZ &\ZZ& \ZZ &\ZZ& \ZZ &\ZZ\\
cbo & 88 & 99 & 100 & 100 & 91 & 100 & 100 & 100 & 60 & 94 & 100 & 100 & \ZZ & 100 & 100 & \ZZ & 1 & 74 & 100 &\ZZ\\
rfc & 100 & 100 & 100 & \ZZ & 8 & 95 & 100 & \ZZ & 10 & 83 & 100 & \ZZ & 100 & 100 & 100 & 100 & 100 & 95 & 100 &\ZZ\\
lcom & \ZZ & 98 & 100 & 100 & 15 & 100 & 100 & 100 & \ZZ & 94 & 100 & \ZZ &\ZZ& 100 & 100 & \ZZ &\ZZ& 100 & 100 & 100 \\
ca & \ZZ & 93 & 100 & \ZZ & 7 & 95 & 100 & \ZZ & 40 & 89 & 100 & \ZZ &\ZZ& 63 & 100 & 100 & \ZZ & 74 & 100 &\ZZ\\
ce & 5 & 100 & 100 & \ZZ & \ZZ & 97 & 100 & \ZZ &\ZZ& 90 & 100 & \ZZ &\ZZ& 100 & 100 & 100 & \ZZ & 64 & 100 &\ZZ\\
npm & \ZZ & 88 & 100 & \ZZ & 8 & 97 & 100 & \ZZ &\ZZ& 93 & 100 & 100 & \ZZ & 100 & 100 & \ZZ &\ZZ& 100 & 100 &\ZZ\\
lcom3 & \ZZ & 90 & 100 & \ZZ & 7 & 95 & 100 & \ZZ & 13 & 79 & 100 & 100 & \ZZ & 63 & 100 & 100 & \ZZ & 92 & 100 & 100 \\
loc & 100 & 99 & 100 & 100 & 97 & 97 & 100 & 100 & 60 & 100 & 100 & 100 & \ZZ & 100 & \ZZ & 100 & 100 & 100 & 100 & 100 \\
dam & \ZZ & 21 & 100 & \ZZ & \ZZ & 22 & 100 & \ZZ &\ZZ& 55 & 100 & \ZZ &\ZZ& 45 & 100 & 100 & \ZZ & 73 & 100 &\ZZ\\
moa & \ZZ & 67 & 100 & \ZZ & \ZZ & 82 & 100 & \ZZ &\ZZ& 60 & 100 & 100 & \ZZ & 54 & 100 & 100 & \ZZ & 58 & 100 &\ZZ\\
mfa & 5 & 93 & 100 & \ZZ & \ZZ & 90 & 100 & \ZZ & 5 & 80 & 100 & \ZZ &\ZZ& 72 & 100 & \ZZ &\ZZ& 72 & 100 &\ZZ\\
cam & \ZZ & 99 & 100 & 100 & 84 & 100 & 100 & 100 & 10 & 94 & 100 & \ZZ &\ZZ& 100 & 100 & \ZZ &\ZZ& 98 & 100 & 100 \\
ic & \ZZ & 52 & 100 & 100 & \ZZ & 70 & \ZZ &\ZZ& \ZZ & 68 & 100 & \ZZ &\ZZ& 36 & 100 & \ZZ &\ZZ& 43 & 100 & 100 \\
cbm & \ZZ & 59 & 100 & \ZZ & \ZZ & 85 & \ZZ &\ZZ& \ZZ & 71 & 100 & \ZZ &\ZZ& 36 & 100 & 100 & \ZZ & 67 & 100 &\ZZ\\
amc & \ZZ & 99 & \ZZ & \ZZ & \ZZ & 95 & 100 & \ZZ & 30 & 100 & \ZZ & \ZZ & \ZZ & 100 & 100 & 100 & \ZZ & 97 & \ZZ &\ZZ\\
max cc & \ZZ & 87 & 100 & 100 & \ZZ & 85 & 100 & 100 & \ZZ & 71 & \ZZ &\ZZ& \ZZ & 45 & 100 & \ZZ &\ZZ& 63 & 100 &\ZZ\\
avg cc & 12 & 99 & 100 & 100 & \ZZ & 95 & 100 & 100 & 13 & 98 & \ZZ &\ZZ& \ZZ & 100 & 100 & 100 & \ZZ & 92 & 100 & \ZZ\\\hline
\end{tabular}
\caption{Results for {\bf RQ2}.
Percentage counts of  how often an approach recommends changing a code metric
(in 40 runs). ``100'' means that this code metrics
was always recommended. Cells marked with ``.'' indicate  0\%. For the Shatnami and Alves et al.
columns,  metrics score 0\% if they always fail the $p \le 0.05$ test of \tion{p}.
For CD, cells are blank when two centroids have the same value for the same code
metrics. For XTREE, cells are blanks when they do not appear in the delta
between branches.  Note
that XTREE mentions specific code metrics
far fewer times than other methods.}\label{fig:counts}
\end{figure*}

### 2016-07-14 tex/rq3.tex
Initial ShareLaTeX Import

\def\checkmark{\tikz\fill[scale=0.3](0,.35) -- (.25,0) -- (1,.7) -- (.25,.15) -- cycle;}
\begin{figure}[tbp!]
\centering
\resizebox{0.89\linewidth}{!}{
\begin{tabular}{{l@{~~~~}l@{~~~~}|r@{~~~~}r@{~~~~}c@{~~~}r}}
\arrayrulecolor{lightgray}
\rowcolor{lightgray}\textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR~~~} & \\
  1 &          ant &    0.01  &  0.01 & \quart{0}{9}{0}{989} \\
  1 &          ivy &    0.01  &  0.01 & \quart{0}{9}{0}{989} \\
  1 &        jedit &    0.02  &  0.01 & \quart{9}{10}{9}{989} \\
  1 &          poi &    0.03  &  0.02 & \quart{9}{20}{19}{989} \\
\hline  2 &       lucene &    0.08  &  0.01 & \quart{69}{10}{69}{989} \\
\hline \end{tabular}}

\caption{Results for \textbf{RQ3} for the jureczko dataset. For each 
dataset, we measure the ambiguity of the leaf nodes (using weighted entropy) and compute the weighted average of all the leaves. Here, values near 0 imply low ambiguity. Therefore, \textit{lower} median values are better.}
\label{fig:rq3}
\end{figure}

### 2016-08-11 Manuscript.tex
Updates from ShareLaTeX

@@
-\documentclass[final,twocolumn,5p]{elsarticle}
+uu \documentclass[final,twocolumn,5p]{elsarticle}
 \usepackage{tikz}
@@
 
-\title{Which ``Bad Smells'' Can Be Ignored?}
+\title{Not Smelly Enough:  Learning What Bad Smells to Ignore}
 
@@
 \textsuperscript{b}Fraunhofer CESE, College Park, USA}
+\pagestyle{arabic}
 
 \begin{abstract} 
-{\bf Context: }The literature lists many bad smells that may be detrimental to a software system. But which are relevant to the current project and which can be ignored?
+{\bf Context: }The SE literature lists many  reasons
+for reorganizing software projects; e.g. long methods are more bug prone
+so it is wise to refactoring
+very large methods into numerous smaller ones.
+At least some of those recommendations are outdated (based on older projects)
+or irrelevant (based on other projects). Yet developers persist
+is following much of that advice, without critical reviewing
+its relevance to the current project.
+
+{\bf Objective:} If a developer is doing some task for reason ``X'', 
+how can that developer's manager assess if ``X'' is a good reason
+that justifies that task?
+
+{\bf Method:} For a particular task (manual refactoring of code in order
+to remove a bad smell), we check   if there is any historical evidence
+to endorse that refactoring.  Ysing the XTREE
+
+bad smells that may be detrimental to a software system. But which are relevant to the current project and which can be ignored?
 Developers, text books, and tools disagree on which bad smells are important. 
@@
 \noindent
+``Managing people is like herding cats'', says management consultant Watler
+Bennis~\cite{bennis97}. Nowhere is this more true than when managing programmers. 
+Programmers can be very intelligent, but very opinionated people whose
+social position within software organizations relies, in part,
+of perceived notions of technical excellence. Hence, it can
+be hard for managers to monitor and guide programmers away from wasting
+time on nonproductive activity, particularly if that programmer can find
+some support for that activity somewhere in the SE literature.
+
+Consider, for example, the activity of refactoring code based on bad smells.
 According to   Fowler ~\cite{fowler99}, bad smells (a.k.a. code smells)
@@
 of which seem ``too small to be worth doing''. 
-The  effect of   these transformations is quite significant. By doing them in small steps you {\em reduce the risk of introducing errors}'' (our italics).
+The  effect of   these transformations is quite significant. By doing them in small steps you {\em reduce the risk 
+of introducing errors}'' (our italics).
 \end{quote}
+The advice on what  bad smells to fix is extensive and, as we show below,
+contradictory (see \fig{smells}) and poorly supported. Yet
+programmers often use the SE literature to justify extensive refactoring efforts.
+For example, this paper began when a Washington-based software company shared
+one of their management challenges with us: their  releases are delayed by developers spending  much time removing bad smells within their code.
+This management team wanted some way to check if all that activity was useful (hence, this article).
+
+Note that these managers are {\em not} asking for better
+automatic refactoring
+tool support. Their human programmers are refactoring
+code all the time, perhaps too much so.
+Hence, their management goal is: 
+\bi
+\item
+{\em Not} to optimize {\em necessary} refactorings;
+\item
+But rather to discourage {\em unnecessary} refactorings.
+\ei
+For those managers, we offer the  following heuristic:
+\bi
+\item If there is no evidence in the historical record that changing ``X'' is useful;
+\item Then discourage developers from doing ``X''.
+\ei
+This paper describes one way to operationalize this heuristic, in the context
+of assessing bad smells. We use data mining to generate two oracles: a {\em primary
+change oracle} and a {\em secondary validation oracle}.
+By combining these two oracles,
+ we can generate and validate useful
+changes to code modules.
+
+In this paper, we use 
+the XTREE cluster delta algorithm as the {\em primary change  oracle} .
+XTREE 
+explores the historical record of a project to find clusters of projects.
+It then proposes a ``minimal'' set of changes $\Delta$ that can move a software module $M$ from a defective cluster $C_0$ to another with fewer defects$C_1$ (so $\Delta$
+is some subset of $C_1 - C_0$). To define ``minimal'', XTREE uses an entropy measure.
+
+As to 
+the {\em secondary validation oracle}, this  checks if the primary oracle is proposing
+sensible changes. For this purpose we  use Random Forests\cite{XXX}, augmented with SMOTE (synthetic  minority over-sampling technique~\cite{YYY}).
+ In our framework,  learning
+the secondary oracle is   a {\em separate} task to learning the primary
+oracle. This  ensures that the validation oracle offers an independent
+opinion on the value of the proposed changes.
+
+When these oracles were applied to defect data from
+open source object-oriented software systems, we discovered a {\em disjunctive fallacy}
+in the bad smell literature~\cite{erni96,bender99,Shatnawi10,Alves2010,hermans15}.
+
+\bi
+\item A common heuristic is to recommend refactoring of a code module if any static
+code measure grow ``unusually  large''
+(see \tion{bst} for   different ways to defining ``unusually large'').
+\item This can lead to a {\em disjunctive recommendation}; i.e. given knowledge
+that some static
+code measures $a_i$ is ``unusually large'' after some threshold $t_i$,
+then refactor code if we ever the see disjunction:
+\[\left(a_1 > t_1 \right) \bigvee \left(a_2 > t_2\right) \bigvee \left(a_3 > t_3 \right)\bigvee   ...\]
+\ei
+This disjunctive recommendation is a fallacy.
+According to XTREE's results,
+there exists an intricate set of associations between static code measures
+such that {\em decreasing}  $a_i$ necessitates {\em increasing} $a_j$.
+It is easy to see why this is so.
+A requirement for  refactoring is that the new code supports the same functionality
+as before. If we pull code out of a function (since that function has grown too
+large), {\em that functionality has to go somewhere else}. What we see in XTREE's change
+recommendation is that if we decrease a module's lines of code  then in the refactored
+code, the functionality is achieved via a communication between several different parts
+of the system. That is, {\em decreasing} the lines of code metric within a module {\em increases}
+that module's coupling metrics.
+
+The XTREE results  confirmed the intuitions
+of the project managers that prompted this investigation:
+Yes,  indeed, their programmers
+were wasting time on   performing refactorings  that  decreased multiple measures when, in fact,
+they should be trying to {\em decrease} some measures while {\em increasing} others.
+Also, in a study of five different JAVA OO systems,
+XTREE found that  only $\frac{4}{20}=20$\% 
+  of the measures were usually found within  change recommendations. That is, it is unlikely
+  that refactoring based on measurements of  80\% of the code measures would be useful.
+
+Based on the above, we recommend the use of XTREES as follows XXX
+
+  The rest of this paper offers details on this study.  
+  %YYYstructure of paper written here
+
+  In order to support dissemination
+  of research results, and to encourage other researchers to repeat our results,
+  all the code used in this paper is publicly available\footntote{XXX: need a public repo}.
+
+  \subsection{Relationship to Prior Work }
+A four page prelininary report on the XTREE system~\cite{krishna2015actionable} has been presented previously\footnote{https://goo.gl/2In3Lr}. That short report offered case studies only two  of
+the eight data sets studied here. Also, that prior work had
+no comparison to any baseline
+method from other researchers, whereas this paper compares XTREE's recommendations
+with those found by researchers exploring bad smells.
+Also, that paper offered
+no secondary oracle, i.e. no way to check if XTREE's recommended changes were sensible.
+Further, syntactically, we note that this report is four times longer than that prior paper.
+
+XXX next text here on CD
+
+\section{Background}
+\subsection{About Bad Smells}
+
+Bad smells are a widely used technique for evaluating code. As of  early 2016, ACM Digital Library reports 
+the Fowler text of {\em Refactoring} has 6434 references~\cite{fowler99}. A search  on {\em ``bad smell''programming} 
+where {\em proceedings=ICSE} finds 1,748 papers since 2006.
+Hence it is important to understand the value of
+this popular topic.  
+Valuable development resources may be wasted on bad smells that are ``bad''; i.e. 
+ irrelevant or misleading
+for some particular project.
+
 The literature is divided on the merits of bad smells.
@@
 lists dozens of papers on smell detection and repair tools. 
-
-Other papers cast doubt on the value of bad smells
+Yet
+other papers cast doubt on the value of bad smells
 as triggers for code improvement~\cite{Mantyla2004,Yamashita2013,Sjoberg2013}. 
@@
 
-Bad smells are a widely used technique for evaluating code. As of  early 2016, ACM Digital Library reports 
-the Fowler text has 6434 references. A search  on {\em ``bad smell''programming} 
-where {\em proceedings=ICSE} finds 1,748 papers since 2006.
-Hence it is important to understand the value of
-this popular topic.  
-Valuable development resources may be wasted on bad smells that are ``bad''; i.e. 
- irrelevant or misleading
-for some particular project.
-
-To address this problem, we propose the XTREE
-tool that uses: 
-     \begin{itemize}
-         \item A historical log of defects seen previously in the code;
-         \item  Bad smells expressed in terms of the 
-          metrics   in that log;
-         \item Some proposed refactorings justified using those bad smells.
-     \end{itemize}
-Given that,  XTREE can determine which
-  proposed refactorings are to be ignored
-since they are not justifiable  
-with respect to the history of the project. XTREE addresses four problems that  make it hard to  learn useful
-bad smells for a particular project.
-
-{\em PROBLEM \#1:} As discussed in the next section, programmer
+In our view, there are four major problems with bad smells.
+
+{\bf PROBLEM \#1:} As discussed in the next section, programmer
   cognitive biases result in different
@@
 bad smell X or Y is most important. 
- XTREE offers a way to assess the value of competing recommendations to address smell X vs. Y.
-
-{\em PROBLEM \#2:} Not all bad smells can be fixed. 
+ XTREE is useful for  assessing the relative importance of
+   X vs. Y.
+
+{\bf PROBLEM \#2:} Not all bad smells can be fixed. 
 When new code must
@@
 
-To address this problem, XTREE {\em reasons optimistically} to find the set
+Hence, XTREE {\em reasons optimistically} to find the set
 $R_0$ of refactorings that \textit{might} be useful (see \tion{rq} on optimistic reasoning).
@@
 
-{\em PROBLEM \#3:}  
+{\bf PROBLEM \#3:}  
 Shantnawi~\cite{Shatnawi10} warns most  studies do not offer
@@
 
-{\em PROBLEM \#4:} It is hard to judge the  effects of removing bad smells.
+{\bf PROBLEM \#4:} It is hard to judge the  effects of removing bad smells.
 Refactored code cannot be assessed just by a rerun of the the test
@@
 % should pass before and after the refactoring). 
-% Also, it many not be practical
-%  to assessing refactorings by making the
-% refactorings,  then seeing what happens to that code for the rest
-% of the project. In a test-driven agile project, as
-% SCRUM meetings change what stories are implemented next,
-% the operational profile that lead to defects in the old
-% code may not be repeated in future executions. 
+Also, it many not be practical
+ to assessing refactorings by making the
+refactorings,  then seeing what happens to that code for the rest
+of the project. In a test-driven agile project, as
+SCRUM meetings change what stories are implemented next,
+the operational profile that lead to defects in the old
+code may not be repeated in future executions.
+
 To resolve this  problem, SE researchers such as 
@@
 Moghadam~\cite{Moghadam2011} and Mkaouer et al.~\cite{Mkaouer14}
-use a pair of systems: 
+use a pair of oracles: 
 \begin{enumerate}
-    \item One system to propose changes;
-\item A separate system to assess
+    \item A {\em primary oracle} system to propose changes;
+\item A {\em secondary validation oracle} (which is learned separately
+to the primary oracle) that   assesses
 how defective is the code before and after some
@@
 may perform poorly when applied to new projects~\cite{localvsglobal}.
-
-To solve this fourth problem, this study  eschews
-older quality models like QMOOD, we use
+Hence, for this study, we  eschew
+older quality models like QMOOD. Instead, we use
 Random Forests~\cite{Breiman2001} to learn defect predictors
@@
 
-The rest of this paper is structured as follows. 
-The next section
-discusses the cognitive
-biases that make developers disagree on the relevance of those bad smells to
-their particular projects
-(that discussion is our motivation for developing 
-tools like XTREE). This is followed by a discussion
-on various methods to learn thresholds for bad smells.
-After evaluating those methods, we discuss various threats to
-validity that threaten our conclusions.
-
-Before  that, we offer one following note on a
-core assumption of XTREE.
-XTREE   is focused on Fowler's bad smells
-as contributors to software defects. Some researchers 
- suggest that discussing bad smells is useful for more just reducing defects. For example, Bosu and Carver~\cite{bosu13} report that
-debates about code smells and refactorings can (a)~introduce new comers to the code base or (b)~share knowledge on a team
-about interactions within the code. In that view, 
-the concept of refactoring can be useful
-even if it does not address issues of defects.
-
-\subsection{Contributions of this Paper }
-The XTREE learner has not been reported
-previously. 
-The comparative analysis of XTREE
-    versus previously published approaches to learning
-    bad smell detectors shows
-    that XTREE   rarely perfoms
-      worse that the other approaches~\cite{Shatnawi10,Alves2010}
-      and often is it   much better at proposing
-      changes that reduce the expected
-      number of of the defects. Further, the number
-    of code metrics mentioned by XTREE is far
-    fewer than other approaches, making it easier to validate refactorings proposed by
-    developers. 
-We
-show here that XTREE is less verbose and offers better recommendations than the CD tool   developed previously with Borges~\cite{me12c}.
- The experimental rig
- used to comparatively assess
-    XTREE is another novel contribution\footnote{tiny.cc/XTREE}. Using the design
-    of that rig,
-    other researchers could confirm/improve/refute
-    the conclusions of this paper.
-
-\section{Motivation}\label{sect:prelim}
+\subsection{Why Not Just Ask Developers to Rank Bad Smells?}\label{sect:prelim}
 
@@
 \section{Learning Bad Smell Thresholds}\label{sect:bst}
-Research studies and tools (e.g., SonarQube~\cite{sq15}) leverage OO metrics as representatives for code smells, as we do in this study.
-In this section, we focus on determining thresholds for interpreting these metrics as ``bad smells'' or not.
 
@@
     These two approaches are discussed below.
-\subsection{  Outlier Statistics}\label{sect:p}
 
@@
 The literature lists several ways to define ``unusually large''.
+
+\subsection{Outlier Statistics}
 
@@
 
-\subsubsection{Discussion }\label{sect:disc}
+\subsubsection{Discussion of Outlier Methods}\label{sect:disc}
 The advantage of the outlier-based
@@
 
-\subsubsection{CD}
+\subsubsection{CD}\label{sec:cdcd}
 Borges and Menzies first proposed the CD centroid delta approach to
@@
 \section{Threats to Validity}\label{sect:valid}
+
+Before  that, we offer one following note on a
+core assumption of XTREE.
+XTREE   is focused on Fowler's bad smells
+as contributors to software defects. Some researchers 
+ suggest that discussing bad smells is useful for more just reducing defects. For example, Bosu and Carver~\cite{bosu13} report that
+debates about code smells and refactorings can (a)~introduce new comers to the code base or (b)~share knowledge on a team
+about interactions within the code. In that view, 
+the concept of refactoring can be useful
+even if it does not address issues of defects.
 

### 2016-08-13 Manuscript.tex
Updates from ShareLaTeX

@@
-uu \documentclass[final,twocolumn,5p]{elsarticle}
+\documentclass[twocolumn,5p]{elsarticle}
 \usepackage{tikz}
@@
 
-\usepackage{tikz}
-\usepackage{xcolor}
+\definecolor{Gray}{rgb}{0.88,1,1}
+\definecolor{Gray}{gray}{0.85}
+\usepackage[svgnames]{xcolor}
 \usepackage[framed]{ntheorem}
 \usepackage{framed}
+\usepackage{tikz}
 \usetikzlibrary{shadows}
@@
 \tikzstyle{thmbox} = [rectangle, rounded corners, draw=black,
-  fill=Gray!20,  drop shadow={fill=black, opacity=1}]
+  fill=Gray!40,  drop shadow={fill=black, opacity=1}]
 \newcommand\thmbox[1]{%
@@
 \begin{minipage}{.94\textwidth}%    
-      \vspace{-3mm}#1\vspace{-3mm}%
+      \vspace{-2mm}#1\vspace{-3mm}%
     \end{minipage}%
@@
 \let\theoremframecommand\thmbox
-\newshadedtheorem{lesson}{Research answer}
+\newshadedtheorem{lesson}{Result}
 
@@
 
-\title{Not Smelly Enough:  Learning What Bad Smells to Ignore}
+\title{How to Stop Useless Refactorings}
 
@@
 \begin{abstract} 
-{\bf Context: }The SE literature lists many  reasons
-for reorganizing software projects; e.g. long methods are more bug prone
-so it is wise to refactoring
-very large methods into numerous smaller ones.
-At least some of those recommendations are outdated (based on older projects)
-or irrelevant (based on other projects). Yet developers persist
-is following much of that advice, without critical reviewing
-its relevance to the current project.
-
-{\bf Objective:} If a developer is doing some task for reason ``X'', 
-how can that developer's manager assess if ``X'' is a good reason
-that justifies that task?
-
-{\bf Method:} For a particular task (manual refactoring of code in order
-to remove a bad smell), we check   if there is any historical evidence
-to endorse that refactoring.  Ysing the XTREE
-
-bad smells that may be detrimental to a software system. But which are relevant to the current project and which can be ignored?
-Developers, text books, and tools disagree on which bad smells are important. 
-Further, it is unclear at what threshold values smell-related metrics
-should trigger code improvement or preventative maintenance. Most studies do not offer {\em both} measurable metrics {\em and} a threshold for their proposed bad smells.
+{\bf Context: } 
+Developers use code bad smells to gudie their refactoring (reorganizing their code).
+Yet developers, text books, and tools disagree on which bad smells are important.
+%Many bad smell detectors recommend refactoring when static code measure
+%cross some threshold boundary. 
+%%However, it is unclear at what threshold values smell-related metrics
+%should trigger code improvement or preventative maintenance.
 
 \noindent 
-{\bf Objective: }We seek to propose a tool to prioritize  bad  smells.
+{\bf Objective: } We seek to a tool that can recognize  useless refactorings.
 
 \noindent
-{\bf Method: } We introduce XTREE, a tool which, given a historical log of defects seen previously in the code, deprioritizes bad smells that have no prior association with defects.
+{\bf Method: } We introduce XTREE, a tool which, given a historical log of defects seen previously in the code, generates
+a set of useful code changes.
+Any bad smell that requires changes outside of that set can be deprioritized 
+(since there is no
+historical evidence that that bad smell causes any problems).
 
@@
 {\bf Results: }Code modules that are changed in response to XTREE's recommendations contain significantly fewer defects than recommendations in previous studies.
-Further, XTREE endorses changes to far fewer code metrics, and that bad smell recommendations (learned from previous studies) are not universal to software projects.
+Further, XTREE endorses changes to very few code metrics, and those bad smell recommendations (learned from previous studies) are not universal to all  software projects.
 
 \noindent
-{\bf Conclusion: }It is important to  prioritize the importance of specific bad smells in the context of each project since not all bad smells are relevant to the current project.
-Based on these results, we endorse using bad smells to guiding refactoring.
+{\bf Conclusion: }
+Before undertaking a refactoring based on a bad smell report,
+use a tool like XTREE to check and ignore any refactoring   that  are useless; i.e. which lacks evidence
+  in the historical record  that it is useful to make that change.
+  Note that this use case applies to both manual refactorings proposed by developers
+as well as refactoring  conducted by automatic methods.
+This recommendation assumes that there is an historical record.
+If none exists, then the results of this paper could be use used as a guide (see our
+Table~8).
 
@@
 \noindent
-``Managing people is like herding cats'', says management consultant Watler
-Bennis~\cite{bennis97}. Nowhere is this more true than when managing programmers. 
-Programmers can be very intelligent, but very opinionated people whose
-social position within software organizations relies, in part,
-of perceived notions of technical excellence. Hence, it can
-be hard for managers to monitor and guide programmers away from wasting
-time on nonproductive activity, particularly if that programmer can find
-some support for that activity somewhere in the SE literature.
-
-Consider, for example, the activity of refactoring code based on bad smells.
+%%``Managing people is like herding cats'', says management consultant Watler
+%Bennis~\cite{bennis97}. Nowhere is this more true than when managing programmers. 
+%Programmers can be very intelligent, but very opinionated people whose
+%social position within software organizations relies, in part,
+%of perceived notions of technical excellence. Hence, it can
+%be hard for managers to suggest to programmers that are
+%wrong about how they are prioritizing their development effort.
+
+%Consider, for example, the activity of refactoring code based on bad smells.
 According to   Fowler ~\cite{fowler99}, bad smells (a.k.a. code smells)
@@
 of which seem ``too small to be worth doing''. 
-The  effect of   these transformations is quite significant. By doing them in small steps you {\em reduce the risk 
-of introducing errors}'' (our italics).
+The  effect of   these \underline{refactoring} transformations is quite significant. By doing them in small steps you reduce the risk 
+of introducing errors''.
 \end{quote}
-The advice on what  bad smells to fix is extensive and, as we show below,
-contradictory (see \fig{smells}) and poorly supported. Yet
-programmers often use the SE literature to justify extensive refactoring efforts.
+Bad smells are a widely used technique for evaluating code. As of  early 2016, ACM Digital Library reports 
+the Fowler text of {\em Refactoring} has 6434 references~\cite{fowler99}. A search  on {\em ``bad smell''programming} 
+where {\em proceedings=ICSE} finds 1,748 papers since 2006.
+Hence it is important to understand the value of
+this popular topic.  
+Valuable development resources may be wasted on bad smells that are ``bad''; i.e. 
+ irrelevant or misleading
+for some particular project.
+
+In our experience, programmers can use the SE literature to justify extensive, perhaps even excessive, refactoring efforts.
 For example, this paper began when a Washington-based software company shared
 one of their management challenges with us: their  releases are delayed by developers spending  much time removing bad smells within their code.
-This management team wanted some way to check if all that activity was useful (hence, this article).
+This management team wanted some way to check if all that activity was useful.
 
@@
 \item
-But rather to discourage {\em unnecessary} refactorings.
+But rather to stop {\em unnecessary} refactorings.
 \ei
@@
 \item If there is no evidence in the historical record that changing ``X'' is useful;
-\item Then discourage developers from doing ``X''.
+\item Then stop developers from doing ``X''.
 \ei
@@
 When these oracles were applied to defect data from
-open source object-oriented software systems, we discovered a {\em disjunctive fallacy}
+open source object-oriented software systems, we discovered a {\em conjunctive fallacy}
 in the bad smell literature~\cite{erni96,bender99,Shatnawi10,Alves2010,hermans15}.
-
-\bi
-\item A common heuristic is to recommend refactoring of a code module if any static
-code measure grow ``unusually  large''
-(see \tion{bst} for   different ways to defining ``unusually large'').
-\item This can lead to a {\em disjunctive recommendation}; i.e. given knowledge
-that some static
-code measures $a_i$ is ``unusually large'' after some threshold $t_i$,
-then refactor code if we ever the see disjunction:
-\[\left(a_1 > t_1 \right) \bigvee \left(a_2 > t_2\right) \bigvee \left(a_3 > t_3 \right)\bigvee   ...\]
-\ei
-This disjunctive recommendation is a fallacy.
-According to XTREE's results,
+A common heuristic is to recommend refactoring of ``bad'' code
+to make it ``better''   as follows: for all static code measures that exceed some threshold, make changes such that the thresholds are no longer exceeded. That is:
+\begin{equation}\label{eq:df}
+\scriptstyle
+\begin{array}{rl}
+\mathit{bad} & = \left(a_1 > t_1 \right) \bigvee \left(a_2 > t_2\right) \bigvee    ... \\
+\mathit{better} & = \neg\;\mathit{bad} = \left(a_1 \le t_1 \right) \bigwedge \left(a_2 \le t_2\right)  \bigwedge  ...
+\end{array}
+\end{equation}
+We say that the above definition of ``better'' is a conjunctive fallacy
+since it assumes that the best way to improve code is to decreases multiple code attribute measures below $t_i$ in order
+to remove the ``bad'' smells. This is wrong since 
 there exists an intricate set of associations between static code measures
@@
 
-The XTREE results  confirmed the intuitions
+  The rest of this paper is structured as follows. First, we offer some background on bad smells. After that,
+  in Section~3, 
+  different methods for determining when code does/does not have bad smell. One of those methods
+  will be XTREE while the others will come from other researchers. Next,    Section~4
+  defines an assessment method that checks which of these methods is most useful. The results from that assessment 
+  are presented in Section~5. Those results will answer five research questions.
+
+ {\bf  RQ1: Effectiveness}: According to the validation oracle, which of the methods  defined in Section~3 is the best  change oracle for identifying what and how
+  code modules should be changed? To answer this question, we used data from five OO Java projects
+  (Ivy, Lucene, Ant, Poi, Jedit). It was found that:
+  \begin{lesson}
+ XTREE is the best oracle on how to change code modules (in order to reduce defects).
+  \end{lesson}
+
+ {\bf RQ2: Succinctness}: Our goal is to critique and, possibly,
+ignore irrelevant bad smell detectors.  If those changes are minimal (i.e. effect fewest attributes) then those changes
+will be easiest to apply and monitor. Hence, we ask, which of the Section~3 methods recommended changes to the fewest
+code attributes?
+\begin{lesson}
+Of all the code change oracles studied here, XTREE recommend  far fewest changes to static code measures.
+\end{lesson}
+
+ {\bf RQ3: Stopping}: Our advice to managers is to stop refactoring based on changes that lack
+historical evidence of being effective. How effective is XTREE at offering such ``stopping points'' (i.e. clear guidance on what {\em not} to do)??
+\begin{lesson}
+In  any  project,  XTREE’s  recommended  changes  only  mentions one to four 
+of the  static code attributes.  Any bad smell defined in terms of the remaining 19 to 16 code attributes (i.e. most of them)
+would hence be deprecated.
+\end{lesson}
+
+ {\bf RQ4: Stability}: Across different projects, how variable are the changes recommended by our best change oracle?
+\begin{lesson}
+The direction of change recommended  XTREE is  very stable across repeated runs of the program 
+\end{lesson}
+
+{\bf RQ5: Conjunctive Fallacy}:  
+Is it always  useful  to aplly \eq{df}; i.e. make code better by   reducing the values of  multiple code attributes? We find that:
+\begin{lesson}
+XTREE usually recommends reducing lines of code (size of the modules).
+That said,  XTREE often recommends {\em increasing} the values of other static code attributes.
+\end{lesson} 
+Note that {\bf RQ3, RQ4, RQ5} 
+confirms the intuitions
 of the project managers that prompted this investigation:
+\bi
+\item
 Yes,  indeed, their programmers
@@
 they should be trying to {\em decrease} some measures while {\em increasing} others.
-Also, in a study of five different JAVA OO systems,
-XTREE found that  only $\frac{4}{20}=20$\% 
-  of the measures were usually found within  change recommendations. That is, it is unlikely
-  that refactoring based on measurements of  80\% of the code measures would be useful.
-
-Based on the above, we recommend the use of XTREES as follows XXX
-
-  The rest of this paper offers details on this study.  
-  %YYYstructure of paper written here
+\item
+Across all studied projects, XTREE found that  around one-fifth  
+  of the measures were usually found within  change recommendations. That is, it is 80\% likely that
+  that refactoring based on reducing any one measurement picked at random will be useful.
+\ei
+Consequently, we  recommend that XTREE be used as follows:
+\bi
+\item Before doing  refactoring based on a bad smell report...
+\item ...check and stop any refactoring   for which there is no proof
+  in the historical record that that change improves the code.
+\ei
+Note that this use case applies to both manual refactorings proposed by developers
+as well as refactoring as conducted by automatic methods~\cite{mkaouer2015many}.
+Note also that
+this recommendation assumes that there is an historical record. If none exists, then the results of this paper could be use used as a guide (see our Table 8).
+
+ \subsection{Replication Package}
 
@@
   of research results, and to encourage other researchers to repeat our results,
-  all the code used in this paper is publicly available\footntote{XXX: need a public repo}.
+  all the code used in this paper is publicly available\footnote{XXX: need a public repo}.
 
@@
 A four page prelininary report on the XTREE system~\cite{krishna2015actionable} has been presented previously\footnote{https://goo.gl/2In3Lr}. That short report offered case studies only two  of
-the eight data sets studied here. Also, that prior work had
+the five data sets studied here. Also, that prior work had:
+\bi
+\item
 no comparison to any baseline
@@
 with those found by researchers exploring bad smells.
-Also, that paper offered
-no secondary oracle, i.e. no way to check if XTREE's recommended changes were sensible.
-Further, syntactically, we note that this report is four times longer than that prior paper.
-
-XXX next text here on CD
-
-\section{Background}
-\subsection{About Bad Smells}
-
-Bad smells are a widely used technique for evaluating code. As of  early 2016, ACM Digital Library reports 
-the Fowler text of {\em Refactoring} has 6434 references~\cite{fowler99}. A search  on {\em ``bad smell''programming} 
-where {\em proceedings=ICSE} finds 1,748 papers since 2006.
-Hence it is important to understand the value of
-this popular topic.  
-Valuable development resources may be wasted on bad smells that are ``bad''; i.e. 
- irrelevant or misleading
-for some particular project.
-
-The literature is divided on the merits of bad smells.
+\item
+no {\em secondary validation oracle}, i.e. no way to check if XTREE's recommended changes were sensible.
+\ei
+Further, of this entire paper, the only sections containing material
+found in prior papers is 3.2.1, 3.2.2 as well as two-fifths of \fig{}.
+%YYY section1,2, 3.1,4,
+% Prior to XTREE, the authors worked on
+% the CD algorithm discussed in ~\tion{cdcd}. 
+% The goal of CD was the same as WHERE-- find recommendations on how to best change software
+% modules. However, as discussed in~\tion{cdcd},
+% CD worked very different to WHERE. Further, as shown in this paper,
+% CD is significantly out-performed by XTREE.
+
+\section{Why Not Just Ask Developers to Rank Bad Smells?}\label{sect:prelim}
+
+Why build tools like XTREE to  critique proposed developer actions?
+Our answer, documented in this section, is that (1)~SE literature is not clear which bad smells are ignorable or  high priority and must be resolved.
+Also, (2)~developers themselves are unclear on what bad smells are most important to fix.
+
 Much research endorses them to guide
@@
 
-In our view, there are four major problems with bad smells.
-
-{\bf PROBLEM \#1:} As discussed in the next section, programmer
-  cognitive biases result in different
-developers declaring that
-bad smell X or Y is most important. 
- XTREE is useful for  assessing the relative importance of
-   X vs. Y.
-
-{\bf PROBLEM \#2:} Not all bad smells can be fixed. 
-When new code must
-be combined with code from a third party, 
-sometimes the constraints of that code 
-lead unavoidably to bad smells violations (e.g.
-developers might need to passed as a single closure a  very long method
-to  a third-party GUI toolkit).   In this case,
-a refactoring proposed to reduce that bad smell
-may be irrelevant since it cannot be applied to this code base.
-
-Hence, XTREE {\em reasons optimistically} to find the set
-$R_0$ of refactorings that \textit{might} be useful (see \tion{rq} on optimistic reasoning).
-The space of \textit{actually usable} refactorings is 
-the subset $R_1 \subseteq R_0$.
-If a developer's proposed refactoring $R_2$ is
-not in $R_0$, then it cannot be in the usable
-set $R_1$.  We show experimentally that XTREE
-often recommends small subsets of
-code metrics as useful guides for refactoring. Thus, we
-can rule out some proposed refactorings
-since many of those proposals fall outside of the space
-useful refactorings ($R_0$) suggested by XTREE.
-
-{\bf PROBLEM \#3:}  
-Shantnawi~\cite{Shatnawi10} warns most  studies do not offer
-{\em both} a metric and a threshold for proposed bad smells. For example,  Darcy and Kemerer~\cite{darcy05}
-discuss object-oriented (OO) design metrics that might defect bad smells (e.g. an excessive
-depth of inheritance tree), but they do not define thresholds
-for when the code starts to smell bad.  
-Shatnawi~\cite{Shatnawi10}
-and  Alves et al.~\cite{Alves2010} are rare cases where both metrics and thresholds are defined (see \tion{bst}).
-However, their approaches do not explore the interconnections between sets of code metrics. This is important if sets of
-code metrics have to be changed at the same time.
-For example, it is not possible to refactor a
-long method if several smaller ones without increasing
-the coupling metrics of a class. 
-More generally, we say that bad smell thresholds should be
-{\em conjunctions} of metric+threshold pairs that need to be changed {\em together}.
-Shatnawi~\cite{Shatnawi10}
-and Alves et al. report {\em disjunctions} of multiple metrics+thresholds~\cite{Shatnawi10,Alves2010} without indicating how changes to these metrics are related.
-
-To address this third problem, 
-XTREE   generates {\em conjunctions} of   thresholds
-than should  be considered at the same time.
-
-{\bf PROBLEM \#4:} It is hard to judge the  effects of removing bad smells.
-Refactored code cannot be assessed just by a rerun of the the test
-suite (since refactorings are supposed to preserve behavior), and otherwise one must wait for new defect reports to evaluate the effect of refactoring changes on code.  
-% waiting to observe 
-% code refactorings is meant to
-% preserve the behavior of the system (i.e. the same tests
-% should pass before and after the refactoring). 
-Also, it many not be practical
- to assessing refactorings by making the
-refactorings,  then seeing what happens to that code for the rest
-of the project. In a test-driven agile project, as
-SCRUM meetings change what stories are implemented next,
-the operational profile that lead to defects in the old
-code may not be repeated in future executions.
-
-To resolve this  problem, SE researchers such as 
-Cheng et al.~\cite{Cheng10}, O'Keefe et al.~\cite{OKeeffe08,OKeeffe07},
-Moghadam~\cite{Moghadam2011} and Mkaouer et al.~\cite{Mkaouer14}
-use a pair of oracles: 
-\begin{enumerate}
-    \item A {\em primary oracle} system to propose changes;
-\item A {\em secondary validation oracle} (which is learned separately
-to the primary oracle) that   assesses
-how defective is the code before and after some
-refactoring.
-\end{enumerate}
-For the second system,
- Cheng, O'Keefe, Moghadam and  Mkaouer et al. use the QMOOD hierarchical
-quality model~\cite{Bansiya02}.
-A shortcoming of QMOOD
-is that quality models learned from other projects
-may perform poorly when applied to new projects~\cite{localvsglobal}.
-Hence, for this study, we  eschew
-older quality models like QMOOD. Instead, we use
-Random Forests~\cite{Breiman2001} to learn defect predictors
-from OO code metrics.
-Note that, unlilke QMOOD, such measurements 
-  are specific to the project, and the measurements can be reconstructed and the predictors rebuilt for other projects.
-
-\subsection{Why Not Just Ask Developers to Rank Bad Smells?}\label{sect:prelim}
-
-Why build tools like XTREE to  critique proposed developer actions?
-Are not those developers the best guide to what is important or irrelevant
-to their code? Developer {\em cognitive biases} can mislead them to
+If the SE literature is contradictory, why not ignore it and use domain experts (software engineers) to decide
+what bad smells to fix? We do not recommend this since developer {\em cognitive biases} can mislead them to
 assert that some things are important and relevant when they are not. 
-This section discusses those biases-- firstly in the general sense
-across all SE beliefs; then secondly in the   context of code smells.
-
 A widespread malaise in software engineering is that
@@
 
-\begin{enumerate} 
+\bi
 % COMMENT FROM LL: This bullet is weak. Maybe goto isn't used in an unrestricted manner because of Djikstra's warning.
@@
 correspond with actual evidence in that project''~\cite{prem16}.
-\end{enumerate}
+\ei
 Devanbu et al. further  comment that ``programmers give personal experience
@@
 
+Having made the case for automatic support for assessing bad smells,
+this section reviews different ways for building those tools (one of those tools,
+XTREE, will be our recommended {\em primary change oracle}).
+Later in this paper, we will offer  a {\em secondary validation oracle}
+that checks the effectiveness of the changes proposed by XTREE.
+
 The SE literature offers  two ways to 
@@
     measures   how well this   model predicts for   defects.
-Any code metric with $p_0>0.05$ is  rejected as being a poor defect predictor. Thresholds are then learned from the surviving metrics $M_c$ using
+Any code metric with $p_0>0.05$ is  ignored as being a poor defect predictor. Thresholds are then learned from the surviving metrics $M_c$ using
 an equation proposed by Bender:
@@
  XTREE looks for a nearby branch that has a lower chance of being defective.
-Finding the \textcolor{green}{{\bf green}} desired  branch,  XTREE reports a bad smell threshold for that module that is the delta between the \textcolor{orange}{{\bf orange}}  current branch  and   \textcolor{green}{{\bf green}} designed branch.
+Finding the \textcolor{green}{{ green}} desired  branch,  XTREE reports a bad smell threshold for that module that is the delta between the \textcolor{orange}{{\bf orange}}  current branch  and   \textcolor{green}{{ green}} designed branch.
  In this case, that threshold relates to:
@@
 Second, the outlier approaches suffers from
-the {\em disjunction} problem.
+the {\em disjunction fallacy}  discussed in the introduction.
 That is, while
  they propose thresholds for many code metrics
-individually, they make no comment on what
-metrics need to be changed at the same time.
+individually, they make no comment on what minimal
+metrics need to be changed at the same time (or whether or not those
+changes need to minimizations or maximations of static code measures).
 
@@
   that avoids the problem of verbose $\Delta$s.
+  It is our recommended {\em primary change oracle} that makes recommendations 
+  of what changes should be made to code modules.
   Instead of reasoning over cluster centroids,
@@
       XTREE then looks for a nearby leaf node with a lower defect
-      count (see the \textcolor{green}{{\bf green}} line in \fig{xtree_samp}). For that evaluated class, XTREE proposes a bad smell
+      count (see the \textcolor{green}{{green}} line in \fig{xtree_samp}). For that evaluated class, XTREE proposes a bad smell
       thresholds that is  the difference between 
-      \textcolor{green}{{\bf green}} and \textcolor{orange}{{\bf orange}}.
+      \textcolor{green}{{green}} and \textcolor{orange}{{\bf orange}}.
 
@@
 \section{Evaluation}
-\subsection{Research Questions}
-% To define our experiments, we  review some details
-% about XTREE.
-
- XTREE proposes
-conjunctions of changes that might perform better than
-the disjunctions proposed by Shatnawi and Alves et al.
-Unlike CD, XTREE should be less verbose since
-it only reports the deltas in the code
-metrics rather than values for all metrics.
-To evaluate XTREE,
-we propose four research questions.
-
-\subsubsection{ RQ1: Effectiveness} \label{sect:rq}
-
-{\em In a comparison of   outlier and cluster delta
-methods, which one most reduces the expected number
-of defects?}
-
-To find an answer to this question, we will assume that developers
+The previous section proposed numerous methods for detecting bad smells that need
+to be resolved. This section offers an experiment of the following form:
+\bi
+\item Using each method as a {\em primary change oracle} to recommend how code should be changed.
+\item Apply those changes. 
+\item Run a {\em secondary validation oracle} to assess the defect-proness of the changed code.
+\item Sort the change oracles on how well they reduce defects (as judged by the validation oracle).
+\ei
+Using this experiment, we can address the research questions dicsussed in the introduction.
+
+{\bf RQ1: Effectiveness: } which of the methods defined in Section 3 is the best change oracle for identifying what and how code modules should be changed? 
+To   answer to this question, we will assume that developers
 refactor their code until the bad smell thresholds is not violated.
@@
 to 100.  
-Using a defect
-predictor learned via Random Forest, we then predict the
+Using the secondary validation oracle,  we then predict the
 number of defects in $d_+,d_-$ in {\em initial} and {\em new}. We evaluate the performance of XTREE, CD, Shatnawi, and Alves methods in setting bad smell thresholds.
@@
 
-\subsubsection{RQ2: Verbosity}
-
-{\em In a comparison of    outlier and cluster delta
-methods, which one proposes the fewest thresholds?}
-
-Note that this is important since our goal is to critique and, possibly,
-reject irrelevant bad smell detectors. As mentioned above,
-  verbosity makes it hard   to critique and prune bad smells
-since any bad smell mentioned by a developer has some support
-somewhere amongst all those proposed thresholds.
-
-To measure verbosity, we will compare the counts of how often
-different approaches assign thresholds to code metrics
-(and the one that makes the least assignments is the least verbose).
-
-\subsubsection{RQ3: Optimality}
-
-{\em How consistent are the leaves of XTREE?}
-
-Before using XTREE to critique bad smell detectors, it is important to analyze the quality XTREE. Such analysis allows users to determine the credibility of the critiques offered.
-
-To measure the optimality we measure the discriminatory power of the tree as suggested by ~\cite{osei04}. (Note: this is done in addition to the most commonly used performance criterion (i.e.
-correct classification rate). For XTREE (with binary target variables) we present the probability of false alarm (PF) and the probability of detection (pf) in \fig{j}.)
-
-\subsubsection{RQ4: Understanding Co-changes}
-
-{\em In a comparison of outlier and cluster delta
-methods, which one is aware of the existing associations between software metrics?}
-
-Our goal is to critique and, possibly, reject irrelevant bad smell detectors.
-However, with low verbosity there exists the risk of ignoring underlying associations that exist between software metrics.
-Failure to respect this challenges the validity of the critiques.
-
-To measure if our methods respect these co-changes in metrics, we will compare the medians of each of the metrics.
-Statistically significant changes in all co-varying metrics will indicate our method's efficacy in respecting these underlying associations.
+{\bf RQ2: Succinctness: } which of the Section 3 methods recommended changes to the fewest code attributes?
+To answer this question, we will report the frequency at which different attributes are selected in repeated runs of our oracles.
+
+{\bf RQ3: Stopping: }    How effective is XTREE at offering   ``stopping points'' (i.e. clear guidance on what {\em not} to do)?   
+To answer this point, we will report how often XTREE's recommendations {\em omit} a code attribute. 
+Note that the {\em more often} XTREE omits an attribute, the more likely it is {\em not} to endorse a bad smell based on the omitted
+attribites.
+
+{\bf RQ4: Stability:} Across different projects, how variable are the changes recommended by XTREE?   To answer this
+question, we conduct a large scale ``what if'' study that reports all the possible recommendations XTREE might make.
+We then count often attributes are {\em not} found in the recommendations arising from this ``what if'' study.
+
+{\bf RQ5: Conjunctive Fallacy:} Is  it  always  useful  to  aplly \eq{df}; i.e.
+make  code  better  by  reducing  the  values  of multiple code attributes?
+To answer this question, we will look at the {\em direction of change} seen in the {\bf RQ4} study; i.e.
+how often does XTREE recommend decreasing or increasing a static code attribute.
 
@@
 metrics, see  \fig{ck}. For details on the rows and versions
-of that data, see the left-hand-side columns of \fig{j}.
-
-\subsection{Assessment Oracles}
+of that data, see the left-hand-side columns of \fig{jur}.
+
+\subsection{Secondary Validation Oracles}
 \label{sect:eval}
-We must be able to assess how defective the code is before and after a proposed refactoring.
-Since we do not have actual  examples of defect counts post-refactoring, we   approximate   defect counts after the   changes   (as changes to the code metrics).
-
-Prior work~\cite{Cheng10,OKeeffe08,OKeeffe07,Moghadam2011,Mkaouer14} 
-used the QMOOD   quality model ~\cite{Bansiya02} to assess the results of their refactorings
-Since the QMOOD method based on old (2002) project data, we use Random Forests~\cite{Breiman2001} to build
-the assessment methods.
+
+As mentioned in the introduction, our proposed framework has two oracles:
+a primary change oracle (XTREE) and the secondary validation oracle described in this section.
+
+It can be difficult  to judge the  effects of removing bad smells.
+Refactored code cannot be assessed just by a rerun of the the test
+suite (since refactorings are supposed to preserve behavior). 
+% waiting to observe 
+% code refactorings is meant to
+% preserve the behavior of the system (i.e. the same tests
+% should pass before and after the refactoring). 
+Also, it many not be practical
+ to assessing refactorings by making the
+refactorings,  then seeing what happens to that code for the rest
+of the project. In a test-driven agile project, as
+SCRUM meetings change what stories are implemented next,
+the operational profile that lead to defects in the old
+code may not be repeated in future executions.
+
+To resolve this  problem, SE researchers such as 
+Cheng et al.~\cite{Cheng10}, O'Keefe et al.~\cite{OKeeffe08,OKeeffe07},
+Moghadam~\cite{Moghadam2011} and Mkaouer et al.~\cite{Mkaouer14}
+use a {\em secondary validation oracle} (which is learned separately
+to the primary oracle) that   assesses
+how defective is the code before and after some
+refactoring. 
+For their second oracle,
+ Cheng, O'Keefe, Moghadam and  Mkaouer et al. use the QMOOD hierarchical
+quality model~\cite{Bansiya02}.
+A shortcoming of QMOOD
+is that quality models learned from other projects
+may perform poorly when applied to new projects~\cite{localvsglobal}.
+Hence, for this study, we  eschew
+older quality models like QMOOD. Instead, we use
+Random Forests~\cite{Breiman2001} to learn defect predictors
+from OO code metrics.
+Note that, unlilke QMOOD, such measurements 
+  are specific to the project, and the measurements can be reconstructed and the predictors rebuilt for other projects.
+
   Random Forests are a decision tree learning method but
@@
 In order to identify the presence (or absence) of defects, we can   use Boolean classes in the  Jureczko data ( \texttt{True} if defects \textgreater 0; \texttt{False} if defects = 0).
-For such data, the quality of the predictor can be measured using (1) the  probability of detection (a.k.a.
-``pd'' or recall):  the percent of faulty classes in the test data detected by the {\em predictor}; and (2) the  probability of false alarm (a.k.a.
+For such data, the quality of the predictor can be measured using (a) the  probability of detection (a.k.a.
+``pd'' or recall):  the percent of faulty classes in the test data detected by the {\em predictor}; and (b) the  probability of false alarm (a.k.a.
 ``pf''): the percent of non-fault classes that are {\em predicted} to be defective.
@@
 \input{tex/rq2.tex}
-\subsection{Results}
+\section{Results}
 
@@
 
-\subsubsection{RQ1: Effectiveness}
-
-\begin{lesson}
-In terms of the expected number of defects
-  after refactoring,
-XTREE is marginally better than Alves. CD and Shatnawi.
-on the other hand, usually perform worst.
-\end{lesson}
-
-{\em In a comparison of   outlier and cluster delta
-methods, which one most reduces the expected number
-of defects?}
+\subsection{RQ1: Effectiveness}
+
+{\em Which of the methods defined in Section 3 is the best change oracle for identifying what and howcode modules should be changed? }
 
 \fig{jur} shows the comparison results.  The Alves and Shatnawi
-entries show the net effects of applying (separately) all the disjuncts
-proposed by those methods. In this part of the  analysis,
+entries show the net effects of applying \eq{df} where the $t_i$ values were found by Alves and Shatnawi.
+ In this part of the  analysis,
 we applied Scott-Knott to all the \eq{diff} values
@@
 
-Another interesting feature of the XTREE results of
-\fig{jur} was that the used code metrics vary
-from data set to data set. While changing lines of
-code {\em loc} was important in all data sets, 
-the other code metrics used were often different.
-
- \subsubsection{RQ2: Verbosity}
-
-{\em In a comparison of outlier and cluster delta methods, which one proposes the fewest thresholds?}
+In summary, our {\bf Result1} is  that, of the change orcales studies here,
+XTREE is the best oracle on how to change code modules (in order to reduce defects).
+
+\input{tex/all_changes.tex}
+
+ \subsection{RQ2: Verbosity}
+
+ {\em Which of the Section 3 methods recommended changes to the fewest code attributes?}
 
@@
 
-When combining  \fig{jur} with \fig{counts}, we   see that
+Hence, our {\bf Result2} is that, of all the code change oracles studied here, XTREE recommended far fewest changes to static code measures.
+Note only that,   combining  \fig{jur} with \fig{counts}, we   see that
 even though XTREE proposes changes to far fewer code metrics, those few
@@
 
-\begin{lesson}
-XTREE finds finds far fewer recommended changes to code metrics, and yet performs as good as or better than other methods in recommending changes that results in fewer defects.
-\end{lesson}
-
-\input{tex/all_changes.tex}
-
-\subsubsection{RQ3: Stability of Decision Trees}
-\input{tex/rq3.tex}
-
-\fig{rq3} shows the measure of ambiguity of the leaves of XTREE.
-As proposed by ~\cite{osei04}, this measure is used to determine the discriminatory power of the decision tree.
-Trees with leaf nodes that have low ambiguity with regards to the class variable is more desirable.
-
-To measure the ambiguity we compute the weighted average of the entropy of the leaf nodes. Leaf nodes with lower ambiguity tend to have much lower entropy.
-
-We note that in all cases, the weighted average of entropy is close zero with very low variance. Therefore,
-
-\begin{lesson}
-In terms of stability, XTREE produces trees with consistently low ambiguity. This mitigates the risk of learning from less than optimum tree.
-\end{lesson}
-
-\subsubsection{RQ4: Understanding Co-changes}
-
-{\em In a comparison of outlier and cluster delta
-methods, which one is aware of the existing associations between software metrics?}
-
-In \fig{changes} we identify the magnitude of changes proposed by the plans offered by XTREE.
-At first glance, \fig{changes} seems strange since it 
-shows many metrics need to be {\em increased} in order
-to reduce defects. Note that such increases  to reduce
-defects would never be proposed by the outlier methods
-of Shatnawi or Alves since their core assumption is that bad
-smells arise from unusually large code metrics.
-
-The increases proposed by 
-\fig{changes} arise from the interdependancies between
-code metrics. For example, consider the {\em Poi} results
-from \fig{counts} that recommends decreasing {\em loc}
-but making large increases to {\em cbo} (coupling between
-objects). Here, XTREE is advising us to break up
-large classes class by into services
-in other classes. Note that such a refactoring will, by
-definition, increase the coupling between objects.
-
-Figure ~\ref{fig:multcomp} highlights all possible changes proposed by XTREE, upon close inspection it becomes apparent that XTREE suggests that it is perhaps better to reduce only certain forms of coupling.
+\subsection{RQ3: Stopping}
+
+{\em  How effective is XTREE at offering   “stopping points” (i.e. clear guidance on what not to do)?}
+
+The {\bf RQ2} results showed that XTREE's recommendations are small in a {\em relative sense}; i.e. they are 
+relatively smaller than the other methods studied here.
+Note only that, but XTREE's recommendations are small in an {\em absolute sense}.
+Consider all frequency at which  \fig{counts} values for XTREE that are over 33\%; i.e. in at a third of our  repeated runs, XTREE mentioned
+a code attribute. For Ant, Ivy, Lucene, Jedit, and Poi, those frequencies
+are  \mbox{3, 3, 3, 4, 1, 2} respectively (out of twenty). This means that, usually, XTREE omits references to \mbox{17,17,17,16,19,18} static
+code attributes (out of 20). 
+Any refactoring based on a bad smell detector that uses  these omitted code attributes could hence  be stopped.
+
+Hence our {\bf Result3} is that, in a any  project,  XTREE’s  recommended  changes  only  mentions one to four 
+of the  static code attributes.  Any bad smell defined in terms of the remaining 19 to 16 code attributes (i.e. most of them)
+would hence be deprecated.
+
+\subsection{RQ4: Stability}
+
+{\em Across different projects, how variable are the changes recommended by our best change oracle? }
+
+\fig{counts} counted how {\em often} XTREE's recommendations mentioned a static code attribute.
+\fig{changes}, on the other hand, shows the {\em direction} of the recommended change:
+\bi
+\item Gray bars show  an  {\em increase} to a static code measure;
+\item White bars shows a   {\em drecrease} to a static code measure;
+\item Bars that are all white or all gray indicate that in our 40 repeated runs, XTREE recommended changing an attribute the same way, all the time.
+\item Bars that are mixtures of white and gray mean that, sometimes, XTREE makes different recommendations about how to change a static
+code attribute.
+\ei
+Based on \fig{changes}, we say that {\bf Result4} is: the direction of change recommended  XTREE is  very stable repeated runs of the program  (evidence:
+the bars are mostly the same color).
+
+\subsection{RQ5: Stability}
+
+{\em  Is  it  always  useful  to  apply \eq{df};  i.e.   make  code  better  by  reducing  the  values  of multiple code attributes?
+
+Note that, in \fig{changes}, the bars are colored white and gray; i.e. XTREE recommends {\em decreasing} and {\em increasing} 
+static attribute values. That is, always decreasing static code measures (as suggested by \eq{df}) is {\em not} recommended by XTREE.
+
+To explore this point further, we conducted the following ``what-if'' study. Once XTREE builds its trees with its leaf clusters then:
+\be
+\item For all clusters $C_0$, $C_1$ where the percent of defects in $C_0$ is greater than $C_1$...
+\item For all attribute measures that are have a statistically significantly different distribution  between $C_0$ and $C_1$...
+\item Report the direction of the change.
+\ee
+Note that the changes found in this way are somewhat more general than those found by XTREE since XTREE's recommendations are limited
+to comments on the test set given to the program. The above three points comments on the direction of {\em all possible changes}
+that XTREE could ever report
+
+Figure ~\ref{fig:multcomp} shows the results of this ``what if'' analysis. As in  \fig{changes}, there many increases
+and decreases. Also, only with  cbo, rfc, loc,cam is a change recommended for a majority of the
+data sets  (three of five, or more). 
+XXXX
+
+ups and down. fucntionalty has to go somehwere else
+
+highlights all possible changes proposed by XTREE, upon close inspection it becomes apparent that XTREE suggests that it is perhaps better to reduce only certain forms of coupling.
 Refactoring operations that reduce one form of coupling at the cost of increasing another can sometimes be beneficial.
@@
 \section{Threats to Validity}\label{sect:valid}
+XXXX assumes anything can change
+
+assumes we can get data
+
+assuems that defect is a;l;l.
 

### 2016-08-13 Manuscript.tex
Updates from ShareLaTeX

@@
 of assessing bad smells. We use data mining to generate two oracles: a {\em primary
-change oracle} and a {\em secondary validation oracle}.
+change oracle} and a {\em secondary verification oracle}.
 By combining these two oracles,
@@
 As to 
-the {\em secondary validation oracle}, this  checks if the primary oracle is proposing
+the {\em secondary verification oracle}, this  checks if the primary oracle is proposing
 sensible changes. For this purpose we  use Random Forests\cite{XXX}, augmented with SMOTE (synthetic  minority over-sampling technique~\cite{YYY}).
@@
 the secondary oracle is   a {\em separate} task to learning the primary
-oracle. This  ensures that the validation oracle offers an independent
+oracle. This  ensures that the verification oracle offers an independent
 opinion on the value of the proposed changes.
@@
 since it assumes that the best way to improve code is to decreases multiple code attribute measures below $t_i$ in order
-to remove the ``bad'' smells. This is wrong since 
-there exists an intricate set of associations between static code measures
+to remove the ``bad'' smells. This is wrong.  
+There exists an intricate set of associations between static code measures
 such that {\em decreasing}  $a_i$ necessitates {\em increasing} $a_j$.
@@
 
-  The rest of this paper is structured as follows. First, we offer some background on bad smells. After that,
+\subsection{Structure of this Paper}
+
+This paper  claims that (a)~XTREES is a  better way than \eq{fd}  to define useful changes to software and (b)~those changes are useful for recognizing   superfluous refactorings since usually refer to a very
+small subset of the static code measures (which allows us to rule out refactorings based on any of the omitted
+static code measures). 
+In support of these claims, 
+the rest of this paper is structured as follows. First, we offer some background on bad smells. After that,
   in Section~3, 
@@
 
- {\bf  RQ1: Effectiveness}: According to the validation oracle, which of the methods  defined in Section~3 is the best  change oracle for identifying what and how
+ {\bf  RQ1: Effectiveness}: According to the verification oracle, which of the methods  defined in Section~3 is the best  change oracle for identifying what and how
   code modules should be changed? To answer this question, we used data from five OO Java projects
@@
 \ei
-Consequently, we  recommend that XTREE be used as follows:
+Consequently, we  recommend the following use case for  XTREE:
 \bi
@@
 \ei
-Note that this use case applies to both manual refactorings proposed by developers
-as well as refactoring as conducted by automatic methods~\cite{mkaouer2015many}.
-Note also that
-this recommendation assumes that there is an historical record. If none exists, then the results of this paper could be use used as a guide (see our Table 8).
-
- \subsection{Replication Package}
-
-  In order to support dissemination
-  of research results, and to encourage other researchers to repeat our results,
-  all the code used in this paper is publicly available\footnote{XXX: need a public repo}.
+This use case described  applies to both manual refactorings proposed by developers
+as well as refactoring as conducted by automatic methods~\cite{mkaouer2015many}. That is, XTREE could optimize automatic
+code refactoring by discouraging refactorings for useless goals.
+
+\subsection{ Threats to Validity}
+
+The results of this paper care biased by out choice of refactoring goal (reducing defects) and our choice
+of measures collected from software project (OO measures such as
+  depth of inheritance, number of child classes, etc).
+
+  That said, it should be possible extend the methods of this paper to  other kinds of other kinds of goals (e.g. maintainability, reliability, security,
+  or the knowledge sharing measures favoured by Bosu and Carver~\cite{bosu13}) and other kinds of inputs (e.g. the process measures favored by Rahman, Devanbu et al.\cite{Rahman2013})  as follows:
+  \bi
+  \item Find a data source for the other measures of interest;
+  \item Implement another secondary verification oracle that can assess maintainability, reliability, security, etc;
+\item Implement a better primary verification oracle that can do ``better'' that XTREES at finding changes (where ``better'' is defined in terms 
+of the opinions of the verification oracle).
+\ei
+To assist other researchers exploring these points, we offer a full replication package for this study at  https://github.com/ai-se/XTREE\_IST.
+
+The results of this paper are also specific to the data sets explored here.
+Such sampling bias threatens any data mining experiment; i.e., what matters
+{\em there} may not be true {\em here}. For example, the data sets used here comes from a survey of
+open source JAVA projects from Jureczko et al.~\cite{jureczko10}. Any biases in their selection procedures
+threaten the validity of these results.
+
+That said,
+the best we can do is define our methods and publicize our data and code so that other researchers can
+try to repeat our results and, perhaps, point out a previously unknown bias
+in our analysis. Hopefully, other researchers will emulate our methods in
+order to repeat, refute, or improve our results.
+
+The recommendation to management, shown on page one of this paper,  was to stop developers doing ``X'' if there was
+nothistorical evidence that ``X'' was useful. 
+This recommendation assumes that such an  historical record can be accessed.
+If not,  then the results of this paper could be use used as a guide (see our Table 8).
+Alternatively, some form of transfer learning~\cite{Nam15,Jing15,krishna16} could be used to import data from another project (but more research would be required to test the validity of combing tools like XTREEs with transfer learning).
 
@@
 \item
-no {\em secondary validation oracle}, i.e. no way to check if XTREE's recommended changes were sensible.
+no {\em secondary verification oracle}, i.e. no way to check if XTREE's recommended changes were sensible.
 \ei
 Further, of this entire paper, the only sections containing material
-found in prior papers is 3.2.1, 3.2.2 as well as two-fifths of \fig{}.
-%YYY section1,2, 3.1,4,
-% Prior to XTREE, the authors worked on
-% the CD algorithm discussed in ~\tion{cdcd}. 
-% The goal of CD was the same as WHERE-- find recommendations on how to best change software
-% modules. However, as discussed in~\tion{cdcd},
-% CD worked very different to WHERE. Further, as shown in this paper,
-% CD is significantly out-performed by XTREE.
+found in prior papers is 3.2.1, 3.2.2 as well as two-fifths of the results in \fig{xxx}.
 
@@
 XTREE, will be our recommended {\em primary change oracle}).
-Later in this paper, we will offer  a {\em secondary validation oracle}
+Later in this paper, we will offer  a {\em secondary verification oracle}
 that checks the effectiveness of the changes proposed by XTREE.
@@
 Shatnawi and Alves et al.~\cite{Shatnawi10,Alves2010} depreciate
-using $\mu+\sigma$ since it does not consider the fault-proneness of classes when the thresholds are computed. Also, the method lacks  empirical validation.
+using $\mu+\sigma$ since it does not consider the fault-proneness of classes when the thresholds are computed. Also, the method lacks  empirical verification.
 
@@
 \item Apply those changes. 
-\item Run a {\em secondary validation oracle} to assess the defect-proness of the changed code.
-\item Sort the change oracles on how well they reduce defects (as judged by the validation oracle).
+\item Run a {\em secondary verification oracle} to assess the defect-proness of the changed code.
+\item Sort the change oracles on how well they reduce defects (as judged by the verification oracle).
 \ei
@@
 to 100.  
-Using the secondary validation oracle,  we then predict the
+Using the secondary verification oracle,  we then predict the
 number of defects in $d_+,d_-$ in {\em initial} and {\em new}. We evaluate the performance of XTREE, CD, Shatnawi, and Alves methods in setting bad smell thresholds.
@@
 
-\subsection{Secondary Validation Oracles}
+\subsection{Secondary verification Oracles}
 \label{sect:eval}
@@
 As mentioned in the introduction, our proposed framework has two oracles:
-a primary change oracle (XTREE) and the secondary validation oracle described in this section.
+a primary change oracle (XTREE) and the secondary verification oracle described in this section.
 
@@
 Moghadam~\cite{Moghadam2011} and Mkaouer et al.~\cite{Mkaouer14}
-use a {\em secondary validation oracle} (which is learned separately
+use a {\em secondary verification oracle} (which is learned separately
 to the primary oracle) that   assesses
@@
 \ei
-Based on \fig{changes}, we say that {\bf Result4} is: the direction of change recommended  XTREE is  very stable repeated runs of the program  (evidence:
+Based on \fig{changes}, we say that {\bf Result4} is that the direction of change recommended  XTREE is  very stable repeated runs of the program  (evidence:
 the bars are mostly the same color).
 
+\fig{changes} also comments on the inter-relationships between static code attributes. Note that while some measures in
+\fig{changes} are decreased, many are increased.  
+For example, consider the {\em Poi} results
+from \fig{counts} that recommends decreasing {\em loc}
+but making large increases to {\em cbo} (coupling between
+objects). Here, XTREE is advising us to break up
+large classes class by into services
+in other classes. Note that such a refactoring will, by
+definition, increase the coupling between objects. 
+Note also that such increases  to reduce
+defects would never be proposed by the outlier methods
+of Shatnawi or Alves since their core assumption is that bad
+smells arise from unusually large code metrics.
+
 \subsection{RQ5: Stability}
 
-{\em  Is  it  always  useful  to  apply \eq{df};  i.e.   make  code  better  by  reducing  the  values  of multiple code attributes?
-
-Note that, in \fig{changes}, the bars are colored white and gray; i.e. XTREE recommends {\em decreasing} and {\em increasing} 
+{\em  Is  it  always  useful  to  apply \eq{df};  i.e.   make  code  better  by  reducing  the  values  of multiple code attributes?}
+
+In  \fig{changes}, the bars are colored both white and gray; i.e. XTREE recommends {\em decreasing} and {\em increasing} 
 static attribute values. That is, always decreasing static code measures (as suggested by \eq{df}) is {\em not} recommended by XTREE.
@@
 \ee
-Note that the changes found in this way are somewhat more general than those found by XTREE since XTREE's recommendations are limited
+Note that the changes found in this way are somewhat more general than the above results
+since they were  limited
 to comments on the test set given to the program. The above three points comments on the direction of {\em all possible changes}
@@
 
-Figure ~\ref{fig:multcomp} shows the results of this ``what if'' analysis. As in  \fig{changes}, there many increases
-and decreases. Also, only with  cbo, rfc, loc,cam is a change recommended for a majority of the
-data sets  (three of five, or more). 
-XXXX
-
-ups and down. fucntionalty has to go somehwere else
-
-highlights all possible changes proposed by XTREE, upon close inspection it becomes apparent that XTREE suggests that it is perhaps better to reduce only certain forms of coupling.
+Figure ~\ref{fig:multcomp} shows the results of this ``what if'' analysis. As might be expected, the recommendation is to
+always reduce lines of code (loc). But for the other attributes, there are many recommendations to increase those values.
+Hence, {\bf Result5} is that while XTREE always  recommends reducing loc,
+it also   often recommends increasing the values of other static code attributes.
+
+% of ``better'' deefined as per \eq{fd} is misleading.
+
+% Also, most attributes are not changed in most data sets.
+% Only our attributes (cbo, rfc, loc,cam) change in a majority of data sets  (three of five, or more).
+
+% XXXX
+
+% ups and down. fucntionalty has to go somehwere else
+
+% highlights all possible changes proposed by XTREE, upon close inspection it becomes apparent that XTREE suggests that it is perhaps better to reduce only certain forms of coupling.
 Refactoring operations that reduce one form of coupling at the cost of increasing another can sometimes be beneficial.
@@
 
-Note that we prefer XTREE to Shatnawi and the Alves
-method since those other methods
-do not reason
-2about decreases {\em and} increases of multiple 
-code metrics, at the same time.
-
-As a final comment, we note
-that  \fig{changes} enables us to explain the uniformity
-of the results seen with Jedit in \fig{jur}.
-Observe how in \fig{changes} the only change ever
-found is a reduction to {\em rfc}. Clearly, in this
-data set, there is very little that can be usefully changed.
-
-\fig{multcomp} shows the frequency with which the methods
-recommend changes to specific code methods.
-Note that XTREE proposes thresholds to
-few code metrics compared to the other approaches.
-
-When combining  \fig{jur}, \fig{counts}, and \fig{multcomp}, we   see that
-even though XTREE proposes changes to far fewer code metrics, those few
-code metrics are usually just as effective (or
-more effective) than the multiple
-thresholds
-proposed by CD, Shatnawi or Alves.  That is, XTREE proposes
-{\em fewer} and better thresholds than the other approaches studied here.
-
-\begin{lesson}
-In addition to recommending useful changes, XTREE recommends changes to all co-varying software metrics.
-\end{lesson}
-
-\section{Threats to Validity}\label{sect:valid}
-XXXX assumes anything can change
-
-assumes we can get data
-
-assuems that defect is a;l;l.
-
-Before  that, we offer one following note on a
-core assumption of XTREE.
-XTREE   is focused on Fowler's bad smells
-as contributors to software defects. Some researchers 
- suggest that discussing bad smells is useful for more just reducing defects. For example, Bosu and Carver~\cite{bosu13} report that
-debates about code smells and refactorings can (a)~introduce new comers to the code base or (b)~share knowledge on a team
-about interactions within the code. In that view, 
-the concept of refactoring can be useful
-even if it does not address issues of defects.
-
-As with any empirical study, several issues can affect the final results. Therefore, any
-conclusions made from this work must be offered with the following
-caveats.
-
-\subsection{External Validity}
-Based on the experimental results above,
-as well as the discussion in \tion{prelim},
-we believe that bad smell indicators (e.g. \mbox{{\em loc}$>$ 100})
-have limited external validity beyond the projects from which they are derived. 
-While specific models are externally valid,
-there may still be general methods like XTREE for finding the good local models.
-
-Our definition of bad smells is limited to those represented by OO code metrics (a premise often used in related work).   
-XTREE, Shatnawi, Alves et al. can  only comment
-on bad smells   expressed as code metrics 
-  in the historical log of a project.
-
-If developers want to justify their refactorings
-via bad smells expressed in other terminology,
-then the  analysis of this paper must:
-\begin{itemize}
-    \item Either wait till 
-data about those new
-terms has been collected. 
-\item Or, apply cutting edge transfer learning
-methods~\cite{Nam15,Jing15} to map data from other projects
-into the current one.
-\end{itemize}
-Note that the transfer learning approach would
-be highly experimental and require more study
-before it can be safely recommended.
-
-Sampling bias threatens any data mining experiment; i.e., what matters
-there may not be true here. For example, the data sets used here comes from Jureczko et al. and any biases in their selection procedures
-threaten the validity of these results. 
-That said,
-the best we can do is define our methods and publicize our data and code so that other researchers can
-try to repeat our results and, perhaps, point out a previously unknown bias
-in our analysis. Hopefully, other researchers will emulate our methods in
-order to repeat, refute, or improve our results.
-
-% Data mining is a large and active field and any single study can only use a small subset of the known classification algorithms.  
-% That said, we have taken care to document in this paper the decisions made by engineering
-% judgement that could effect our conclusions.
+% Note that we prefer XTREE to Shatnawi and the Alves
+% method since those other methods
+% do not reason
+% 2about decreases {\em and} increases of multiple 
+% code metrics, at the same time.
+
+% As a final comment, we note
+% that  \fig{changes} enables us to explain the uniformity
+% of the results seen with Jedit in \fig{jur}.
+% Observe how in \fig{changes} the only change ever
+% found is a reduction to {\em rfc}. Clearly, in this
+% data set, there is very little that can be usefully changed.
+
+% \fig{multcomp} shows the frequency with which the methods
+% recommend changes to specific code methods.
+% Note that XTREE proposes thresholds to
+% few code metrics compared to the other approaches.
+
+% When combining  \fig{jur}, \fig{counts}, and \fig{multcomp}, we   see that
+% even though XTREE proposes changes to far fewer code metrics, those few
+% code metrics are usually just as effective (or
+% more effective) than the multiple
+% thresholds
+% proposed by CD, Shatnawi or Alves.  That is, XTREE proposes
+% {\em fewer} and better thresholds than the other approaches studied here.
+
+% \begin{lesson}
+% In addition to recommending useful changes, XTREE recommends changes to all co-varying software metrics.
+% \end{lesson}
+
+% \section{Threats to Validity}\label{sect:valid}
+% XXXX assumes anything can change
+
+% assumes we can get data
+
+% assuems that defect is a;l;l.
+
+% Before  that, we offer one following note on a
+% core assumption of XTREE.
+% XTREE   is focused on Fowler's bad smells
+% as contributors to software defects. Some researchers 
+%  suggest that discussing bad smells is useful for more just reducing defects. For example, Bosu and Carver~\cite{bosu13} report that
+% debates about code smells and refactorings can (a)~introduce new comers to the code base or (b)~share knowledge on a team
+% about interactions within the code. In that view, 
+% the concept of refactoring can be useful
+% even if it does not address issues of defects.
+
+% As with any empirical study, several issues can affect the final results. Therefore, any
+% conclusions made from this work must be offered with the following
+% caveats.
+
+% \subsection{External Validity}
+% Based on the experimental results above,
+% as well as the discussion in \tion{prelim},
+% we believe that bad smell indicators (e.g. \mbox{{\em loc}$>$ 100})
+% have limited external validity beyond the projects from which they are derived. 
+% While specific models are externally valid,
+% there may still be general methods like XTREE for finding the good local models.
+
+% Our definition of bad smells is limited to those represented by OO code metrics (a premise often used in related work).   
+% XTREE, Shatnawi, Alves et al. can  only comment
+% on bad smells   expressed as code metrics 
+%   in the historical log of a project.
+
+% If developers want to justify their refactorings
+% via bad smells expressed in other terminology,
+% then the  analysis of this paper must:
+% \begin{itemize}
+%     \item Either wait till 
+% data about those new
+% terms has been collected. 
+% \item Or, apply cutting edge transfer learning
+% methods~\cite{Nam15,Jing15} to map data from other projects
+% into the current one.
+% \end{itemize}
+% Note that the transfer learning approach would
+% be highly experimental and require more study
+% before it can be safely recommended.
+
+% Sampling bias threatens any data mining experiment; i.e., what matters
+% there may not be true here. For example, the data sets used here comes from Jureczko et al. and any biases in their selection procedures
+% threaten the validity of these results. 
+% That said,
+% the best we can do is define our methods and publicize our data and code so that other researchers can
+% try to repeat our results and, perhaps, point out a previously unknown bias
+% in our analysis. Hopefully, other researchers will emulate our methods in
+% order to repeat, refute, or improve our results.
+
+% % Data mining is a large and active field and any single study can only use a small subset of the known classification algorithms.  
+% % That said, we have taken care to document in this paper the decisions made by engineering
+% % judgement that could effect our conclusions.
 
@@
 
-\subsection{  Internal Validity}\label{sect:coc}
-
-% The main internal validity threat   in this study was the use of
-% optimistic reasoning when generating the changed code modules.
-We assumed in \tion{rq}
-that any code module can be changed in order
-to stop triggering a bad smell detector. This is not necessarily
-true, as noted in {\em PROBLEM \#2} in this paper's introduction.
-To mitigate this issue:
-\begin{itemize}
-    \item We do not propose using XTREE as a bad
-smell generator;
-\item Rather, we offer it as  a critique agent for bad smells
-proposed by some other oracle (e.g. a human developer).
-\end{itemize}
-We showed about that XTREE's recommendations are not verbose.
-That is, even if XTREE recommends the superset of possibly important bad smells,
-that superset is not so large as to  overlap with many
- bad smell proposed at random 
-by   developers.
-
-XTREE does not require a working defect predictor to generate
-its bad smell thresholds. However, to {\em certify}
-that those thresholds are satisfactory, some
-second quality predictor must be applied.
+% \subsection{  Internal Validity}\label{sect:coc}
+
+% % The main internal validity threat   in this study was the use of
+% % optimistic reasoning when generating the changed code modules.
+% We assumed in \tion{rq}
+% that any code module can be changed in order
+% to stop triggering a bad smell detector. This is not necessarily
+% true, as noted in {\em PROBLEM \#2} in this paper's introduction.
+% To mitigate this issue:
+% \begin{itemize}
+%     \item We do not propose using XTREE as a bad
+% smell generator;
+% \item Rather, we offer it as  a critique agent for bad smells
+% proposed by some other oracle (e.g. a human developer).
+% \end{itemize}
+% We showed about that XTREE's recommendations are not verbose.
+% That is, even if XTREE recommends the superset of possibly important bad smells,
+% that superset is not so large as to  overlap with many
+%  bad smell proposed at random 
+% by   developers.
+
+% XTREE does not require a working defect predictor to generate
+% its bad smell thresholds. However, to {\em certify}
+% that those thresholds are satisfactory, some
+% second quality predictor must be applied.
 A data set containing defect counts before and after refactoring activities would enable an accurate assessment of the performance of the threshold-setting and recommender methods, however, such a data set is not available at this time.
 
- Historically,
-SE researchers~\cite{Cheng10,OKeeffe08,OKeeffe07,Moghadam2011,Mkaouer14} have used the QMOOD hierarchical quality model~\cite{Bansiya02}.
-Since such quality models may be very project specific~\cite{localvsglobal}, we prefer building local 
-defect predictors using Random Forests. We chose this approach,  based on its reputation for having the better  performance of 21 other learners for defect prediction~\cite{lessmann}.  
-Our results show that when a defect log contains too few
-non-defective examples then defector predictors
-perform poorly (see the data sets in the last few lines of \fig{j})
-as do their associated bad smell threshold generators
-(recall the performance of Lucene and Poi in~\fig{jur}). It should be noted that this is not a limitation of XTREE-- rather
-it seems fundamental to the problem of certifying bad smells.
-As evidence of this, recall that {\em all} the bad smell threshold generators of~\fig{jur}
-had issues with the defect data sets with  many defects
-(Lucene and Poi).
-
-% \subsection{ Learner Bias}
-% This study used two kinds of learners: (1) methods for suggesting
-% changes to code like Shatnawi, Alves et al., CD and XTREE;
-% (2) methods for assessing the changes proposed by these learners.
-% Prior studies implemented (2) using  the QMOOD hierarchical quality model
-% which is so old, that we suspect it may no longer be current. Hence,
-% we used Random Forests to build the assessment oracles that were specific
-% to the data sets used in this study. We chose this approach,  based on its reputation for having the better  performance of 21 other learners for defect prediction~\cite{lessmann}.
-
-% \subsection{  Sampling bias} 
-% Sampling bias threatens any data mining experiment; i.e., what matters
-% there may not be true here. For example, the data sets used here comes from two  Jureczko et al. and any biases in their selection procedures
-% threaten the validity of these results. 
-% That said,
-% the best we can do is define our methods and publicize our data and code so that other researchers can
-% try to repeat our results and, perhaps, point out a previously unknown bias
-% in our analysis. Hopefully, other researchers will emulate our methods in
-% order to repeat, refute, or improve our results.
+%  Historically,
+% SE researchers~\cite{Cheng10,OKeeffe08,OKeeffe07,Moghadam2011,Mkaouer14} have used the QMOOD hierarchical quality model~\cite{Bansiya02}.
+% Since such quality models may be very project specific~\cite{localvsglobal}, we prefer building local 
+% defect predictors using Random Forests. We chose this approach,  based on its reputation for having the better  performance of 21 other learners for defect prediction~\cite{lessmann}.  
+% Our results show that when a defect log contains too few
+% non-defective examples then defector predictors
+% perform poorly (see the data sets in the last few lines of \fig{j})
+% as do their associated bad smell threshold generators
+% (recall the performance of Lucene and Poi in~\fig{jur}). It should be noted that this is not a limitation of XTREE-- rather
+% it seems fundamental to the problem of certifying bad smells.
+% As evidence of this, recall that {\em all} the bad smell threshold generators of~\fig{jur}
+% had issues with the defect data sets with  many defects
+% (Lucene and Poi).
+
+% % \subsection{ Learner Bias}
+% % This study used two kinds of learners: (1) methods for suggesting
+% % changes to code like Shatnawi, Alves et al., CD and XTREE;
+% % (2) methods for assessing the changes proposed by these learners.
+% % Prior studies implemented (2) using  the QMOOD hierarchical quality model
+% % which is so old, that we suspect it may no longer be current. Hence,
+% % we used Random Forests to build the assessment oracles that were specific
+% % to the data sets used in this study. We chose this approach,  based on its reputation for having the better  performance of 21 other learners for defect prediction~\cite{lessmann}.
+
+% % \subsection{  Sampling bias} 
+% % Sampling bias threatens any data mining experiment; i.e., what matters
+% % there may not be true here. For example, the data sets used here comes from two  Jureczko et al. and any biases in their selection procedures
+% % threaten the validity of these results. 
+% % That said,
+% % the best we can do is define our methods and publicize our data and code so that other researchers can
+% % try to repeat our results and, perhaps, point out a previously unknown bias
+% % in our analysis. Hopefully, other researchers will emulate our methods in
+% % order to repeat, refute, or improve our results.
 
@@
 \section{Conclusions}
-Which  bad smells can  be ignored? 
+How to stop useless refactorings?
 We say: ignore those not supported by the historical log of data from
 the current project.  
-
 When that data is not available (e.g. early
@@
 
+For our better guess at how to reduce defects by changing code attributes,
+  see  Figure ~\ref{fig:multcomp}. But given the large variance if the change recommendations, we strongly advice teams to use
+  XTREE on their data to find their own best local changes.
+
 XTREE improves on prior methods for generating bad smells:
@@
     from   current project data.
-    \item As described in in \tion{bst}, 
-    XTREE generates conjunctions of code metric thresholds
-    that need to be satisfied at the same time.
-    Older methods, such as those proposed by  Shatnawi and Alves
-    offer only disjunctions that might be inappropriately applied
-    to yield impossible refactorings (e.g. reducing lines of code
-    and coupling at the same time).
 
     \item XTREE's conjunctions proved to be arguably as effective
-    as those of Alves (see \fig{jur}) but far less verbose (see \fig{counts}) thus making XTREE a better tool for critiquing and rejecting
-    more bad smells proposed by developers.
+    as those of Alves (see \fig{jur}) but far less verbose (see \fig{counts}). Since XTREE {\em approves} of fewer changes
+    it hence {\em disapproves} of most changes. This makes it a better tool for critiquing and rejecting
+    many of the refactorings.
 \end{itemize}
-In summary, this paper offers a baseline result
-that XTREE can be used as a {\em diagnostic tool}
-for identifying which bad smells can be ignored.
-But can it be used as a {\em prescriptive tool}
-to recommend new refactorings?
-
-As discussed in {\em PROBLEM \#2}
-(from the introduction), XTREE might propose
-changes to code metrics that are
-not feasible  (due to the local domain constraints
-of the code). To repair this, XTREE needs to be extended
-with architectural knowledge of the code it is studying.
-Elsewhere, we have had some   success
-with reasoning about such architectural knowledge
-(expressed as software product lines~\cite{sayyad13a,sayyad13b}). In future
-work, we will explore extending XTREE 
-with  
-architectural knowledge such that it can
-become a tool which perscribes
-feasible refactorings.
+Finally, XTREE does not suffer from the conjunctive fallacy.
+    Older methods, such as those proposed by  Shatnawi and Alves assumed
+    that the best way to improve code is to remove outlier  values. This may not work since when code is refactored,
+    {\em the functionality has to go somewhere}. Hence,  reducing the lines of code in one module necessitates   
+    {\em increasing} the coupling that module
+    to other parts of the code. In future, we recommend software team use bad smell detectors that know what attribute measures
+    need {\em decreasing} as well as {\em increasing}.
+
+% In summary, this paper offers a baseline result
+% that XTREE can be used as a {\em diagnostic tool}
+% for identifying which bad smells can be ignored.
+% Can it be used as a {\em prescriptive tool}
+% to recommend new refactorings? This would require
+
+% As discussed in {\em PROBLEM \#2}
+% (from the introduction), XTREE might propose
+% changes to code metrics that are
+% not feasible  (due to the local domain constraints
+% of the code). To repair this, XTREE needs to be extended
+% with architectural knowledge of the code it is studying.
+% Elsewhere, we have had some   success
+% with reasoning about such architectural knowledge
+% (expressed as software product lines~\cite{sayyad13a,sayyad13b}). In future
+% work, we will explore extending XTREE 
+% with  
+% architectural knowledge such that it can
+% become a tool which perscribes
+% feasible refactorings.
 

### 2016-08-14 Manuscript.tex
Updates from ShareLaTeX

@@
 \definecolor{Gray}{gray}{0.85}
-\usepackage[svgnames]{xcolor}
+% \usepackage[svgnames]{xcolor}
 \usepackage[framed]{ntheorem}
@@
 \textsuperscript{b}Fraunhofer CESE, College Park, USA}
-\pagestyle{arabic}
+\pagenumbering{arabic}
 
@@
 
-\noindent
-%%``Managing people is like herding cats'', says management consultant Watler
-%Bennis~\cite{bennis97}. Nowhere is this more true than when managing programmers. 
-%Programmers can be very intelligent, but very opinionated people whose
-%social position within software organizations relies, in part,
-%of perceived notions of technical excellence. Hence, it can
-%be hard for managers to suggest to programmers that are
-%wrong about how they are prioritizing their development effort.
-
-%Consider, for example, the activity of refactoring code based on bad smells.
 According to   Fowler ~\cite{fowler99}, bad smells (a.k.a. code smells)
@@
 the {\em secondary verification oracle}, this  checks if the primary oracle is proposing
-sensible changes. For this purpose we  use Random Forests\cite{XXX}, augmented with SMOTE (synthetic  minority over-sampling technique~\cite{YYY}).
+sensible changes. For this purpose we use Random Forests\cite{breiman2001random}, augmented with SMOTE (synthetic  minority over-sampling technique~\cite{chawla2002smote}).
  In our framework,  learning
@@
 Further, of this entire paper, the only sections containing material
-found in prior papers is 3.2.1, 3.2.2 as well as two-fifths of the results in \fig{xxx}.
+found in prior papers is 3.2.1, 3.2.2 as well as two-fifths of the results in \fig{jur}.
 

### 2016-08-18 Manuscript.tex
Updates from ShareLaTeX

@@
 
-\title{How to Stop Useless Refactorings}
+\title{How to Discourage Useless Refactorings}
 
@@
 {\bf Context: } 
-Developers use code bad smells to gudie their refactoring (reorganizing their code).
+Developers use code bad smells to guide their refactoring (reorganizing their code).
 Yet developers, text books, and tools disagree on which bad smells are important.
@@
 \noindent 
-{\bf Objective: } We seek to a tool that can recognize  useless refactorings.
+{\bf Objective: } We seek to introduce a tool that can recognize  useless refactorings.
 
@@
 (since there is no
-historical evidence that that bad smell causes any problems).
+historical evidence that the bad smell causes any problems).
 
@@
 \item
-But rather to stop {\em unnecessary} refactorings.
+But rather to discourage {\em unnecessary} refactorings.
 \ei
@@
 \item If there is no evidence in the historical record that changing ``X'' is useful;
-\item Then stop developers from doing ``X''.
+\item Then discourage developers from doing ``X''.
 \ei
@@
 In this paper, we use 
-the XTREE cluster delta algorithm as the {\em primary change  oracle} .
+the XTREE cluster delta algorithm as the {\em primary change  oracle}.
 XTREE 
@@
 It then proposes a ``minimal'' set of changes $\Delta$ that can move a software module $M$ from a defective cluster $C_0$ to another with fewer defects$C_1$ (so $\Delta$
-is some subset of $C_1 - C_0$). To define ``minimal'', XTREE uses an entropy measure.
+is some subset of $C_1 - C_0$). % To define ``minimal'', XTREE uses an entropy measure.
 
@@
 the {\em secondary verification oracle}, this  checks if the primary oracle is proposing
-sensible changes. For this purpose we use Random Forests\cite{breiman2001random}, augmented with SMOTE (synthetic  minority over-sampling technique~\cite{chawla2002smote}).
+sensible changes. For this purpose we use Random Forest\cite{breiman2001random}, augmented with SMOTE (synthetic  minority over-sampling technique~\cite{chawla2002smote}).
  In our framework,  learning
-the secondary oracle is   a {\em separate} task to learning the primary
+the secondary oracle is   a {\em separate} task from that of learning the primary
 oracle. This  ensures that the verification oracle offers an independent
@@
 
-This paper  claims that (a)~XTREES is a  better way than \eq{fd}  to define useful changes to software and (b)~those changes are useful for recognizing   superfluous refactorings since usually refer to a very
+This paper  claims that (a)~XTREES is a  better way than \eq{df}  to define useful changes to software and (b)~those changes are useful for recognizing   superfluous refactorings since they usually refer to a very
 small subset of the static code measures (which allows us to rule out refactorings based on any of the omitted
@@
   in Section~3, 
-  different methods for determining when code does/does not have bad smell. One of those methods
+  different methods are presented for determining when code does/does not have bad smell. One of those methods
   will be XTREE while the others will come from other researchers. Next,    Section~4
@@
  {\bf RQ2: Succinctness}: Our goal is to critique and, possibly,
-ignore irrelevant bad smell detectors.  If those changes are minimal (i.e. effect fewest attributes) then those changes
+ignore irrelevant bad smell detectors.  If those changes are minimal (i.e. affect fewest attributes) then those changes
 will be easiest to apply and monitor. Hence, we ask, which of the Section~3 methods recommended changes to the fewest
@@
 
- {\bf RQ3: Stopping}: Our advice to managers is to stop refactoring based on changes that lack
+ {\bf RQ3: Stopping}: Our advice to managers is to discourage refactoring based on changes that lack
 historical evidence of being effective. How effective is XTREE at offering such ``stopping points'' (i.e. clear guidance on what {\em not} to do)??
 \begin{lesson}
-In  any  project,  XTREE’s  recommended  changes  only  mentions one to four 
+In  any  project,  XTREE's  recommended  changes  only  mentions one to four 
 of the  static code attributes.  Any bad smell defined in terms of the remaining 19 to 16 code attributes (i.e. most of them)
@@
 \item Before doing  refactoring based on a bad smell report...
-\item ...check and stop any refactoring   for which there is no proof
-  in the historical record that that change improves the code.
+\item ...check and discourage any refactoring   for which there is no proof
+  in the historical record that the change improves the code.
 \ei
 This use case described  applies to both manual refactorings proposed by developers
-as well as refactoring as conducted by automatic methods~\cite{mkaouer2015many}. That is, XTREE could optimize automatic
+as well as refactoring conducted by automatic methods~\cite{mkaouer2015many}. That is, XTREE could optimize automatic
 code refactoring by discouraging refactorings for useless goals.
@@
 
-The results of this paper care biased by out choice of refactoring goal (reducing defects) and our choice
+The results of this paper are biased by out choice of refactoring goal (reducing defects) and our choice
 of measures collected from software project (OO measures such as
@@
 
-  That said, it should be possible extend the methods of this paper to  other kinds of other kinds of goals (e.g. maintainability, reliability, security,
+  That said, it should be possible extend the methods of this paper to other kinds of goals (e.g. maintainability, reliability, security,
   or the knowledge sharing measures favoured by Bosu and Carver~\cite{bosu13}) and other kinds of inputs (e.g. the process measures favored by Rahman, Devanbu et al.\cite{Rahman2013})  as follows:
@@
   \item Implement another secondary verification oracle that can assess maintainability, reliability, security, etc;
-\item Implement a better primary verification oracle that can do ``better'' that XTREES at finding changes (where ``better'' is defined in terms 
+\item Implement a better primary verification oracle that can do ``better'' that XTREE at finding changes (where ``better'' is defined in terms 
 of the opinions of the verification oracle).
@@
 
-The recommendation to management, shown on page one of this paper,  was to stop developers doing ``X'' if there was
-nothistorical evidence that ``X'' was useful. 
+The recommendation to management, shown on page one of this paper,  was to discourage developers doing ``X'' if there was no historical evidence that ``X'' was useful. 
 This recommendation assumes that such an  historical record can be accessed.
@@
   \subsection{Relationship to Prior Work }
-A four page prelininary report on the XTREE system~\cite{krishna2015actionable} has been presented previously\footnote{https://goo.gl/2In3Lr}. That short report offered case studies only two  of
+A four page preliminary report on the XTREE system~\cite{krishna2015actionable} has been presented previously\footnote{https://goo.gl/2In3Lr}. That short report offered case studies on only two  of
 the five data sets studied here. Also, that prior work had:
@@
 in column one. 
-The {\em developer survey}   (in the right-hand-side column),
-  this shows the results of an hour-long whiteboard sessions with a group of 12 developers from a Washington
+The {\em developer survey} (in the right-hand-side column) shows the results of an hour-long whiteboard sessions with a group of 12 developers from a Washington
     D.C. web tools development company. Participants
@@
 indicates where   other work has chosen to ignore
-one the   bad smells in column one. 
+one of the bad smells in column one. 
 Note that most of the cells are blank, and that the studies ignore the majority of the Fowler bad smells.
@@
 
-The SE literature offers  two ways to 
-learning bad smell thresholds.
+The SE literature offers two ways of learning bad smell thresholds.
 One approach relies on 
@@
 Hence, they generate one bad smell threshold for any metric
-with such an ``unusually large'' measurements. 
+with such an ``unusually large'' measurement. 
 The literature lists several ways to define ``unusually large''.
+
+\input{xtree_tut.tex}
 
@@
 Given classes described with the  code metrics of \fig{ck},
-Enri and Lewerentzz~\cite{erni96} found the   mean $\mu$ and the standard deviation $\sigma$
+Enri and Lewerentz~\cite{erni96} found the   mean $\mu$ and the standard deviation $\sigma$
 of each
@@
 
-\begin{figure*}[!t]
-~\hrule~
-\begin{minipage}{.53\linewidth}
-\small
- \begin{tabular}{p{0.95\linewidth}} 
- On the right-hand-side is a tree
- generated by iterative dichomization. 
- This tree can be read like a nested if-then-else statement; e.g.
- \begin{itemize}
-     \item Lines 3 and 8 show two branches for lines of code (denoted here as {\em `\$loc}) below 698 and above 698.
-     \item Any line with a colon ":" character shows  a  leaf  of  this  nesting.
-For  example,  if  some  new  code module is passed down this tree and falls to the line marked in \textcolor{orange}{{\bf orange}},  the colon on that line indicates a prediction that this module has a 100\% chance of being defective.
-     \end{itemize}
-Using this tree,
- XTREE looks for a nearby branch that has a lower chance of being defective.
-Finding the \textcolor{green}{{ green}} desired  branch,  XTREE reports a bad smell threshold for that module that is the delta between the \textcolor{orange}{{\bf orange}}  current branch  and   \textcolor{green}{{ green}} designed branch.
- In this case, that threshold relates to:
- \begin{itemize}
-     \item Lines of code and comments ({\em lcom}) 
-     \item The cohesion between classes ({\em cam}) which measures similarity of parameter lists to assess the relatedness amongst class   methods.
-     \end{itemize}\\ 
- \end{tabular}
- \end{minipage}~~~~
- \begin{minipage}{.45\linewidth}
-\includegraphics[width=\linewidth]{figs/XTREE_samp.png}
-\end{minipage}
-~\hrule~
- \caption{A brief tutorial on XTREE.} \label{fig:xtree_samp}
-\end{figure*}
-
 \subsubsection{Discussion of Outlier Methods}\label{sect:disc}
@@
 metrics need to be changed at the same time (or whether or not those
-changes need to minimizations or maximations of static code measures).
+changes lead to minimization or maximization of static code measures).
 
@@
 
-Hence our {\bf Result3} is that, in a any  project,  XTREE’s  recommended  changes  only  mentions one to four 
+Hence our {\bf Result3} is that, in a any  project,  XTREE's  recommended  changes  only  mentions one to four 
 of the  static code attributes.  Any bad smell defined in terms of the remaining 19 to 16 code attributes (i.e. most of them)
@@
 
-% of ``better'' deefined as per \eq{fd} is misleading.
+% of ``better'' deefined as per \eq{df} is misleading.
 
@@
 % that any code module can be changed in order
-% to stop triggering a bad smell detector. This is not necessarily
+% to discourage triggering a bad smell detector. This is not necessarily
 % true, as noted in {\em PROBLEM \#2} in this paper's introduction.
@@
 \section{Conclusions}
-How to stop useless refactorings?
+How to discourage useless refactorings?
 We say: ignore those not supported by the historical log of data from

### 2016-08-18 xtree_tut.tex
Updates from ShareLaTeX

\begin{figure*}[t!]
~\hrule~
\begin{minipage}{.53\linewidth}
\small
 \begin{tabular}{p{0.95\linewidth}} 
 On the right-hand-side is a tree
 generated by iterative dichomization. 
 This tree can be read like a nested if-then-else statement; e.g.
 \begin{itemize}
     \item Lines 3 and 8 show two branches for lines of code (denoted here as {\em `\$loc}) below 698 and above 698.
     \item Any line with a colon ":" character shows  a  leaf  of  this  nesting.   For  example,  if  some  new  code module is passed down this tree and falls to the line marked in \textcolor{orange}{{\bf orange}},  the colon on that line indicates a prediction that this module has a 100\% chance of being defective. 
     \end{itemize}
Using this tree,
 XTREE looks for a nearby branch that has a lower chance of being defective. Finding the \textcolor{green}{{ green}} desired  branch,  XTREE reports a bad smell threshold for that module that is the delta between the \textcolor{orange}{{\bf orange}}  current branch  and   \textcolor{green}{{ green}} designed branch. 
 In this case, that threshold relates to:
 \begin{itemize}
     \item Lines of code and comments ({\em lcom}) 
     \item The cohesion between classes ({\em cam}) which measures similarity of parameter lists to assess the relatedness amongst class   methods.
     \end{itemize}\\ 
 \end{tabular}
 \end{minipage}~~~~
 \begin{minipage}{.45\linewidth}
\includegraphics[width=\linewidth]{figs/XTREE_samp.png}
\end{minipage}
~\hrule~
 \caption{A brief tutorial on XTREE.} \label{fig:xtree_samp}
\end{figure*}

### 2016-08-22 Manuscript.tex
Updates from ShareLaTeX

@@
 
-\title{How to Discourage Useless Refactorings}
+% \title{How to Discourage Useless Refactorings}
+\title{Toward Intelligent Refactoring Recommendations}
 
@@
 {\bf Context: } 
-Developers use code bad smells to guide their refactoring (reorganizing their code).
-Yet developers, text books, and tools disagree on which bad smells are important.
+Developers use bad code smells to guide refactoring.
+Yet developers, text books, tools, and researchers disagree on which bad smells are important.
 %Many bad smell detectors recommend refactoring when static code measure
@@
 \noindent 
-{\bf Objective: } We seek to introduce a tool that can recognize  useless refactorings.
+{\bf Objective:} To evaluate the likelihood that a refactoring to address bad code smells will yield improvement in the defect-proneness of the code.
 
 \noindent
-{\bf Method: } We introduce XTREE, a tool which, given a historical log of defects seen previously in the code, generates
-a set of useful code changes.
-Any bad smell that requires changes outside of that set can be deprioritized 
-(since there is no
-historical evidence that the bad smell causes any problems).
+{\bf Method: } We introduce XTREE, a tool that analyzes a historical log of defects seen previously in the code and generates a set of useful\footnote{Need to define useful in precise terms} code changes.
+Any bad smell that requires changes outside of that set can be deprioritized (since there is no historical evidence that the bad smell causes any problems).
 
@@
 Before undertaking a refactoring based on a bad smell report,
-use a tool like XTREE to check and ignore any refactoring   that  are useless; i.e. which lacks evidence
+use a tool like XTREE to check and ignore any refactorings   that  are useless; i.e. which lacks evidence
   in the historical record  that it is useful to make that change.
@@
 \end{quote}
-Bad smells are a widely used technique for evaluating code. As of  early 2016, ACM Digital Library reports 
-the Fowler text of {\em Refactoring} has 6434 references~\cite{fowler99}. A search  on {\em ``bad smell''programming} 
-where {\em proceedings=ICSE} finds 1,748 papers since 2006.
-Hence it is important to understand the value of
-this popular topic.  
-Valuable development resources may be wasted on bad smells that are ``bad''; i.e. 
- irrelevant or misleading
-for some particular project.
-
-In our experience, programmers can use the SE literature to justify extensive, perhaps even excessive, refactoring efforts.
-For example, this paper began when a Washington-based software company shared
-one of their management challenges with us: their  releases are delayed by developers spending  much time removing bad smells within their code.
+
+Bad smells are a widely used technique for evaluating code.
+While the original bad small concept was largely subjective [REF], researchers including Marinescu [REF] and others has provided formal definitions of ``bad smells'' in terms of static code attributes such size, complexity, coupling, and other metrics.
+Consequently, code smells are captured by popular static analysis tools such as PMD [REF], CheckStyle [REF], FindBugs [REF], and SonarQube [REF], although not always explicitly labeled as such.
+
+Refactoring bad smells from code is generally accepted as a recommended practice, but refactoring by definition does not change the external functionality of the system and thus may have no perceived value.
+For example, this paper began when a Washington-based software company shared one of their management challenges with us: their  releases are delayed by developers spending  much time removing bad smells within their code.
+%This management team wanted some way to check if all that activity was useful. 
+Kim et al.\cite{kim2012field} surveyed developers at Microsoft and found that refactoring incurs significant cost and risks.
+A Google search on the terms ``refactoring cost'' yields numerous threads on StackOverlfow from developers asking how to justify refactoring and when the costs of refactoring outweight its benefits.
+
+% As of  early 2016, the ACM Digital Library reports 
+% the Fowler text of {\em Refactoring} has 6434 references~\cite{fowler99}. A search  on \texttt{``bad smell'' programming 
+% where proceedings=ICSE} in the ACM Digital Library finds 1,748 papers since 2006.
+% Hence it is important to understand the value of
+% this popular topic.  
+% Valuable development resources may be wasted on bad smells that are ``bad''; i.e. 
+%  irrelevant or misleading
+% for some particular project.
+
+% In our experience, programmers can use the SE literature to justify extensive, perhaps even excessive, refactoring efforts.
+% For example, this paper began when a Washington-based software company shared
+% one of their management challenges with us: their  releases are delayed by developers spending  much time removing bad smells within their code.
 This management team wanted some way to check if all that activity was useful.
 
+% In addition to tools that capture bad smells such as FindBugs and SonarQube, a multitude of tools have been proposed to support refactoring (e.g., \cite{ge2014manual,lee2013drag,foster2012witchdoctor,ge2012reconciling}).
 Note that these managers are {\em not} asking for better
-automatic refactoring
-tool support. Their human programmers are refactoring
-code all the time, perhaps too much so.
-Hence, their management goal is: 
-\bi
-\item
-{\em Not} to optimize {\em necessary} refactorings;
-\item
-But rather to discourage {\em unnecessary} refactorings.
-\ei
-For those managers, we offer the  following heuristic:
+% automatic refactoring
+% tool support. 
+% Their human programmers are refactoring
+% code all the time, perhaps too much so.
+% Hence, the management goal
+The challenge is to encourage refactorings that result in perceivable benefits (such as reduced defect proneness or lower maintenance costs) and avoid refactorings with no demonstrable benefit and thus waste effort.
+
+This paper describes one approach to evaluate whether refactorings that change the structure of code are likely to have a perceivable benefit by evaluating:
 \bi
@@
 \ei
-This paper describes one way to operationalize this heuristic, in the context
-of assessing bad smells. We use data mining to generate two oracles: a {\em primary
+We use data mining to generate two oracles: a {\em primary
 change oracle} and a {\em secondary verification oracle}.
@@
  we can generate and validate useful
-changes to code modules.
+changes to code modules. We focus on ``bad smells'' indicated by code metrics such as size and complexity as captured in popular tools such as SonarQube [REF] and Klocwerk [REF].
 
@@
 XTREE 
-explores the historical record of a project to find clusters of projects.
-It then proposes a ``minimal'' set of changes $\Delta$ that can move a software module $M$ from a defective cluster $C_0$ to another with fewer defects$C_1$ (so $\Delta$
+explores the historical record of a project to find clusters of module.
+It then proposes a ``minimal'' set of changes $\Delta$ that can move a software module $M$ from a defective cluster $C_0$ to another with fewer defects $C_1$ (so $\Delta$
 is some subset of $C_1 - C_0$). % To define ``minimal'', XTREE uses an entropy measure.
@@
 the {\em secondary verification oracle}, this  checks if the primary oracle is proposing
-sensible changes. For this purpose we use Random Forest\cite{breiman2001random}, augmented with SMOTE (synthetic  minority over-sampling technique~\cite{chawla2002smote}).
+sensible changes. For this purpose we use Random Forest~\cite{breiman2001random}, augmented with SMOTE (synthetic  minority over-sampling technique~\cite{chawla2002smote}).
  In our framework,  learning
@@
 since it assumes that the best way to improve code is to decreases multiple code attribute measures below $t_i$ in order
-to remove the ``bad'' smells. This is wrong.  
-There exists an intricate set of associations between static code measures
+to remove the ``bad'' smells. In reality, there exists an intricate set of associations between static code measures
 such that {\em decreasing}  $a_i$ necessitates {\em increasing} $a_j$.
@@
 
-This paper  claims that (a)~XTREES is a  better way than \eq{df}  to define useful changes to software and (b)~those changes are useful for recognizing   superfluous refactorings since they usually refer to a very
+This paper  claims that (a)~XTREE is a  better way than \eq{df}  to define useful changes to software and (b)~those changes are useful for recognizing   superfluous refactorings since they usually refer to a very
 small subset of the static code measures (which allows us to rule out refactorings based on any of the omitted
@@
 In support of these claims, 
-the rest of this paper is structured as follows. First, we offer some background on bad smells. After that,
-  in Section~3, 
+the rest of this paper is structured as follows. In Section~2, we offer some background on bad smells. In Section~3, 
   different methods are presented for determining when code does/does not have bad smell. One of those methods
-  will be XTREE while the others will come from other researchers. Next,    Section~4
+  will be XTREE while the others will come from other researchers. Section~4
   defines an assessment method that checks which of these methods is most useful. The results from that assessment 
@@
 
- {\bf  RQ1: Effectiveness}: According to the verification oracle, which of the methods  defined in Section~3 is the best  change oracle for identifying what and how
+ {\bf  RQ1: Effectiveness}\footnote{test}: According to the verification oracle, which of the methods  defined in Section~3 is the best  change oracle for identifying what and how
   code modules should be changed? To answer this question, we used data from five OO Java projects
@@
   \begin{lesson}
- XTREE is the best oracle on how to change code modules (in order to reduce defects).
+ XTREE is the most accurate oracle on how to change code modules in order to reduce defects.
   \end{lesson}
@@
 \begin{lesson}
-Of all the code change oracles studied here, XTREE recommend  far fewest changes to static code measures.
+Of all the code change oracles studied here, XTREE recommends the fewest number of changes to static code measures.
 \end{lesson}
@@
 \begin{lesson}
-The direction of change recommended  XTREE is  very stable across repeated runs of the program 
+The direction of change recommended by XTREE is  very stable across repeated runs of the program 
 \end{lesson}
@@
 
+\subsection{Outlier Statistics}
+
 The outlier approach assume that unusually large measurements indicate risk-prone code.
@@
 \input{xtree_tut.tex}
-
-\subsection{Outlier Statistics}
 
@@
 thresholds which, following Shatnawi's guidance, we set to
-$p_0=p_1=0.05$.
+$p_0=p_1=0.05$.\footnote{There is no p0 in the equation.}
 
@@
     $\beta$ is the coefficient for maximizing log-likelihood;
-  and $p_0$  
+  and $p_0$\footnote{There is no p0 in the equation.}  
     measures   how well this   model predicts for   defects.
@@
 with Shatnawi, we explore the correlation between
-the code metrics and the defect counts and   reject code metrics that are poor predictors of defects (i.e.   those  with $p > 0.05$).
+the code metrics and the defect counts and   reject code metrics that are poor predictors of defects (i.e.
+those  with $p > 0.05$).\footnote{Okay, why focus on Shatnawi and not the others?
+this statement seems out of place.}
 
@@
 Second, the outlier approaches suffers from
-the {\em disjunction fallacy}  discussed in the introduction.
+the {\em disjunction fallacy}\footnote{It was conjunctive fallacy in the introduction -- which is right?}  discussed in the introduction.
 That is, while
@@
 modules than $C_-$;
-\item Compute the  delta   in code metrics between the clusters using \mbox{$\Delta = C_+ - C_-$}, i.e.
+\item Compute the  delta   in code metrics between the clusters using \mbox{$\Delta = C_+ - C_-$}\footnote{Isn't this backward?
+Doesn't $C_- - C_+$ give you the changes to be made to $C_+$, e.g.
+$C_+$ = 1000LOC, $C_-$ = 100 LOC, $C_- - C_+$ = -900 LOC which is the transformation you want to apply to $C_+$}, i.e.
 {\em towards} the cluster with lower defects;
@@
   that avoids the problem of verbose $\Delta$s.
-  It is our recommended {\em primary change oracle} that makes recommendations 
+  XTREE is our {\em primary change oracle} that makes recommendations 
   of what changes should be made to code modules.
@@
 first converts the values for each code
-metrics into a small number of ranges.
+metric into a small number of ranges.
 Consider a code metric is split into $r$ ranges and each range is of
   size
-    $n_r$ is
+    $n_r$\footnote{How do you select $r$ and/or $n_r$?} is
   associated with a set of defect counts $x$ with standard deviation
@@
   across all the discretized ranges of that metric.
-  Iterative dichomization sorts the metrics by $M_c$
+  Iterative dichomization sorts the metrics by $M_v$
   to find the best ``splitter'' for the data
@@
   is then split on the ranges of the splitter and
-  iterative dichomization recurses on each range.  In this way,
+  iterative dichotimization recurses on each range\footnote{I get lost here.
+You found the ranges to split from the smallest $M_v$ and you split the data on that.
+But what is the ``iterative dichotimization that recurses on each range'' at this point?}  In this way,
   each split is the root of a sub-tree.
@@
 		\item Find the {\em better} siblings; i.e. those 50\% (or less)
-		fewer defects than $C_+$.
+		fewer defects than $C_+$.\footnote{This example is for number of defects.
+What is your criteria for defect-proneness classification as in the Figure?}\footnote{Does XTREE stop as soon as it finds a better sibling?
+If it finds better siblings at level X, how do you know there are not BETTER better siblings at level X+1?
+It SEEMS like your dichotimization is optimized on the best performing classifier and thus you find recommendations that will result in a change, but are not optimized to find the BEST END RESULT (e.g., maximum reduction in \# of defects, maximum reduction in \% likelihood of defect proneness.}
 		   If none found, then repeat for $lvl += 1$. Also,
@@
 	 for discrete attributes, the delta is the value from {\em desired};
-	    for numerics  expressed as ranges, the delta is a random number selected from the low and high boundaries of the that range.
+	    for numerics  expressed as ranges, the delta is a random number selected from the low and high boundaries of the that range.\footnote{This could lead to conflicting recommendations in different runs of XTREE, right?
+Consider Figure 3.
+Suppose $C_+$ has cbo=(27.00,157.00):1.00.
+XTREE ascends one level and descends to the leaves of next subtree.
+XTREE suppose that $C_-$ is a leaft where cbo=(1.00,50:00):0.15 (instead of cam as in Figure 3).
+By selecting something random in the range, you could recommend either an increase or a decrease to CBO.
+I would think that this is an instance where XTREE should say 'I don't know what to do with CBO, but you should improve LCOM.' Alternately, if you took the median value (instead of random) and coompared, you could at least recommend a direction, i.e., ``the best benefits come from REDUCING lcom while maintaining a LOWER cbo''}
 
@@
 To   answer to this question, we will assume that developers
-refactor their code until the bad smell thresholds is not violated.
+refactor their code until the bad smell thresholds are not violated.
 This refactoring will start with some {\em initial} code
@@
 question, we conduct a large scale ``what if'' study that reports all the possible recommendations XTREE might make.
-We then count often attributes are {\em not} found in the recommendations arising from this ``what if'' study.
-
-{\bf RQ5: Conjunctive Fallacy:} Is  it  always  useful  to  aplly \eq{df}; i.e.
+We then count how often attributes are {\em not} found in the recommendations arising from this ``what if'' study.
+
+{\bf RQ5: Conjunctive Fallacy:} Is  it  always  useful  to  apply \eq{df}; i.e.
 make  code  better  by  reducing  the  values  of multiple code attributes?
@@
 
-\subsection{Statistics}
+\subsection{Experiment}
+Describe what you actually did, including: 
+\bi
+\item what metrics you used to identify refactorings using the 4 methods. Also, what is your data here? Is it the rows and columns of CK/OO metrics for each file?
+\item how you applied the recommended changes from the 4 methods to the data 
+\item how you chose to handle the ``conjuctive fallacy' of non-CD, non-XTREE methods
+\item What are you considering correct, i.e., if the change to the code metrics yielded a non-defective (i.e., \# defects = 0) file, then the refactoring is good. 
+\item how you aggregated the results from your 40 runs for each method
+\ei
+
+\subsection{Statistics}\footnote{You need a section before this called "Experiment"}.
 
@@
 \fig{counts} shows the frequency with which the methods
-recommend changes to specific code methods.
+recommend changes to specific code metrics.
 Note that XTREE proposes thresholds to
@@
 
-{\em  How effective is XTREE at offering   “stopping points” (i.e. clear guidance on what not to do)?}
+{\em  How effective is XTREE at offering   ``stopping points'' (i.e. clear guidance on what not to do)?}
 
@@
 
-\subsection{RQ5: Stability}
+\subsection{RQ5: Conjunctive Fallacy}
 
@@
 
-To explore this point further, we conducted the following ``what-if'' study. Once XTREE builds its trees with its leaf clusters then:
+To explore this point further, we conducted the following ``what-if'' study\footnote{What is the advantage of this ``what-if'' approach over just looking at the recommendations from the 40 runs in your experiments?
+Why not both?}.
+Once XTREE builds its trees with its leaf clusters then:
 \be

### 2016-08-22 xtree_tut.tex
Updates from ShareLaTeX

@@
  XTREE looks for a nearby branch that has a lower chance of being defective.
-Finding the \textcolor{green}{{ green}} desired  branch,  XTREE reports a bad smell threshold for that module that is the delta between the \textcolor{orange}{{\bf orange}}  current branch  and   \textcolor{green}{{ green}} designed branch.
+Finding the \textcolor{green}{{ green}} desired  branch,  XTREE reports a bad smell threshold for that module that is the delta between the \textcolor{orange}{{\bf orange}}  current branch  and   \textcolor{green}{{ green}} designed branch.\footnote{But XTREE makes no recommendations for CBO even though it is in the organge branch.
+Is this because there is nothing about CBO in the desired branch?
+Should there be?}
  In this case, that threshold relates to:

### 2016-08-24 Manuscript.tex
Dr. L

@@
 
-\input{tex/refactor}
+	\input{refactor}
 
@@
 
-\input{tex/jur_char}
+	\input{jur_char}
 
@@
 	is to use the VARL method (Value of Acceptable Risk Level) proposed by Bender~\cite{bender99} in his epidemiology studies.  This approach uses two
-thresholds which, following Shatnawi's guidance, we set to
-$p_0=p_1=0.05$.\footnote{There is no p0 in the equation.}
+	constants to compute the thresholds which, following Shatnawi's guidance, we set to
+	$p_0=p_1=0.05$.
 
@@
 	$\beta$ is the coefficient for maximizing log-likelihood;
-  and $p_0$\footnote{There is no p0 in the equation.}  
+	and $p_0$ 
 	measures   how well this  model predicts for  defects.
-Any code metric with $p_0>0.05$ is  ignored as being a poor defect predictor. Thresholds are then learned from the surviving metrics $M_c$ using
+A univariate logistic regression was conducted comparing metrics to defect counts.
+Any code metric with $p>0.05$ is ignored as being a poor defect predictor.
+Thresholds are then learned from the surviving metrics $M_c$ using
 	an equation proposed by Bender:
+	$$ \mathit{bad\; smell\; if\;} M_c > VARL$$
 	\begin{equation}
- \mathit{bad\; smell\; if\;} M_c > \frac{1}{\beta }\left( {\log \left( {\frac{{{p_1}}}{{1 - {p_1}}}} \right) - \alpha } \right) 
+		VARL = p^{-1}(p_0) =  \frac{1}{\beta }\left( {\log \left( {\frac{{{p_1}}}{{1 - {p_1}}}} \right) - \alpha } \right) 
 	\end{equation}
@@
 
-For consistency
-with Shatnawi, we explore the correlation between
-the code metrics and the defect counts and   reject code metrics that are poor predictors of defects (i.e.
+	For consistency with Shatnawi, we explore the correlation between the code metrics and the defect counts and  reject code metrics that are poor predictors of defects (i.e.
 those  with $p > 0.05$).\footnote{Okay, why focus on Shatnawi and not the others?
@@
 Without a means for prioritizing the  thresholds and metrics against one another, developers may have numerous or conflicting recommendations on what to improve.
-Second, the outlier approaches suffers from
-the {\em disjunction fallacy}\footnote{It was conjunctive fallacy in the introduction -- which is right?}  discussed in the introduction.
-That is, while
- they propose thresholds for many code metrics
-individually, they make no comment on what minimal
-metrics need to be changed at the same time (or whether or not those
-changes lead to minimization or maximization of static code measures).
+Second, the outlier approaches suffers from {\em conjunctive fallacy}  discussed in the introduction.
+That is, while	they propose thresholds for many code metrics
+	individually, they make no comment on what minimal metrics need to be changed at the same time (or whether or not those changes lead to minimization or maximization of static code measures).
 
@@
 		modules than $C_-$;
-\item Compute the  delta   in code metrics between the clusters using \mbox{$\Delta = C_+ - C_-$}\footnote{Isn't this backward?
-Doesn't $C_- - C_+$ give you the changes to be made to $C_+$, e.g.
-$C_+$ = 1000LOC, $C_-$ = 100 LOC, $C_- - C_+$ = -900 LOC which is the transformation you want to apply to $C_+$}, i.e.
+		\item Compute the  delta   in code metrics between the clusters using \mbox{$\Delta = C_- - C_+ = \left\{\delta|\delta\in C_-, \delta \notin C_+\right\}$}, i.e.
 		{\em towards} the cluster with lower defects;
-\item $\Delta$ are changes needed in defective modules of $C_+$ to
+		\item The set $\Delta$ are changes needed in defective modules of $C_+$ to
 		make them more like the less-defective modules of $C_-$
@@
 
- XTREE uses an iterative dichotomizer that
-first converts the values for each code
-metric into a small number of ranges.
-Consider a code metric is split into $r$ ranges and each range is of
-  size
-    $n_r$\footnote{How do you select $r$ and/or $n_r$?} is
-  associated with a set of defect counts $x$ with standard deviation
+	XTREE uses a multi-interval discretizer based on an iterative dichotomization scheme, first proposed by Fayyad and Irani~\cite{fi}.
+This method converts the values for each code metric into a small number of nominal ranges.
+It works as follows:
+	\begin{itemize}
+		\item A code metric is split into $r$ ($r=2$) ranges, each range is of
+		size $n_r$ and is associated with a set of defect counts $x$ with standard deviation
 		$\sigma_r$. 
-  The best split for that range is
-  the one that minimizes the expected value of the
-  defect variance, after the split; i.e.
-  $\sum_r\frac{n_r}{n}\sigma_x$ (where $n=\sum_r n_r$).
-  This discretizer then recurses on each part of the split
-  to find other splits.
+		\item The best split for that range is the one that minimizes the expected value of the
+		defect variance, after the split; i.e. $\sum_r\frac{n_r}{n}\sigma_x$ (where $n=\sum_r n_r$). 
+		\item This discretizer then recurses on each part of the split to find other splits in a recursive fashion.
+As suggested by Fayyad and Irani, minimum descriptor length (MDL) is used as a termination criterion for the recursive partitioning.
+	\end{itemize}
 
@@
 	Iterative dichomization sorts the metrics by $M_v$
-  to find the best ``splitter'' for the data
-  (the code metric with smallest $M_v$). The data
-  is then split on the ranges of the splitter and
-  iterative dichotimization recurses on each range\footnote{I get lost here.
-You found the ranges to split from the smallest $M_v$ and you split the data on that.
-But what is the ``iterative dichotimization that recurses on each range'' at this point?}  In this way,
-  each split is the root of a sub-tree.
-
-  While not usually labelled as such, iterative dichomization can
-  be viewed as a clustering algorithm that groups together code modules
-  with similar defect counts and some shared ranges of code metrics.
+	to find the code metric that best splits the data i.e., the code metric with smallest $M_v$.
+
+	A decision tree is then constructed on the discretized metrics. The metric that generated the best split forms the root of the tree with its discrete ranges acting as the nodes.
+
+	When all the metrics are arranged this way, the process is very similar to a hierarchical clustering algorithm that groups together code modules with similar defect counts and some shared ranges of code metrics.
 	For our purposes, we score each cluster found in this way according
-  to the percent of classes with known defects. For example,
-  the last line of \fig{xtree_samp} shows a tree lead with 75\%
+	to the percent of classes with known defects. For example, the last line of \fig{xtree_samp} shows a tree leaf with 75\%
 	defective modules.
@@
 
-Using the training data,  XTREE uses  
-iterative dichomization to
-  divide  $N$ code modules  into  clusters of
-size $\sqrt{N}$.
+	Using the training data construct a decision tree as suggested above.
+
+%	uses  
+%	iterative dichomization to
+%	divide  $N$ code modules  into  clusters of
+%	size $\sqrt{N}$.
 
 	Next, for each test code module, 
-	  find $C_+$ as follows take each test , run it down to a leaf in the decision tree.  
+	find $C_+$ as follows: take each test, run it down the decision tree to find a leaf in the decision tree that mostly matches the test case.  
 	After that,	find $C_-$ as follows:
@@
 		\item Starting at the  $C_+$ leaf, ascend $lvl\in \{0,1,2...\}$ tree levels;
-		\item Identify {\em sibling} leaves; i.e. leaf clusters that can be reached from level $lvl$ that are not same as {\em current }
+		\item Identify {\em sibling} leaves; i.e. leaf clusters that can be reached from level $lvl$ that are not same as {\em current $C_+$};
 		\item Find the {\em better} siblings; i.e. those 50\% (or less)
-		fewer defects than $C_+$.\footnote{This example is for number of defects.
-What is your criteria for defect-proneness classification as in the Figure?}\footnote{Does XTREE stop as soon as it finds a better sibling?
-If it finds better siblings at level X, how do you know there are not BETTER better siblings at level X+1?
-It SEEMS like your dichotimization is optimized on the best performing classifier and thus you find recommendations that will result in a change, but are not optimized to find the BEST END RESULT (e.g., maximum reduction in \# of defects, maximum reduction in \% likelihood of defect proneness.}
-		   If none found, then repeat for $lvl += 1$. Also,
-		    return nil  if the new $lvl$ is above the root. 
+		fewer defects than $C_+$. If none found, then repeat for $lvl += 1$. Also, return \texttt{nil} if the new $lvl$ is above the root. 
 		\item  Set $C_-$ to the  {\em closest} better sibling where distance is measured between the mean centroids of that sibling and {\em current}
 		\ei
-	 Now find $\Delta = C_+ - C_-$  by reflecting
-	 on the set difference between  conditions in the decision tree branch to $C_-$ and $C_+$. To find that delta,
-	 for discrete attributes, the delta is the value from {\em desired};
-	    for numerics  expressed as ranges, the delta is a random number selected from the low and high boundaries of the that range.\footnote{This could lead to conflicting recommendations in different runs of XTREE, right?
-Consider Figure 3.
-Suppose $C_+$ has cbo=(27.00,157.00):1.00.
-XTREE ascends one level and descends to the leaves of next subtree.
-XTREE suppose that $C_-$ is a leaft where cbo=(1.00,50:00):0.15 (instead of cam as in Figure 3).
-By selecting something random in the range, you could recommend either an increase or a decrease to CBO.
-I would think that this is an instance where XTREE should say 'I don't know what to do with CBO, but you should improve LCOM.' Alternately, if you took the median value (instead of random) and coompared, you could at least recommend a direction, i.e., ``the best benefits come from REDUCING lcom while maintaining a LOWER cbo''}
-
-\input{tex/prediction_stats.tex}      
+		Now find $\Delta = C_- - C_+$  by reflecting
+		on the set difference between  conditions in the decision tree branching from $C_+$ to $C_-$. To find that delta,
+		for discrete attributes, delta is the value of the {\em desired}; for numerics  expressed as ranges, the delta could be any value that lies between $\left[ LOW, HIGH\right]$ in that range (random number selected from the low and high boundaries of the that range.)
+
+		\input{prediction_stats.tex}      
 		\section{Evaluation}
@@
 
-\subsection{Experiment}
-Describe what you actually did, including: 
-\bi
-\item what metrics you used to identify refactorings using the 4 methods. Also, what is your data here? Is it the rows and columns of CK/OO metrics for each file?
-\item how you applied the recommended changes from the 4 methods to the data 
-\item how you chose to handle the ``conjuctive fallacy' of non-CD, non-XTREE methods
-\item What are you considering correct, i.e., if the change to the code metrics yielded a non-defective (i.e., \# defects = 0) file, then the refactoring is good. 
-\item how you aggregated the results from your 40 runs for each method
-\ei
-
-\subsection{Statistics}\footnote{You need a section before this called "Experiment"}.
+%		\subsection{Experiment}
+%		Describe what you actually did, including: 
+%		\bi
+%		\item what metrics you used to identify refactorings using the 4 methods. Also, what is your data here? Is it the rows and columns of CK/OO metrics for each file?
+%		\item how you applied the recommended changes from the 4 methods to the data 
+%		\item how you chose to handle the ``conjuctive fallacy' of non-CD, non-XTREE methods
+%		\item What are you considering correct, i.e., if the change to the code metrics yielded a non-defective (i.e., \# defects = 0) file, then the refactoring is good. 
+%		\item how you aggregated the results from your 40 runs for each method
+%		\ei
+%
+
+		\subsection{Statistics}
 
@@
 
-\input{tex/results_jur.tex}
+		\input{results_jur.tex}
 
@@
 
-\input{tex/rq2.tex}
+		\input{rq2.tex}
 		\section{Results}
@@
 
-\input{tex/all_changes.tex}
+		\input{all_changes.tex}
 
@@
 
-To explore this point further, we conducted the following ``what-if'' study\footnote{What is the advantage of this ``what-if'' approach over just looking at the recommendations from the 40 runs in your experiments?
-Why not both?}.
-Once XTREE builds its trees with its leaf clusters then:
+		To explore this point further, we conducted the following ``what-if'' study. Once XTREE builds its trees with its leaf clusters then:
 		\be
@@
 
-% \input{tex/results_models.tex}
+		% \input{results_models.tex}
 

### 2016-08-24 algos.tex
Dr. L

	\begin{figure}[tbp!]
	\begin{shaded}
  ~\hrule~

 {\bf Figure 3.A: Measuring Variability}

	For  continuous and discrete values,
the {\em variability} can be measured using standard deviation $\sigma$ or entropy $e$.
Note that \mbox{$\sigma = \sqrt{\sum^n_{i=1} \left( \frac{(x_i - \bar{x})^2}{n-1}\right)}$}
where $\bar{x}$ is the mean of  numeric features $x_1,x_2,..x_n$.
Also \mbox{$e = - \sum^n_{i=1} p_i \mathit{log}_2(p_i)$} 
for  $n$ discrete values  at frequency
$f_1,f_2,.. f_n$ for \mbox{$N = \sum^n_{i=1} f_i$} and $p_i = f_i/N$.

  ~\hrule~

	{\bf Figure 3.B: Measuring distance}

	We use
		 Aha et al.'s standard Euclidean distance measure~\cite{aha91}.  For $F$ independent features, the measure returns   $d(X,Y)=\sqrt{\sum_i^F  w_i\Delta(X_i,Y_i)^2}$. Here, $w_i$ is a weight term for each feature
		 (usually set to 1).
			Within $\Delta$, if   $X_i,Y_i$ are both missing  values, then  return 1.
			Otherwise, replace any  missing items with values that maximizes the following.
			For numerics, $\Delta$ normalizes $X_i,Y_i$ (to the range 0,1 for min,max) then
			returns 
			$X_i - Y_i$. For discrete variables, $\Delta$ returns 0,1 if $X_i,Y_i$ are the
			same,different (respectively).

 ~\hrule~

	{\bf Figure 3.C: Top-down Clustering with WHERE}

				WHERE  divides data into  groups of size $\alpha=\sqrt{N}$. 
		Using this measure, WHERE runs as follows:
		\begin{enumerate}[leftmargin=3mm]
			\item Find   two   distance cases,  $X,Y$
			by picking any case $W$ at random, then setting $X$ to its most
			distant case, then setting $Y$ to the case most distant from
			$X$
			(which requires only $O(2N)$ comparisons).
			\item Project each case $Z$
			to position $x$ on a    lines running from $X$ to $Y$: if $a,b$  are distances  $Z$ to $X,Y$  then  $x = (a^2+c^2 - b^2)/(2ac)$.
			\item Split the data at the median $x$ value of all cases.
			\item For   splits larger than  $\alpha=\sqrt{N}$, recurse from step1.
		\end{enumerate}
 In terms of related work,
	  the above is similar in approach to Boley's PDDP algorithm~\cite{boley98}, but PDDP requires an $O(N^2)$ calculation
	  at each recursive level to find the PCA principle component. Our method, on the other hand,
	  performs the same task with only $O(2N)$ distance calculations 	using the 
	  FASTMAP heuristic~\cite{Faloutsos1995} shown in step1. Platt~\cite{platt05} notes that FASTMAP is a  Nystr\"om approximation to the first component of PCA.

	   ~\hrule~

	{\bf Figure 3.D: Top-down division with Decision Trees}

	Find a split in the values of  independent features that most reduces the variability
  of the dependent feature (measured using \fig{where}.A). Construct a standard decision tree using these splits.

	 ~\hrule~

	 	{\bf Figure 3.E: Finding the most informative rows}

Discretize all numeric features using the Fayyad-Iranni discretizer~\cite{FayIra93Multi}
(divide numeric columns into bins $B_i$, each of which  select for the fewest cluster ids).
Let feature $F$ have bins $B_i$, each of which contains $n_i$ rows
and 
let each bin $B_i$ have entropy $e_i$ computed from the frequency of clusters seen in that bin (computed from \fig{where}.A).
Cull the the features as per~\cite{papa13}; i.e. just use the $\beta=33\%$ most informative features
where  the   value of  feature $F$ is $\sum_i e_i\frac{n_i}{N}$ ($N$ is the number of rows).

~\hrule~

	  \end{shaded}
		\caption{Some algorithms used in this paper.}\label{fig:where}
		\end{figure}

### 2016-08-24 dtree.tex
Dr. L

\begin{figure}[t] 
	\begin{shaded}
  ~\hrule~

Using the training data,  divide the data using the decision tree algorithm of \fig{where}.D into groups of
size $\alpha=\sqrt{N}$.
For test item, 
	  find the {\em current } leaf: take each test instance, run it down to a leaf in the decision tree.  
After that,	  find the {\em desired} leaf:
		\begin{itemize}[leftmargin=3mm]
		\item Starting at {\em current}, ascend the tree $lvl\in \{0,1,2...\}$ levels;
		\item Identify {\em sibling} leaves; i.e. leaf clusters that can be reached from level $lvl$ that are not same as {\em current }
		\item Using the {\em score} defined above, find the {\em better} siblings; i.e. those with a {\em score} less than $\gamma=0.5$ times the mean score of {\em current}. 
		   If none found, then repeat for $lvl += 1$. Also,
		    return no plan if the new $lvl$ is above the root. 
		\item  Return the {\em closest} better sibling where distance is measured between the mean centroids of that sibling and {\em current}
		\ei
	 Also, find the {\em delta}; i.e. the set difference between  conditions in the decision tree branch to {\em desired} and {\em current}. To find that delta: (1)~for discrete attributes, delta is the value from {\em desired}; (2)~for  numerics, delta is the numeric difference; (3)~for numerics  discretized into ranges, delta is a random number selected from the low and high boundaries of the that range.

		Finally, return the delta as the plan for improving the test instance.
		~\hrule~
		\end{shaded}
		\caption{XTREE}		\label{fig:xtrees_bare}
	\end{figure}

### 2016-08-24 Manuscript.tex
Updates from ShareLaTeX

@@
 
-	For consistency with Shatnawi, we explore the correlation between the code metrics and the defect counts and  reject code metrics that are poor predictors of defects (i.e.
-those  with $p > 0.05$).\footnote{Okay, why focus on Shatnawi and not the others?
-this statement seems out of place.}
+	For consistency with Shatnawi, we explore the correlation between the code metrics and the defect counts and  reject code metrics that are poor predictors of defects (i.e.   those  with $p > 0.05$).
 
@@
 
-		% of ``better'' deefined as per \eq{df} is misleading.
-
-		% Also, most attributes are not changed in most data sets.
-		% Only our attributes (cbo, rfc, loc,cam) change in a majority of data sets  (three of five, or more).
-
-		% XXXX
-
-		% ups and down. fucntionalty has to go somehwere else
-
-		% highlights all possible changes proposed by XTREE, upon close inspection it becomes apparent that XTREE suggests that it is perhaps better to reduce only certain forms of coupling.
-Refactoring operations that reduce one form of coupling at the cost of increasing another can sometimes be beneficial.
-This is most noticeable in Ivy, where one of the better approaches is to reduce coupling between objects (cbo) (efferent coupling) while increasing the afferent coupling (CA), again implying a redistribution of responsibilities.
-Using thresholds may not always appreciate the existence of these co-changes between metrics, and as a result many refactoring operations are usually left unexplored.
-
-		% Note that we prefer XTREE to Shatnawi and the Alves
-		% method since those other methods
-		% do not reason
-		% 2about decreases {\em and} increases of multiple 
-		% code metrics, at the same time.
-
-		% As a final comment, we note
-		% that  \fig{changes} enables us to explain the uniformity
-		% of the results seen with Jedit in \fig{jur}.
-		% Observe how in \fig{changes} the only change ever
-		% found is a reduction to {\em rfc}. Clearly, in this
-		% data set, there is very little that can be usefully changed.
-
-		% \fig{multcomp} shows the frequency with which the methods
-		% recommend changes to specific code methods.
-		% Note that XTREE proposes thresholds to
-		% few code metrics compared to the other approaches.
-
-		% When combining  \fig{jur}, \fig{counts}, and \fig{multcomp}, we   see that
-		% even though XTREE proposes changes to far fewer code metrics, those few
-		% code metrics are usually just as effective (or
-		% more effective) than the multiple
-		% thresholds
-		% proposed by CD, Shatnawi or Alves.  That is, XTREE proposes
-		% {\em fewer} and better thresholds than the other approaches studied here.
-
-		% \begin{lesson}
-		% In addition to recommending useful changes, XTREE recommends changes to all co-varying software metrics.
-		% \end{lesson}
-
-		% \section{Threats to Validity}\label{sect:valid}
-		% XXXX assumes anything can change
-
-		% assumes we can get data
-
-		% assuems that defect is a;l;l.
-
-		% Before  that, we offer one following note on a
-		% core assumption of XTREE.
-		% XTREE   is focused on Fowler's bad smells
-		% as contributors to software defects. Some researchers 
-		%  suggest that discussing bad smells is useful for more just reducing defects. For example, Bosu and Carver~\cite{bosu13} report that
-		% debates about code smells and refactorings can (a)~introduce new comers to the code base or (b)~share knowledge on a team
-		% about interactions within the code. In that view, 
-		% the concept of refactoring can be useful
-		% even if it does not address issues of defects.
-
-		% As with any empirical study, several issues can affect the final results. Therefore, any
-		% conclusions made from this work must be offered with the following
-		% caveats.
-
-		% \subsection{External Validity}
-		% Based on the experimental results above,
-		% as well as the discussion in \tion{prelim},
-		% we believe that bad smell indicators (e.g. \mbox{{\em loc}$>$ 100})
-		% have limited external validity beyond the projects from which they are derived. 
-		% While specific models are externally valid,
-		% there may still be general methods like XTREE for finding the good local models.
-
-		% Our definition of bad smells is limited to those represented by OO code metrics (a premise often used in related work).   
-		% XTREE, Shatnawi, Alves et al. can  only comment
-		% on bad smells   expressed as code metrics 
-		%   in the historical log of a project.
-
-		% If developers want to justify their refactorings
-		% via bad smells expressed in other terminology,
-		% then the  analysis of this paper must:
-		% \begin{itemize}
-		%     \item Either wait till 
-		% data about those new
-		% terms has been collected. 
-		% \item Or, apply cutting edge transfer learning
-		% methods~\cite{Nam15,Jing15} to map data from other projects
-		% into the current one.
-		% \end{itemize}
-		% Note that the transfer learning approach would
-		% be highly experimental and require more study
-		% before it can be safely recommended.
-
-		% Sampling bias threatens any data mining experiment; i.e., what matters
-		% there may not be true here. For example, the data sets used here comes from Jureczko et al. and any biases in their selection procedures
-		% threaten the validity of these results. 
-		% That said,
-		% the best we can do is define our methods and publicize our data and code so that other researchers can
-		% try to repeat our results and, perhaps, point out a previously unknown bias
-		% in our analysis. Hopefully, other researchers will emulate our methods in
-		% order to repeat, refute, or improve our results.
-
-		% % Data mining is a large and active field and any single study can only use a small subset of the known classification algorithms.  
-		% % That said, we have taken care to document in this paper the decisions made by engineering
-		% % judgement that could effect our conclusions.
-
-		% \subsection{Trusting the Changes}\label{sect:trust}
-		%   XTREE is evaluated by  comparing
-		% predicted performance scores before and after a planner makes changes to the feature values of an example:
-		% After making those
-		% changes, we may have a new example that has never been seen before. Therefore, it must be asked
-		% {\em ``can we trust the predictions made on such new examples?''}
-
-		% To answer this question, we note
-		% that data miners explore two  ``clouds'' of data: (1) the cloud of training examples and (2) the  cloud   of test examples
-		% (for a visualization of these clouds, see \fig{howxy}).
-		% \begin{figure}[!t]
-		%   \includegraphics[width=\linewidth]{figs/2d.eps} 
-		%  % \includegraphics[width=1\linewidth]{figs/BDBC.eps}
-		% \caption{Gray, red, green show (1) training examples, (2) test examples and 
-		%   (3) tests that have been altered by planners.
-		%   This figure uses axes generated from the first two components of a PCA analysis of all points. 
-		% }\label{fig:howxy}
-		% \end{figure}
-		% We should mistrust the predictions made by a  model   if it is being applied to examples  that are
-		% too far away from the
-		% training cloud.
-		% To test for ``too far'', we can run a data mining experiment that tests how well
-		% a model learned from the training data applies to the test data. Such experiments return some performance value.
-
-		% Note that predictions  about changes that  fall within the space of the training+test data, will be at least
-		% as accurate as the predictions of the original test data.
-With this, we assert that the predictions for changes that move examples towards/away from the training data can be trusted more/less (respectively).
-
-		% Accordingly, we need {\em trust-increasing} planners to generate new examples {\em closer} to the
-		% training examples.  To see how this works, 
-		%  \fig{howxy} is from the {\em ivy} data
-		% set (one of the Jureczko data sets used in this paper). It shows: (1)~the training examples in gray, (2)~the test examples in red, and (3)~the
-		% changed  examples displaced after applying a plan (in green).
-		%  Note that the  the   changed examples
-		% cases  (shown in green)  fall closer to the training cases (shown in gray) than
-		% the test cases (shown in red).
-
-		% In that green region of changed examples, our belief in the value of predictions
-		% will be just as much as, if not more than, our belief in the value of the predictions in the red region (that
-		% contains the original test data).
-		% This pattern of \fig{howxy} (where the new examples are found closer to  the training cases than the test cases) has been observed in all the other data sets studied in this
-		% paper. Hence,  we can assert that
-		% predictors learned from these training examples have some authority in the regions
-		% containing the changes examples.
-
-		% That said, the above comes with some important caveats:
-		% \bi
-		% \item 
-		% The quality of the prediction depends on the nature of the training data.
-Thus, we strongly recommend that both the data set and the predictor be assessed prior to planning.
-This ensures that the predictor's performance is adequate for a data set.
-We tackle this issue in detail in \tion{tesd}.
-		% \item
-		% Planners should be designed to be {\em trust increasing}. We list four such planning methods in \tion{planners}.
-		% \item
-		% Where possible, planners should be assessed via some external
-		% oracle that can accurately assess new examples. For an example of that kind of analysis,
-		% see  \tion{coc}.
-		% \ei
-
-		% \subsection{  Internal Validity}\label{sect:coc}
-
-		% % The main internal validity threat   in this study was the use of
-		% % optimistic reasoning when generating the changed code modules.
-		% We assumed in \tion{rq}
-		% that any code module can be changed in order
-		% to discourage triggering a bad smell detector. This is not necessarily
-		% true, as noted in {\em PROBLEM \#2} in this paper's introduction.
-		% To mitigate this issue:
-		% \begin{itemize}
-		%     \item We do not propose using XTREE as a bad
-		% smell generator;
-		% \item Rather, we offer it as  a critique agent for bad smells
-		% proposed by some other oracle (e.g. a human developer).
-		% \end{itemize}
-		% We showed about that XTREE's recommendations are not verbose.
-		% That is, even if XTREE recommends the superset of possibly important bad smells,
-		% that superset is not so large as to  overlap with many
-		%  bad smell proposed at random 
-		% by   developers.
-
-		% XTREE does not require a working defect predictor to generate
-		% its bad smell thresholds. However, to {\em certify}
-		% that those thresholds are satisfactory, some
-		% second quality predictor must be applied.
-A data set containing defect counts before and after refactoring activities would enable an accurate assessment of the performance of the threshold-setting and recommender methods, however, such a data set is not available at this time.
-
-		%  Historically,
-		% SE researchers~\cite{Cheng10,OKeeffe08,OKeeffe07,Moghadam2011,Mkaouer14} have used the QMOOD hierarchical quality model~\cite{Bansiya02}.
-		% Since such quality models may be very project specific~\cite{localvsglobal}, we prefer building local 
-		% defect predictors using Random Forests. We chose this approach,  based on its reputation for having the better  performance of 21 other learners for defect prediction~\cite{lessmann}.  
-		% Our results show that when a defect log contains too few
-		% non-defective examples then defector predictors
-		% perform poorly (see the data sets in the last few lines of \fig{j})
-		% as do their associated bad smell threshold generators
-		% (recall the performance of Lucene and Poi in~\fig{jur}). It should be noted that this is not a limitation of XTREE-- rather
-		% it seems fundamental to the problem of certifying bad smells.
-		% As evidence of this, recall that {\em all} the bad smell threshold generators of~\fig{jur}
-		% had issues with the defect data sets with  many defects
-		% (Lucene and Poi).
-
-		% % \subsection{ Learner Bias}
-		% % This study used two kinds of learners: (1) methods for suggesting
-		% % changes to code like Shatnawi, Alves et al., CD and XTREE;
-		% % (2) methods for assessing the changes proposed by these learners.
-		% % Prior studies implemented (2) using  the QMOOD hierarchical quality model
-		% % which is so old, that we suspect it may no longer be current. Hence,
-		% % we used Random Forests to build the assessment oracles that were specific
-		% % to the data sets used in this study. We chose this approach,  based on its reputation for having the better  performance of 21 other learners for defect prediction~\cite{lessmann}.
-
-		% % \subsection{  Sampling bias} 
-		% % Sampling bias threatens any data mining experiment; i.e., what matters
-		% % there may not be true here. For example, the data sets used here comes from two  Jureczko et al. and any biases in their selection procedures
-		% % threaten the validity of these results. 
-		% % That said,
-		% % the best we can do is define our methods and publicize our data and code so that other researchers can
-		% % try to repeat our results and, perhaps, point out a previously unknown bias
-		% % in our analysis. Hopefully, other researchers will emulate our methods in
-		% % order to repeat, refute, or improve our results.
-
-		% \input{results_models.tex}
+		\section{Threats to Validity}\label{sect:valid}
+
+The results of this paper are biased by out choice of refactoring goal (reducing defects) and our choice
+of measures collected from software project (OO measures such as
+  depth of inheritance, number of child classes, etc).
+
+  That said, it should be possible extend the methods of this paper to other kinds of goals (e.g. maintainability, reliability, security,
+  or the knowledge sharing measures favoured by Bosu and Carver~\cite{bosu13}) and other kinds of inputs (e.g. the process measures favored by Rahman, Devanbu et al.\cite{Rahman2013})  as follows:
+  \bi
+  \item Find a data source for the other measures of interest;
+  \item Implement another secondary verification oracle that can assess maintainability, reliability, security, etc;
+\item Implement a better primary verification oracle that can do ``better'' that XTREE at finding changes (where ``better'' is defined in terms 
+of the opinions of the verification oracle).
+\ei
+To assist other researchers exploring these points, we offer a full replication package for this study at  https://github.com/ai-se/XTREE\_IST.
+
+The results of this paper are also specific to the data sets explored here.
+Such sampling bias threatens any data mining experiment; i.e., what matters
+{\em there} may not be true {\em here}. For example, the data sets used here comes from a survey of
+open source JAVA projects from Jureczko et al.~\cite{jureczko10}. Any biases in their selection procedures
+threaten the validity of these results.
+
+That said,
+the best we can do is define our methods and publicize our data and code so that other researchers can
+try to repeat our results and, perhaps, point out a previously unknown bias
+in our analysis. Hopefully, other researchers will emulate our methods in
+order to repeat, refute, or improve our results.
+
+The recommendation to management, shown on page one of this paper,  was to stop developers doing ``X'' if there was no historical evidence that ``X'' was useful. 
+This recommendation assumes that such an  historical record can be accessed.
+If not,  then the results of this paper could be use used as a guide (see our Table 8).
+Alternatively, some form of transfer learning~\cite{Nam15,Jing15,krishna16} could be used to import data from another project (but more research would be required to test the validity of combing tools like XTREEs with transfer learning).
+
+		As with any empirical study, several issues can affect the final results. Therefore, any
+		conclusions made from this work must be offered with the following
+		caveats.
+
+		\subsection{External Validity}
+		Based on the experimental results above,
+		as well as the discussion in \tion{prelim},
+		we believe that bad smell indicators (e.g. \mbox{{\em loc}$>$ 100})
+		have limited external validity beyond the projects from which they are derived. 
+		While specific models are externally valid,
+		there may still be general methods like XTREE for finding the good local models.
+
+		Our definition of bad smells is limited to those represented by OO code metrics (a premise often used in related work).   
+		XTREE, Shatnawi, Alves et al. can  only comment
+		on bad smells   expressed as code metrics 
+		  in the historical log of a project.
+
+		If developers want to justify their refactorings
+		via bad smells expressed in other terminology,
+		then the  analysis of this paper must:
+		\begin{itemize}
+		    \item Either wait till 
+		data about those new
+		terms has been collected. 
+		\item Or, apply cutting edge transfer learning
+		methods~\cite{Nam15,Jing15} to map data from other projects
+		into the current one.
+		\end{itemize}
+		Note that the transfer learning approach would
+		be highly experimental and require more study
+		before it can be safely recommended.
+
+		Sampling bias threatens any data mining experiment; i.e., what matters
+		there may not be true here. For example, the data sets used here comes from Jureczko et al. and any biases in their selection procedures
+		threaten the validity of these results. 
+		That said,
+		the best we can do is define our methods and publicize our data and code so that other researchers can
+		try to repeat our results and, perhaps, point out a previously unknown bias
+		in our analysis. Hopefully, other researchers will emulate our methods in
+		order to repeat, refute, or improve our results.
+
+		% Data mining is a large and active field and any single study can only use a small subset of the known classification algorithms.  
+		% That said, we have taken care to document in this paper the decisions made by engineering
+		% judgement that could effect our conclusions.
 

### 2016-08-24 Manuscript.tex
Updates from ShareLaTeX

@@
 		% \title{How to Discourage Useless Refactorings}
-		\title{Toward Intelligent Refactoring Recommendations}
+		\title{Recommendations For Intelligent Code Reorganization}
 
@@
 			{\bf Context: } 
-			Developers use bad code smells to guide refactoring.
+			Developers use bad code smells to guide code reorganization.
 			Yet developers, text books, tools, and researchers disagree on which bad smells are important.
@@
 			\noindent 
-			{\bf Objective:} To evaluate the likelihood that a refactoring to address bad code smells will yield improvement in the defect-proneness of the code.
+			{\bf Objective:} To evaluate the likelihood that a code reorganization to address bad code smells will yield improvement in the defect-proneness of the code.
 
@@
 			{\bf Conclusion: }
-			Before undertaking a refactoring based on a bad smell report,
-			use a tool like XTREE to check and ignore any refactorings   that  are useless; i.e. which lacks evidence
+			Before undertaking a code reorganization based on a bad smell report,
+			use a tool like XTREE to check and ignore any code reorganizations   that  are useless; i.e. which lacks evidence
 			in the historical record  that it is useful to make that change.
-			Note that this use case applies to both manual refactorings proposed by developers
+			Note that this use case applies to both manual code reorganizations proposed by developers
 			as well as refactoring  conducted by automatic methods.
@@
 	Bad smells are a widely used technique for evaluating code.
-While the original bad small concept was largely subjective [REF], researchers including Marinescu [REF] and others has provided formal definitions of ``bad smells'' in terms of static code attributes such size, complexity, coupling, and other metrics.
-Consequently, code smells are captured by popular static analysis tools such as PMD [REF], CheckStyle [REF], FindBugs [REF], and SonarQube [REF], although not always explicitly labeled as such.
-
-	Refactoring bad smells from code is generally accepted as a recommended practice, but refactoring by definition does not change the external functionality of the system and thus may have no perceived value.
+While the original bad small concept was largely subjective~\cite{fowler99}, researchers including Marinescu~\cite{marinescu06} and others has provided formal definitions of ``bad smells'' in terms of static code attributes such size, complexity, coupling, and other metrics.
+Consequently, code smells are captured by popular static analysis tools such as PMD\footnote{https://github.com/pmd/pmd}, CheckStyle\footnote{http://checkstyle.sourceforge.net/}, FindBugs\footnote{http://findbugs.sourceforge.net/}, and SonarQube\footnote{http://www.sonarqube.org/}, although not always explicitly labeled as such.
+
+	Refactoring bad smells from code is generally accepted as a recommended practice, but code reorganization by definition does not change the external functionality of the system and thus may have no perceived value.
 For example, this paper began when a Washington-based software company shared one of their management challenges with us: their  releases are delayed by developers spending  much time removing bad smells within their code.
@@
 	% Hence, the management goal
-	The challenge is to encourage refactorings that result in perceivable benefits (such as reduced defect proneness or lower maintenance costs) and avoid refactorings with no demonstrable benefit and thus waste effort.
-
-	This paper describes one approach to evaluate whether refactorings that change the structure of code are likely to have a perceivable benefit by evaluating:
+	The challenge is to encourage code reorganizations that result in perceivable benefits (such as reduced defect proneness or lower maintenance costs) and avoid code reorganizations with no demonstrable benefit and thus waste effort.
+
+	This paper describes one approach to evaluate whether code reorganizations that change the structure of code are likely to have a perceivable benefit by evaluating:
 	\bi
@@
 	we can generate and validate useful
-	changes to code modules. We focus on ``bad smells'' indicated by code metrics such as size and complexity as captured in popular tools such as SonarQube [REF] and Klocwerk [REF].
+	changes to code modules. We focus on ``bad smells'' indicated by code metrics such as size and complexity as captured in popular tools such as SonarQube and Klocwerk [REF].
 
@@
 	in the bad smell literature~\cite{erni96,bender99,Shatnawi10,Alves2010,hermans15}.
-	A common heuristic is to recommend refactoring of ``bad'' code
+	A common heuristic is to recommend code reorganization of ``bad'' code
 	to make it ``better'' as follows: for all static code measures that exceed some threshold, make changes such that the thresholds are no longer exceeded. That is:
@@
 	It is easy to see why this is so.
-	A requirement for  refactoring is that the new code supports the same functionality
+	A requirement for  code reorganization is that the new code supports the same functionality
 	as before. If we pull code out of a function (since that function has grown too
@@
 
-	This paper  claims that (a)~XTREE is a  better way than \eq{df}  to define useful changes to software and (b)~those changes are useful for recognizing   superfluous refactorings since they usually refer to a very
-	small subset of the static code measures (which allows us to rule out refactorings based on any of the omitted
+	This paper  claims that (a)~XTREE is a  better way than \eq{df}  to define useful changes to software and (b)~those changes are useful for recognizing   superfluous code reorganizations since they usually refer to a very
+	small subset of the static code measures (which allows us to rule out code reorganizations based on any of the omitted
 	static code measures). 
@@
 
-	{\bf RQ3: Stopping}: Our advice to managers is to discourage refactoring based on changes that lack
+	{\bf RQ3: Stopping}: Our advice to managers is to discourage code reorganization based on changes that lack
 	historical evidence of being effective. How effective is XTREE at offering such ``stopping points'' (i.e. clear guidance on what {\em not} to do)??
@@
 	Yes,  indeed, their programmers
-	were wasting time on   performing refactorings  that  decreased multiple measures when, in fact,
+	were wasting time on   performing code reorganizations  that  decreased multiple measures when, in fact,
 	they should be trying to {\em decrease} some measures while {\em increasing} others.
@@
 	of the measures were usually found within  change recommendations. That is, it is 80\% likely that
-	that refactoring based on reducing any one measurement picked at random will be useful.
+	that code reorganization based on reducing any one measurement picked at random will be useful.
 	\ei
@@
 	\bi
-	\item Before doing  refactoring based on a bad smell report...
-	\item ...check and discourage any refactoring   for which there is no proof
+	\item Before doing  code reorganization based on a bad smell report...
+	\item ...check and discourage any code reorganization   for which there is no proof
 	in the historical record that the change improves the code.
 	\ei
-	This use case described  applies to both manual refactorings proposed by developers
+	This use case described  applies to both manual code reorganizations proposed by developers
 	as well as refactoring conducted by automatic methods~\cite{mkaouer2015many}. That is, XTREE could optimize automatic
 	code refactoring by discouraging refactorings for useless goals.
-
-	\subsection{ Threats to Validity}
-
-	The results of this paper are biased by out choice of refactoring goal (reducing defects) and our choice
-	of measures collected from software project (OO measures such as
-	depth of inheritance, number of child classes, etc).
-
-	That said, it should be possible extend the methods of this paper to other kinds of goals (e.g. maintainability, reliability, security,
-	or the knowledge sharing measures favoured by Bosu and Carver~\cite{bosu13}) and other kinds of inputs (e.g. the process measures favored by Rahman, Devanbu et al.\cite{Rahman2013})  as follows:
-	\bi
-	\item Find a data source for the other measures of interest;
-	\item Implement another secondary verification oracle that can assess maintainability, reliability, security, etc;
-	\item Implement a better primary verification oracle that can do ``better'' that XTREE at finding changes (where ``better'' is defined in terms 
-	of the opinions of the verification oracle).
-	\ei
-	To assist other researchers exploring these points, we offer a full replication package for this study at  https://github.com/ai-se/XTREE\_IST.
-
-	The results of this paper are also specific to the data sets explored here.
-	Such sampling bias threatens any data mining experiment; i.e., what matters
-	{\em there} may not be true {\em here}. For example, the data sets used here comes from a survey of
-	open source JAVA projects from Jureczko et al.~\cite{jureczko10}. Any biases in their selection procedures
-	threaten the validity of these results.
-
-	That said,
-	the best we can do is define our methods and publicize our data and code so that other researchers can
-	try to repeat our results and, perhaps, point out a previously unknown bias
-	in our analysis. Hopefully, other researchers will emulate our methods in
-	order to repeat, refute, or improve our results.
-
-	The recommendation to management, shown on page one of this paper,  was to discourage developers doing ``X'' if there was no historical evidence that ``X'' was useful. 
-	This recommendation assumes that such an  historical record can be accessed.
-If not,  then the results of this paper could be use used as a guide (see our Table 8).
-Alternatively, some form of transfer learning~\cite{Nam15,Jing15,krishna16} could be used to import data from another project (but more research would be required to test the validity of combing tools like XTREEs with transfer learning).
 
@@
 	Much research endorses them to guide
-	code improvement (e.g., refactoring or preventative maintenance). A recent literature review by Tufano et al.~\cite{Tufano2015}  
+	code improvement (e.g., code reorganization or preventative maintenance). A recent literature review by Tufano et al.~\cite{Tufano2015}  
 	lists dozens of papers on smell detection and repair tools. 
@@
 	that very few  code smells are   high priority issues
-	requiring refactoring.
+	requiring code reorganization.
 
@@
 	$$ \mathit{bad\; smell\; if\;} M_c > VARL$$
+	Where,
 	\begin{equation}
@@
 		refactor their code until the bad smell thresholds are not violated.
-		This refactoring will start with some {\em initial} code
+		This code reorganization will start with some {\em initial} code
 		base that is changed to a {\em new} code base. 
@@
 		Also, it many not be practical
-		to assessing refactorings by making the
-		refactorings,  then seeing what happens to that code for the rest
+		to assessing code reorganizations by making the
+		code reorganizations,  then seeing what happens to that code for the rest
 		of the project. In a test-driven agile project, as
@@
 		how defective is the code before and after some
-		refactoring. 
+		code reorganization. 
 		For their second oracle,
@@
 		code attributes (out of 20). 
-		Any refactoring based on a bad smell detector that uses  these omitted code attributes could hence  be stopped.
+		Any code reorganization based on a bad smell detector that uses  these omitted code attributes could hence  be stopped.
 
@@
 		large classes class by into services
-		in other classes. Note that such a refactoring will, by
+		in other classes. Note that such a code reorganization will, by
 		definition, increase the coupling between objects. 
@@
 
-The results of this paper are biased by out choice of refactoring goal (reducing defects) and our choice
+The results of this paper are biased by our choice of code reorganization goal (reducing defects) and our choice
 of measures collected from software project (OO measures such as
@@
 		\section{Conclusions}
-		How to discourage useless refactorings?
+		How to discourage useless code reorganizations?
 		We say: ignore those not supported by the historical log of data from
@@
 			it hence {\em disapproves} of most changes. This makes it a better tool for critiquing and rejecting
-			many of the refactorings.
+			many of the code reorganizations.
 		\end{itemize}

### 2016-08-24 Manuscript.tex
Validity Section Update. Figures reorganized.

@@
 	we can generate and validate useful
-	changes to code modules. We focus on ``bad smells'' indicated by code metrics such as size and complexity as captured in popular tools such as SonarQube and Klocwerk [REF].
+	changes to code modules.
+We focus on ``bad smells'' indicated by code metrics such as size and complexity as captured in popular tools such as SonarQube and Klockwork\footnote{http://www.klocwork.com/}.
 
@@
 	exploring bad smells.
-
-	For consistency with Shatnawi, we explore the correlation between the code metrics and the defect counts and  reject code metrics that are poor predictors of defects (i.e.   those  with $p > 0.05$).
+For consistency with Shatnawi, we explore the correlation between the code metrics and the defect counts and  reject code metrics that are poor predictors of defects (i.e.
+those  with $p > 0.05$).
 
@@
 
-		\section{Threats to Validity}\label{sect:valid}
-
-The results of this paper are biased by our choice of code reorganization goal (reducing defects) and our choice
-of measures collected from software project (OO measures such as
-  depth of inheritance, number of child classes, etc).
-
-  That said, it should be possible extend the methods of this paper to other kinds of goals (e.g. maintainability, reliability, security,
-  or the knowledge sharing measures favoured by Bosu and Carver~\cite{bosu13}) and other kinds of inputs (e.g. the process measures favored by Rahman, Devanbu et al.\cite{Rahman2013})  as follows:
+\section{Reliability and Validity of Conclusions}
+\label{sect:valid}
+
+The results of this paper are biased by our choice of code reorganization 
+goal (reducing defects) and our choice of measures collected from software 
+project (OO measures such as depth of inheritance, number of child classes, 
+etc). That said, it should be possible extend the methods of this paper to other 
+kinds of goals (e.g. maintainability, reliability, security, or the knowledge sharing
+measures favoured by Bosu and Carver~\cite{bosu13}) and other kinds of 
+inputs (e.g. the process measures favored by Rahman, 
+Devanbu et al.~\cite{Rahman2013})
+
+\subsection{Reliability}
+Reliability refers to the consistency of the results obtained
+from the research. It has at least two components: internal
+and external reliability.
+
+Internal reliability checks if an independent researcher
+reanalyzing the data would come to the same conclusion. 
+To assist other researchers exploring this point, we offer a full replication package for this study at  
+https://github.com/ai-se/XTREE\_IST.
+
+External reliability assesses how well independent researchers
+could reproduce the study. To increase external
+reliability, this paper has taken care to clearly define our
+algorithms. Also, all the data used in this work is available
+online.
+
+For the research wishing to reproduce our work to other kinds of goals, we offer the following advice:
+
 \bi
@@
 \item Implement another secondary verification oracle that can assess maintainability, reliability, security, etc;
-\item Implement a better primary verification oracle that can do ``better'' that XTREE at finding changes (where ``better'' is defined in terms 
+\item Implement a better primary verification oracle that can do ``better'' than XTREE at finding changes (where ``better'' is defined in terms 
 of the opinions of the verification oracle).
 \ei
-To assist other researchers exploring these points, we offer a full replication package for this study at  https://github.com/ai-se/XTREE\_IST.
-
+
+\subsection{Validity}
+
+Validity refers to the extent to which a piece of research actually
+investigates what the researcher purports to investigate.
+Validity has at least three components: internal and
+external validity.
+
+\subsection{Internal Validity}
 The results of this paper are also specific to the data sets explored here.
@@
 
-		% Data mining is a large and active field and any single study can only use a small subset of the known classification algorithms.  
-		% That said, we have taken care to document in this paper the decisions made by engineering
-		% judgement that could effect our conclusions.
-
 		\section{Conclusions}

### 2016-08-31 Manuscript.tex
Updates from ShareLaTeX

@@
 
-		% \title{How to Discourage Useless Refactorings}
-		\title{Recommendations For Intelligent Code Reorganization}
+		\title{Recommendations for Intelligent Code Reorganization}
 
@@
 			\noindent
-			{\bf Method: } We introduce XTREE, a tool that analyzes a historical log of defects seen previously in the code and generates a set of useful\footnote{Need to define useful in precise terms} code changes.
+			{\bf Method: } We introduce XTREE, a tool that analyzes a historical log of defects seen previously in the code and generates a set of useful code changes.
 			Any bad smell that requires changes outside of that set can be deprioritized (since there is no historical evidence that the bad smell causes any problems).
@@
 			Before undertaking a code reorganization based on a bad smell report,
-			use a tool like XTREE to check and ignore any code reorganizations   that  are useless; i.e. which lacks evidence
+			use a tool like XTREE to check and ignore any such operations that  are useless; i.e. which lacks evidence
 			in the historical record  that it is useful to make that change.
 			Note that this use case applies to both manual code reorganizations proposed by developers
-			as well as refactoring  conducted by automatic methods.
+			as well as those conducted by automatic methods.
 			This recommendation assumes that there is an historical record.
@@
 
-	According to   Fowler ~\cite{fowler99}, bad smells (a.k.a. code smells)
+	According to   Fowler~\cite{fowler99}, bad smells (a.k.a. code smells)
 	are ``a surface indication that usually corresponds to a deeper problem''.
-	Fowler strongly recommends   removing   code smells   by
+	Fowler  recommends   removing   code smells   by
 	\begin{quote}
@@
 		of which seem ``too small to be worth doing''. 
-		The  effect of   these \underline{refactoring} transformations is quite significant. By doing them in small steps you reduce the risk 
+		The  effect of   these refactoring transformations is quite significant. By doing them in small steps you reduce the risk 
 		of introducing errors''.
@@
 
-	Bad smells are a widely used technique for evaluating code.
-While the original bad small concept was largely subjective~\cite{fowler99}, researchers including Marinescu~\cite{marinescu06} and others has provided formal definitions of ``bad smells'' in terms of static code attributes such size, complexity, coupling, and other metrics.
-Consequently, code smells are captured by popular static analysis tools such as PMD\footnote{https://github.com/pmd/pmd}, CheckStyle\footnote{http://checkstyle.sourceforge.net/}, FindBugs\footnote{http://findbugs.sourceforge.net/}, and SonarQube\footnote{http://www.sonarqube.org/}, although not always explicitly labeled as such.
-
-	Refactoring bad smells from code is generally accepted as a recommended practice, but code reorganization by definition does not change the external functionality of the system and thus may have no perceived value.
+% 	Bad smells are a widely used technique for evaluating code. 
+	While the original concept of bad smells was largely subjective, researchers including Marinescu~\cite{marinescu06} and Munro~\cite{munro2005product} provide definitions of ``bad smells'' in terms of static code attributes such size, complexity, coupling, and other metrics.
+Consequently, code smells are captured by popular static analysis tools such as PMD\footnote{https://github.com/pmd/pmd}, CheckStyle\footnote{http://checkstyle.sourceforge.net/}, FindBugs\footnote{http://findbugs.sourceforge.net/}, and SonarQube\footnote{http://www.sonarqube.org/}.
+
+	The value of correcting bad smells is not always perceivable.
 For example, this paper began when a Washington-based software company shared one of their management challenges with us: their  releases are delayed by developers spending  much time removing bad smells within their code.
-	%This management team wanted some way to check if all that activity was useful. 
-	Kim et al.\cite{kim2012field} surveyed developers at Microsoft and found that refactoring incurs significant cost and risks.
-A Google search on the terms ``refactoring cost'' yields numerous threads on StackOverlfow from developers asking how to justify refactoring and when the costs of refactoring outweight its benefits.
+Kim et al.~\cite{kim2012field} surveyed developers at Microsoft and found that code reorganizations incur significant cost and risks.
+Researchers are actively attempting to demonstrate the actual costs and benefits of fixing bad smells~\cite{nugroho2011empirical,zazworka2011prioritizing,zazworka2013case}, though more case studies are needed.
+
+			We refer to the process of removing bad smells as \textit{code reorganization}.
+Code reorganization is an amalgum of perfective and preventive maintenance~\cite{iso14764}.
+In contrast to refactoring, code reorganization is not guaranteed to preserve behavior.
+
+	Fowler~\cite{fowler99} and other influential software practitioners~\cite{mcconnell2004code,horror} recommend refactoring and code reorganization to remove bad smells.
+Experiments suggest a relationship between code smells and poor maintainability or defect proneness~\cite{yamashita2013code,yama13,zazworka2011investigating}, though these findings are not always consistent~\cite{olbrich2010all}.
+In this paper, we focus on the challenge of recommending code reorganizations that result in perceivable benefits (such as reduced defect proneness) and avoid those reorganizations which have no demonstrable benefit and thus waste effort.
+
+	%A Google search on the terms ``refactoring cost'' yields numerous developer questions on StackOverflow asking how to justify bad smell removal and when the costs outweigh the benefits.
 
@@
 	% Hence, the management goal
-	The challenge is to encourage code reorganizations that result in perceivable benefits (such as reduced defect proneness or lower maintenance costs) and avoid code reorganizations with no demonstrable benefit and thus waste effort.
-
-	This paper describes one approach to evaluate whether code reorganizations that change the structure of code are likely to have a perceivable benefit by evaluating:
-	\bi
-	\item If there is no evidence in the historical record that changing ``X'' is useful;
-	\item Then discourage developers from doing ``X''.
-	\ei
+
+	This paper evaluates XTREE~\cite{krishna2015actionable}, a framework to evaluate whether a code reorganization is likely to have a perceivable benefit in terms of defect-proneness.
+We focus on bad smells indicated by code metrics such as size and complexity as captured in popular tools such as SonarQube and Klockwork\footnote{http://www.klocwork.com/}.
+		XTREE examines the historical record of code metrics for a project.
+If there is no evidence that changing code metric ``X'' is useful (e.g., lowering ``X'' reduces defect-proneness), then developers should be discouraged from wasting effort on that change.
+	% 	\bi
+% 	\item If there is no evidence in the historical record that changing ``X'' is useful;
+% 	\item Then discourage developers from doing ``X''.
+% 	\ei
+
 	We use data mining to generate two oracles: a {\em primary
@@
 	By combining these two oracles,
-	we can generate and validate useful
-	changes to code modules.
-We focus on ``bad smells'' indicated by code metrics such as size and complexity as captured in popular tools such as SonarQube and Klockwork\footnote{http://www.klocwork.com/}.
-
-	In this paper, we use 
+	we can identify and validate useful
+	code reorganizations.
+
+	We use 
 	the XTREE cluster delta algorithm as the {\em primary change  oracle}.
 	XTREE 
-	explores the historical record of a project to find clusters of module.
+	explores the historical record of a project to find clusters of modules (e.g., files or binaries).
 	It then proposes a ``minimal'' set of changes $\Delta$ that can move a software module $M$ from a defective cluster $C_0$ to another with fewer defects $C_1$ (so $\Delta$
@@
 
-	As to 
-	the {\em secondary verification oracle}, this  checks if the primary oracle is proposing
-	sensible changes. For this purpose we use Random Forest~\cite{breiman2001random}, augmented with SMOTE (synthetic  minority over-sampling technique~\cite{chawla2002smote}).
+	The {\em secondary verification oracle} checks if the primary oracle is proposing
+	sensible changes. We create the verification oracle using Random Forest~\cite{breiman2001random} augmented with SMOTE (synthetic  minority over-sampling technique~\cite{chawla2002smote}).
 	In our framework,  learning
@@
 
-	When these oracles were applied to defect data from
-	open source object-oriented software systems, we discovered a {\em conjunctive fallacy}
-	in the bad smell literature~\cite{erni96,bender99,Shatnawi10,Alves2010,hermans15}.
-	A common heuristic is to recommend code reorganization of ``bad'' code
-	to make it ``better'' as follows: for all static code measures that exceed some threshold, make changes such that the thresholds are no longer exceeded. That is:
+	An advantage to the XTREE cluster delta approach is that it avoids the 
+% 	When these oracles were applied to defect data from
+% 	open source object-oriented software systems, we discovered a 
+	{\em conjunctive fallacy}.
+	A common heuristic in the bad smell literature~\cite{erni96,bender99,Shatnawi10,Alves2010,hermans15} is: for all static code measures that exceed some threshold, make changes such that the thresholds are no longer exceeded.
+That is:
 	\begin{equation}\label{eq:df}
@@
 	We say that the above definition of ``better'' is a conjunctive fallacy
-	since it assumes that the best way to improve code is to decreases multiple code attribute measures below $t_i$ in order
-	to remove the ``bad'' smells. In reality, there exists an intricate set of associations between static code measures
-	such that {\em decreasing}  $a_i$ necessitates {\em increasing} $a_j$.
+	since it assumes that the best way to improve code is to decreases multiple code attribute measures to below $t_i$ in order
+	to remove the ``bad'' smells. In reality, the associations between static code measures are more intricate, for example,
+	such that {\em decreasing}  $a_i$ may necessitate {\em increasing} $a_j$.
 	It is easy to see why this is so.
-	A requirement for  code reorganization is that the new code supports the same functionality
-	as before. If we pull code out of a function (since that function has grown too
-	large), {\em that functionality has to go somewhere else}. What we see in XTREE's change
-	recommendation is that if we decrease a module's lines of code  then in the refactored
-	code, the functionality is achieved via a communication between several different parts
-	of the system. That is, {\em decreasing} the lines of code metric within a module {\em increases}
-	that module's coupling metrics.
-
-	\subsection{Structure of this Paper}
-
-	This paper  claims that (a)~XTREE is a  better way than \eq{df}  to define useful changes to software and (b)~those changes are useful for recognizing   superfluous code reorganizations since they usually refer to a very
-	small subset of the static code measures (which allows us to rule out code reorganizations based on any of the omitted
+% 	A requirement for  code reorganization is that the new code supports the same functionality
+% 	as before. 
+	For example, Fowler recommends that the Large Class smell be addressed by the Extract Class or Extract Subclass refactoring~\cite{fowler99}.
+If we pull code out of a function since that function has grown too
+	large, that functionality has to go somewhere else.
+Thus, when \textit{decreasing} lines of code in one module, we may \textit{increase} its coupling to another module.
+XTREE's identifies such associations between metrics, thus avoiding the conjunctive fallacy.
+% 	recommendation is that if we decrease a module's lines of code  then in the reorganized
+% 	code, the functionality is achieved via a communication between several different parts
+% 	of the system. That is, {\em decreasing} the lines of code metric within a module {\em increases}
+% 	that module's coupling metrics.
+
+	\subsection{Research Questions}
+
+	This paper  claims that (a)~XTREE is more useful than \eq{df} to identify code reorganizations, and (b)~XTREE recommends a small subset of static code measures to change and thus can be used to identify superfluous code reorganizations (i.e., reorganizations based on omitted
 	static code measures).
-	In support of these claims, 
-	the rest of this paper is structured as follows. In Section~2, we offer some background on bad smells. In Section~3, 
-	different methods are presented for determining when code does/does not have bad smell. One of those methods
-	will be XTREE while the others will come from other researchers. Section~4
-	defines an assessment method that checks which of these methods is most useful. The results from that assessment 
-	are presented in Section~5. Those results will answer five research questions.
-
-	{\bf  RQ1: Effectiveness}\footnote{test}: According to the verification oracle, which of the methods  defined in Section~3 is the best  change oracle for identifying what and how
-	code modules should be changed? To answer this question, we used data from five OO Java projects
+To evaluate these claims, we compared the performance of XTREE with three other methods for recommending code reorganizations~\cite{Shatnawi10,Alves2010,me12c} according to the following research questions:
+
+% 	In support of these claims, 
+% 	the rest of this paper is structured as follows. In Section~2, we offer some background on bad smells. In Section~3, 
+% 	different methods are presented for determining when code does/does not have bad smell. One of those methods
+% 	will be XTREE while the others will come from other researchers.
+Section~4 contains the methods used in this study, the results of which are shown in  .
+Those results will answer five research questions.
+
+	{\bf  RQ1: Effectiveness}: According to the verification oracle, which of the methods is most accurate in recommending code reorganizations that result in reduced numbers of defective files? 
+% 	is the best  change oracle for identifying what and how	code modules should be changed? 
+To answer this question, we used data from five OO Java projects
 	(Ivy, Lucene, Ant, Poi, Jedit). It was found that:
 	\begin{lesson}
-		XTREE is the most accurate oracle on how to change code modules in order to reduce defects.
+		XTREE is the most accurate oracle on how to change code modules in order to reduce the number of defective files.
 	\end{lesson}
@@
 	{\bf RQ2: Succinctness}: Our goal is to critique and, possibly,
-	ignore irrelevant bad smell detectors.  If those changes are minimal (i.e. affect fewest attributes) then those changes
-	will be easiest to apply and monitor. Hence, we ask, which of the Section~3 methods recommended changes to the fewest
+	ignore irrelevant bad smell detectors.  If the recommended changes are minimal (i.e. affect fewest attributes) then those changes
+	will be easiest to apply and monitor. Which method recommends changes to the fewest
 	code attributes?
 	\begin{lesson}
-		Of all the code change oracles studied here, XTREE recommends the fewest number of changes to static code measures.
+		Of all the code change oracles studied, XTREE recommends changes to the fewest number of static code measures.
 	\end{lesson}
 
-	{\bf RQ3: Stopping}: Our advice to managers is to discourage code reorganization based on changes that lack
-	historical evidence of being effective. How effective is XTREE at offering such ``stopping points'' (i.e. clear guidance on what {\em not} to do)??
+	{\bf RQ3: Stopping}: Our goal is to discourage code reorganization based on changes that lack
+	historical evidence of being effective. How effective is XTREE at identifying what {\em not} to change?
 	\begin{lesson}
-		In  any  project,  XTREE's  recommended  changes  only  mentions one to four 
+		In  any  project,  XTREE's  recommended  changes  to 1--4 
 		of the  static code attributes.  Any bad smell defined in terms of the remaining 19 to 16 code attributes (i.e. most of them)
@@
 
-	{\bf RQ4: Stability}: Across different projects, how variable are the changes recommended by our best change oracle?
+	{\bf RQ4: Stability}: Across different projects, how consistent are the changes recommended by our best change oracle?
 	\begin{lesson}
-		The direction of change recommended by XTREE is  very stable across repeated runs of the program 
+		The direction of change recommended by XTREE (e.g., to LOWER lines of code while RAISING coupling) is stable across repeated runs of change oracle.  
 	\end{lesson}
@@
 	{\bf RQ5: Conjunctive Fallacy}:  
-	Is it always  useful  to aplly \eq{df}; i.e. make code better by   reducing the values of  multiple code attributes? We find that:
+	Is it always  useful  to apply \eq{df}; i.e. make code better by   reducing the values of  multiple code attributes? We find that:
 	\begin{lesson}
@@
 	confirms the intuitions
-	of the project managers that prompted this investigation:
+	of the project managers that prompted this investigation. We find evidence that:
 	\bi
-	\item
-	Yes,  indeed, their programmers
-	were wasting time on   performing code reorganizations  that  decreased multiple measures when, in fact,
-	they should be trying to {\em decrease} some measures while {\em increasing} others.
-	\item
-	Across all studied projects, XTREE found that  around one-fifth  
-	of the measures were usually found within  change recommendations. That is, it is 80\% likely that
-	that code reorganization based on reducing any one measurement picked at random will be useful.
+	\item Code reorganizations that decrease multiple measures may not yield improvement, In fact,  programmers may need to {\em decrease} some measures while {\em increasing} others.
+    \item In the studied projects, XTREE recommends changes to approximately 20\% of the code measures, and thus reorganizations based on the remaining 80\% are unlikely to provide benefit.
     \ei
+%     one-fifth  
+% 	of the measures were usually found within  change recommendations. That is, it is 80\%\footnote{Isn't it 20\% likely that you will find a useful measurement?} likely that
+% 	that code reorganization based on reducing any one measurement picked at random will be useful.
+%     \ei
+% 	\bi
+% 	\item
+% 	Yes,  indeed, their programmers
+% 	were wasting time on   performing code reorganizations  that  decreased multiple measures when, in fact,
+% 	they should be trying to {\em decrease} some measures while {\em increasing} others.
+% 	\item
+% 	Across all studied projects, XTREE found that  around one-fifth  
+% 	of the measures were usually found within  change recommendations. That is, it is 80\% likely that
+% 	that code reorganization based on reducing any one measurement picked at random will be useful.
+% 	\ei
 	Consequently, we  recommend the following use case for  XTREE:
@@
 	This use case described  applies to both manual code reorganizations proposed by developers
-	as well as refactoring conducted by automatic methods~\cite{mkaouer2015many}. That is, XTREE could optimize automatic
-	code refactoring by discouraging refactorings for useless goals.
+	as well as the code reorganizations conducted by automatic methods~\cite{mkaouer2015many}. That is, XTREE could optimize automatic
+	code reorganization by discouraging reorganizations for useless goals.
 
 	\subsection{Relationship to Prior Work }
-	A four page preliminary report on the XTREE system~\cite{krishna2015actionable} has been presented previously\footnote{https://goo.gl/2In3Lr}. That short report offered case studies on only two  of
-	the five data sets studied here. Also, that prior work had:
+	A four page preliminary repor\footnote{https://goo.gl/2In3Lr}t on the XTREE system has been presented previously~\cite{krishna2015actionable}. That short report offered case studies on only two  of
+	the five data sets studied here. We greatly expand on this prior work by:
 	\bi
 	\item
-	no comparison to any baseline
-	method from other researchers, whereas this paper compares XTREE's recommendations
-	with those found by researchers exploring bad smells.
+	Evaluating XTREE's recommendations against recommendations from three others methods by researchers exploring bad smells.
 	\item
-	no {\em secondary verification oracle}, i.e. no way to check if XTREE's recommended changes were sensible.
+	Evaluating if XTREE's and other methods' recommended changes were sensible using the {\em secondary verification oracle}
 	\ei
-	Further, of this entire paper, the only sections containing material
-	found in prior papers is 3.2.1, 3.2.2 as well as two-fifths of the results in \fig{jur}.
+	Only sections 3.2.1, 3.2.2, and two-fifths of the results in \fig{jur} contain material
+	found in prior papers.
 
@@
 
-	Much research endorses them to guide
+	Much research endorses code smells as a guide for
 	code improvement (e.g., code reorganization or preventative maintenance). A recent literature review by Tufano et al.~\cite{Tufano2015}  
@@
 	are consistent with other research suggesting that universal bad
-	smells that ignore project context are not useful to guide refactoring~\cite{Mantyla2004,Yamashita2013,Sjoberg2013}.
+	smells that ignore project context are not useful to guide code reorganizations~\cite{Mantyla2004,Yamashita2013,Sjoberg2013}.
 
@@
 Even when the evidence for or against a treatment or intervention is clear, medical providers and patients may not accept it~\cite{aschwanden10}.
-Aschwanden warns that {\em cognitive biases} such as confirmation bias (the tendency to look for evidence that supports what you already know and to ignore the rest) influence how we process information~\cite{aschwanden15}.
+Aschwanden~\cite{aschwanden15} warns that {\em cognitive biases} such as confirmation bias (the tendency to look for evidence that supports what you already know and to ignore the rest) influence how we process information.
 
@@
 	Devanbu et al. further  comment that ``programmers give personal experience
-	as the strongest influence in forming their opinions''. This is a troubling
-	result, especially given the above comments from Passos and  J{\o}rgensen et al.~\cite{passos11,jorgensen09} about how quickly practitioners form, freeze, and rarely revist those opinions.
+	as the strongest influence in forming their opinions''. This is troubling
+	especially given the comments from Passos and J{\o}rgensen et al.~\cite{passos11,jorgensen09} about how quickly practitioners form, freeze, and rarely revisit those opinions.
 
@@
 	columns show data from other studies on which bad smells matter most.
-	The columns marked as Lanza'06 and Yamashita'13 are from peer reviewed literature. The column maked SonarQube is a popular open source
+	The columns marked as Lanza'06 and Yamashita'13 are from peer reviewed literature. The column marked SonarQube is a popular open source
 	code assessment tool that includes detectors for six of the bad smells
@@
 	A  blank cell in \fig{smells}
-	indicates where   other work has chosen to ignore
+	indicates where   other work omits 
 	one of the bad smells in column one. 
-	Note that most of the cells are blank, and that the studies ignore the majority of the Fowler bad smells.
+	Note that most of the cells are blank, and that the studies omit the majority of the Fowler bad smells.
 	SonarQube has no detectors for many of the column one bad smells.
 	Also, nearly half the Yamashita list of bad smells
-	does not appear in the Fowler and Kerievsky list. The eight numbers
+	does not appear in column 1. The eight numbers
 	in the  Yamashita'13 column show the rankings for the bad smells 
-	that overlap with Fowler and Kerievsky; Yamashita also discussed other smells not covered in Fowler'99.
+	that overlap with Fowler and Kerievsky; Yamashita also discussed other smells not covered in Fowler'99~\cite{fowler99}.
 
 	Two of the studies in \fig{smells} offers some comments on the relative importance
-	of the different bad smells in the Yamashita'13 study and the developer study.
+	of the different bad smells.
 Three of the bad smells listed in the top half of the Yamashita'13 rankings also score very high in the developer survey.
@@
 
-	Having made the case for automatic support for assessing bad smells,
+	Having made the case for automated, evidence-based support for assessing bad smells,
 	this section reviews different ways for building those tools (one of those tools,
 	XTREE, will be our recommended {\em primary change oracle}).
-	Later in this paper, we will offer  a {\em secondary verification oracle}
-	that checks the effectiveness of the changes proposed by XTREE.
+	Later in this paper, we describe  a {\em secondary verification oracle}
+	that checks the effectiveness of the proposed changes.
 
@@
 	{\em outlier statistics}~\cite{erni96,bender99}. This approach
-	has been used   by Shatnawi~\cite{Shatnawi10}, Alvenes et al.~\cite{Alves2010}
+	has been used   by Shatnawi~\cite{Shatnawi10}, Alves et al.~\cite{Alves2010}
 	and Hermans et al.~\cite{hermans15}.
@@
 	The literature lists several ways to define ``unusually large''.
-
-	\input{xtree_tut.tex}
 
@@
 
-	\subsubsection{ Shatnawi}
+	\subsubsection{ Shatnawi}\label{sect:shatnawi}
 	Shatnawi~\cite{Shatnawi10}'s preferred alternative to $\mu+\sigma$
@@
 
+	\input{xtree_tut.tex}
 	VARL encodes the defect count
@@
 	to finding thresholds that  utilizes the underlying statistical distribution and scale of the metrics. 
-	Metric values for each class are weighted according to the source lines of code (SLOC) of the class. All the weighted metrics are then normalized by the sum of all weights of for the system. 
+	Metric values for each class are weighted according to the source lines of code (SLOC) of the class. All the weighted metrics are then normalized by the sum of all weights for the system. 
 	The normalized metric values are ordered in an ascending fashion (this is equivalent to computing a density function, in which the x-axis represents the weight ratio (0-100\%), and the y-axis the metric scale).
@@
 For consistency with Shatnawi, we explore the correlation between the code metrics and the defect counts and  reject code metrics that are poor predictors of defects (i.e.
-those  with $p > 0.05$).
+those  with $p > 0.05$).\footnote{I still do not understand the reference to Shatnawi at the end of this paragraph on Alves.
+Are you doing some correlation using the Alves criteria?}
 
@@
 	generate {\em conjunctions} of code metrics
-	that need to be changes at the same time
+	that need to be changed at the same time
 	in order to reduce defects~\cite{me12c}.
-	CD used the WHERE clustering algorithm developed by the
+	CD uses the WHERE clustering algorithm developed by the
 	authors for a prior application~\cite{localvsglobal}.
@@
 
-	As shown below, one drawback with with CD is that it is {\em verbose}
+	One drawback with with CD is that it is {\em verbose}
 	since
@@
 
-	\subsubsection{XTREE: Overview}
+	\subsubsection{XTREE: Mining Project History for Defect-Proneness Attributes}
 
@@
 	\begin{itemize}
-		\item A code metric is split into $r$ ($r=2$) ranges, each range is of
-		size $n_r$ and is associated with a set of defect counts $x$ with standard deviation
+		\item A code metric is split into $r$ ($r=2$)\footnote{Why do you select r=2?} ranges, each range is of
+		size $n_r$ and is associated with a set of defect counts $x_r$ with standard deviation
 		$\sigma_r$. 
@@
 		\item This discretizer then recurses on each part of the split to find other splits in a recursive fashion.
-As suggested by Fayyad and Irani, minimum descriptor length (MDL) is used as a termination criterion for the recursive partitioning.
+As suggested by Fayyad and Irani, minimum description length (MDL) is used as a termination criterion for the recursive partitioning.
 	\end{itemize}
@@
 
-	\subsubsection{XTREE:   Details}
+	\subsubsection{XTREE: Recommending a Code Reorganizations}
 
@@
 		\item Identify {\em sibling} leaves; i.e. leaf clusters that can be reached from level $lvl$ that are not same as {\em current $C_+$};
-		\item Find the {\em better} siblings; i.e. those 50\% (or less)
-		fewer defects than $C_+$. If none found, then repeat for $lvl += 1$. Also, return \texttt{nil} if the new $lvl$ is above the root. 
-		\item  Set $C_-$ to the  {\em closest} better sibling where distance is measured between the mean centroids of that sibling and {\em current}
+		\item Find the {\em better} siblings; i.e.
+those with defect proneness 50\% or less than that of $C_+$ (e.g., if defect-proneness of $C_+$ is 70\%, find the nearest sibling with defect proneness $\leq$ 35\%).
+If none found, then repeat for $lvl += 1$.
+Also, return \texttt{nil} if the new $lvl$ is above the root.
+		\item  Set $C_-$ to the  {\em closest} better sibling where distance is measured between the mean centroids of that sibling and {\em $C_+$}
 		\ei
@@
 		on the set difference between  conditions in the decision tree branching from $C_+$ to $C_-$. To find that delta,
-		for discrete attributes, delta is the value of the {\em desired}; for numerics  expressed as ranges, the delta could be any value that lies between $\left[ LOW, HIGH\right]$ in that range (random number selected from the low and high boundaries of the that range.)
+		for discrete attributes, delta is the value of the {\em desired}; for numerics  expressed as ranges, the delta could be any value that lies between $\left[ LOW, HIGH\right]$ in that range (for example, a random number selected from the low and high boundaries of the that range.\footnote{Please justify why you select a random value.
+random selection.
+My footnote from an earlier version has not been addressed and at least needs to be a limitation of XTREE: defect proneness.
+PRevious footnote: This could lead to conflicting recommendations in different runs of XTREE, right?
+Consider Figure 3.
+Suppose C+ has cbo=(27.00,157.00):1.00.
+XTREE ascends one level and descends to the leaves of next subtree.
+XTREE suppose that C" is a leaft where cbo=(1.00,50:00):0.15 (instead of cam as in Figure 3).
+By selecting something random in the range, you could recommend either an increase or a decrease to CBO.
+I would think that this is an instance where XTREE should say 'I don’t know what to do with CBO, but you should improve LCOM.' Alternately, if you took the median value (instead of random) and compared, you could at least recommend a direction, i.e., ``the best benefits come from REDUCING lcom while maintaining a LOWER cbo'')}
+
+		Note that XTREE's recommendation does not exhaustively search the tree for the change that reduces defect proneness the most, but rather finds the nearest sibling.
+This is by design.
+This design allows XTREE to a) provide recommendations quickly, and b) to recommend changes to a small number of attributes.
 
 		\input{prediction_stats.tex}      
-		\section{Evaluation}
+		\section{Setup}
 		The previous section proposed numerous methods for detecting bad smells that need
-		to be resolved. This section offers an experiment of the following form:
+		to be resolved. This section offers a way to evaluate them as follows:
 		\bi
-		\item Using each method as a {\em primary change oracle} to recommend how code should be changed.
-		\item Apply those changes. 
-		\item Run a {\em secondary verification oracle} to assess the defect-proness of the changed code.
-		\item Sort the change oracles on how well they reduce defects (as judged by the verification oracle).
+		\item Use each method as a {\em primary change oracle} to recommend how code should be changed in our test data set (Section~\ref{sect:tesd}).
+		\item Apply those changes. (This is emulated by changing the code metrics in order that all the $\Delta$'s are addressed.)
+		\item Run a {\em secondary verification oracle} to assess the defect-proneness of the changed code.
+		\item Sort the change oracles on how well they reduce defects as judged by the verification oracle.
 		\ei
-		Using this experiment, we can address the research questions dicsussed in the introduction.
-
-		{\bf RQ1: Effectiveness: } which of the methods defined in Section 3 is the best change oracle for identifying what and how code modules should be changed? 
-		To   answer to this question, we will assume that developers
-		refactor their code until the bad smell thresholds are not violated.
+		Using this, we can address the research questions discussed in the introduction.
+
+		{\bf RQ1: Effectiveness: } Which of the methods defined in Section 3 is the best change oracle for identifying what and how code modules should be changed? 
+		we will assume that developers
+		update and reorganize their code until the bad smell thresholds are not violated.
 		This code reorganization will start with some {\em initial} code
-		base that is changed to a {\em new} code base. 
-		For example, if the bad smell is \mbox{{\em loc $>100$}} and a 
+		base that is changed to a {\em new} code base. For example, if the bad smell is \mbox{{\em loc $>100$}} and a 
 		code module has 500 lines of code, we reason
 		optimistically that we can change that code metric
-		to 100.  
-		Using the secondary verification oracle,  we then predict the
-		number of defects in $d_+,d_-$ in {\em initial} and {\em new}. We evaluate the performance of XTREE, CD, Shatnawi, and Alves methods in setting bad smell thresholds.
-		The best bad smell threshold method is the one that maximizes
+		to 100.  Using the secondary verification oracle,  we then predict the
+		number of defective files in {\em new}.
+
+		We compare $d_+$, the number of defective files in the \textit{initial} code base to $d_-$, the number of defective files in the \textit{new} code base.
+		We evaluate the performance of XTREE, CD, Shatnawi, and Alves change oracles in methods. The best change oracle is the one that maximizes
 		\begin{equation}\label{eq:diff}
@@
 
-		{\bf RQ2: Succinctness: } which of the Section 3 methods recommended changes to the fewest code attributes?
+		{\bf RQ2: Succinctness: } Which of the Section 3 methods recommended changes to the fewest code attributes?
 		To answer this question, we will report the frequency at which different attributes are selected in repeated runs of our oracles.
@@
 		Note that the {\em more often} XTREE omits an attribute, the more likely it is {\em not} to endorse a bad smell based on the omitted
-		attribites.
+		attributes.
 
@@
 To answer this question, we will look at the {\em direction of change} seen in the {\bf RQ4} study; i.e.
-		how often does XTREE recommend decreasing or increasing a static code attribute.
+		how often XTREE recommends decreasing or increasing a static code attribute.
 
@@
 
-		To explore these research questions,
-		we used data from
-		Jureczko et al.'s collection of object-oriented Java systems~\cite{jureczko10}. To access that data, go to   git.io/vGYxc.
+		To explore these research questions, we used data from Jureczko et al.'s collection of object-oriented Java systems~\cite{jureczko10}. To access that data, go to   git.io/vGYxc.
 		The Jureczko data records the number of known defects for each class using a post-release bug tracking system.
@@
 For details on the Jureczko code
-		metrics, see  \fig{ck}. For details on the rows and versions
-		of that data, see the left-hand-side columns of \fig{jur}.
-
-		\subsection{Secondary verification Oracles}
+		metrics, see  \fig{ck}. For details on the rows and versions of that data, see the left-hand-side columns of \fig{jur}.
+
+		\subsection{Building the Secondary Verification Oracle}
 		\label{sect:eval}
@@
 		It can be difficult  to judge the  effects of removing bad smells.
-		Refactored code cannot be assessed just by a rerun of the the test
-		suite (since refactorings are supposed to preserve behavior). 
+		Code that is reorganized cannot be assessed just by a rerun of the the test
+		suite since such reorganizations may not change the system behavior (e.g., refactorings). 
+		%Further, a test suite may not be available or the compilation environment reproducible. 
 		% waiting to observe 
@@
 		% should pass before and after the refactoring). 
-		Also, it many not be practical
-		to assessing code reorganizations by making the
-		code reorganizations,  then seeing what happens to that code for the rest
-		of the project. In a test-driven agile project, as
-		SCRUM meetings change what stories are implemented next,
-		the operational profile that lead to defects in the old
-		code may not be repeated in future executions.
+% 				Also, it many not be practical
+% 		to assessing code reorganizations by making the
+% 		code reorganizations,  then seeing what happens to that code for the rest
+% 		of the project. In a test-driven agile project, as
+% 		SCRUM meetings change what stories are implemented next,
+% 		the operational profile that lead to defects in the old
+% 		code may not be repeated in future executions.
 
@@
 		Moghadam~\cite{Moghadam2011} and Mkaouer et al.~\cite{Mkaouer14}
-		use a {\em secondary verification oracle} (which is learned separately
-		to the primary oracle) that   assesses
+		use a {\em secondary verification oracle} that is learned separately
+		from the primary oracle. The verification oracles assesses
 		how defective is the code before and after some
@@
 		from OO code metrics.
-		Note that, unlilke QMOOD, such measurements 
-		are specific to the project, and the measurements can be reconstructed and the predictors rebuilt for other projects.
+		Unlike QMOOD, the predictors 
+		are specific to the project.
+% 		, and the measurements can be reconstructed and the predictors rebuilt for other projects.
 
@@
 
-		\fig{j} shows   studies with Random Forests and
+		\fig{j} shows  our experiments with Random Forests and
 		the Jureczko data.
-Given   $V$ released versions, we test on version $V$ and train on the available data from $V-1$ earlier releases (as shown in \fig{j}.
+The goal is to build a verification oracle based on Random Forest that accurately distinguishes between defective and non-defective files based on code metrics.
+Given $V$ released versions, we test on version $V$ and train on the available data from $V-1$ earlier releases.
 Note the   \colorbox{lavenderpink}{three bottom rows}   marked with $\times$: these contain predominately defective classes (two-thirds, or more).
-In such data, it is hard to distinguish good examples (due to all the bad examples).
-
-		In order to identify the presence (or absence) of defects, we can   use Boolean classes in the  Jureczko data ( \texttt{True} if defects \textgreater 0; \texttt{False} if defects = 0).
-For such data, the quality of the predictor can be measured using (a) the  probability of detection (a.k.a.
-``pd'' or recall):  the percent of faulty classes in the test data detected by the {\em predictor}; and (b) the  probability of false alarm (a.k.a.
-``pf''): the percent of non-fault classes that are {\em predicted} to be defective.
+It is hard to build a model that distinguishes non-defective files from defective files in these data sets due to the high percentage of defective file examples.
+
+		We use Boolean classes in the  Jureczko data to identify the presence or absence of defects: \texttt{True} if defects \textgreater 0; \texttt{False} if defects = 0.
+The quality of the predictor is measured using (a) the  probability of detection \textit{pd} (i.e., recall):  the percent of faulty classes in the test data detected by the {\em predictor}; and (b) the  probability of false alarm \textit{pf} (i.e., false positives): the percent of non-fault classes that are {\em predicted} to be defective.
 
 		The ``untuned'' columns of \fig{j}
-		show a preliminary study. This study used
-		Random Forest with its ``off-the-shelf'' tunings (i.e.  
-		100 trees per forest).  
+		show a preliminary experiment using Random Forest with its ``off-the-shelf'' tuning of 100 trees per forest.  
 		The forests were built from training data and applied to test data
@@
 an over-sampling of minority-class examples and an under-sampling of majority-class examples.
-Fu et al.~\cite{fu:ase15} report that parameter tuning with differential evolution~\cite{storn97} can quickly explore the tuning options of Random Forest to find better settings for the (e.g.) size of the forest, the termination criteria
-		for tree generation, etc. We note that SMOTE-ing and
+Fu et al.~\cite{fu:ase15} report that parameter tuning with differential evolution~\cite{storn97} can quickly explore the tuning options of Random Forest to find better settings for the size of the forest, the termination criteria
+		for tree generation, and other settings. We note that SMOTE-ing and
 		parameter tunings were applied to the training data only and not to the test data.
@@
 		We eliminate the data sets for which we could not build an adequately performing Random Forest classifier with $\mathit{pd}\ge 60 \wedge \mathit{pf} \le 30$\%.
-Thus, our analysis uses the {\em jedit, ivy, ant, lucene} and {\em poi} for evaluating recommended changes.
+Thus, our analysis uses the {\em jedit, ivy, ant, lucene} and {\em poi} data sets for evaluating recommended changes.
 
@@
 
-		We use 40 repeated runs, each with different random number seeds (we use 40 since that is  more than the 30 samples  needed to satisfy the central limit theorem).
-Each run collects the \eq{diff} values.
-		We use multiple runs since two of our methods use some random choices: CD uses the  stochastic WHERE clustering algorithm~\cite{localvsglobal}
+		We use 40 repeated runs for each code reorganization recommendation method for each of the five data sets (we use 40 since that is  more than the 30 samples  needed to satisfy the central limit theorem).
+Each code organization method is trained on versions $1...N-1$ of $N$ available versions in each data set.
+		Each run collects the improvement scores defined in \eq{diff}: the reduction in the percentage of defective files as identified by the verification oracle after applying the recommended code metric changes.
+
+		We use multiple runs with different random number seeds since two of our methods use some random choices: CD uses the  stochastic WHERE clustering algorithm~\cite{localvsglobal}
 		while XTREE non-deterministically picks thresholds randomly from
@@
 		The Scott-Knott  results are presented in the form of line diagrams like those shown on the right-hand-side of \fig{jur}.
-		The black dot shows the median \eq{diff} values and the horizontal lines stretch 
-		from the 25th percentile to the 75th percentile (the inter-quartile range, IQR).
+		The black dot shows the median \eq{diff} values and the horizontal lines stretches 
+		from the 25\textsuperscript{th} percentile to the 75\textsuperscript{th} percentile (the inter-quartile range, IQR). 
 		As an example of how to read this table, consider the {\em Ant}
@@
 Note that all the methods have \eq{diff} \textgreater $ 0\%$; i.e.
-all these methods reduced the expected value of the performance score in that experiment while XTREE achieved the greatest reduction (of 56\% from the original value).
+all these methods reduced the expected value of the performance score while XTREE achieved the greatest reduction (of 56\% from the original value).
 		These results table has a  left-hand-side  {\bf Rank} column, computed using the
@@
 				While \fig{counts} are the {\em number} of times a code metric was changed,
-				this  figure shows {\em how far} each code metric was changed. Each vertical bar
-				marks the 27,50,75th percentile change seen in 40 repeats.
+				this  figure shows the {\em magnitude} each code metric was changed. Each vertical bar
+				marks the 27,50,75\textsuperscript{th} percentile change seen in 40 repeats.
 				All numbers are ratios of initial to final values.
@@
 
-		{\em Which of the methods defined in Section 3 is the best change oracle for identifying what and howcode modules should be changed? }
-
-		\fig{jur} shows the comparison results.  The Alves and Shatnawi
-		entries show the net effects of applying \eq{df} where the $t_i$ values were found by Alves and Shatnawi.
-		In this part of the  analysis,
-		we applied Scott-Knott to all the \eq{diff} values
-		seen when code metrics were changed
-		according to the  Alves and Shatnawi
-
+		{\em Which of the methods defined in Section 3 is the best change oracle for identifying what and how code modules should be changed? }
+
+		\fig{jur} shows the comparison results.  
+% 		The Alves and Shatnawi
+% 		entries show the net effects of applying \eq{df} where the $t_i$ values were found by Alves and Shatnawi.
+% 		In this part of the  analysis,
+% 		we applied Scott-Knott to all the \eq{diff} values
+% 		seen when code metrics were changed
+% 		according to the  Alves and Shatnawi
 		Two data sets are very responsive to defect reduction suggestions:
@@
 		find the same ways to reduce the expected number of
-		defects.   For an explanation of the Jedit uniformity, see \tion{inc}.
+		defects.   For an explanation of the Jedit uniformity, see \tion{inc}\footnote{Broken reference?}.
 
@@
 
-		In summary, our {\bf Result1} is  that, of the change orcales studies here,
-		XTREE is the best oracle on how to change code modules (in order to reduce defects).
+		In summary, our {\bf Result1} is  that, of the change oracles studies here,
+		XTREE is the best oracle on how to change code modules in order to reduce defects in our data sets.
 
@@
 		\fig{counts} counted how {\em often} XTREE's recommendations mentioned a static code attribute.
-		\fig{changes}, on the other hand, shows the {\em direction} of the recommended change:
+		\fig{changes}, on the other hand, shows the {\em direction} of XTREE's recommended change:
 		\bi
 		\item Gray bars show  an  {\em increase} to a static code measure;
-		\item White bars shows a   {\em drecrease} to a static code measure;
+		\item White bars shows a   {\em decrease} to a static code measure;
 		\item Bars that are all white or all gray indicate that in our 40 repeated runs, XTREE recommended changing an attribute the same way, all the time.
@@
 		\item For all clusters $C_0$, $C_1$ where the percent of defects in $C_0$ is greater than $C_1$...
-		\item For all attribute measures that are have a statistically significantly different distribution  between $C_0$ and $C_1$...
+		\item For all attribute measures that have a statistically significantly different distribution  between $C_0$ and $C_1$...
 		\item Report the direction of the change.
@@
 kinds of goals (e.g. maintainability, reliability, security, or the knowledge sharing
-measures favoured by Bosu and Carver~\cite{bosu13}) and other kinds of 
+measures) and other kinds of 
 inputs (e.g. the process measures favored by Rahman, 
@@
 
-For the research wishing to reproduce our work to other kinds of goals, we offer the following advice:
+For the researcher wishing to reproduce our work to other kinds of goals, we offer the following advice:
 
@@
 
-Validity refers to the extent to which a piece of research actually
+This paper is a case study that studied the effects of  limiting unnecessary code reorganization on some data sets.
+This section discusses limitations of such case studies.
+In this context, validity refers to the extent to which a piece of research actually
 investigates what the researcher purports to investigate.
-Validity has at least three components: internal and
+Validity has at least two components: internal and
 external validity.
 
-\subsection{Internal Validity}
-The results of this paper are also specific to the data sets explored here.
-Such sampling bias threatens any data mining experiment; i.e., what matters
-{\em there} may not be true {\em here}. For example, the data sets used here comes from a survey of
-open source JAVA projects from Jureczko et al.~\cite{jureczko10}. Any biases in their selection procedures
-threaten the validity of these results.
-
-That said,
-the best we can do is define our methods and publicize our data and code so that other researchers can
-try to repeat our results and, perhaps, point out a previously unknown bias
-in our analysis. Hopefully, other researchers will emulate our methods in
-order to repeat, refute, or improve our results.
-
-The recommendation to management, shown on page one of this paper,  was to stop developers doing ``X'' if there was no historical evidence that ``X'' was useful. 
-This recommendation assumes that such an  historical record can be accessed.
+% \subsection{Internal Validity}
+% The results of this paper are also specific to the data sets explored here.
+% Such sampling bias threatens any data mining case-study; i.e., what matters
+% {\em there} may not be true {\em here}. For example, the data sets used here comes from a survey of
+% open source JAVA projects from Jureczko et al.~\cite{jureczko10}. Any biases in their selection procedures
+% threaten the validity of these results.
+
+% That said,
+% the best we can do is define our methods and publicize our data and code so that other researchers can
+% try to repeat our results and, perhaps, point out a previously unknown bias
+% in our analysis. Hopefully, other researchers will emulate our methods in
+% order to repeat, refute, or improve our results.
+
+% The recommendation to management, shown on page one of this paper,  was to stop developers doing ``X'' if there was no historical evidence that ``X'' was useful. 
+% This recommendation assumes that such an  historical record can be accessed.
 If not,  then the results of this paper could be use used as a guide (see our Table 8).
-Alternatively, some form of transfer learning~\cite{Nam15,Jing15,krishna16} could be used to import data from another project (but more research would be required to test the validity of combing tools like XTREEs with transfer learning).
-
-As with any empirical study, several issues can affect the final results. Therefore, any
-conclusions made from this work must be offered with the following
-caveats.
-
-\subsection{External Validity}
-Based on the experimental results above,
+Alternatively, some form of transfer learning~\cite{Nam15,Jing15,krishna16} could be used to import data from another project (but more research would be required to test the validity of combing tools like XTREE with transfer learning).
+
+% As with any empirical study, several issues can affect the final results. Therefore, any
+% conclusions made from this work must be offered with the following
+% caveats.
+
+% \subsection{External Validity}
+% This section assesses the external validity as favoured by Bosu and Carver~\cite{bosu13}.
+
+Based on the case study presented above,
 as well as the discussion in \tion{prelim},
@@
 
-If developers want to justify their refactorings
+If developers want to justify their code reorganizations
 via bad smells expressed in other terminology,
@@
 	\item Or, apply cutting edge transfer learning
-	methods~\cite{Nam15,Jing15} to map data from other projects
+	methods~\cite{Nam15,Jing15, krishna16} to map data from other projects
 	into the current one.
@@
 
-	Sampling bias threatens any data mining experiment; i.e., what matters
+	Sampling bias threatens any data mining analysis; i.e., what matters
 	there may not be true here. For example, the data sets used here comes from Jureczko et al. and any biases in their selection procedures
@@
 		Older methods, such as those proposed by  Shatnawi and Alves assumed
-		that the best way to improve code is to remove outlier  values. This may not work since when code is refactored,
+		that the best way to improve code is to remove outlier  values. This may not work since when code is reorganized,
 		{\em the functionality has to go somewhere}. Hence,  reducing the lines of code in one module necessitates   
@@
 		% architectural knowledge such that it can
-		% become a tool which perscribes
+		% become a tool which prescribes
 		% feasible refactorings.

### 2017-02-07 doc/IST/Manuscript.tex
MacBook Local Changes

\documentclass[twocolumn,5p]{elsarticle}
\pdfoutput=1
\usepackage{hyperref}
\usepackage{tikz}
\def\firstcircle{(90:1.75cm) circle (2.5cm)}
\def\secondcircle{(210:1.75cm) circle (2.5cm)}
\def\thirdcircle{(330:1.75cm) circle (2.5cm)}
\usepackage{comment}
\usepackage{framed,graphicx}
\usepackage{multirow}
\usepackage{rotating}
\usepackage{amsmath}
\usepackage{bigstrut}
\usepackage{color}
\usepackage{graphics}
\usepackage{eqparbox}
\usepackage{graphics}
\usepackage{colortbl}
%\usepackage{times}
\usepackage{mathptmx} \usepackage[scaled=.90]{helvet} \usepackage{courier}
\usepackage{balance}
\usepackage{picture}
\usepackage{algorithm}
\usepackage{algorithmicx}
\usepackage{algpseudocode}
\usepackage[export]{adjustbox}
\renewcommand{\footnotesize}{\scriptsize}
\definecolor{lightgray}{gray}{0.8}
\definecolor{darkgray}{gray}{0.6}
\definecolor{lavenderpink}{rgb}{0.98, 0.68, 0.82}
\definecolor{celadon}{rgb}{0.67, 0.88, 0.69}
\renewcommand{\algorithmicrequire}{\textbf{Input:}}
\renewcommand{\algorithmicensure}{\textbf{Output:}}
%%% graph
\newcommand{\crule}[3][darkgray]{\textcolor{#1}{\rule{#2}{#3}}}

\newcommand{\quart}[4]{\begin{picture}(80,4)%1
	{\color{black}\put(#3,2){\circle*{4}}\put(#1,2){\line(1,0){#2}}}\end{picture}}

\definecolor{Gray}{gray}{0.95}
\definecolor{LightGray}{gray}{0.975}

\newcommand{\rahul}[1]{{\color{steel}{#1}}}
\newcommand{\menzies}[1]{{\color{magenta}{#1}}}
\newcommand{\lucas}[1]{{\color{red}{#1}}}

%% timm tricks
\newcommand{\bi}{\begin{itemize}[leftmargin=0.4cm]}
	\newcommand{\ei}{\end{itemize}}
\newcommand{\be}{\begin{enumerate}}
	\newcommand{\ee}{\end{enumerate}}
\newcommand{\tion}[1]{\S\ref{sect:#1}}
\newcommand{\fig}[1]{Figure~\ref{fig:#1}}
\newcommand{\tab}[1]{Table~\ref{tab:#1}}
\newcommand{\eq}[1]{Equation~\ref{eq:#1}}
\newcommand{\review}[1]{\noindent\textit{#1\\}}

\usepackage[shortlabels]{enumitem}
\usepackage{url}

\definecolor{steel}{rgb}{0,0,0}
\definecolor{Gray}{rgb}{0.88,1,1}
\definecolor{Gray}{gray}{0.85}
% \usepackage[svgnames]{xcolor}
\usepackage[framed]{ntheorem}
\usepackage{framed}
\usepackage{tikz}
\usetikzlibrary{shadows}
%\newtheorem{Lesson}{Lesson}
\theoremclass{Lesson}
\theoremstyle{break}

% inner sep=10pt,
\tikzstyle{thmbox} = [rectangle, rounded corners, draw=black,
fill=Gray!40,  drop shadow={fill=black, opacity=1}]
\newcommand\thmbox[1]{%
	\noindent\begin{tikzpicture}%
	\node [thmbox] (box){%
		\begin{minipage}{.94\textwidth}%
		\vspace{-2mm}#1\vspace{-3mm}%
		\end{minipage}%
	};%
	\end{tikzpicture}}

\let\theoremframecommand\thmbox
\newshadedtheorem{lesson}{Result}

\begin{document}

	\begin{frontmatter}

		\title{Less is More: Minimizing  Code Reorganization using XTREE}

		\author{Rahul Krishna\corref{cor1}\textsuperscript{a,}}
		\ead{i.m.ralk@gmail.com}
		\author{Tim Menzies\corref{cor1}\textsuperscript{a,}}
		\ead{tim.menzies@gmail.com}
		\author{Lucas Layman\textsuperscript{b}}
		\ead{ llayman@cese.fraunhofer.org }
		\cortext[cor1]{Corresponding author: Tel:+1-919-396-4143(Rahul)}
		\address{\textsuperscript{a}Department of Computer Science, North 
		Carolina State University, Raleigh, NC, USA\\
			\textsuperscript{b}Fraunhofer CESE, College Park, USA}
		\pagenumbering{arabic}

		\begin{abstract}
			{\bf Context: }
			Developers use bad code smells to guide code reorganization.
			Yet developers, textbooks, tools, and researchers disagree on 
			which bad smells are important. How can we offer reliable
                        advice to developers about which bad smells to fix?

			\noindent
			{\bf Objective:} To evaluate the likelihood that a code 
			reorganization to address bad code smells will yield improvement in 
			the defect-proneness of the code.

			\noindent
			{\bf Method: } We introduce XTREE, a framework that analyzes a 
			historical log of defects seen previously in the code and generates 
			a set of useful code changes.
			Any bad smell that requires changes outside of that set can be 
			deprioritized (since there is no historical evidence that the bad 
			smell causes any problems).

			\noindent
			{\bf Evaluation: } We evaluate XTREE's recommendations for bad 
			smell improvement against recommendations from previous work 
			(Shatnawi, Alves, and Borges) using multiple data sets of code 
			metrics and defect counts.

			\noindent
			{\bf Results: }Code modules that are changed in response to XTREE's 
			recommendations contain significantly fewer defects than 
			recommendations from previous studies. Further, XTREE endorses 
			changes to very few code metrics, so XTREE requires programmers to do less
                        work. Further, XTREE's recommendations are more 
                        responsive to the
                        particulars of different data sets.

			\noindent
			{\bf Conclusion: }
			Before undertaking a code reorganization based on a bad smell 
			report, use a framework like XTREE to check and ignore any such 
			operations that  are useless; i.e. ones which lack evidence in the 
			historical record  that it is useful to make that change. Note 
			that 
			this use case applies to both manual code reorganizations proposed 
			by developers as well as those conducted by automatic methods. 
			This 
			recommendation assumes that there is an historical record. If none 
			exists, then the results of this paper could be used as a guide 
			(see the last figure of this paper).

		\end{abstract}
	\end{frontmatter}
	\pagenumbering{arabic} %XXX delete before submission

	\vspace{1mm}
	\noindent
	{\bf Keywords:} Bad smells,
	performance prediction,  decision trees.

	\section{Introduction}
	\label{sect:intro}
	According to   Fowler~\cite{fowler99}, bad smells (a.k.a. code smells)
	are ``a surface indication that usually corresponds to a deeper problem''.
	Fowler  recommends   removing   code smells   by
	\begin{quote}
		``$\ldots$ applying a series of small behavior-preserving 
		transformations, 
		each
		of which seem `too small to be worth doing'.
		The  effect of   these refactoring transformations is quite 
		significant. By doing them in small steps you reduce the risk
		of introducing errors''.
	\end{quote}

	While the original concept of bad smells was largely subjective, 
	researchers including Marinescu~\cite{Lanza2006} and 
	Munro~\cite{munro2005product} provide definitions of ``bad smells'' in 
	terms of static code attributes such as size, complexity, coupling, and 
	other metrics. Consequently, code smells are captured by popular static 
	analysis tools, like PMD\footnote{https://github.com/pmd/pmd}, 
	CheckStyle\footnote{http://checkstyle.sourceforge.net/}, 
	FindBugs\footnote{http://findbugs.sourceforge.net/}, and 
	SonarQube\footnote{http://www.sonarqube.org/}.

        We refer to the process of removing bad smells as \textit{code 
	reorganization}. Code reorganization is an amalgum of perfective and 
	preventive maintenance~\cite{iso14764}. In contrast to refactoring, code 
	reorganization is not guaranteed to preserve behavior.
	Fowler~\cite{fowler99} and other influential software 
	practitioners~\cite{mcconnell2004code,horror} recommend refactoring and 
	code reorganization to remove bad smells. Studies suggest a relationship 
	between code smells and poor maintainability or defect 
	proneness~\cite{yamashita2013code,yama13,zazworka2011investigating}, though 
	these findings are not always consistent~\cite{olbrich2010all}.

	The premise of this paper is that not every bad smell needs to be fixed.
        For example, 
	the origins of this paper was a meeting with a  Washington-based software company where managers
        shared one of 
	their challenges: their  releases were delayed by 
	developers spending  much time removing bad smells within their code. There is much evidence
        that this is a common problem. Kim 
	et al.~\cite{kim2012field} surveyed developers at Microsoft and found that 
	code reorganizations incur significant cost and risks. Researchers are 
	actively attempting to demonstrate the actual costs and benefits of fixing 
	bad 
	smells~\cite{nugroho2011empirical,zazworka2011prioritizing,zazworka2013case},
	 though more case studies are needed.

	 In this 
	paper, we focus on the challenge of recommending code reorganizations that 
	result in perceivable benefits (such as reduced defect proneness) and avoid 
	those reorganizations which have no demonstrable benefit and thus waste 
	effort.
	 To this end, this
	paper evaluates XTREE~\cite{krishna2015actionable}, a framework to evaluate 
	whether a code reorganization is likely to have a perceivable benefit in 
	terms of defect-proneness. We focus on bad smells indicated by code 
	metrics 
	such as size and complexity as captured in popular tools such as SonarQube 
	and Klockwork\footnote{http://www.klocwork.com/}.
	XTREE examines the historical record of code metrics for a project. If 
	there is no evidence that changing code metric ``X'' is useful (e.g., 
	lowering ``X'' reduces defect-proneness), then developers should be 
	discouraged from wasting effort on that change.

	Our method uses two oracles: a {\em primary
		change oracle} and a {\em secondary verification oracle}.
	By combining these two oracles,
	we can identify and validate useful
	code reorganizations.

	We use
	the XTREE cluster delta algorithm as the {\em primary change  oracle}.
	XTREE
	explores the historical record of a project to find clusters of modules 
	(e.g., files or binaries).
	It then proposes a ``minimal'' set of changes $\Delta$ that can move a 
	software module $M$ from a defective cluster $C_0$ to another with fewer 
	defects $C_1$ (so $\Delta$
	is some subset of $C_1 - C_0$). % To define ``minimal'', XTREE uses an 
	%entropy measure.

	The {\em secondary verification oracle} checks if the primary oracle is 
	proposing
	sensible changes. We create the verification oracle using Random 
	Forest~\cite{Breiman2001} augmented with SMOTE (synthetic  minority 
	over-sampling technique~\cite{chawla2002smote}).
	In our framework,  learning
	the secondary oracle is   a {\em separate} task from that of learning the 
	primary
	oracle. This  ensures that the verification oracle offers an independent
	opinion on the value of the proposed changes.

	An advantage to the XTREE cluster delta approach is that it avoids the
	{\em conjunctive fallacy}.
	A common heuristic in the bad smell 
	literature~\cite{erni96,bender99,Shatnawi10,Alves2010,hermans15} is: for 
	all static code measures that exceed some threshold, make changes such that 
	the thresholds are no longer exceeded. That is:
	\begin{equation}\label{eq:df}
		\scriptstyle
		\begin{array}{rl}
			\mathit{bad}    & = \left(a_1 > t_1 \right) \bigvee \left(a_2 > 
			t_2\right) \bigvee    ...                             \\
			\mathit{better} & = \neg\;\mathit{bad} = \left(a_1 \le t_1 \right) 
			\bigwedge \left(a_2 \le t_2\right)  \bigwedge  ... 
		\end{array}
	\end{equation}
	We say that the above definition of ``better'' is a conjunctive fallacy
	since it assumes that the best way to improve code is to decreases multiple 
	code attribute measures to below $t_i$ in order
	to remove the ``bad'' smells. In reality, the associations between static 
	code measures are more intricate, for example, {\em decreasing}  $a_i$ may 
	necessitate {\em increasing} $a_j$.
	It is easy to see why this is so.
	For example, Fowler recommends that the Large Class smell be addressed by 
	the Extract Class or Extract Subclass refactoring~\cite{fowler99}. If we 
	pull code out of a function since that function has grown too
	large, that functionality has to go somewhere else. Thus, when 
	\textit{decreasing} lines of code in one module, we may \textit{increase} 
	its coupling to another module. XTREE identifies such associations between 
	metrics, thus avoiding the conjunctive fallacy.

	\subsection{Research Questions}
	\label{sect:rqs}
	This paper  claims that (a)~XTREE is more useful than \eq{df} to identify 
	code reorganizations, and (b)~XTREE recommends a small subset of static 
	code measures to change and thus can be used to identify superfluous code 
	reorganizations (i.e., reorganizations based on omitted
	static code measures).

	\rahul{To evaluate these claims, we compared the 
	performance of XTREE with three other methodologies/tools for recommending 
	code reorganizations: (1) VARL based thresholds~\cite{Shatnawi10}; (2) 
	Statistical threshold generation~\cite{Alves2010}; (3) CD, cluster based 
	framework~\cite{me12c} according to the following research questions:}

	{\bf  RQ1: Effectiveness}: According to the verification oracle, which of 
	the frameworks introduced above is most accurate in recommending code 
	reorganizations that 
	result in reduced numbers of defective modules?

	To answer this question, we used data from five OO Java projects
	(Ivy, Lucene, Ant, Poi, Jedit). It was found that:
	\begin{lesson}
		XTREE is the most accurate oracle on how to change code modules in 
		order to reduce the number of defects.
	\end{lesson}

	{\bf RQ2: Succinctness}: Our goal is to critique and, possibly,
	ignore irrelevant recommendations for removing bad smells.  If the 
	recommended changes are 
	minimal (i.e. affect fewest attributes) then those changes
	will be easiest to apply and monitor. So, which framework recommends 
	changes to the fewest code attributes?
	\begin{lesson}
		Of all the code change oracles studied, XTREE recommends changes to the 
		fewest number of static code measures.
	\end{lesson}

	{\bf RQ3: Stopping}: Our goal is to discourage code reorganization based on 
	changes that lack
	historical evidence of being effective. So, how effective is XTREE at 
	identifying what {\em not} to change?
	\begin{lesson}
		In  any  project,  XTREE's  recommended  changes  to 1--4
		of the  static code attributes.  Any bad smell defined in terms of the 
		remaining 19 to 16 code attributes (i.e. most of them)
		would hence be deprecated.
	\end{lesson}

	{\bf RQ4: Stability}: Across different projects, how consistent are the 
	changes recommended by our best change oracle?
	\begin{lesson}
		The direction of change recommended by XTREE (e.g., to LOWER lines of 
		code while RAISING coupling) is stable across repeated runs of change 
		oracle.
	\end{lesson}

	{\bf RQ5: Conjunctive Fallacy}:
	Is it always  useful  to apply \eq{df}; i.e. make code better by   
	reducing 
	the values of  multiple code attributes? We find that:
	\begin{lesson}
		XTREE usually recommends reducing lines of code (size of the modules).
		That said,  XTREE often recommends {\em increasing} the values of other 
		static code attributes.
	\end{lesson}
	Note that {\bf RQ3, RQ4, RQ5}
	confirms the intuitions
	of the project managers that prompted this investigation. We find evidence 
	that:
	\bi
	\item Code reorganizations that decrease multiple measures may not yield 
	improvement. In fact,  programmers may need to {\em decrease} some 
	measures 
	while {\em increasing} others.
	\item In the studied projects, XTREE recommends changes to approximately 
	20\% of the code measures, and thus reorganizations based on the remaining 
	80\% are unlikely to provide benefit.
	\ei

	{\color{steel}In terms of concrete recommendations for
		practitioners, we say {\em look before you leap}:
		\bi
		\item Before doing  code reorganization based on a bad smell 
		report$\ldots$ 
		\item $\ldots$ check and discourage any code reorganization   for which 
		there 
		is no proof
		in the historical record that the change improves the code.
		\ei
		Aside: this recommendation   applies to both manual code 
		reorganizations proposed by developers
		as well as the code reorganizations conducted by automatic 
		methods~\cite{mkaouer2015many}. That is, XTREE could optimize automatic
		code reorganization by discouraging reorganizations for useless goals.}

	\section{Relationship to Prior Work }
	{\color{steel}	
	\subsection{Prioritizing Reorganization Efforts}
	\label{sect:prior}

		There have been several efforts to prioritize refactoring efforts. 
		These attempts address code smells in particular and have garnered more 
		attention over the past few years. Ouni et al.~\cite{ouni3,ouni1,ouni2} 
		use search 
		based software engineering to suggest refactoring solutions. They 
		recommend the use of four 
		factors: (1) priority; (2) severity; (3) risk; and (4) importance, all 
		of which are determined by developers. Both the developer's 
		recommendations and the aforementioned factors can and do vary over 
		time especially as classes are modified. Additionally, they also vary 
		with projects.

		A similar direction was taken by Vidal et al.~\cite{vidal14}. They 
		presented a semi-automated approach for prioritizing code smells. They 
		then recommend a suitable refactoring based on a developer survey. The 
		determination of severity is based primarily on three criteria: (1) the 
		stability of the component in which the smell was found; (2) the 
		subjective assessment that the developer makes of each kind of smell 
		using an ordinal scale; and (3) the related modifiability scenarios.

		The standard approach is to develop and evaluate these findings by 
		interviewing human developers. We, however, dissuade practitioners 
		from taking this approach for reasons discussed in depth in 
		\tion{prelim}.

		In a more recent study, a slightly different approach was proposed by 
		Vidal et al.~\cite{font1}. In their work, static code metrics are used 
		to detect the presence of code smells. This is followed by a ranking 
		scheme to measure the severity of code smells. This was a fully 
		automated approach. However, the authors fail to report the accuracy 
		of 
		detection of code smells. This issue is further compounded by the use 
		of mean and standard deviation of metrics to detect the presence of 
		code smells which has been criticized by several  
		researchers~\cite{Shatnawi10,Alves2010}. Those authors do acknowledge 
		that the prioritization of detection results obtained using their 
		"intensity" measure, at the time of publication, lacked comprehensive 
		experimental validation.

		\subsection{Preliminary Report on Code Reorganization}
		There is a distinction between our work and all methods listed above. 
		The code smell prioritization efforts assist developers in choosing 
		\textit{which} refactoring operation to undertake first. Instead of 
		prioritizing refactoring, our work places more focus on assisting 
		developers by recommending useful code changes which in turn helps 
		deprioritize certain code reorganization efforts. Our preferred 
		framework 
		to 
		achieve this is XTREE.}

	XTREE was first introduced as a four page preliminary 
	report\footnote{https://goo.gl/2In3Lr} which was presented 
	previously~\cite{krishna2015actionable}. That short report offered case 
	studies on only two  of
	the five data sets studied here. We greatly expand on this prior work by:
	\bi
	\item
	Evaluating XTREE's recommendations against recommendations from frameworks 
	developed using three other methods proposed by other researchers exploring 
	bad 
	smells.
	\item
	Evaluating if XTREE's and other methods' recommended changes were sensible 
	using the {\em secondary verification oracle}
	\ei
	Note that only sections \tion{cdcd}, \tion{xtreextree}, and two-fifths of the results 
	in \fig{jur2} 
	contain material
	found in prior papers.

	\subsection{Why Not Just Ask Developers to Rank Bad 
	Smells?}\label{sect:prelim}

	Why build tools like XTREE to  critique proposed developer actions?
	Much research endorses code smells as a guide for
	code improvement (e.g., code reorganization or preventative maintenance). 
	A 
	recent literature review by Tufano et al.~\cite{Tufano2015}
	lists dozens of papers on smell detection and repair tools.
	Yet
	other papers cast doubt on the value of bad smells
	as triggers for code 
	improvement~\cite{Mantyla2004,Yamashita2013,Sjoberg2013}.

	If the SE literature is contradictory, why not ignore it and use domain 
	experts (software engineers) to decide
	what bad smells to fix? We do not recommend this since developer {\em 
	cognitive biases} can mislead them to
	assert that some things are important and relevant when they are not.
	According to Passos et al.~\cite{passos11},  developers often  assume that 
	the lessons they learn from a few past projects are general to all their 
	future projects. They comment, ``past experiences were taken into account 
	without much consideration for their context''~\cite{passos11}.  
	J{\o}rgensen \& Gruschke~\cite{jorgensen09} offer a similar warning. They 
	report that the supposed software engineering ``gurus'' rarely use lessons 
	from past projects to improve their future reasoning and that such poor 
	past advice can be detrimental to new projects.~\cite{jorgensen09}.

        Other 
	studies have shown some widely-held views are   now questionable given new 
	evidence.
	Devanbu et al. examined responses from 564 Microsoft software developers 
	from around
	the world. They comment programmer beliefs can vary with each project, but do not necessarily
	correspond with actual evidence in that project~\cite{prem16}.
	\input{refactor}
	If the above remarks hold true for bad smells, then we would expect
	to see much disagreement on which bad smells are important and relevant
	to  a particular project.

        This is indeed the case.
	The first column of \fig{smells}
	lists  commonly mentioned bad smells and comes from Fowler's 1999 
	text~\cite{fowler99} and a subsequent 2005 text by Kerievsky that is widely 
	cited~\cite{Kerievsky2005}.
	The other
	columns show data from other studies on which bad smells matter most.
	The columns marked as Lanza'06 and Yamashita'13 are from peer reviewed 
	literature. The column marked SonarQube is a popular open source
	code assessment tool that includes detectors for six of the bad smells
	in column one.
	The {\em developer survey} (in the right-hand-side column) shows the 
	results of an hour-long whiteboard session with a group of 12 developers 
	from a Washington
	D.C. web tools development company. Participants
	worked in a round robin manner to rank the bad smells they thought were
	important (and any disagreements were discussed with the whole group).
	Amongst the group, there was  some
	consensus on  the priority of which bad smells to fix
	(see the annotations VH=very high,
	H=high, L=low, VL=very low, and ``?''= no consensus).

	\input{jur_char}

	A  blank cell in \fig{smells}
	indicates where   other work omits
	one of the bad smells in column one.
	Note that most of the cells are blank, and that the studies omit the 
	majority of the Fowler bad smells.
	SonarQube has no detectors for many of the column one bad smells.
	Also, nearly half the Yamashita list of bad smells
	does not appear in column 1. The eight numbers
	in the  Yamashita'13 column show the rankings for the bad smells
	that overlap with Fowler and Kerievsky; Yamashita also discussed other 
	smells not covered in Fowler'99~\cite{fowler99}.

	Two of the studies in \fig{smells} offers some comments on the relative 
	importance
	of the different bad smells. Three of the bad smells listed in the top 
	half 
	of the Yamashita'13 rankings also score very high in the developer survey. 
	Those three were {\em duplicated code, large class},
	and {\em long method}.
	Note that this agreement also means that the
	Yamashita'13 study and the developer survey
	believe
	that very few  code smells are   high priority issues
	requiring code reorganization.

	In summary, just because one developer strongly believes in the importance 
	of a bad smell, it does not mean that belief transfers to other developers 
	or 
	projects.
	Developers can be clever, but their thinking can also be distorted
	by cognitive biases.
	Hence, as shown in \fig{smells}, developers, text books, and tools
	can disagree on which bad smells are important.
	Special tools are needed to assess their beliefs, for example, their 
	beliefs in
	bad smells.

	{\color{steel}
		\section{Why Use Defect Data?}
		\label{sect:dataset}
		To assess our planning methods, we opted to use data gathered by 
		Jureczko et al. for object-oriented JAVA systems~\cite{jureczko10}. 
		The 
		``Jureczko'' data records the number of known defects for each class 
		using a post-release bug tracking system. The classes are described in 
		terms of nearly two dozen metrics such as number of children (noc), 
		lines of code (loc), etc. For details on the Jureczko data, see 
		\fig{ck}. The nature of collected data and  its relevance to defect 
		prediction is discussed in greater detail by Madeyski \& 
		Jureczko~\cite{madeyski15}.

		A sample set of values from a data set (ant 1.3) is shown 
		in 
		\fig{example}. Each instance notes a class under 
		consideration, 20 static code metric values, and 2 columns counting the 
		defects in the code.

		The term ``defect'' in our work always refers to 
		\textit{defective 
		classes}. The defects themselves are represented in two ways:

		\be

		\item Raw defect counts (denoted as \texttt{nDefects}): This refers 
		total number of defects present in a given class. This is an integer 
		value, such that, $nDefects~\in~\{0,1,2,\ldots\}$. This~representation 
		of defects is used by all the \textit{primary change oracles}.
		\item Boolean defects (denoted as \texttt{isDefective}): This is a 
		Boolean representation of defects. It is \texttt{TRUE} if 
		$\texttt{nDefects}>~0$ otherwise it is 
		\texttt{FALSE}.~This~representation of defects is used by 
		the \textit{secondary verification oracle}.

		\ee

		We use defects to operationalize smell definitions 
		following the 
		findings of several researchers. Li \& Shatnawi~\cite{li07} 
		investigated the relationship between the bad smells and module defect 
		probability. Their study found that, in the context of the 
		post-release 
		system evolution process, bad smells were positively associated with 
		the defect probability in the three error-severity levels. They also 
		reported that Shotgun Surgery, God Class, and God Method smells are 
		associated with higher levels of defects. Olbrich et 
		al.~\cite{olbrich2010all} show the impact that God and Brain Class 
		smells have on code directly influences defects in systems.

		In a more recent study, Hall et al.~\cite{Hall2014} further corroborate 
		the claim that smells indicate defect-prone code in several 
		circumstances. Their evaluation of smell detection performance shows 
		that it is difficult to define and quantify smell definitions, either 
		for automatic or manual smell detection. Generally, agreement levels 
		on 
		what code contains a smell are poor between tools, between tools and 
		humans, and even between humans. This in general leads to poor 
		performance of tools that detect code smells. More importantly, they 
		note that arbitrary refactoring is unlikely to significantly reduce 
		fault-proneness and in some cases may increase fault-proneness. Our 
		findings also show that smells have different effects on different 
		systems many of which cannot be quantified with just code smell 
		metrics. These findings lead us to conclusion that using static code 
		metrics and associated defects would best support code reorganization.}

		\input{sample_data.tex}
	\section{Learning Bad Smell Thresholds}\label{sect:bst}

	Having made the case for automated, evidence-based support for assessing 
	bad smells,
	this section reviews different ways for building those tools (one of those 
	tools,
	XTREE, will be our recommended {\em primary change oracle}).
	Later in this paper, we describe  a {\em secondary verification oracle}
	that checks the effectiveness of the proposed changes.

	The SE literature offers two ways of learning bad smell thresholds.
	One approach relies on
	{\em outlier statistics}~\cite{erni96,bender99}. This approach
	has been used   by Shatnawi~\cite{Shatnawi10}, Alves et al.~\cite{Alves2010}
	and Hermans et al.~\cite{hermans15}.
	Another approach is
	based on {\em cluster deltas} that we developed
	for   Centroid Deltas~\cite{me12c} and
	is used here for XTREE.
	These two approaches are discussed below.

	\subsection{Outlier Statistics}

	The outlier approach assumes that unusually large measurements indicate 
	risk-prone code.
	Hence, they generate one bad smell threshold for any metric
	with such an ``unusually large'' measurement.
	The literature lists several ways to define ``unusually large''.

	\subsubsection{Enri \& Lewerentz}
	Given classes described with the  code metrics of \fig{ck},
	Enri and Lewerentz~\cite{erni96} found the   mean $\mu$ and the standard 
	deviation $\sigma$
	of each
	code metrics. Their definition of problematic outlier was any code
	metric with a measurement greater than $\mu+\sigma$.
	Shatnawi and Alves et al.~\cite{Shatnawi10,Alves2010} depreciate
	using $\mu+\sigma$ since it does not consider the fault-proneness of 
	classes when the thresholds are computed. Also, the approach lacks  
	empirical 
	verification.

	\subsubsection{ Shatnawi}\label{sect:shatnawi}
	Shatnawi~\cite{Shatnawi10}'s preferred alternative to $\mu+\sigma$
	is to extend the use VARL (Value of Acceptable Risk Level) which was 
	initially proposed by 
	Bender~\cite{bender99} for his epidemiology studies.  This approach uses two
	constants ($p_0$ and $p_1$) to compute the thresholds which, following 
	Shatnawi's guidance, we set to
	$p_0=p_1=0.05$.

	\input{xtree_tut.tex}
	VARL encodes the defect count
	for each class as 0 (no defects known in class) or 1 (defects known in 
	class).
	Univariate binary logistic regression is applied to learn three 
	coefficients:
	$\alpha$ is the intercept constant;
	$\beta$ is the coefficient for maximizing log-likelihood;
	and $p_0$
	measures   how well this  model predicts for  defects. A univariate 
	logistic regression was conducted comparing metrics to defect counts. Any 
	code metric with $p>0.05$ is ignored as being a poor defect predictor. 
	Thresholds are then learned from the surviving metrics $M_c$ using
	the risk equation proposed by Bender:
	$$ \mathit{bad\; smell\; if\;} M_c > VARL$$
	Where,
	\begin{equation}
		VARL = p^{-1}(p_0) =  \frac{1}{\beta }\left( {\log \left( 
		{\frac{{{p_1}}}{{1 - {p_1}}}} \right) - \alpha } \right)
	\end{equation}

	\subsubsection{ Alves et al.}
	Alves et al.~\cite{Alves2010} propose another approach
	that  uses the underlying statistical 
	distribution and scale of the metrics.
	Metric values are weighted according to the source lines of 
	code (SLOC) of the class. All the weighted metrics are then normalized by 
	the sum of all weights for the system.
	The normalized metric values are ordered in an ascending fashion (this is 
	equivalent to computing a density function, in which the x-axis represents 
	the weight ratio (0-100\%), and the y-axis the metric scale).
	Alves et al. then select a percentage value (they suggest 70\%) which 
	represents the ``normal'' values for metrics. The metric threshold, then, 
	is the metric value for which 70\% of the classes fall below. The 
	intuition  is that the worst code has outliers beyond 70\% of the normal 
	code measurements i.e., they state that the risk of there existing a defect 
	is moderate to high when the threshold value of 70\% is exceeded.

	Hermans et al.~\cite{hermans15} used this approach in their  2015 paper on
	exploring bad smells. We explore the correlation between the code metrics 
	and the defect counts with a univariate logistic regression and  reject 
	code metrics that are poor predictors of defects (i.e.   those  with $p > 
	0.05$).

	\subsubsection{Discussion of Outlier Methods}\label{sect:disc}
	The advantage of the outlier-based
	approaches is that they are simple to implement, but the approaches have   
	two  major disadvantages.
	First, they are {\em verbose}. A threshold can be calculated for every 
	metric -- so, which one should the developers focus on changing? Without a 
	means for prioritizing the  thresholds and metrics against one another, 
	developers may have numerous or conflicting recommendations on what to 
	improve. Second, the outlier approaches suffers from {\em conjunctive 
	fallacy}  discussed in the introduction. That is, while	they propose 
	thresholds for many code metrics
	individually, they make no comment on what minimal metrics need to be 
	changed at the same time (or whether or not those changes lead to 
	minimization or maximization of static code measures).

	\subsection{Cluster Deltas}

	Cluster deltas are a general framework
	for learning {\em conjunctions} of changes
	that need to be applied at the same time.
	This approach works as follows:
	\begin{itemize}
		\item Cluster the data.
		\item Find
		neighboring clusters $C_+,C_-$ (where $C_+$ has more examples of 
		defective
		modules than $C_-$);
		\item Compute the  delta   in code metrics between the clusters using 
		\mbox{$\Delta = C_- - C_+ = \left\{\delta|\delta\in C_-, \delta \notin 
		C_+\right\}$}, i.e.
		{\em towards} the cluster with lower defects;
		\item The set $\Delta$ are changes needed in defective modules of $C_+$ 
		to
		make them more like the less-defective modules of $C_-$
	\end{itemize}
	Note that $\Delta$ is a conjunction of  recommendations.
	Since it is computed
	from neighboring clusters, the examples contain similar distributions and 
	$\Delta$ respects the naturally occurring constraints in the data. For 
	example,
	given a bad smell pertaining to large methods,   $\Delta$   will not  
	suggest lowering lines of code
	without also increasing a coupling measure.
	Cluster deltas are used in CD~\cite{me12c} and XTREE.

	\subsubsection{CD}\label{sect:cdcd}
	Borges and Menzies first proposed CD centroid deltas to
	generate {\em conjunctions} of code metrics
	that need to be changed at the same time
	in order to reduce defects~\cite{me12c}.
	CD uses the WHERE clustering algorithm developed by the
	authors for a prior application~\cite{me12d}.
	Each cluster was then replaced by its centroid
	and $\Delta$ was calculated directly from the difference
	between code metric values between one centroid
	and its nearest neighbor.

	One drawback with CD is that it is {\em verbose}
	since
	CD   recommended changes to all code
	metrics with different values in those two centroids.
	This makes it hard to use CD to   critique and prune away bad smells. 
	Further, CD will be shown not to be as effective
	in proposing changes to reduce defects as XTREE.

	\subsubsection{XTREE: Mining Project History for Defect-Proneness 
	Attributes}
	\label{sect:xtreextree}
	XTREE  is a cluster delta algorithm
	that avoids the problem of verbose $\Delta$s.
	XTREE is our {\em primary change oracle} that makes recommendations
	of what changes should be made to code modules.
	Instead of reasoning over cluster centroids,
	XTREE utilizes a decision tree learning approach
	to find the fewest differences between clusters of examples.

	XTREE uses a multi-interval discretizer based on an iterative 
	dichotomization scheme, first proposed by Fayyad and Irani~\cite{fi}. This 
	method converts the values for each code metric into a small number of 
	nominal ranges. It works as follows:
	\begin{itemize}
		\item A code metric is split into $r$ ($r=2$) ranges, each range is of
		size $n_r$ and is associated with a set of defect counts $x_r$ with 
		standard deviation
		$\sigma_r$.
		\item The best split for that range is the one that minimizes the 
		expected value of the
		defect variance, after the split; i.e. $\sum_r\frac{n_r}{n}\sigma_x$ 
		(where $n=\sum_r n_r$).
		\item This discretizer then recurses on  split to find 
		other splits in a recursive fashion. As suggested by Fayyad and Irani, 
		minimum description length (MDL) is used as a termination criterion for 
		the recursive partitioning.
	\end{itemize}

	When discretization finishes, each code metric $M$ has a
	final expected value $M_v$ for the defect standard deviation
	across all the discretized ranges of that metric.
	Iterative dichomization sorts the metrics by $M_v$
	to find the code metric that best splits the data i.e., the code metric 
	with smallest $M_v$.

	A decision tree is then constructed on the discretized metrics. The metric 
	that generated the best split forms the root of the tree with its discrete 
	ranges acting as the nodes.

	When all the metrics are arranged this way, the process is very similar to 
	a hierarchical clustering algorithm that groups together code modules with 
	similar defect counts and some shared ranges of code metrics.
	For our purposes, we score each cluster found in this way according
	to the percent of classes with known defects. For example, the last line 
	of 
	\fig{xtree_samp} shows a tree leaf with 75\%
	defective modules.

	\fig{xtree_samp} offers
	a small example of how XTREE builds
	$\Delta$ by comparing branches that lead to leaf clusters
	with different defect percentages. In this example, assume a project with 
	a 
	table of code metrics data describing its classes in the form of 
	\fig{example}. 
	After code inspections and running test cases or operational
	tests, each such class is augmented with a defect count.
	Iterative dichomization takes that table of data and,
	generates the tree of \fig{xtree_samp}.

	Once the tree is built, a class with code metric data is passed into the 
	tree and evaluated down the tree to a leaf node (see the 
	\textcolor{orange}{{\bf orange}} line in \fig{xtree_samp}).
	XTREE then looks for a nearby leaf node with a lower defect
	count (see the \textcolor{green}{{green}} line in \fig{xtree_samp}). For 
	that evaluated class, XTREE proposes bad smell
	thresholds that are the differences between
	\textcolor{green}{{green}} and \textcolor{orange}{{\bf orange}}.

	\subsubsection{XTREE: Recommending Code Reorganizations}

	Using the training data construct a decision tree as suggested above.

	Next, for each test code module,
	find $C_+$ as follows: take each test, run it down the decision tree to 
	find a leaf in the decision tree that best matches the test case.
	After that,	find $C_-$ as follows:
	\begin{itemize}
		\item Starting at the  $C_+$ leaf (level N), ascend $lvl\in 
		\{N,N-1,N-2, 
		...\}$ tree 
		levels;
		\item Identify {\em sibling} leaves; i.e. leaf clusters that can be 
		reached from level $lvl$ that are not same as {\em current $C_+$};
		\item Find the {\em better} siblings; i.e. those with defect proneness 
		50\% or less than that of $C_+$ (e.g., if defect-proneness of $C_+$ is 
		70\%, find the nearest sibling with defect proneness $\leq$ 35\%). If 
		none found, then repeat for $lvl$--$=1$. Also, return \texttt{nil} if 
		the new $lvl$ is above the root.
		\item  Set $C_-$ to the  {\em closest} better sibling where distance is 
		measured between the mean centroids of that sibling and {\em $C_+$}
	\end{itemize}
	Now find $\Delta = C_- - C_+$  by reflecting
	on the set difference between  conditions in the decision tree branching 
	from $C_+$ to $C_-$. To find that delta,
	for discrete attributes, delta is the value of the {\em desired}; for 
	numerics  expressed as ranges, the delta could be any value that lies 
	between $\left( LOW, HIGH\right]$ in that range.

	Note that XTREE's recommendation does not exhaustively search the tree for 
	the change that reduces defect proneness the most, but rather finds the 
	nearest sibling. This is by design. This design allows XTREE to a) 
	provide 
	recommendations quickly, and b) to recommend changes to a small number of 
	attributes.

	\section{Setup}
	\label{sect:setup}
	The previous section proposed numerous methods for detecting bad smells 
	that need
	to be resolved. This section offers a way to evaluate them as follows:
	\bi
	\item Use each framework discussed in \tion{bst} as a {\em primary change 
	oracle} to recommend how 
	code should be changed in our test data set (Section~\ref{sect:tesd}).
	\item Apply those changes. (This is emulated by changing the code metrics 
	in order that all the $\Delta$'s are addressed.)\footnote{Note: This was 
	done by selecting a random number from the $\left(LOW,  HIGH\right]$ 
	boundaries of the recommended delta(s). The random number indicates what 
	may happen if a developer were to make changes to their code to comply with 
	the recommendations.}
	\item Run a {\em secondary verification oracle} to assess the 
	defect-proneness of the changed code.
	\item Sort the change oracles on how well they reduce defects as judged by 
	the verification oracle.
	\ei
	Using this, we can address the research questions discussed in the 
	introduction.

	{\bf RQ1: Effectiveness: } Which of the methods defined in Section 3 is the 
	best change oracle for identifying what and how code modules should be 
	changed?
	We will assume that developers
	update and reorganize their code until the bad smell thresholds are not 
	violated.
	This code reorganization will start with some {\em initial} code
	base that is changed to a {\em new} code base.

	\rahul{
	For example, assume that a log 
	history of defects has shown that modules 
	with \mbox{{\em loc $>100$}} have more defects (per class) than smaller 
	modules and a
	code module has 500 lines of code. The action is to reduce the size of that 
	module; we reason
	optimistically that we can change that code metric
	to 100.  Using the secondary verification oracle,  we then predict the
	number of defects in {\em new}.}

	We compare $d_+$, the number of defects in the \textit{initial} code base 
	to $d_-$, the number of defects in the \textit{new} code base.
	We evaluate the performance of XTREE, CD, Shatnawi, and Alves change 
	oracles. The best change oracle is the one that maximizes
	\begin{equation}\label{eq:diff}
		\mathit{improvement} = 100* \left(1 - \frac{ d_- }{ d_+}\right)
	\end{equation}

	{\bf RQ2: Succinctness: } Which of the Section 3 methods recommended 
	changes to the fewest code attributes?
	To answer this question, we will report the frequency at which different 
	attributes are selected in repeated runs of our oracles.

	{\bf RQ3: Stopping: }    How effective is XTREE at offering   ``stopping 
	points'' (i.e. clear guidance on what {\em not} to do)?
	To answer this point, we will report how often XTREE's recommendations {\em 
	omit} a code attribute. Note that the {\em more often} XTREE omits an 
	attribute, the more likely it is {\em not} to endorse addressing a bad 
	smell based on the omitted attributes.

	{\bf RQ4: Stability:} Across different projects, how variable are the 
	changes recommended by XTREE?   To answer this
	question, we conduct a large scale ``what if'' study that reports all the 
	possible recommendations XTREE might make. We then count how often 
	attributes are {\em not} found in the recommendations arising from this 
	``what if'' study.

	{\bf RQ5: Conjunctive Fallacy:} Is  it  always  useful  to  apply \eq{df}; 
	i.e.   make  code  better  by  reducing  the  values  of multiple code 
	attributes? To answer this question, we will look at the {\em direction of 
	change} seen in the {\bf RQ4} study; i.e.
	how often XTREE recommends decreasing or increasing a static code attribute.

	\subsection{Test Data}\label{sect:tesd}

	To explore these research questions, we used data from Jureczko et al.'s 
	collection of object-oriented Java systems~\cite{jureczko10}. To access 
	that data, go to   git.io/vGYxc.
	The Jureczko data records the number of known defects for each class using 
	a post-release bug tracking system. The classes are described in terms of 
	nearly two dozen metrics included in the Chidamber and Kemerer metric 
	suite, such as number of children (noc), lines of code (loc), etc. For 
	details on the Jureczko code
	metrics, see  \fig{ck} and corresponding text in \tion{dataset}. For 
	details on the versions of that data that were used for training and 
	testing purposed see the left-hand-side columns of \fig{j}.

	\subsection{Building the Secondary Verification Oracle}
	\label{sect:eval}

	As mentioned in the introduction, our proposed framework has two oracles:
	a primary change oracle (XTREE) and the secondary verification oracle 
	described in this section.

	\rahul{
	It can be difficult  to judge the  effects of removing bad 
	smells.
	Code that is reorganized cannot be assessed just by a rerun of the test
	suite for three reasons: (1) Test suites may not 
	be 
	designed to identify code smells, they only report pass/fail based on 
	whether or not a specific module runs. It is entirely possible that a test 
	case may pass for code that contains one or more code smells; (2) While 
	smells are certainly symptomatic of design flaws, not all smells cause the 
	system to fail in manner suitable for identification by test cases; and (3) 
	It make take a significant amount of effort to write new test cases that 
	identify bad smells, especially for relatively stable software systems. 
	Additionally, since we 
	can not be sure if reorganizations do/don't change the system behavior, for 
	instance cases where a reorganization effort involves only refactoring, it 
	becomes difficult to assert when a test case will pass or fail.}

		\input{prediction_stats.tex}

	To resolve this problem, SE researchers such as
	Cheng et al.~\cite{Cheng10}, O'Keefe et al.~\cite{OKeeffe08,OKeeffe07},
	Moghadam~\cite{Moghadam2011} and Mkaouer et al.~\cite{Mkaouer14}
	use a {\em secondary verification oracle} that is learned separately
	from the primary oracle. The verification oracles assesses
	how defective the code is before and after some
	code reorganization.
	For their second oracle,
	Cheng, O'Keefe, Moghadam and  Mkaouer et al. use the QMOOD hierarchical
	quality model~\cite{Bansiya02}.
	A shortcoming of QMOOD
	is that quality models learned from other projects
	may perform poorly when applied to new projects~\cite{me12d}.
	Hence, for this study, we  eschew
	older quality models like QMOOD. Instead, we use
	Random Forests~\cite{Breiman2001} to learn defect predictors
	from OO code metrics.
	Unlike QMOOD, the predictors
	are specific to the project.
	% 		, and the measurements can be reconstructed and the predictors 
	%rebuilt for other projects.

	Random Forests are a decision tree learning method but
	instead of building one tree, hundreds are built using
	randomly selected subsets of the data. The final predictions
	come from averaging the predictions over all the trees.
	Recent studies endorsed the use
	of  Random Forests for  defect prediction~\cite{lessmann}.

	\fig{j} shows  our results with Random Forests and
	the Jureczko data. The goal is to build a verification oracle based on 
	Random Forest that accurately distinguishes between defective and 
	non-defective files based on code metrics. Given $V$ released versions, we 
	test on version $V$ and train on the available data from $V-1$ earlier 
	releases.

	The \colorbox{lavenderpink}{three bottom rows}  are marked 
	with $\times$: these contain predominately defective classes (two-thirds, 
	or more).  It is hard to build a model that distinguishes non-defective 
	files from defective files in these data sets due to the high percentage of 
	defective file examples.

	We use Boolean classes in the  Jureczko data to identify the presence or 
	absence of defects: \texttt{True} if defects \textgreater 0; \texttt{False} 
	if defects = 0. The quality of the predictor is measured using (a) the  
	probability of detection \textit{pd} (i.e., recall):  the percent of faulty 
	classes in the test data detected by the {\em predictor}; and (b) the  
	probability of false alarm \textit{pf} (i.e., false positives): the percent 
	of non-fault classes that are {\em predicted} to be defective.

	\rahul{
	\subsubsection{Impact of Tuning}
	\label{sect:tune}

	The ``untuned'' columns of \fig{j}
	show a preliminary study using Random Forest with its ``off-the-shelf'' 
	tuning of 100 trees per forest.
	The forests were built from training data and applied to test data
	not seen during training.  In this
	study, we called a data set ``usable'' if   Random Forest was able to 
	classify the instances with a performance threshold of $\mathit{pd}\ge 60 
	\wedge \mathit{pf} \le 30$\% (determined from standard results in other 
	publications~\cite{me07b}). We found that no  data set satisfy
	this criteria.

	To salvage Random Forest we first applied the SMOTE algorithm to improve 
	the 
	performance of the classifier by handling class imbalance in the data sets. 
	Pelayo 
	and Dick~\cite{pelayo07} report that defect prediction is improved by 
	SMOTE~\cite{chawla2002smote}; i.e. an over-sampling of minority-class 
	examples and an under-sampling of majority-class examples.

	In a recent paper, Fu et al.~\cite{fu:ase15} reported that parameter 
	tuning with differential evolution~\cite{storn97} can quickly explore the 
	tuning options of Random Forest to find better settings for the size of the 
	forest, the termination criteria for tree generation, and other parameters. 
	In a setting similar to theirs, we implemented a multiobjective 
	differential evolution to tune Random Forests for each of the above 
	datasets.

	Setting goals for tuning can be a very difficult task. Fu et 
	al. warn that choosing goals must be undertaken with caution. Opting to 
	optimize individual goals such as recall/precision of a learner can have 
	undesirable outcomes. For instance, by tuning for recall we can achieve 
	near 100\% recall -- but at the cost of a near 100\% false alarms. On the 
	other hand, when we tune for false alarms, we can achieve near zero percent 
	false alarm rates by effectively turning off the detector (so the 
	recall falls to nearly zero). Therefore, in our work, we used used a 
	``multiobjective'' search to tune for both recall and false alarm at the 
	same time. A multiobjective search attempts to find settings that achieve a 
	\textit{trade-off} between the goals (in this case maximizing recall and 
	minimizing false alarm at the same time).

	The effect of tuning and using SMOTE were remarkable.The rows 
	\colorbox{celadon}{marked with a $\star$} in \fig{j} show data 
	sets whose performance was improved by these techniques. For 
	example, in {\em poi}, the recall increased by 4\% while the false alarm 
	rate dropped by 21\%. In \textit{Ivy, Jedit, Lucene,} and \textit{Xalan} 
	there was a 
	significant improvement in one measure (recall or false alarm) with no 
	deterioration in the other measure. Finally, in \textit{Poi} and 
	\textit{Ant} there was a significantly large improvement in one metric with 
	a very small deterioration in the other.

	However, as expected, we could not salvage all the data 
	sets. Therefore, we eliminated the data sets for which we could not build 
	an adequately performing Random Forest classifier with $\mathit{pd}\ge 60 
	\wedge \mathit{pf} \le 30$\%. Thus, our analysis uses the {\em jedit, ivy, 
	ant, lucene} and {\em poi} data sets for evaluating recommended changes.}

	We note that SMOTE-ing and
	parameter tunings were applied to the training data only and not to the 
	test data.

	\subsection{Statistics}

	We use 40 repeated runs for each code reorganization recommendation 
	framework 
	for each of the five data sets (we use 40 since that is  more than the 30 
	samples  needed to satisfy the central limit theorem). Each code 
	organization framework is trained on versions $1...N-1$ of $N$ available 
	versions in each data set.
	Each run collects the improvement scores defined in \eq{diff}: the 
	reduction in the percentage of defective classes as identified by the 
	verification oracle after applying the recommended code metric changes.

	We use multiple runs with different random number seeds since two of our 
	methods use some random choices: CD uses the  stochastic WHERE clustering 
	algorithm~\cite{me12d}
	while XTREE non-deterministically picks thresholds randomly from
	the high and low boundary of a range.
	Hence, to compare all
	four methods, we must run the analysis many times.

	\input{results_jur.tex}

	To rank these 40 numbers collected from CD, XTREE, Shatnawi, and Alves et 
	al., we use the Scott-Knott test recommended by Mittas and 
	Angelis~\cite{mittas13}.
	Scott-Knott is a top-down clustering approach used to rank different
	treatments. If that clustering finds an interesting division of the data, 
	then
	some statistical test is applied to the two divisions to check if they
	are statistically significant different. If so, Scott-Knott recurses
	into both halves.

	To  apply Scott-Knott,
	we
	sorted a list of  $l=40$ values of \eq{diff} values found in  $ls=4$ 
	different methods.
	Then, we split $l$ into sub-lists $m,n$ in order to maximize the expected 
	value of differences in the observed performances before and after 
	divisions. E.g. for lists $l,m,n$ of size $ls,ms,ns$ where $l=m\cup n$: 
	\[E(\Delta)=\frac{ms}{ls}abs(m.\mu - l.\mu)^2 + \frac{ns}{ls}abs(n.\mu - 
	l.\mu)^2\]
	We then apply a apply a statistical hypothesis test $H$ to check
	if $m,n$ are significantly different  (in our case, the conjunction of A12 
	and bootstrapping). If so, Scott-Knott recurses on the splits. In other 
	words, we divide the data if \textit{both} bootstrap sampling and effect 
	size test agree that a division is statistically significant (with a 
	confidence of 99\%) and not a small effect ($A12 \ge 0.6$).
	For a justification of the use of non-parametric bootstrapping, see Efron 
	\& Tibshirani~\cite[p220-223]{efron93}. For a justification of the use of 
	effect size tests see Shepperd\&MacDonell~\cite{shepperd12a}; 
	Kampenes~\cite{kampenes07}; and Kocaguenli et 
	al.~\cite{Kocaguneli2013:ep}. 
	These researchers warn that even if a hypothesis test declares two 
	populations to be ``significantly'' different, then that result is 
	misleading if the ``effect size'' is very small. Hence, to assess the 
	performance differences we first must rule out small effects using A12, a 
	test   recently endorsed by Arcuri and Briand at ICSE'11~\cite{arcuri11}.

	The Scott-Knott  results are presented in the form of line diagrams like 
	those shown on the right-hand-side of \fig{jur2}.
	The black dot shows the median \eq{diff} values and the horizontal lines 
	stretches
	from the 25\textsuperscript{th} percentile to the 75\textsuperscript{th} 
	percentile (the inter-quartile range, IQR).
	As an example of how to read this table, consider the {\em Ant}
	results. Those rows are  sorted on the median values of each framework. 
	Note 
	that all the methods have \eq{diff}~\textgreater~$0\%$; i.e. all these 
	methods reduced the expected value of the performance score while XTREE 
	achieved the greatest reduction (of 56\% from the original value).
	These results table has a  left-hand-side  {\bf Rank} column, computed 
	using the
	Scott-Knott test described above. In the {\em Ant}
	results, XTREE is ranked the best, while CD is  ranked   worst.

	\input{rq2.tex}
	\section{Results}

	\begin{figure*}[!t]
		\centering
		\includegraphics[width=\linewidth]{changes01}
		\caption{Results  from XTREE.
			While \fig{counts} are the {\em number} of times a code metric was 
			changed,
			this  figure shows the {\em magnitude} each code metric was 
			changed. Each vertical bar
			marks the 27,50,75\textsuperscript{th} percentile change seen in 40 
			repeats.
			All numbers are ratios of initial to final values.
			All bar regions marked in gray show {\em increases}.
			The interesting feature of these results are that many
			of the changes proposed by XTREE require {\em increases}
			(this puzzling observation is explained in the text).}
		\label{fig:changes}
	\end{figure*}

	\subsection{RQ1: Effectiveness}

	{\em Which of the methods defined in Section 3 is the best change oracle 
	for identifying what and how code modules should be changed? }

	\fig{jur2} shows the comparison results.
	Two data sets are very responsive to defect reduction suggestions:
	Ant and Ivy (both of which show best case improvements over 50\%).
	The  expected value of defects
	is changed less in Jedit. This data set's results are
	surprisingly uniform; i.e.   all methods
	find the same ways to reduce the expected number of
	defects.

	\fig{changes} enables us to explain the uniformity
	of the results seen with Jedit in \fig{jur2}.
	Observe how in \fig{changes} the only change ever
	found is a reduction to {\em rfc}. Clearly, in this
	data set, there is very little that can be usefully changed.

	Two data sets are not very responsive to defect reduction:
	Poi and Lucene. The reason for this can be see in \fig{j}:
	both these data sets contain more than 50\% defective modules.
	In that space, all our  methods lack a large sample of
	defect-free examples.

	Also consider the relative
	rank of the different approaches,
	CD and Shatnawi usually  perform comparatively worse while  XTREE gets top 
	ranked position the most
	number of times. That said, Alves sometimes beats XTREE (see Ivy)
	while sometimes it ties (see Jedit).

	In summary, our {\bf Result1} is  that, of the change oracles studies here,
	XTREE is the best oracle on how to change code modules in order to reduce 
	defects in our data sets.

	\input{all_changes.tex}

	\subsection{RQ2: Verbosity}

	{\em Which of the Section 3 methods recommended changes to the fewest code 
	attributes?}

	\fig{counts} shows the frequency with which the methods
	recommend changes to specific code metrics.
	Note that XTREE proposes thresholds to
	few code metrics compared to the other approaches.

	% COMMENT From LL: This is such a strange way of putting this lesson, and 
	%you haven't actually evaluated this.
	%

	Hence, our {\bf Result2} is that, of all the code change oracles 
	studied here, XTREE recommended far fewer changes to static code 
	measures. Note only that,   combining  \fig{jur2} with \fig{counts}, 
	we   see that
	even though XTREE proposes changes to far fewer code metrics, those few
	code metrics are usually just as effective (or
	more effective) than the multiple
	thresholds
	proposed by CD, Shatnawi or Alves.  That is, XTREE proposes
	{\em fewer} and better thresholds than the other approaches.

	\subsection{RQ3: Stopping}

	{\em  How effective is XTREE at offering   ``stopping points'' (i.e. clear 
	guidance on what not to do)?}

	The {\bf RQ2} results showed that XTREE's recommendations are small in a 
	{\em relative sense}; i.e. they are
	relatively smaller than the other methods studied here.
	Note also that, XTREE's recommendations are small in an {\em absolute 
	sense}.
	Consider the frequency of changes in \fig{counts}. There are very few 
	values for XTREE that are over 33\% (in our sense this translates to at 
	least a third of our repeated runs where XTREE mentioned a code 
	attribute). 
	For Ant, Ivy, Lucene, Jedit, and Poi, those frequencies
	are  \mbox{3, 3, 3, 4, 1, 2} respectively (out of twenty). This means 
	that, 
	usually, XTREE omits references to \mbox{17,17,17,16,19,18} static code 
	attributes (out of 20). Any code reorganization based on a bad smell 
	detector that uses  these omitted code attributes could hence  be stopped.

	Hence our {\bf Result3} is that, in a any  project,  XTREE's  recommended  
	changes affect only one to four of the 20 static code attributes.  Any bad 
	smell defined in terms of the remaining 19 to 16 code attributes (i.e. 
	most 
	of them) would be deprecated.

	\subsection{RQ4: Stability}

	{\em Across different projects, how variable are the changes recommended by 
	our best change oracle? }

	\fig{counts} counted how {\em often} XTREE's recommendations mentioned a 
	static code attribute.
	\fig{changes}, on the other hand, shows the {\em direction} of XTREE's 
	recommended change:
	\bi
	\item Gray bars show  an  {\em increase} to a static code measure;
	\item White bars shows a   {\em decrease} to a static code measure;
	\item Bars that are all white or all gray indicate that in our 40 repeated 
	runs, XTREE recommended changing an attribute the same way, all the time.
	\item Bars that are mixtures of white and gray mean that, sometimes, XTREE 
	makes different recommendations about how to change a static
	code attribute.
	\ei
	Based on \fig{changes}, we see {\bf Result4} states that the direction of 
	change recommended  XTREE is  very stable repeated runs of the program  
	(evidence:
	the bars are mostly the same color).

	\fig{changes} also comments on the inter-relationships between static code 
	attributes. Note that while some measures in
	\fig{changes} are decreased, many are increased.
	For example, consider the {\em Poi} results
	from \fig{counts} that recommends decreasing {\em loc}
	but making large increases to {\em cbo} (coupling between
	objects). Here, XTREE is advising us to break up
	large classes class by into services
	in other classes. Note that such a code reorganization will, by
	definition, increase the coupling between objects.
	Note also that such increases  to reduce
	defects would never be proposed by the outlier methods
	of Shatnawi or Alves since their core assumption is that bad
	smells arise from unusually large code metrics.

	\subsection{RQ5: Conjunctive Fallacy}
	\label{sect:conjunct}
	{\em  Is  it  always  useful  to  apply \eq{df};  i.e.   make  code  
	better  by  reducing  the  values  of multiple code attributes?}

	\rahul{
	In  \fig{changes}, the bars are colored both white and gray; i.e. XTREE 
	recommends {\em decreasing} and {\em increasing}
	static attribute values. That is, always decreasing static code measures 
	(as suggested by \eq{df}) is {\em not} recommended by XTREE. This comments 
	on the interconnectedness of metrics and it is important for a few reasons:

	\be
	\item When developers follow suggestions offered based on static code 
	metrics, they are often required to reduce several metrics at once. For 
	example, in \fig{counts} we notice all methods except XTREE recommend 
	changes to \textit{every} metric. This is not a practical approach and it 
	renders these suggestions useless.
	\item When XTREE recommends changes, it respects the interconnectedness of  
	metrics. If we were to reduce LOC, other metrics to do with coupling (cbo, 
	ca, ce, ...) would have to be changed as well. XTREE is aware of this and 
	suggests changes to 
	these metrics in conjunction with LOC. Additionally, it offers a direction 
	of change (increase or decrease). 
	\ee

	Now when programmers follow the recommendations of XTREE instead for 
	reorganization, they do so fully aware of the impact that change can have 
	on other metrics. For instance, a programmer who chooses to reduce LOC is 
	now aware that a consequence would be increased coupling. She/he can 
	continue to make this change because similar changes with lower 
	LOC and higher coupling have historically been known to result in fewer 
	defects.

	}

	To explore this point further, we conducted the following ``what-if'' 
	study. Once XTREE builds its trees with its leaf clusters then:
	\bi
	\item Gather all clusters $C_0$ for $C_1$ such that the percent of defects 
	in $C_0$ 
	is greater than $C_1$ \ldots
	\item For all attribute measures, identify ones that have a statistically 
	significantly different distribution between each $C_0$ and $C_1 $...
	\item Report the direction of change ($+$ indicates an \textit{increase} in 
	values 
	and $-$ indicates a \textit{decrease})
	\ei

	{\color{steel}
	Note that the changes found in this way are somewhat more general than the 
	results presented in~\fig{jur2}. Those results were limited to comments on 
	the test set given to the program given that the tree is constructed using 
	the training set.

	Performing a ``what-if'' analysis using the three steps presented above 
	allow us to reflect on {\em all possible changes} for any dataset (not 
	limited to only one instance from the test set). This is significant 
	because it comments on some of the commonly held notions regarding static 
	code attributes. Figure ~\ref{fig:multcomp} which shows the results of this 
	``what if'' analysis can better help understand this. Consider as an 
	example the metric loc, as might be expected, the recommendation is to
	\textit{always} reduce lines of code (loc). But for the other attributes 
	like afferent and efferent coupling, contrary to popularly recommendations,
	XTREE in fact suggests to increase those values or leave them unchanged, 
	but \textit{not} decrease. Similarly, coupling between objects (cbo) needs 
	to be decreased in Ant and Ivy but increased in Poi and Lucene. Finally, 
	many metrics such as depth of inheritance tree (dit), are best left 
	unchanged in all cases.

	This is quite significant for practitioners 
	attempting to perform code reorganization to similar projects without a 
	historical log. They can use these findings as guide to: (1) deprecate 
	changes the show no demonstrable benefits; and (2) not limit themselves to 
	reducing values all the metrics because an increase can sometimes be more 
	beneficial.

	Hence, {\bf Result5} is that while XTREE always recommends reducing loc,
	it also   often recommends increasing the values of other static code 
	attributes.}

	\section{Limitations and Future Work}
	\label{sect:future}
	\rahul{

		XTREE offers to assist reorganization efforts in an intelligent 
		fashion, it suffers from two key limitations: (1) They use supervised 
		learning to learn about the domain, therefore they need a sufficiently 
		large dataset so as to be ``trained''. \fig{j} shows the dataset used 
		in this study all have at least two prior releases; (2) Ability to 
		build a reliable secondary verification oracle. We used the current 
		state of the art in build our verification oracle (Tuned and SMOTE-ed 
		Random Forest).

        In this work, both the primary change oracle and the secondary 
        verification oracle 
        used OO metrics in conjunction with the number of associated defects to 
        operationalize code smells. We note this goal can very easily be 
        replaced by other quantifiable objectives. For example, there is much 
        research on \textit{technical debts} in recent years.
        The notion of technical debt reflects the extra work arising
        from developers making pragmatic short-term decisions
        that make it harder, in the long-term, to maintain the software.
        A recent study by 
        Ernst et al.~\cite{ernst15} showed that practitioners agree on the 
        importance of the issue but existing tools are not currently helpful in 
        managing the debts. A systematic literature survey conducted by Li et 
        al.~\cite{li15td} report that dedicated technical debt management (TDM) 
        tools are needed for managing various types of technical debts. XTREE 
        could be adapted for this purpose-- providing that there existed
        a working ``secondary oracle'' (of the kind we define in our introduction)
        that can recognize quick-and-dirty sections of code.

		Our research shows that it is potentially na\"{\i}ve to explore 
		thresholds in static code attributes in isolation to each other. 
		This work clearly demonstrates how changing one necessitates changing 
		other associated metrics. So, for future work, we recommend that 
		researchers and practitioners look for tools that recommend changes to 
		sets 
		of code changes. When exploring candidate technologies, apart from 
		XTREE, 
		researchers may potentially use: (1) Association rule learning; (2) 
		Thresholds generated across synthetic dimensions (eg. PCA); and (3) 
		Techniques that cluster data and look for deltas between them. (Note: 
		we 
		offer XTREE as a possible example of this point).

		Lastly, we also
		plan on extending our work by exploring scalable 
		solutions 
		to achieve similar results in much larger datasets. After this, we 
		shall 
		look at applications beyond that of measuring static 
		code attributes. For example, as an initial attempt, we have been 
		looking 
		at sentiment analysis in stack overflow exchanges to learn dialog 
		pattern 
		that most select for relevant entries.}

	\section{Reliability and Validity of Conclusions}
	\label{sect:valid}

	The results of this paper are biased by our choice of code reorganization
	goal (reducing defects) and our choice of measures collected from software
	project (OO measures such as depth of inheritance, number of child classes,
	etc). That said, it should be possible extend the methods of this paper to 
	other
	kinds of goals (e.g. maintainability, reliability, security, or the 
	knowledge sharing
	measures) and other kinds of
	inputs (e.g. the process measures favored by Rahman,
	Devanbu et al.~\cite{Rahman2013})

	\subsection{Reliability}
	Reliability refers to the consistency of the results obtained
	from the research. It has at least two components: internal
	and external reliability.

	Internal reliability checks if an independent researcher
	reanalyzing the data would come to the same conclusion.
	To assist other researchers exploring this point, we offer a full 
	replication package for this study at
	https://github.com/ai-se/XTREE\_IST.

	External reliability assesses how well independent researchers
	could reproduce the study. To increase external
	reliability, this paper has taken care to clearly define our
	algorithms. Also, all the data used in this work is available
	online.

	For the researcher wishing to reproduce our work to other kinds of goals, 
	we offer the following advice:

	\bi
	\item Find a data source for the other measures of interest;
	\item Implement another secondary verification oracle that can assess 
	maintainability, reliability, security, technical debt, etc;
	\item Implement a better primary verification oracle that can do ``better'' 
	than XTREE at finding changes (where ``better'' is defined in terms
	of the opinions of the verification oracle). 
	\ei

	\subsection{Validity}

	This paper is a case study that studied the effects of  limiting 
	unnecessary code reorganization on some data sets. This section discusses 
	limitations of such case studies. In this context, validity refers to the 
	extent to which a piece of research actually
	investigates what the researcher purports to investigate.
	Validity has at least two components: internal and
	external validity.

	Based on the case study presented above,
	as well as the discussion in \tion{prelim},
	we believe that bad smell indicators (e.g. \mbox{{\em loc}$>$ 100})
	have limited external validity beyond the projects from which they are 
	derived.
	While specific models are externally valid,
	there may still be general methods like XTREE for finding the good local 
	models.

	Our definition of bad smells is limited to those represented by OO code 
	metrics (a premise often used in related work).
	XTREE, Shatnawi, Alves et al. can  only comment
	on bad smells   expressed as code metrics
	in the historical log of a project.

	If developers want to justify their code reorganizations
	via bad smells expressed in other terminology,
	then the  analysis of this paper must:
	\begin{itemize}
		\item Either wait till
		data about those new
		terms has been collected.
		\item Or, apply cutting edge transfer learning
		methods~\cite{Nam15,Jing15, krishna16} to map data from other projects
		into the current one.
	\end{itemize}
	Note that the transfer learning approach would
	be highly experimental and require more study
	before it can be safely recommended.

	Sampling bias threatens any data mining analysis; i.e., what matters
	there may not be true here. For example, the data sets used here comes 
	from 
	Jureczko et al. and any biases in their selection procedures
	threaten the validity of these results.
	That said,
	the best we can do is define our methods and publicize our data and code so 
	that other researchers can
	try to repeat our results and, perhaps, point out a previously unknown bias
	in our analysis. Hopefully, other researchers will emulate our methods in
	order to repeat, refute, or improve our results.

	\section{Conclusions}
	How to discourage useless code reorganizations?
	We say:
        \begin{quote}{\em Ignore those changes
            not supported by the historical log of data from
	the current project.}\end{quote}
	When that data is not available (e.g. early
	in the project) then developers could use the general list of
	bad smells shown in \fig{smells}. However,
	our results
	show that  bad smell detectors are most
	effective when they are based
	on a small handful of code metrics (as done by XTREE).
	Hence, using all the bad smells of \fig{smells} may not be optimal.

	For our better guess at how to reduce defects by changing code attributes,
	see  Figure ~\ref{fig:multcomp}. But given the large variance if the 
	change 
	recommendations, we strongly advice teams to use
	XTREE on their data to find their own best local changes.

	XTREE improves on prior methods for generating bad smells:
	\begin{itemize}
		\item As described in \tion{prelim}, bad smells generated by humans may 
		not be applicable to the current project. On the other hand, XTREE can 
		automatically learn specific thresholds
		for bad smells for the current project.
		\item Prior methods used an old quality predictor (QMOOD) which we 
		replace with defect predictors learned via Random Forests
		from   current project data.

		\item XTREE's conjunctions proved to be arguably as effective
		as those of Alves (see \fig{jur2}) but far less verbose (see 
		\fig{counts}). Since XTREE {\em approves} of fewer changes
		it hence {\em disapproves} of most changes. This makes it a better 
		framework 
		for critiquing and rejecting
		many of the code reorganizations.
	\end{itemize}
	Finally, XTREE does not suffer from the conjunctive fallacy.
	Older methods, such as those proposed by  Shatnawi and Alves assumed
	that the best way to improve code is to remove outlier  values. This may 
	not work since when code is reorganized,
	{\em the functionality has to go somewhere}. Hence,  reducing the lines of 
	code in one module necessitates
	{\em increasing} the coupling that module
	to other parts of the code. In future, we recommend software team use bad 
	smell detectors that know what attribute measures
	need {\em decreasing} as well as {\em increasing}.

	% In summary, this paper offers a baseline result
	% that XTREE can be used as a {\em diagnostic tool}
	% for identifying which bad smells can be ignored.
	% Can it be used as a {\em prescriptive tool}
	% to recommend new refactorings? This would require

	% As discussed in {\em PROBLEM \#2}
	% (from the introduction), XTREE might propose
	% changes to code metrics that are
	% not feasible  (due to the local domain constraints
	% of the code). To repair this, XTREE needs to be extended
	% with architectural knowledge of the code it is studying.
	% Elsewhere, we have had some   success
	% with reasoning about such architectural knowledge
	% (expressed as software product lines~\cite{sayyad13a,sayyad13b}). In 
	%future
	% work, we will explore extending XTREE
	% with
	% architectural knowledge such that it can
	% become a tool which prescribes
	% feasible refactorings.

	\section*{Acknowledgements}
	The work is partially funded by NSF  awards \#1506586 and \#1302169.

	% \bibliographystyle{plain}
	\balance
	\bibliographystyle{unsrt}
	\bibliography{References}

%	
%	
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%	%%% RESPONSE TO REVIEWERS
%	
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%	\pagebreak
%	\newpage
%	\appendix
%	\renewcommand*{\thesection}{\Alph{section}}
%	\nobalance
%	\section*{RESPONSE TO REVIEWERS}
%	\section*{Comments from the editor}
%	\review{The reviewers have finished to  evaluate your work. 
%	As you 
%	can observe, they raised some concerns that deserve your attention~$\ldots$}
%	
%	\noindent Thank you very much indeed for your comments.\\
%	
%	
%	\review{ $\ldots$  It is important that you take into account their 
%	comments and 
%	evolve the paper accordingly. Please,  evolve the paper to make clear the 
%	defect model, hypothesis, limitations and readability}
%	
%	We offer clarifications to all the issues highlighted by the reviewers. In 
%	addition to these, we have made several key modifications to our paper. We 
%	have changed the title of our paper to reflect the changes we have made. In 
%	order to assist reviewers in tracking our changes, we have ensured all 
%	new additions are {\color{steel} highlighted in blue}. 
%	A brief summary of our changes are listed below:
%	\be
%	\item At the suggestion of Reviewers 1 and 2, we have included a section on 
%	the choice of datasets. Additionally, we have greatly expanded the section 
%	on defect prediction to highlight its importance and its relevance to our 
%	work.
%	\item To address comments by Reviewer~\#1 on how this work fits in with the 
%	body of knowledge, we have compiled a new section (see~\tion{prior}) on the 
%	previous attempts to address similar issues. 
%	\item Further, at the suggestion of Reviewer~\#1, we have included a 
%	section remarking on the key limitations of our work. It now appears as a 
%	new section (see \tion{future}).
%	\item Also, as a response to Reviewer~\#1's comments, we have modified the 
%	future work section to reflect the implications of our findings on 
%	\textit{technical debt}. 
%	\item We acknowledge Reviewer~\#2's comment that our initial submission 
%	lacks a formal introduction of software ``defects" and its relevance to 
%	code reorganization. In order to address this, we have attempted to 
%	clarify 
%	the interpretation of defects in our work. As for other issues related to 
%	defects, we have added a new section on the choice of datasets 
%	(see~\tion{dataset}).
%	\item Also, keeping in mind the suggestions of Reviewer~\#2, we have 
%	rewritten the research questions (especially, RQ1 and RQ5).
%	\item Additionally, at the suggestion of Reviewer~\#2, we clarify our 
%	descriptions of several figures included in this paper. Specifically, we 
%	expand on the importance of tuning which relates to \fig{j} (previously 
%	Figure 4). We also expand on the significance of \fig{multcomp} 
%	(previously 
%	Figure 8).
%	\item Finally, we have evolved our paper in the most appropriate areas in 
%	response to all the major and minor issues raised by both Reviewer~\#1 and 
%	Reviewer~\#2.
%	\ee
%	
%	\section*{Response to Reviewer~\#1}
%	
%	Thank you for your detailed comments. Our new draft contains many 
%	corrections, clarifications, and extensions as directed by your feedback.
%	All our changes are marked in the body and appears in {\color{steel} 
%	blue}.\\
%	
%	\review{I missed a section discussing possible implications for 
%	researchers 
%	and practitioners. How the results of this work contribute to future 
%	research activities in the area? How practitioners can benefit from the 
%	results achieved in the paper?}
%	
%	
%	You're quite correct, there was no future work section in the paper. The
%        following text
%	has been included in the revised submission and appears in~\tion{future} 
%	(see {\color{steel} Reviewer 1a}). 
%	
%	
%	\begin{quote}``Our research shows that it is potentially na\"{\i}ve to 
%explore 
%	thresholds in static code attributes in isolation to each other. 
%	This work clearly demonstrates how changing one necessitates changing 
%	other associated metrics. So, for future work, we recommend that 
%	researchers and practitioners look for tools that recommend changes to sets 
%	of code changes. When exploring candidate technologies, apart from XTREE, 
%	researchers may potentially use: (1) Association rule learning; (2) 
%	Thresholds generated across synthetic dimensions (eg. PCA); and (3) 
%	Techniques that cluster data and look for deltas between them. (Note: we 
%	offer XTREE as a possible example of this point).''
%	
%	``Additionally, we plan on extending our work by exploring scalable 
%solutions 
%	to achieve similar results in much larger datasets. After this, we shall 
%	look at applications beyond that of measuring static 
%	code attributes. For example, as an initial attempt, we have been looking 
%	at sentiment analysis in stack overflow exchanges to learn dialog pattern 
%	that most select for relevant entries.''
%        \end{quote}
%	
%	
%	\review{I also missed a section presenting the main limitations of 
%	the 
%	work. Although some words have been said about it, I believe it is 
%	important to have a more structured discussion on a specific section.}
%
%	You are quite correct that we have missed a section highlighting the key 
%	limitations of our work. In the revised paper, we have dedicated a section 
%	to discussing the 
%	limitations and future work (see {\color{steel} Reviewer1b} in 
%	~\tion{future}).\\
%	
%	\review{It would be interesting to have further discussion at the 
%	end 
%	indicating how this work complements the body of knowledge about code 
%	smells. Do 
%	reached results indicate a similar direction? contradictory? Does This work 
%	somehow confirms the results of other studies or points to new 
%	directions?}
%
%	Thank you for your comment, we admit the last version of the paper has 
%	an inadequate discussion on this matter. This revised version now includes 
%an 
%	expanded prior work section which places greater emphasis on these issues 
%	(see {\color{steel} Reviewer1c} in 
%	\tion{prior}). 
%	
%	As to your specific comment that this be included in the 
%	end, we feel our response to this recommendation is an important note on 
%	the state-of-the-art in this area. We have therefore added it towards the 
%	beginning of the paper instead, so it may premise the rest of our work.\\
%		
%	\review{$\ldots$ this work evaluated XTREE, a framework to 
%	evaluate whether a code reorganization is likely to have a perceivable 
%	benefit in terms of defect-proneness. It is fine to have this scope 
%	(defect-proneness) in terms of evaluation. However, it would be nice to 
%	have a discussion on why this characteristic (defect-proneness) is good to 
%	support the decision on code reorganization and/or how it could complement 
%	other characteristics.}
%	
%	You are quite right in pointing out that we need a better description of 
%	defect proneness. We have now added a section on defect-proneness and its 
%	relevance to our paper (please see content marked with {\color{steel} 
%	Reviewer1d} in~\tion{dataset}).\\
%
%	\review{$\ldots$ nowadays we are seeing a growing discussion on 
%	technical debt, 
%	that brings financial aspects (interest, principal, debt…) to the 
%	decision-making process on development activities. Could we use XTREE as a 
%	strategy to prioritize the payment of technical debt items?}
%	
%	Thank you for that suggestion. We do think XTREE can be used as a 
%	recommendation system to prioritize technical debt. In our revised paper, 
%	we expanded the introduction to highlight this possibility (see 
%	content prefixed with {\color{steel}Reviewer1e} in \tion{future}).\\
%	
%	\review{Finally, I have one last question: is there any reason for 
%	do not 
%	use the GQM template to state the goal of the study and also to define null 
%	and alternative hypotheses for the research questions?}
%
%        We can certainly do that if you wish. As to why we {\em didn't} do it,
%        this paper is clearly MSR-conference-style and not
%        ESEM-conference-style (GQM is less uses at MSR than ESEM).
%
%        To whether or not that is a ``good thing'' or not, we cannot say. What
%        we would say is that we think our use of stand-out boxes for research
%        findings makes our results easy to access within this paper.
%
%        That said, if the reviewer thinks this paper needs further structuring
%        to clarify our message then, of course, we would follow that direction.
%        
%%	\texttt{XXX}
%	
%	\section*{Response to Reviewer~\#2}
%	
%	Thank you for your detailed review. We have made several 
%	corrections, clarifications, and revisions as directed by your comments, 
%	this new draft is significantly improved thanks to your feedback. 
%	
%	\noindent All our 
%	changes are marked in the body and appears in 
%	{\color{steel} blue}.\\
%	
%	\review{The introduction talks about Fowler’s bad smells and 
%	refers to 
%	literature on the (often contradictory) effects of such smells. And Figure 
%	1 shows a list of bad smells. However, without making it clear, the paper 
%	continues to talk about smells but the real topic is not the smells but the 
%	metrics that are used to identify various smells. What’s the connection 
%	between whether a smell is bad or not and the threshold values of the 
%	various code metrics?}
%
%	Thank you for this comment. At your suggestion, we have significantly 
%	expanded \tion{dataset} in order to discuss the use of static code metrics 
%	with regards to code smells.\\
%	
%	\review{I also find it very difficult to understand the conceptual model of 
%	defects in this paper~\ldots}
%	
%	We do apologize for the inconvenience.
%Your remark clearly indicates that we need to further clarify our use
%        of the term.
%        So at your suggestion, we have 
%	dedicated a section to discussing the choice of dataset in \tion{dataset} 
%	(please see content marked with 
%	{\color{steel} Reviewer2a}).\\
%	
%	\review{\ldots~The concept of “number of defects (defect counts)” 
%	is fully mixed with the concept of “percent of classes with 
%	defects/defective modules/ presence or absence of defects”. What does it 
%	then mean to “reduce defects in our data sets”? Is it the total number of 
%	defects in the data set (system?) or the number of “infected modules” in 
%	the data set?}
%	
%	We have clarified this in \tion{dataset}. Briefly, with respect to the 
%	datasets used in this study, when we say, ``reduce defects in our data 
%	sets,'' we refer to 
%	reorganizing code such that our secondary oracle reports
%    that the number of infected modules (i.e., classes with 
%	$\texttt{nDefects}>0$) is reduced to having \textit{no defects}.
%    For notes on our {\em primary} and {\em secondary} oracle, see page2, 
%    column1, of this paper.
%	
%	In response to your  comment, we have expanded \tion{dataset}, to 
%	better explain this in much greater detail (please see content marked with 
%	{\color{steel}Reviewer2b} in \tion{dataset}). \\
%
%   \review{ Section 2 discusses the idea of why not just ask developers
%     about the effect of code smells when the research literature is
%     contradictory. The authors argue that practitioners
%     should not be expected resolve contradictions. My point is that it is
%     so obvious that most of Section 2 should be deleted. Figure 1 as part
%     of a related work section may remain.}
%
%       This is an interesting comment since it is the {\em opposite} of the 
%feedback we got on a earlier draft of this paper. In fact, we had
%       a certain senior SE person (who the reviewer might actually know....) 
%demanding ``why not just use best practices from the literature?''.
%       That comment lead to the Fig1 survey.
%
%
%       That said, we quite take your point that our current 
%       section~\tion{prelim} is far 
%       too long. For this draft, prompted by
%       your comment, we have cut its length in half.\\
%	
%	\review{\ldots~How does a log of defects look 
%	like? What kind of information is recorded? ...  In case 
%	four new modules are developed, is there then also a log 
%	history that shows how the total number of modules in the system correlates 
%	with the total number of defects? Are we talking about total number of 
%	defects or only the number of “infected modules”?}
%
%	
%	To answer these issues, we have provided a sample defect data set in 
%	\fig{example}. The example shows a few rows of data from Ant 1.3 
%	containing: (1) Module 
%	name; (2) 20 CK-Metrics; and (3) Defects (as a count of raw defects and a 
%	boolean variable). Note that \fig{j} lists all the remaining datasets and 
%	they all have been formated in the same way. \\
%	
%	\review{From RQ1: ``This code reorganization will start with some initial 
%	code base that is changed to a new code base. For example, if the bad smell 
%	is loc $>$ 100 and a code module has 500 lines of code, we reason 
%	optimistically that we can change that code metric to 100. Using the 
%	secondary verification oracle, we then predict the number of defects in 
%	new.'' What is the idea here?}
%	
%	Thank you for the question. Your observation regarding this --- \emph{Is 
%	the point that a log 
%	history of defects has shown that modules 
%	with more than 100 loc have more defects (per lines of code?) than smaller 
%	modules, and then the action is to reduce the size of that module?} --- is 
%	accurate.  We have now modified the content in corresponding section to 
%	further explain this in \textbf{RQ1} (please see content marked with 
%	{\color{steel} Reviewer2c} in \tion{setup}).\\	
%	
%	
%	\review{RQ1 is  ``which of the methods is most accurate?'' without 
%	presenting 
%	the methods. They are just referred to in three other papers that probably 
%	describe them. What are your selection criteria for comparing the tool (or 
%	framework or system as you also call it) XTREE with exactly these methods?}
%	
%	Thank you for your comment. We have fixed the description of \textbf{RQ1} 
%	to be more specific (please see content marked with 
%	{\color{steel} Reviewer2d} in \tion{rqs}). As to selecting primary change 
%	oracles, we undertook a survey of literature to identify commonly used 
%	methods to do this. We found three other techniques: CD from a previous 
%	work, VARL based thresholds~\cite{Shatnawi10}, and Statistical 
%	thresholding~\cite{Alves2010}.
%	\\
%
%        \review{It is stated that this paper reports a case study. I know that 
%within the SW community is its common to use the term case study to denote 
%just 
%a demonstration of an example performed by the researchers. But in more mature 
%disciplines, which we should aim to become a member of, “case study” has a 
%certain meaning (e.g. Yin 2003). It would mean an evaluation in a real 
%software 
%development context. This is note the case here. See also the work by Runeson 
%and Host 2009 on case studies in software engineering.}
%
%        Thank you for that comment. We can show that our definition of
%        ``case study'' is aligned with how Per Runeson uses the term.
%        In 2013, we were  working on revising a data mining paper for TSE paper
%        where Runeson was the associate editor. He pushed us hard for better 
%terminilogy and definitions, including our term ``case study''. To address his 
%concerns, we wrote the following
%        notes about ``case studies'' and data mining papers. Note that
%        he accepted the point offered below and accepted the paper.
%
%
%        \begin{quote}
%
%As we read standard texts on empirical software engineering
%(e.g. Runeson \& Host\footnote{P. Runeson and M. Host, ``Guidelines for 
%conducting and reporting
%case study research in software engineering,'' Empirical Software
%Engineering, vol. 14, pp. 131–164, 2009} ) the term ``case study'' often 
%refers to some act which includes observing or changing
%the conditions under which humans perform some software
%engineering action.
%
%In the age of data mining and modelbased
%optimization this definition should be further extended
%to include case studies exploring how data collected from
%different projects can be generalized across multiple projects.
%As Cruzes et al. comment:
%\begin{quote}
%``Choosing a suitable method for synthesizing evidence
%across a set of case studies is not straightforward...
%limited access to raw data may limit the ability
%to fully understand and synthesize studies.\footnote{P. R. M. H. Daniela 
%Cruzes, Tore Dyba, ``Case studies synthesis:
%Brief experience and challenges for the future,'' in ESEM’11: the
%International Symposium on Empirical Software Engineering and Measurement,
%2011.}''
%\end{quote}
%        \end{quote}
%        Note that the above quote from Cruzes et al. is almost a summary of the
%specific goals of this paper: given limited amounts of software
%project data, how can we rank bad smells such as to avoid making unecessary, 
%or bad, changes.
%\\
%%\clearpage
%
%\review{Regarding case study, what kind of work remains before the proposed 
%tool could be used by practitioners?}
%
%We need to address a scale-up problem (which is the current focus of Mr. 
%Krishna's Ph.D. work) and once that is done,
%we will make this a Python package freely available to the world on Windows,
%Linux, and Mac machines via the simple command `\texttt{pip install xtree}'.
%After that is installed, the code would search a directory of project data to 
%automatically generate the figures of this paper.\\
%        
%	\review{What’s the difference between tool, framework, and method in this 
%	paper?}
%		
%	Thank you for pointing that out. We offer the following definitions: (1) 
%	Framework: A basic structure underlying recommending reorganization. It 
%	comprises of a primary change oracle and a secondary verification oracle; 
%	(2) Method: Refers to how the primary change oracle offers these 
%	recommendation. 
%	In this work it may be based on Cluster Deltas (XTREE) or threshold based 
%	(Shatnawi and Alves); and (3) Tool: Comprises of any one primary change 
%	oracle (XTREE) and a secondary verification oracle (Tuned Random Forest). 
%	
%	We may have used these interchangeably in the first draft of our paper. 
%	This has been fixed in this revision.\\
%	
%	\review{How does this work related to the work by Arcelli Fontana, in 
%	particular: Arcelli Fontana, F., Mantyla, M.V., Zanoni, M. et al. Comparing 
%	and experimenting machine learning techniques for code smell detection, 
%	Empir Software Eng (2016) 21: 1143. doi:10.1007/s10664-015-9378-4?}	
%	
%	Thank you for the reference. Our work differs from this specific paper in 
%	one 
%	key aspect --- we attempt to assist reorganization of code and prevent 
%	needless reorganization while they focus on 
%	detecting code smells using machine learning techniques. Our work is much 
%	closer to other work by Arcelli Fontana~\cite{font1}. We discuss this 
%	in~\tion{prior}. \\
%	
%	
%	\review{Improving on one metric may cause degradation 
%	on another one. This issue could have been much more spelt out with good 
%	examples in the paper. It's stated that XTREE “recommends” 
%	(or “suggests”) increasing coupling while reducing LOC of a module. Sure, 
%	if you split a module into several smaller modules, or move code from one 
%	large module to other, smaller modules, usually the overall coupling will 
%	increase.  But isn't that an avoidable consequence that will occur 
%	implicitly in the process of module splitting or moving code between 
%	modules? The way it’s formulated now gives the impression that the 
%	programmers should follow the recommendation of increasing the coupling, 
%	that is, as if it’s a conscious action. Or am I missing the point?}
%	
%	You are quite right, we have now rewritten associated text with 
%	\textbf{RQ5} in \tion{conjunct} to better explain 
%	the underlying connectedness of the metrics ({\color{steel} Reviewer2e} in 
%	\tion{conjunct}). 
%	
%	To summarize, we were trying to convey the following information with this 
%	specific example:
%	
%	\be
%	
%	\item
%	Attempting to reduce certain code metrics (like LOC) necessitates 
%	increasing other metrics. Any recommendation that fails to respect these 
%	``co-changes'' may not the practical to follow.
%	\item  XTREE is aware of 
%	the relationship between metrics and always recommends changes to 
%	conjunctions of metrics. These changes are pragmatic in that XTREE 
%	sometimes suggests the same metric be either increased or decreased based 
%	on the dataset. As an example, consider \fig{changes} in Ant coupling 
%	between objects (CBO) has to be reduced while in Lucene CBO has to be 
%	increased.
%	\ee
%	
%	Developers are now aware of these interconnected changes. They can proceed 
%	to make these changes because of the historical evidence of its 
%	effectiveness.\\
%	
%	
%	\review{In Section 4: ``It can be difficult to judge the effects of 
%	removing 
%	bad smells. Code that is reorganized cannot be assessed just by a rerun of 
%	the test suite since such reorganizations may not change the system 
%	behavior (e.g., refactorings).'' Isn't the point about removing bad smells 
%	to improve the code without changing the behavior (refactorings)? Why 
%	cannot a test suite be run before and after if the behavior is not changed?}
%	
%	It is true that refactoring improves the code by performing behavior 
%	preserving modifications. Evaluating this code with test suites that are 
%	designed to 
%	identify faults would not work for three reasons: (1) Test suites may not 
%	be 
%	designed to identify code smells, they only report pass/fail based on 
%	whether or not a specific module runs. It is entirely possible that a test 
%	case may pass for code that contains one or more code smells; (2) While 
%	smells are certainly symptomatic of design flaws, not all smells cause the 
%	system to fail in manner suitable for identification by test cases; and (3) 
%	It make take a significant amount of effort to write new test cases that 
%	identify bad smells, especially for stable software.
%	
%	Finally, in our work we tackle reorganization which subsumes refactoring. 
%	Since not all reorganization efforts comprise of refactoring, that makes it 
%	difficult to assert when test case will pass or fail. Thus, using test 
%	suites is not a reliable option. 
%	
%	At your suggestion, we have now added this in \tion{eval} (please see text 
%	marked {\color{steel} Reviewer2f}).\\
%	
%	\balance	
%	
%	\review{Figure 4 shows the effect of tuning, and the authors write: ``The 
%	rows marked with a * in Figure 4 show data sets whose performance was 
%	improved remarkably  by  these  techniques. For example, in poi, the recall 
%	increased by 4\% while the false alarm rate dropped by 21\%.'' This is a 
%	good example of researcher bias. Your example is the most favorable example 
%	from your point of view. It is one of only two of the eight data sets that 
%	improved on both pd and pf.}
%	
%	You are right \ldots ~there are only a few cases where we see an 
%	improvement 
%	in both recall and false alarm at the same time (poi, synapse and log4j). 
%	But, we don't think is due to a researcher bias. Instead, this due to the 
%	specifics of tuning and the goals used for this. We would like to draw your 
%	attention to two other kinds of improvements as 
%	a result of tuning: 
%	
%	\be 
%	
%	\item Cases where there is a significant 
%	improvement in one measure (recall or false alarm) with no deterioration in 
%	the other measure (Ivy, Jedit, Lucene, and Xalan); and 
%	
%	\item Cases where there is a significantly large improvement in one measure 
%	with acceptable deterioration in the other metric (Poi and Ant).
%	
%	\ee
%	
%	\noindent We attribute these to the nature of multiobjective search 
%	performed by 
%	differential evolution. As highlighted by Fu et 
%	al.~\cite{fu:ase15} (page 2, \S2.2), defining objectives for tuning is a 
%	notoriously 
%	difficult task. They find that tuning for recall or false alarms 
%	independently can lead to some undesirable results. Tuning on recall yields 
%	oracles that have near 100\% recall but with almost 100\% false alarm. 
%	Similarly, tuning for only false alarm results in oracles that have 0\% 
%	false alarm with 0\% recall. We take their advice and tune on metrics that 
%	combine both precision and recall, thereby turning this into a 
%	multiobjective search. Results in \fig{j} (previously Figure 4) show recall 
%	and false alarms have reached a ``trade-off'' with maximum improvement, 
%	such 
%	is the nature of multiobjective differential evolution.
%	
%	
%	Thank you for your comments, we ought to have had a formal discussion of 
%	these in the paper. At your suggestion, these observations and reasons for 
%	the same have now been dealt with in much greater detail in the current 
%	version on the paper (see text marked with {\color{steel} Reviewer2g} in 
%	\tion{tune})
%	\\
%	
%		
%	\review{The authors state that if there are no historical records of 
%	defects, the results of this paper can be used as a guide (which results?). 
%	It is referred to Table 8 in the abstract but there is no Table 8. Is it 
%	meant to be Figure 8? In case, it’s very hard to understand how that figure 
%	could be used.}
%	
%	A good catch ... there seems to be a typo, Table 8 has now 
%	been replaced by \fig{multcomp} in the abstract. Regarding the 
%	understandability 
%	of~\fig{multcomp}, you are quite right in that we haven't provided 
%	sufficient information explaining this. As per your suggestion, we have now 
%	expanded the section that refers to this 
%	figure (see text prefixed with {\color{steel} Reviewer2h} in 
%	\tion{conjunct}) to better explain how the 
%	conclusions 
%	from this figure may be used when historical records are absent.

\end{document}

### 2017-02-07 src/.dump/accuracy.py

@@ -1,0 +1,93 @@
+from __future__ import print_function, division
+__author__ = 'rkrsn'
+from Planners.CD import *
+from Planners.xtree import xtree
+from tools.sk import rdivDemo
+from tools.misc import explore, say
+from tools.stats import ABCD
+from tools.tune.dEvol import tuner
+from tools.oracle import *
+# Timing
+from time import time
+from logo import logo
+
+# Parallelism
+from functools import partial
+from multiprocessing import Pool
+
+
+def RF(indx):
+
+  train,test = explore(dir='Data/Jureczko/')
+
+  # print("Data,\t Pd,\t Pf,\t Pd,\t Pf")
+  # print("\t,Naive,\t\t,Tuned,\t,\t")
+  tr,te = train[indx],test[indx]
+  print(tr[0].split('/')[-2])
+  E0, E1 = [],[]
+  Pd=[tr[0].split('/')[-2]]
+  Pf=[tr[0].split('/')[-2]]
+  G =[tr[0].split('/')[-2]]
+  tunings = tuner(tr)
+  actual, preds = rforest(tr, te, tunings=None, smoteit=False)
+  abcd = ABCD(before=actual, after=preds)
+  F = np.array([k.stats()[-2] for k in abcd()])
+  Pd0 = np.array([k.stats()[0] for k in abcd()])
+  Pf0 = np.array([k.stats()[1] for k in abcd()])
+  init = tr[0].split('/')[-2]+'\t, %0.2f,\t %0.2f,\t'%(Pd0[1], 1-Pf0[1])
+  # init1 = tr[0].split('/')[-2]+'\t, %0.2f,\t'%(F[1])
+
+  # Tune+SMOTE
+  smote= True
+  actual, preds = rforest(tr, te, tunings=tunings, smoteit=True)
+  abcd = ABCD(before=actual, after=preds)
+  F = np.array([k.stats()[-2] for k in abcd()])
+  Pd0 = np.array([k.stats()[0] for k in abcd()])
+  Pf0 = np.array([k.stats()[1] for k in abcd()])
+  say(init + '%0.2f,\t %0.2f\n' % (Pd0[1], 1 - Pf0[1]))
+  # say(init1+'%0.2f\n'%(F[1]))
+  return init+'%0.2f,\t %0.2f\n'%(Pd0[1], 1-Pf0[1])
+
+def SVM(indx):
+  train,test = explore(dir='Data/Jureczko/')
+  # set_trace()
[…]

### 2017-02-07 src/.dump/defects.py

@@ -1,0 +1,130 @@
+from __future__ import print_function, division
+
+__author__ = 'rkrsn'
+from Planners.xtree import xtree
+from Planners.xtree2 import xtree as xtree2
+from tools.sk import rdivDemo
+from tools.oracle import *
+# Timing
+import numpy as np
+
+
+class temporal:
+    def __init__(self):
+        pass
+
+    def deltas(self):
+        from collections import Counter
+        counts = {}
+
+        def save2plot(header, counts, labels, N):
+            for h in header: say(h + ' ')
+            print('')
+            for l in labels:
+                say(l[1:] + ' ')
+                for k in counts.keys():
+                    print("%0.2f " % (counts[k][l] * 100 / N), end="")
+                print('')
+
+        for name in ['ant', 'ivy', 'jedit', 'lucene', 'poi']:
+            print("##", name)
+            e = []
+            train, test = explore(dir='Data/Jureczko/', name=name)
+            for planners in [xtree]:  # , method1, method2, method3]:
+                # aft = [planners.__doc__]
+                for _ in xrange(10):
+                    keys = []
+                    everything, changes = planners(train, test, justDeltas=True)
+                    for ch in changes: keys.extend(ch.keys())
+                    counts.update({planners.__doc__: Counter(keys)})
+            header = ['Features'] + counts.keys()
+            save2plot(header, counts, everything, N=len(changes))
+
+    def deltas0(self):
+        from collections import Counter
+        counts = {}
+
+        def save2plot(header, counts, labels, numCh, N):
+            #   for h in header: say(h+' ')
+            print('')
+            for id, l in enumerate(labels):
+                # say(l[1:]+' ')
+                #   for k in counts.keys():
+                # print(counts[k])
+                try:
+                    if numCh[l] / N > 0.2:
+                        # print(numCh[l]/N)
+                        say(l[1:] + " %d %0.2f %0.2f %0.2f" % (
+                            id + 1, np.median(counts[l]), np.percentile(counts[l], 25), np.percentile(counts[l], 75)))
+                    else:
+                        say(l[1:] + " %d 0 0 0" % (id + 1))
+
+                except:
+                    # set_trace()
+                    say(l[1:] + " %d 0 0 0" % (id + 1))
+                # set_trace()
+                print('')
+                # set_trace()
+
+        for name in ['ant', 'ivy', 'jedit', 'lucene', 'poi']:
+            print("##", name)
+            e = []
[…]

### 2017-02-07 src/Data/other_data/ck/rewriteCSV.py

@@ -1,0 +1,34 @@
+from __future__ import print_function
+import pandas as pd
+from os import walk
+from pdb import set_trace
+import csv
+import re
+
+def do():
+  for (a,b,c) in walk('./'):
+    if not '.svn' in a:
+      if not a =='./':
+        for file in c:
+          if '.csv' in file:
+            print(a+'/'+file)
+            arff = pd.read_csv(a+'/'+file)
+            # set_trace()
+            tags = arff.columns.values
+            first3 = ['?'+h for h in tags[0:3]]
+            indep = ['$'+h for h in tags[3:-1]]
+            header = first3+indep
+            header.append('?>'+tags[-1])
+            # set_trace()
+            # name = []
+            with open(a+'/'+file, 'w+') as csvfile:
+              writer = csv.writer(csvfile, delimiter=',', quotechar='|')
+              writer.writerow(header)
+              for body in arff.values:
+                writer.writerow(body)
+          # else:
+          #   print('arff' in file)
+          #   # set_trace()
+
+if __name__ == '__main__':
+  do()

### 2017-02-07 src/Data/other_data/mccabe/toCSV.py

@@ -1,0 +1,31 @@
+from __future__ import print_function
+from scipy.io.arff import loadarff
+from os import walk
+from pdb import set_trace
+import csv
+import re
+
+def do():
+  for (a,b,c) in walk('./'):
+    if not '.svn' in a:
+      if not a =='./':
+        for file in c:
+          if 'arff' in file:
+            print(a+'/'+file)
+            arff = loadarff(a+'/'+file)
+            tags = [aa for aa in arff[1]]
+            header = ['$'+h for h in tags[:-1]]
+            header.append('$>'+tags[-1])
+            # set_trace()
+            name = []
+            with open(a+'/'+re.sub('.arff|[ ]','',file)+'.csv', 'w+') as csvfile:
+              writer = csv.writer(csvfile, delimiter=',', quotechar='|')
+              writer.writerow(header)
+              for body in arff[0].tolist():
+                writer.writerow(body)
+          # else:
+          #   print('arff' in file)
+          #   # set_trace()
+
+if __name__ == '__main__':
+  do()

### 2017-02-07 src/Planners/.old/thresholds.py

@@ -1,0 +1,50 @@
+"""
+CK Thresholds
+"""
+from __future__ import print_function, division
+from sklearn.linear_model import LogisticRegression
+from sklearn.feature_selection import f_classif, f_regression
+import sys
+import texttable
+sys.path.append('..')
+from tools.oracle import *
+from pdb import set_trace
+
+
+
+def VARL(coef,inter,p0=0.05):
+  return (np.log(p0/(1-p0))-inter)/coef
+
+def thresholds():
+  for name in ['ant', 'ivy', 'jedit', 'lucene', 'poi']:
+    print("##", name)
+    train, test = explore(dir='../Data/Jureczko/', name=name)
+    data_DF=csv2DF(train, toBin=True)
+    metrics=[str[1:] for str in data_DF[data_DF.columns[:-1]]]
+    ubr = LogisticRegression()
+    X = data_DF[data_DF.columns[:-1]].values
+    y = data_DF[data_DF.columns[-1]].values
+    ubr.fit(X,y)
+    inter, coef, pVal = ubr.intercept_[0], ubr.coef_[0], f_classif(X,y)[1]
+
+    table= texttable.Texttable()
+    table.set_cols_align(["l","l","l"])
+    table.set_cols_valign(["m","m","m"])
+    table.set_cols_dtype(['t', 't', 't'])
+    table_rows=[["Metric", "Threshold", "P-Value"]]
+
+    for i in xrange(len(metrics)):
+      if VARL(coef[i], inter, p0=0.05)>0 and pVal[i]<0.05:
+        thresh="%0.2f"%VARL(coef[i], inter, p0=0.1)
+        table_rows.append([metrics[i], thresh, "%0.3f"%pVal[i]])
+
+    table.add_rows(table_rows)
+    print(table.draw())
+
+  # === DEBUG ===
+  set_trace()
+  return None
+
+if __name__=="__main__":
+  thresholds()
+  pass

### 2017-02-07 src/Planners/.old/xtree.py

@@ -1,0 +1,177 @@
+"""
+XTREE
+"""
+from __future__ import print_function, division
+import pandas as pd, numpy as np
+from pdb import set_trace
+import sys
+sys.path.append('..')
+from tools.sk import *
+from tools.misc import *
+from tools.oracle import *
+import tools.pyC45 as pyC45
+from tools.Discretize import discretize
+from timeit import time
+from random import uniform
+from numpy.random import normal as randn
+from tools.tune.dEvol import tuner
+
+def trueValue(all,test):
+  set_trace()
+
+def flatten(x):
+  """
+  Takes an N times nested list of list like [[a,b],[c, [d, e]],[f]]
+  and returns a single list [a,b,c,d,e,f]
+  """
+  result = []
+  for el in x:
+    if hasattr(el, "__iter__") and not isinstance(el, basestring):
+      result.extend(flatten(el))
+    else:
+      result.append(el)
+  return result
+
+
+class changes():
+  """
+  Record changes.
+  """
+  def __init__(self):
+    self.log = {}
+
+  def save(self, name=None, old=None, new=None):
+    if not old == new:
+      self.log.update({name: (old-new)/old*100})
+
+class patches:
+
+  def __init__(i,train,test,trainDF,testDF,rfTrain,tree=None,tunings=None,config=False):
+    i.train=train
+    i.trainDF = trainDF
+    i.rftrain = rfTrain
+    i.test=test
+    i.testDF=testDF
+    i.config=config
+    i.tree=tree
+    i.change =[]
+    i.tunings = tunings#if tunings else tuner(i.rftrain)
+
+  def leaves(i, node):
+    """
+    Returns all terminal nodes.
+    """
+    L = []
+    if len(node.kids) > 1:
+      for l in node.kids:
+        L.extend(i.leaves(l))
+      return L
+    elif len(node.kids) == 1:
+      return [node.kids]
+    else:
+      return [node]
+
+  def find(i, testInst, t):
+    if len(t.kids)==0:
+      return t
+    for kid in t.kids:
+      if i.config:
+        if kid.val[0]==testInst[kid.f].values[0]:
+          return i.find(testInst,kid)
+      else:
+        try:
+          if kid.val[0]<=testInst[kid.f].values[0]<kid.val[1]:
+            return i.find(testInst,kid)
[…]

### 2017-02-07 src/Planners/.old/xtree2.py

@@ -1,0 +1,131 @@
+"""
+XTREE
+"""
+from __future__ import print_function, division
+import pandas as pd, numpy as np
+from pdb import set_trace
+import sys
+sys.path.append('..')
+from tools.sk import *
+from tools.misc import *
+from tools.oracle import *
+import tools.pyC45 as pyC45
+from tools.Discretize import discretize
+from timeit import time
+from random import uniform
+from numpy.random import normal as randn
+from tools.tune.dEvol import tuner
+from collections import Counter
+
+def flatten(x):
+  """
+  Takes an N times nested list of list like [[a,b],[c, [d, e]],[f]]
+  and returns a single list [a,b,c,d,e,f]
+  """
+  result = []
+  for el in x:
+    if hasattr(el, "__iter__") and not isinstance(el, basestring):
+      result.extend(flatten(el))
+    else:
+      result.append(el)
+  return result
+
+
+class changes():
+  """
+  Record changes.
+  """
+  def __init__(self):
+    self.log = {}
+
+  def save(self, name=None, old=None, new=None):
+    if not old == new:
+      d = new/old if new>old else -new/old #*100
+      d = d if np.isfinite(d) else 0# (new-old)/new*100
+      self.log.update({name: d})
+
+class patches:
+
+  def __init__(i,train,test,trainDF,testDF,rfTrain,tree=None,tunings=None,config=False):
+    i.train    = train
+    i.trainDF  = trainDF
+    i.rftrain  = rfTrain
+    i.test     = test
+    i.testDF   = testDF
+    i.config   = config
+    i.tree     = tree
+    i.change   = []
+    i.tunings  = tunings#if tunings else tuner(i.rftrain)
+
+  def leaves(i, node):
+    """
+    Returns all terminal nodes.
+    """
+    L = []
+    if len(node.kids) > 1:
+      for l in node.kids:
+        L.extend(i.leaves(l))
+      return L
+    elif len(node.kids) == 1:
+      return [node.kids]
+    else:
+      return [node]
+
+  def find(i, testInst, t):
+    if len(t.kids)==0:
+      return t
+    for kid in t.kids:
+      if i.config:
+        if kid.val[0]==testInst[kid.f].values[0]:
+          return i.find(testInst,kid)
+      else:
+        try:
[…]

### 2017-02-07 src/Planners/CD/CD.py

@@ -1,0 +1,221 @@
+"""
+XTREE
+"""
+from __future__ import print_function, division
+import sys
+sys.path.append('..')
+from tools.sk import *
+from tools.oracle import *
+from tools.where import where
+from random import choice
+from scipy.spatial.distance import euclidean as edist
+from sklearn.tree import DecisionTreeClassifier as CART
+
+def fWeight(tbl):
+    """
+    Sort features based on entropy
+    """
+    clf = CART(criterion='entropy')
+    features = tbl.columns[:-1]
+    klass = tbl[tbl.columns[-1]]
+    clf.fit(tbl[features], klass)
+    lbs = clf.feature_importances_
+    return np.argsort(lbs)[::-1]
+
+def flatten(x):
+  """
+  Takes an N times nested list of list like [[a,b],[c, [d, e]],[f]]
+  and returns a single list [a,b,c,d,e,f]
+  """
+  result = []
+  for el in x:
+    if hasattr(el, "__iter__") and not isinstance(el, basestring):
+      result.extend(flatten(el))
+    else:
+      result.append(el)
+  return result
+
+
+
+class node:
+  """
+  A data structure to hold all the rows in a cluster.
+  Also return an exemplar: the centroid.
+  """
+
+  def __init__(i, rows, what='centroid'):
+    i.rows = []
+    for r in rows:
+      i.rows.append(r)
+    i.sample = i.exemplar(what)
+
+  def exemplar(i, what='choice'):
+    if what == 'choice':
+      return choice(i.rows)
+    if what == 'centroid':
+      return np.median(np.array(i.rows), axis=0)
+    elif what == 'mean':
+      return np.mean(np.array(i.rows), axis=0)
+
+
+class changes():
+  """
+  Record changes.
+  """
+  def __init__(i):
+    i.log = {}
+
+  def save(i, name=None, old=None, new=None):
+    if not old == new:
+      i.log.update({name: (old, new)})
+
+class CD:
+
+  def __init__(i,train,test,trainDF,testDF,fsel=True,clst=None):
+    i.train=train
+    i.trainDF = trainDF
+    i.test=test
+    i.testDF=testDF
+    i.clstr=clst
+    i.change =[]
+    i.fsel=fsel
+    if fsel:
+      i.lbs = fWeight(trainDF)
+
+  def closest(i, arr):
+    """
[…]

### 2017-02-07 src/Planners/XTREE/Planner/CROSSTREES.py

@@ -1,0 +1,310 @@
+#! /Users/rkrsn/anaconda/bin/python
+from __future__ import print_function
+from __future__ import division
+
+from pdb import set_trace
+from os import environ, getcwd
+from os import walk
+from os import remove as rm
+from os.path import expanduser
+from pdb import set_trace
+import sys
+
+# Update PYTHONPATH
+HOME = expanduser('~')
+axe = HOME + '/git/axe/axe/'  # AXE
+pystat = HOME + '/git/pystats/'  # PySTAT
+cwd = getcwd()  # Current Directory
+sys.path.extend([axe, pystat, cwd])
+
+from pdb import set_trace
+from random import uniform, randint, shuffle
+import csv
+
+from sklearn.ensemble import AdaBoostClassifier
+from sklearn.ensemble import RandomForestClassifier
+from sklearn.neighbors import KNeighborsClassifier
+from sklearn.tree import DecisionTreeClassifier
+
+from collections import Counter
+
+from Planners.XTREE.lib import *
+from tools.axe.abcd import _Abcd
+from smote import *
+import Planners.XTREE.lib.makeAmodel as mam
+from methods1 import *
+import numpy as np
+import pandas as pd
+import tools.sk
+
+
+def genTable(tbl, rows):
+  name = str(randint(0, 1000))
+  header = [h.name for h in tbl.headers[:-1]]
+  with open('tmp0.csv', 'w') as csvfile:
+    writer = csv.writer(csvfile, delimiter=',')
+    writer.writerow(header)
+    for el in rows:
+      writer.writerow(el[:-1])
+  new = createTbl(['tmp0.csv'])
+  rm('tmp0.csv')
+  return new
+
+
+
+class changes():
+
+  def __init__(self):
+    self.log = {}
+
+  def save(self, name=None, old=None, new=None):
+    if not old == new:
+      self.log.update({name: (old, new)})
+
+
+class deltas():
+
+  def __init__(self, row, myTree, majority=True):
+    self.row = row
+    self.loc = drop(row, myTree)
+    self.contrastSet = None
+    self.newRow = row
+    self.score = self.scorer(self.loc)
+    self.change = []
+
+  def scorer(self, node):
+    return np.mean([r.cells[-2] for r in node.rows])
+
+  def createNew(self, stuff, keys, N=1):
+    newElem = []
+    tmpRow = self.row
+    for _ in xrange(N):
+      C = changes()
+      for s in stuff:
+        lo, hi = s[1]
[…]

### 2017-02-07 src/Planners/XTREE/Planner/HOW.py

@@ -1,0 +1,235 @@
+#! /Users/rkrsn/miniconda/bin/python
+from __future__ import division
+from __future__ import print_function
+
+import os
+import sys
+from os import getcwd
+from os import remove as rm
+from os.path import expanduser
+from random import randint
+
+# Update PYTHONPATH
+root = os.path.abspath(os.path.join(os.getcwd().split('src')[0], 'src'))
+if not root in sys.path: sys.path.append(root)
+
+from Planners.XTREE.lib.weights import weights as W
+import csv
+
+from Prediction import *
+from smote import *
+from methods1 import *
+import numpy as np
+
+
+# import sk
+
+
+class changes():
+    def __init__(self):
+        self.log = {}
+
+    def save(self, name=None, old=None, new=None):
+        if not old == new:
+            self.log.update({name: (old, new)})
+
+
+def genTable(tbl, rows):
+    name = str(randint(0, 1e6))
+    header = [h.name for h in tbl.headers[:-1]]
+    with open('tmp0.csv', 'w') as csvfile:
+        writer = csv.writer(csvfile, delimiter=',')
+        writer.writerow(header)
+        for el in rows:
+            writer.writerow(el[:-1])
+    new = createTbl(['tmp0.csv'])
+    rm('tmp0.csv')
+    return new
+
+
+class o:
+    def __init__(i, **d):
+        i.has().update(**d)
+
+    def has(i):
+        return i.__dict__
+
+    def update(i, **d):
+        i.has().update(d)
+        return i
+
+    def __repr__(i):
+        show = [':%s %s' % (k, i.has()[k])
+                for k in sorted(i.has().keys())
+                if k[0] is not "_"]
+        txt = ' '.join(show)
+        if len(txt) > 60:
+            show = map(lambda x: '\t' + x + '\n', show)
+        return '{' + ' '.join(show) + '}'
+
+
+def settings(**d):
+    return o(
+        name="WHAT",
+        what="WHAT - A Contrast Set Planner",
+        author="Rahul Krishna",
+        copyleft="(c) 2014, MIT license, http://goo.gl/3UYBp",
+        seed=1,
+        f=None,
+    ).update(**d)
+
+
+opt = settings()
+
+
+class vertex():
+    def __init__(self, ID, rows):
+        self._id = ID
+        self.rows = rows
+        self.represent = None
+
+    def score(self):
+        return np.mean([r.cells[-2] for r in self.rows])
+
+    def representative(self):
[…]

### 2017-02-07 src/Planners/XTREE/Planner/WHAT_bin.py

@@ -1,0 +1,253 @@
+#! /Users/rkrsn/miniconda/bin/python
+from __future__ import print_function
+from __future__ import division
+from os import environ
+from os import getcwd
+from pdb import set_trace
+from random import uniform as rand
+from random import randint as randi
+import sys
+
+# Update PYTHONPATH
+HOME = environ['HOME']
+axe = HOME + '/git/axe/axe/'  # AXE
+pystat = HOME + '/git/pystat/'  # PySTAT
+cwd = getcwd()  # Current Directory
+sys.path.extend([axe, pystat, '../'])
+
+from sklearn.ensemble import AdaBoostClassifier
+from sklearn.ensemble import RandomForestClassifier
+from sklearn.neighbors import KNeighborsClassifier
+from sklearn.tree import DecisionTreeClassifier
+from Planners.XTREE.lib.weights import weights as W
+
+from Prediction import *
+# from Planners.XTREE.lib.settingsWhere import o
+from cliffsDelta import *
+from hist import *
+from smote import *
+import Planners.XTREE.lib.makeAmodel as mam
+from methods1 import *
+import numpy as np
+import pandas as pd
+from counts import *
+# import sk
+
+
+class o:
+
+  def __init__(i, **d):
+    i.has().update(**d)
+
+  def has(i):
+    return i.__dict__
+
+  def update(i, **d):
+    i.has().update(d)
+    return i
+
+  def __repr__(i):
+    show = [':%s %s' % (k, i.has()[k])
+            for k in sorted(i.has().keys())
+            if k[0] is not "_"]
+    txt = ' '.join(show)
+    if len(txt) > 60:
+      show = map(lambda x: '\t' + x + '\n', show)
+    return '{' + ' '.join(show) + '}'
+
+
+def settings(**d):
+  return o(
+      name="WHAT",
+      what="WHAT - A Contrast Set Planner",
+      author="Rahul Krishna",
+      copyleft="(c) 2014, MIT license, http://goo.gl/3UYBp",
+      seed=1,
+      f=None,
+  ).update(**d)
+
+opt = settings()
+
+
+class vertex():
+
+  def __init__(self, ID, rows):
+    self._id = ID
+    self.rows = rows
+    self.represent = None
+
+  def score(self):
+    return np.mean([r.cells[-2] for r in self.rows])
+
+  def representative(self, method='mean'):
+    if method == 'mean':
+      return [float(np.mean([k.cells[indx] for k in self.rows]))
[…]

### 2017-02-07 src/Planners/XTREE/Planner/strawman.py

@@ -1,0 +1,341 @@
+#! /Users/rkrsn/miniconda/bin/python
+from __future__ import print_function, division
+from numpy import array, asarray, mean, median, percentile, size, sum, sqrt
+from pdb import set_trace
+from os import remove as rm
+from random import randint
+from methods1 import createTbl
+from Prediction import rforest, rforest2
+from Planners.XTREE.lib.weights import weights as W
+from os import environ, getcwd
+from os import walk
+from os.path import expanduser
+from pdb import set_trace
+import sys
+
+# Update PYTHONPATH
+HOME = expanduser('~')
+axe = HOME + '/git/axe/axe/'  # AXE
+pystat = HOME + '/git/pystats/'  # PySTAT
+cwd = getcwd()  # Current Directory
+sys.path.extend([axe, pystat, cwd])
+
+from tools.axe.table import clone
+import csv
+
+def avoid(name='BDBC'):
+  if name == 'Apache':
+    return []
+  elif name == 'BDBC':
+    return [7, 13]
+  elif name == 'BDBJ':
+    return [0, 1, 2, 5, 6, 10, 13, 14, 16, 17, 18]
+  elif name == 'LLVM':
+    return [0]
+  elif name == 'X264':
+    return [0, 8, 12]
+  elif name == 'SQL':
+    return [0, 2, 7, 10, 23]
+
+
+def alternates(name='BDBJ'):
+  if name == 'Apache':
+    return []
+  if name == 'BDBC':
+    return [range(8, 13), range(14, 18)]
+  if name == 'BDBJ':
+    return [[11, 12], [3, 4], [7, 8], [23, 24]]
+  if name == 'LLVM':
+    return []
+  if name == 'X264':
+    return [[9, 10, 11], [13, 14, 15]]
+  if name == 'SQL':
+    return [range(3, 7), [25, 27], [28, 29, 30], [32, 33], range(35, 39)]
+
+def flatten(x):
+  """
+  Takes an N times nested list of list like [[a,b],[c, [d, e]],[f]]
+  and returns a single list [a,b,c,d,e,f]
+  """
+  result = []
+  for el in x:
+    if hasattr(el, "__iter__") and not isinstance(el, basestring):
+      result.extend(flatten(el))
+    else:
+      result.append(el)
+  return result
+
+
+class changes():
+
+  def __init__(self):
+    self.log = {}
+
+  def save(self, name=None, old=None, new=None):
[…]

### 2017-02-07 src/Planners/XTREE/Planner/xtress_bin.py

@@ -1,0 +1,363 @@
+#! /Users/rkrsn/anaconda/bin/python
+from __future__ import print_function
+from __future__ import division
+from os import environ, getcwd, path
+from os import remove as rm
+from pdb import set_trace
+from random import uniform, randint, shuffle
+import sys
+
+# Update PYTHONPATH
+HOME = path.expanduser("~")
+axe = HOME + '/git/axe/axe/'  # AXE
+pystat = HOME + '/git/pystat/'  # PySTAT
+cwd = getcwd()  # Current Directory
+sys.path.extend([axe, pystat, cwd])
+
+from sklearn.ensemble import AdaBoostClassifier
+from sklearn.ensemble import RandomForestClassifier
+from sklearn.neighbors import KNeighborsClassifier
+from sklearn.tree import DecisionTreeClassifier
+
+from collections import Counter
+
+from Planners.XTREE.lib import *
+from smote import *
+import Planners.XTREE.lib.makeAmodel as mam
+from methods1 import *
+import numpy as np
+import pandas as pd
+import sk
+import csv
+
+
+def genTable(tbl, rows):
+  name = str(randint(0, 1000))
+  header = [h.name for h in tbl.headers[:-1]]
+  with open(name + '.csv', 'w') as csvfile:
+    writer = csv.writer(csvfile, delimiter=',')
+    writer.writerow(header)
+    for el in rows:
+      writer.writerow(el[:-1])
+  new = createTbl([name + '.csv'])
+  rm(name + '.csv')
+  return new
+
+def avoid(name='BDBC'):
+  if name == 'Apache':
+    return []
+  elif name == 'BDBC':
+    return [7, 13]
+  elif name == 'BDBJ':
+    return [0, 1, 2, 5, 6, 10, 13, 14, 16, 17, 18]
+  elif name == 'LLVM':
+    return [0]
+  elif name == 'X264':
+    return [0, 8, 12]
+  elif name == 'SQL':
+    return [0, 2, 7, 10, 23]
+
+
+def alternates(name='BDBJ'):
+  if name == 'Apache':
+    return []
+  if name == 'BDBC':
+    return [range(8, 13), range(14, 18)]
+  if name == 'BDBJ':
+    return [[11, 12], [3, 4], [7, 8], [23, 24]]
+  if name == 'LLVM':
+    return []
+  if name == 'X264':
+    return [[9, 10, 11], [13, 14, 15]]
[…]

### 2017-02-07 src/Planners/XTREE/Prediction.py

@@ -1,0 +1,299 @@
+from __future__ import division
+from pdb import set_trace
+from os import environ, getcwd
+from os import walk
+from os.path import expanduser
+from pdb import set_trace
+import sys
+
+# Update PYTHONPATH
+HOME = expanduser('~')
+axe = HOME + '/git/axe/axe/'  # AXE
+pystat = HOME + '/git/pystats/'  # PySTAT
+cwd = getcwd()  # Current Directory
+sys.path.extend([axe, pystat, cwd])
+
+from scipy.stats.mstats import mode
+from scipy.spatial.distance import euclidean
+from numpy import mean
+from random import choice, uniform as rand
+from sklearn.ensemble import AdaBoostClassifier
+from sklearn.ensemble import RandomForestClassifier, RandomForestRegressor
+from sklearn.linear_model import LogisticRegression
+from sklearn.neighbors import KNeighborsClassifier
+from sklearn.tree import DecisionTreeClassifier
+from smote import *
+import pandas as pd
+from tools.axe.abcd import _Abcd
+from methods1 import *
+from tools.sk import rdivDemo
+
+
+def formatData(tbl):
+  Rows = [i.cells for i in tbl._rows]
+  headers = [i.name for i in tbl.headers]
+  return pd.DataFrame(Rows, columns=headers)
+
+
+def Bugs(tbl):
+  cells = [i.cells[-2] for i in tbl._rows]
+  return cells
+
+#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
+# PREDICTION SYSTEMS:
+# ```````````````````
+# 1. WHERE2 2. RANDOM FORESTS, 3. DECISION TREES, 4. ADABOOST,
+# 5. LOGISTIC REGRESSION
+#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
+
+
+def where2prd(train, test, tunings=[None, None], smoteit=False, thresh=1):
+  "WHERE2"
+
+  def flatten(x):
+    """
+    Takes an N times nested list of list like [[a,b],[c, [d, e]],[f]]
+    and returns a single list [a,b,c,d,e,f]
+    """
+    result = []
+    for el in x:
+      if hasattr(el, "__iter__") and not isinstance(el, basestring):
[…]

### 2017-02-07 src/Planners/XTREE/defects.py

@@ -1,0 +1,365 @@
+#! /Users/rkrsn/miniconda/bin/python
+from __future__ import print_function, division
+
+import os
+import sys
+
+# Update PYTHONPATH
+root = os.path.abspath(os.path.join(os.getcwd().split('src')[0], 'src'))
+if not root in sys.path: sys.path.append(root)
+
+import numpy as np
+import csv
+from random import seed as rseed
+# from cliffsDelta import cliffs
+from lib.dEvol import tuner
+from tools.sk import rdivDemo
+from numpy import sum
+
+from Prediction import rforest, Bugs
+from methods1 import *
+
+from Planner.CROSSTREES import xtrees
+from Planner.HOW import treatments as HOW
+from Planner.strawman import strawman
+
+
+def say(x):
+    sys.stdout.write(str(x))
+
+
+def write2file(data, fname='Untitled', ext='.txt'):
+    with open('.temp/' + fname + ext, 'w') as fwrite:
+        writer = csv.writer(fwrite, delimiter=',')
+        if not isinstance(data[0], list):
+            writer.writerow(data)
+        else:
+            for b in data:
+                writer.writerow(b)
+
+
+def genTable(tbl, rows, name='tmp'):
+    header = [h.name for h in tbl.headers[:-1]]
+    with open(name + '.csv', 'w') as csvfile:
+        writer = csv.writer(csvfile, delimiter=',')
+        writer.writerow(header)
+        for el in rows:
+            if len(el[:-1]) < len(header):
+                writer.writerow(el)
+            else:
+                writer.writerow(el[:-1])
+
+    return createTbl([name + '.csv'])
+
+
+class run():
+    def __init__(
+            self, pred=rforest, _smoteit=True, _n=-1, _tuneit=False, dataName=None, reps=1):
+        self.pred = pred
+        self.dataName = dataName
+        self.out, self.out_pred = [self.dataName], []
+        self._smoteit = _smoteit
+        self.train, self.test = self.categorize()
+        self.reps = reps
+        self._n = _n
+        self.tunedParams = None if not _tuneit \
+            else tuner(self.pred, self.train[_n])
+        self.headers = createTbl(
+            self.train[
+                self._n],
+            isBin=False,
+            bugThres=1).headers
+
+    def categorize(self):
+        dir = os.path.join(root, 'Data/Jureczko')
+        self.projects = [Name for _, Name, __ in walk(dir)][0]
[…]

### 2017-02-07 src/Planners/XTREE/methods1.py

@@ -1,0 +1,102 @@
+#! /Users/rkrsn/anaconda/bin/python
+from pdb import set_trace
+from os import environ, getcwd
+from os import walk
+from os.path import expanduser
+from pdb import set_trace
+import sys
+
+# Update PYTHONPATH
+HOME = expanduser('~')
+axe = HOME + '/git/axe/axe/'  # AXE
+pystat = HOME + '/git/pystats/'  # PySTAT
+cwd = getcwd()  # Current Directory
+sys.path.extend([axe, pystat, './where2'])
+from tools.axe.dtree import *
+from tools.axe.table import *
+# from w2 import *
+from lib.w2 import where2, prepare, leaves
+from lib.makeAmodel import makeAModel
+import matplotlib.mlab as mlab
+# import matplotlib.pyplot as plt
+import smote
+
+
+def explore(dir):
+  datasets = []
+  for (dirpath, dirnames, filenames) in walk(dir):
+    datasets.append(dirpath)
+
+  training = []
+  testing = []
+  for k in datasets[1:]:
+    train = [[dirPath, fname] for dirPath, _, fname in walk(k)]
+    test = [train[0][0] + '/' + train[0][1].pop(-1)]
+    training.append(
+        [train[0][0] + '/' + p for p in train[0][1] if not p == '.DS_Store'])
+    testing.append(test)
+  return training, testing
+
+
+def newTable(tbl, headerLabel, Rows):
+  tbl2 = clone(tbl)
+  newHead = Sym()
+  newHead.col = len(tbl.headers)
+  newHead.name = headerLabel
+  tbl2.headers = tbl.headers + [newHead]
+  return clone(tbl2, rows=Rows)
+
+
+def createTbl(
+    data,
+    settings=None,
+    _smote=False,
+    isBin=False,
+    bugThres=1,
+        duplicate=False):
+  """
+  kwargs:
+  _smote = True/False : SMOTE input data (or not)
+  _isBin = True/False : Reduce bugs to defects/no defects
+  _bugThres = int : Threshold for marking stuff as defective,
+                    default = 1. Not defective => Bugs < 1
+  """
+  makeaModel = makeAModel()
+  _r = []
+  for t in data:
+    m = makeaModel.csv2py(t, _smote=_smote, duplicate=duplicate)
+    _r += m._rows
+  m._rows = _r
+  # Initialize all parameters for where2 to run
[…]

### 2017-02-07 src/Planners/XTREE/smote.py

@@ -1,0 +1,111 @@
+#! /Users/rkrsn/anaconda/bin/python
+from pdb import set_trace
+from os import environ, getcwd
+from os import walk
+from os.path import expanduser
+from pdb import set_trace
+import sys
+
+# Update PYTHONPATH
+HOME = expanduser('~')
+axe = HOME + '/git/axe/axe/'  # AXE
+pystat = HOME + '/git/pystats/'  # PySTAT
+cwd = getcwd()  # Current Directory
+sys.path.extend([axe, pystat, cwd])
+
+from scipy.spatial.distance import euclidean
+from random import choice, seed as rseed, uniform as rand
+import pandas as pd
+from tools.axe.table import *
+
+
+def SMOTE(data=None, k=5, atleast=100, atmost=100, bugIndx=2, resample=False):
+
+  def Bugs(tbl):
+    cells = [i.cells[-bugIndx] for i in tbl._rows]
+    return cells
+
+  def minority(data):
+    unique = list(set(sorted(Bugs(data))))
+    counts = len(unique) * [0]
+#     set_trace()
+    for n in xrange(len(unique)):
+      for d in Bugs(data):
+        if unique[n] == d:
+          counts[n] += 1
+    return unique, counts
+
+  def knn(one, two):
+    pdistVect = []
+#    set_trace()
+    for ind, n in enumerate(two):
+      pdistVect.append([ind, euclidean(one.cells[:-1], n.cells[:-1])])
+    indices = sorted(pdistVect, key=lambda F: F[1])
+    return [two[n[0]] for n in indices]
+
+  def extrapolate(one, two):
+    new = one
+#    set_trace()
+    if bugIndx == 2:
+      new.cells[3:-1] = [max(min(a, b),
+                             min(min(a, b) + rand() * (abs(a - b)),
+                                 max(a, b))) for a, b in zip(one.cells[3:-1],
+                                                             two.cells[3:-1])]
+      new.cells[-2] = int(new.cells[-2])
+    else:
+      new.cells[3:] = [min(a, b) + rand() * (abs(a - b)) for
+                       a, b in zip(one.cells[3:], two.cells[3:])]
+      new.cells[-1] = int(new.cells[-1])
+    return new
+
+  def populate(data):
+    newData = []
+    # reps = (len(data) - atleast)
+    for _ in xrange(atleast):
+      for one in data:
+        neigh = knn(one, data)[1:k + 1]
[…]

### 2017-02-07 src/Planners/XTREE/testOracle.py

@@ -1,0 +1,81 @@
+#! /Users/rkrsn/miniconda/bin/python
+from __future__ import print_function, division
+
+import os
+import sys
+
+# Update PYTHONPATH
+root = os.path.abspath(os.path.join(os.getcwd().split('src')[0], 'src'))
+if not root in sys.path: sys.path.append(root)
+
+from tools.axe.abcd import _Abcd
+from Prediction import *
+from Planners.XTREE.lib import dEvol
+from methods1 import *
+import numpy as np
+
+class data():
+    """
+    This data structure holds training and testing data
+    """
+
+    def __init__(self, dataName='ant', dir=root + "/Data/Jureczko"):
+        projects = [Name for _, Name, __ in walk(dir)][0]
+        numData = len(projects)  # Number of data
+        one, two = explore(dir)
+        data = [one[i] + two[i] for i in xrange(len(one))]
+
+        def withinClass(data):
+            N = len(data)
+            return [(data[:n], [data[n]]) for n in range(1, N)]
+
+        def whereis():
+            for indx, name in enumerate(projects):
+                if name == dataName:
+                    return indx
+
+        self.train = [dat[0] for dat in withinClass(data[whereis()])]
+        self.test = [dat[1] for dat in withinClass(data[whereis()])]
+
+
+class testOracle():
+    def __init__(self, file='ant', tuned=True):
+        self.file = file
+        self.train = createTbl(data(dataName=self.file).train[-1], isBin=True)
+        self.test = createTbl(data(dataName=self.file).test[-1], isBin=True)
+        self.param = dEvol.tuner(rforest, data(dataName=self.file).train[-1]) if \
+            tuned else None
+
+    def main(self):
+        Pd, Pf = [], []
+        actual = Bugs(self.test)
+        predicted = rforest(
+            self.train,
+            self.test,
+            tunings=self.param,
+            smoteit=True)
+        pd, pf, _ = _Abcd(actual, predicted)
+        return pd, pf
+
+
+if __name__ == "__main__":
+    for file in ['ant', 'camel', 'ivy',
+                 'jedit', 'log4j', 'pbeans',
+                 'lucene', 'poi', 'synapse',
+                 'velocity', 'xalan', 'xerces']:
+        PD_tuned, PF_tuned = [], []
+        PD_untuned, PF_untuned = [], []
+
+        for _ in xrange(10):
[…]

### 2017-02-07 src/Planners/threshold/naive.py

@@ -1,0 +1,281 @@
+"""
+XTREE
+"""
+from __future__ import print_function, division
+# import pandas as pd, numpy as np
+# from pdb import set_trace
+
+import sys
+sys.path.append('..')
+from tools.oracle import *
+from sklearn.linear_model import LogisticRegression
+from sklearn.feature_selection import f_classif, f_regression
+from random import uniform
+from xtree import  xtree
+from tools.sk import rdivDemo
+from texttable import *
+from CD import method1
+# from tools.sk import *
+# from tools.misc import *
+# import tools.pyC45 as pyC45
+# from tools.Discretize import discretize
+# from timeit import time
+# from numpy.random import normal as randn
+# from tools.tune.dEvol import tuner
+
+def VARL(coef,inter,p0=0.05):
+  """
+  :param coef: Slope of   (Y=aX+b)
+  :param inter: Intercept (Y=aX+b)
+  :param p0: Confidence Interval. Default p=0.05 (95%)
+  :return: VARL threshold
+
+            1   /     /  p0   \             \
+  VARL = ----- | log | ------ | - intercept |
+         slope \     \ 1 - p0 /             /
+
+  """
+  return (np.log(p0/(1-p0))-inter)/coef
+
+def apply(changes, row):
+  all = []
+  for idx, thres in enumerate(changes):
+    newRow = row
+    if thres>0:
+      if newRow[idx]>thres:
+        newRow[idx] = uniform(0, thres)
+      all.append(newRow)
+
+  return all
+
+def apply2(changes, row):
+  newRow = row
+  for idx, thres in enumerate(changes):
+    if thres>0:
+      if newRow[idx]>thres:
+        newRow[idx] = uniform(0, thres)
+
+  return newRow
+
+def shatnawi10(train, test, rftrain=None, tunings=None, verbose=False):
+
+  "Threshold based planning"
+
+  """ Compute Thresholds
+  """
+  data_DF=csv2DF(train, toBin=True)
+  metrics=[str[1:] for str in data_DF[data_DF.columns[:-1]]]
+  ubr = LogisticRegression() # Init LogisticRegressor
+  X = data_DF[data_DF.columns[:-1]].values # Independent Features (CK-Metrics)
[…]

### 2017-02-07 src/misc/logo.py

@@ -1,0 +1,67 @@
+from __future__ import print_function
+
+def logo():
+  print("""
+.______           ___           ___      .___________.
+|   _  \         /   \         /   \     |           |
+|  |_)  |       /  ^  \       /  ^  \    `---|  |----`
+|      /       /  /_\  \     /  /_\  \       |  |
+|  |\  \----. /  _____  \   /  _____  \      |  |
+| _| `._____|/__/     \__\ /__/     \__\     |__|
+
+
+(R)ahul's (A)ctionable (A)nalytics (T)oolkit
+
+       __             ___
+      // )    ___--""    "-.
+ \ |,"( /`--""              `.
+  \/ o                        \\
+  (   _.-.              ,'"    ;
+   |\"   /`.\  ,        /       |
+   | \  ' .'`.; |      |       \.______________________________
+     _-'.'    | |--..,,,\_    \________------------````````````
+    '''"   _-'.'       ___"-   )
+          '''"        '''---~""
+""")
+
+def logo2():
+  print("""
+           __   _________ _____  ______ ______
+           \ \ / /__   __|  __ \|  ____|  ____|
+            \ V /   | |  | |__) | |__  | |__
+             > <    | |  |  _  /|  __| |  __|
+            / . \   | |  | | \ \| |____| |____
+           /_/ \_\  |_|  |_|  \_\______|______|
+
+
+                                                   .
+                                        .         ;
+           .              .              ;%     ;;
+             ,           ,                :;%  %;
+              :         ;                   :;%;'     .,
+     ,.        %;     %;            ;        %;'    ,;
+       ;       ;%;  %%;        ,     %;    ;%;    ,%'
+        %;       %;%;      ,  ;       %;  ;%;   ,%;'
+         ;%;      %;        ;%;        % ;%;  ,%;'
+          `%;.     ;%;     %;'         `;%%;.%;'
+           `:;%.    ;%%. %@;        %; ;@%;%'
+              `:%;.  :;bd%;          %;@%;'
+                `@%:.  :;%.         ;@@%;'
+                  `@%.  `;@%.      ;@@%;
+                    `@%%. `@%%    ;@@%;
+                      ;@%. :@%%  %@@%;
+                        %@bd%%%bd%%:;
+                          #@%%%%%:;;
+                          %@@%%%::;
+                          %@@@%(o);  . '
+                          %@@@o%;:(.,'
+                      `.. %@@@o%::;
[…]

### 2017-02-07 src/tools/Discretize.py

@@ -1,0 +1,159 @@
+"""
+An instance filter that discretizes a range of numeric attributes in the dataset into nominal attributes. Discretization is by Fayyad & Irani's MDL method (the default).
+
+For more information, see:
+
+Usama M. Fayyad, Keki B. Irani: Multi-interval discretization of continuous valued attributes for classification learning. In: Thirteenth International Joint Conference on Artificial Intelligence, 1022-1027, 1993.
+
+Igor Kononenko: On Biases in Estimating Multi-Valued Attributes. In: 14th International Joint Conference on Articial Intelligence, 1034-1040, 1995.
+
+Dougherty, James, Ron Kohavi, and Mehran Sahami. "Supervised and unsupervised discretization of continuous features." Machine learning: proceedings of the twelfth international conference. Vol. 12. 1995.
+"""
+from __future__ import division, print_function
+import pandas as pd
+from collections import Counter
+from misc import *
+import numpy as np
+from pdb import set_trace
+from sklearn.tree import DecisionTreeClassifier as CART
+
+
+
+def fWeight(tbl):
+    """
+    Sort features based on entropy
+    """
+    clf = CART(criterion='entropy')
+    features = tbl.columns[:-1]
+    klass = tbl[tbl.columns[-1]]
+    clf.fit(tbl[features], klass)
+    lbs = clf.feature_importances_
+    return [tbl.columns[i] for i in np.argsort(lbs)[::-1]]
+
+def discretize(feature, klass, atleast=-1, discrete=False):
+
+  """
+  Recursive Minimal Entropy Discretization
+  ````````````````````````````````````````
+  Inputs:
+    feature: A list or a numpy array of continuous attributes
+    klass: A list, or a numpy array of discrete class labels.
+    atleast: minimum splits.
+  Outputs:
+    splits: A list containing suggested spilt locations
+  """
+  def measure(x):
+    def ent(x):
+      C = Counter(x)
+      N = len(x)
+      return sum([-C[n]/N*np.log(C[n]/N) for n in C.keys()])
+    def stdev(x):
+      if np.isnan(np.var(x)**0.5):
+        return 0
+      return np.var(x)**0.5
+    if not discrete: return ent(x)
+    else: return stdev(x)
+
[…]

### 2017-02-07 src/tools/axe/abcd.py

@@ -1,0 +1,85 @@
+from __future__ import division
+
+import sys
+from pdb import set_trace
+
+sys.dont_write_bytecode = True
+
+
+class Abcd:
+    def __init__(i, db="all", rx="all"):
+        i.db = db;
+        i.rx = rx;
+        i.yes = i.no = 0
+        i.known = {};
+        i.a = {};
+        i.b = {};
+        i.c = {};
+        i.d = {}
+
+    def __call__(i, actual=None, predicted=None):
+        return i.keep(actual, predicted)
+
+    def tell(i, actual, predict):
+        i.knowns(actual)
+        i.knowns(predict)
+        if actual == predict:
+            i.yes += 1
+        else:
+            i.no += 1
+        for x in i.known:
+            if actual == x:
+                if predict == actual:
+                    i.d[x] += 1
+                else:
+                    i.b[x] += 1
+            else:
+                if predict == x:
+                    i.c[x] += 1
+                else:
+                    i.a[x] += 1
+
+    def knowns(i, x):
+        if not x in i.known:
+            i.known[x] = i.a[x] = i.b[x] = i.c[x] = i.d[x] = 0.0
+        i.known[x] += 1
+        if (i.known[x] == 1):
+            i.a[x] = i.yes + i.no
+
+
+    def ask(i):
+        def p(y):
+            return int(100 * y + 0.5)
+
+        def n(y):
+            return int(y)
+
+        pd = pf = pn = prec = g = f = acc = 0
+        for x in i.known:
+            if x == 1: # Only for defects (x=0 -> no defects)
+                a = i.a[x];
+                b = i.b[x];
+                c = i.c[x];
+                d = i.d[x]
+                if (b + d): pd = d / (b + d)
+                if (a + c): pf = c / (a + c)
+                if (a + c): pn = (b + d) / (a + c)
+                if (c + d): prec = d / (c + d)
+                if (1 - pf + pd): g = 2 * (1 - pf) * pd / (1 - pf + pd)
+                if (prec + pd): f = 2 * prec * pd / (prec + pd)
+                if (i.yes + i.no): acc = i.yes / (i.yes + i.no)
+                return p(pd), p(pf), p(prec)
+
+
+def _Abcd(before=None, after=None):
+    abcd = Abcd(db='Actual', rx='Predicted')
+    train = before
+    test = after
+    for actual, predicted in zip(train, test):
+        abcd.tell(actual, predicted)
+
+    return abcd.ask()
+
+
+if __name__ == "__main__":
+    _Abcd()

### 2017-02-07 src/tools/axe/dtree.py

@@ -1,0 +1,331 @@
+from __future__ import division
+from lib    import *
+from demos  import *
+from table import *
+from fi     import *
+from abcd   import *
+from learn  import *
+from dtree  import *
+
+import sys
+sys.dont_write_bytecode = True
+
+
+def rankedFeatures(rows,t,features=None):
+  features = features if features else t.indep
+  klass = t.klass[0].col
+  def ranked(f):
+    syms, at, n  = {}, {}, len(rows)
+    for x in f.counts.keys(): 
+      syms[x] = Sym()
+    for row in rows: 
+      key = row.cells[f.col]
+      val = row.cells[klass]
+      syms[key] + val
+      at[key] = at.get(key,[]) + [row]
+    e = 0
+    for val in syms.values(): 
+      if val.n:
+        e += val.n/n * val.ent()
+    return e,f,syms,at
+  return sorted(ranked(f) for f in features)
+
+def infogain(t,opt=The.tree):
+  def norm(x): return (x - lo)/(hi - lo+0.0001)
+  for f in t.headers:
+    f.selected=False
+  lst = rankedFeatures(t._rows,t)
+  n = int(len(lst)*opt.infoPrune)
+  n = max(n,1)
+  for _,f,_,_ in lst[:n]:
+    f.selected=True
+  return [f for e,f,syms,at in lst[:n]]
+
+def tdiv1(t,rows,lvl=-1,asIs=10**32,up=None,features=None,branch=[],
+                  f=None,val=None,opt=None):
+  here = Thing(t=t,kids=[],f=f,val=val,up=up,lvl=lvl,rows=rows,modes={},branch=branch)
+  if f and opt.debug: 
+    print ('|.. ' * lvl) + f.name ,"=",val,len(rows)
+  here.mode = classStats(here).mode()
+  if lvl > 10 : return here
+  if asIs==0: return here
+  _, splitter, syms,splits = rankedFeatures(rows,t,features)[0]  
+  for key in sorted(splits.keys()):
+    someRows = splits[key] 
+    toBe = syms[key].ent()
+    if opt.variancePrune and lvl > 1 and toBe >= asIs:
+        continue
+    if opt.min <= len(someRows) < len(rows) :
+      here.kids += [tdiv1(t,someRows,lvl=lvl+1,asIs=toBe,features=features,
+                          up=here,f=splitter,val=key,branch=branch + [(splitter,key)],opt=opt)]
[…]

### 2017-02-07 src/tools/misc.py

@@ -1,0 +1,59 @@
+from pandas import DataFrame, read_csv, concat
+from os import walk
+import numpy as np
+from pdb import set_trace
+import sys
+
+def say(text):
+  sys.stdout.write(str(text))
+
+def shuffle(df, n=1, axis=0):     
+    df = df.copy()
+    for _ in range(n):
+        df.apply(np.random.shuffle, axis=axis)
+    return df
+    
+
+def csv2DF(dir, as_mtx=False, toBin=False):
+  files=[]
+  for f in dir:
+    df=read_csv(f)
+    headers = [h for h in df.columns if '?' not in h]
+    # set_trace()
+    if isinstance(df[df.columns[-1]][0], str):
+      df[df.columns[-1]] = DataFrame([0 if 'N' in d or 'n' in d else 1 for d in df[df.columns[-1]]])
+    if toBin:
+      df[df.columns[-1]]=DataFrame([1 if d > 0 else 0 for d in df[df.columns[-1]]])
+    files.append(df[headers])
+  "For N files in a project, use 1 to N-1 as train."
+  data_DF = concat(files)
+  if as_mtx: return data_DF.as_matrix()
+  else: return data_DF
+
+def explore(dir='../Data/Jureczko/', name=None):
+  datasets = []
+  for (dirpath, dirnames, filenames) in walk(dir):
+    datasets.append(dirpath)
+  training = []
+  testing = []
+  if name:
+      for k in datasets[1:]:
+        if name in k:
+          if 'Jureczko' or 'mccabe' in dir:
+            train = [[dirPath, fname] for dirPath, _, fname in walk(k)]
+            test = [train[0][0] + '/' + train[0][1].pop(-1)]
+            # set_trace()
+            training = [train[0][0] + '/' + p for p in train[0][1] if not p == '.DS_Store' and '.csv' in p]
+            testing = test
+            return training, testing
+          elif 'Seigmund' in dir:
+            train = [dir+name+'/'+fname[0] for dirPath, _, fname in walk(k)]
+            return train
+  else:
+    for k in datasets[1:]:
+      train = [[dirPath, fname] for dirPath, _, fname in walk(k)]
+      test = [train[0][0] + '/' + train[0][1].pop(-1)]
+      training.append(
+          [train[0][0] + '/' + p for p in train[0][1] if not p == '.DS_Store'])
+      testing.append(test)
+    return training, testing

### 2017-02-07 src/tools/oracle.py

@@ -1,0 +1,211 @@
+from __future__ import division
+from sklearn.ensemble import RandomForestClassifier, RandomForestRegressor
+from collections import Counter
+from scipy.spatial.distance import euclidean
+from random import choice, seed as rseed, uniform as rand
+import pandas as pd
+import numpy as np
+from texttable import Texttable
+from stats import ABCD
+from misc import *
+from pdb import set_trace
+from sklearn.neighbors import NearestNeighbors, BallTree, KDTree
+from sklearn.svm import SVC, SVR
+import warnings
+from time import time
+warnings.filterwarnings('ignore')
+
+def SMOTE(data=None, atleast=50, atmost=100, a=None,b=None, k=5, resample=False):
+  "Synthetic Minority Oversampling Technique"
+  # set_trace()
+  def knn(a,b):
+    "k nearest neighbors"
+    b=np.array([bb[:-1] for bb in b])
+    tree = BallTree(b)
+    __, indx = tree.query(a[:-1], k=6)
+
+    return [b[i] for i in indx]
+    # set_trace()
+    # return sorted(b, key=lambda F: euclidean(a[:-1], F[:-1]))
+
+  def kfn(me,my_lot,others):
+    "k farthest neighbors"
+    my_closest = None
+    return sorted(b, key=lambda F: euclidean(a[:-1], F[:-1]))
+
+  def extrapolate(one, two):
+    # t=time()
+    new = len(one)*[None]
+    new[:-1] = [a + rand(0,1) * (b-a) for
+                     a, b in zip(one[:-1], two[:-1])]
+    new[-1] = int(one[-1])
+    return new
+
+  def populate(data, atleast):
+    t=time()
+    newData = [dd.tolist() for dd in data]
+    if atleast-len(newData)<0:
+      try:
+        return [choice(newData) for _ in xrange(atleast)]
+      except:
+        set_trace()
+    else:
+      for _ in xrange(atleast-len(newData)):
+        one = choice(data)
+        neigh = knn(one, data)[1:k + 1]
+        try:
+          two = choice(neigh)
+        except IndexError:
+          two = one
+        newData.append(extrapolate(one, two))
+      return newData
+
+  def populate2(data1, data2):
+    newData = []
+    for _ in xrange(atleast):
+      for one in data1:
+        neigh = kfn(one, data)[1:k + 1]
+        try:
[…]

### 2017-02-07 src/tools/pyC45.py

@@ -1,0 +1,211 @@
+"""
+PC45 - Python C4.5 Framework
+````````````````````````````
+A Method for generating a pruned C4.5 decision tree. Based on,
+[1] Quinlan, J. Ross. "Improved use of continuous attributes in C4. 5." Journal of artificial intelligence research (1996): 77-90.
+[2] Quinlan, J. Ross. C4. 5: programs for machine learning. Elsevier, 2014.
+
+Also uses,
+[3] Usama M. Fayyad, Keki B. Irani. "Multi-interval discretization of continuous valued attributes for classification learning." Thirteenth International Joint Conference on Artificial Intelligence, 1022-1027, 1993.
+
+"""
+from __future__ import division, print_function
+from tools.Discretize import discretize, fWeight
+import pandas as pd
+import numpy as np
+from containers import Thing
+from collections import Counter
+from misc import explore, csv2DF
+from pdb import set_trace
+
+def dtree(tbl, rows=None, lvl=-1, asIs=10 ** 32, up=None, klass = -1, branch=[],
+          f=None, val=None, opt=None):
+  if not opt:
+      opt = Thing(
+         min=1,
+         maxLvL=10,
+         infoPrune=0.5,
+         klass=-1,
+         prune=True,
+         debug=True,
+         verbose=True)
+
+  here = Thing(t=tbl, kids=[], f=f, val=val, up=up, lvl=lvl
+              , rows=rows, modes={}, branch=branch)
+
+  features = fWeight(tbl)
+
+  if opt.prune and lvl<0:
+    features = fWeight(tbl)[:int(len(features)*opt.infoPrune)]
+
+  name = features.pop(0)
+  remaining = tbl[features+[tbl.columns[opt.klass]]]
+  feature = tbl[name].values
+  klass = tbl[tbl.columns[opt.klass]].values
+  N = len(klass)
+  here.score = np.mean(klass)
+  splits = discretize(feature, klass)
+  LO, HI = min(feature), max(feature)
+  def pairs(lst):
+    while len(lst)>1:
+      yield (lst.pop(0), lst[0])
+  cutoffs = [t for t in pairs(sorted(list(set(splits+[LO,HI]))))]
+
+  if lvl>(opt.maxLvL if opt.prune else int(len(features)*opt.infoPrune)):
+    return here
+  if asIs == 0:
+    return here
[…]

### 2017-02-07 src/tools/tune/model.py

@@ -1,0 +1,69 @@
+from __future__ import division, print_function
+import os, sys, subprocess
+from time import time
+# Get the git root directory
+root=repo_dir = subprocess.Popen(['git'
+                                      ,'rev-parse'
+                                      , '--show-toplevel']
+                                      , stdout=subprocess.PIPE
+                                    ).communicate()[0].rstrip()
+sys.path.append(root)
+
+import numpy as np
+from random import uniform
+from tools.oracle import rforest
+from tools.misc import *
+from tools.stats import ABCD
+
+class rf:
+  """
+  Random Forest
+  """
+  def __init__(i, data, obj=2,n_dec=7,smoteTune=True):
+    i.n_dec = n_dec
+    i.train = csv2DF(data[:-1], toBin=True)
+    i.test = csv2DF([data[-1]], toBin=True)
+    i.n_obj = obj # 2=precision
+    i.dec_lim = [(10, 1000)  # n_estimators
+                , (1, 100)  # max_features
+                , (1, 10)   # min_samples_leaf
+                , (2, 10)   # min_samples_split
+                , (2, 50)   # max_leaf_nodes
+                , (1,  8)   # Minority sampling factor
+                , (0,  4)]  # Majority sampling factor
+    i.smoteTune=smoteTune
+
+  def generate(i,n):
+    return [[uniform(i.dec_lim[indx][0]
+                     , i.dec_lim[indx][1]) for indx in xrange(i.n_dec)
+             ] for _ in xrange(n)]
+
+  def solve(i,dec):
+    # t=time()
+    actual, predicted = rforest(i.train, i.test, tunings=dec, smoteit=True
+    ,smoteTune=i.smoteTune)
+    # except: set_trace()
+    # print(time()-t)
+    abcd = ABCD(before=actual, after=predicted)
+    qual = np.array([k.stats() for k in abcd()])
+    # set_trace()
+    pd=qual[1][0]
+    pf=qual[1][1]
+    acc=qual[1][2]
+    prec=qual[1][3]
+    f1=qual[1][4]
+    g1=qual[1][5]
+    # print(pf)
+
+    out=1-pf if pf>0.7 else 0
+    out1=1-pd if pd>0.6 else 0
+    # set_trace()
+    return [prec, prec]
+    # return [out,out1]
+    # return [pf if pf>0.6 else 0, pd if pd>0.6 else 0]
+    # return [qual[0][1], qual[1][1]]
+
[…]

### 2017-02-07 src/tools/where.py

@@ -1,0 +1,67 @@
+from __future__ import division, print_function
+from pdb import set_trace
+import pandas as pd
+import numpy as np
+from os import walk
+from random import randint as randi, seed as rseed
+__author__ = 'rkrsn'
+
+def where(data):
+  """
+  Recursive FASTMAP clustering.
+  """
+  rseed(0)
+  if isinstance(data, pd.core.frame.DataFrame):
+    data = data.as_matrix()
+  if not isinstance(data, np.ndarray):
+    raise TypeError('Incorrect data format. Must be a pandas Data Frame, or a numpy nd-array.')
+
+  N = np.shape(data)[0]
+  clusters = []
+  norm = np.max(data, axis=0)[:-1] -np.min(data, axis=0)[:-1]
+
+  def aDist(one, two):
+    return np.sqrt(np.sum((np.array(one[:-1])/norm-np.array(two[:-1])/norm)**2))
+
+  def farthest(one,rest):
+    return sorted(rest, key=lambda F: aDist(F,one))[-1]
+
+  def recurse(dataset):
+    R, C = np.shape(dataset) # No. of Rows and Col
+    # Find the two most distance points.
+    one=dataset[randi(0,R-1)]
+    mid=farthest(one, dataset)
+    two=farthest(mid, dataset)
+
+    # Project each case on
+    def proj(test):
+      a = aDist(one, test)
+      b = aDist(two, test)
+      c = aDist(one, two)
+      return (a**2-b**2+c**2)/(2*c)
+
+    if R<np.sqrt(N):
+      clusters.append(dataset)
+    else:
+      _ = recurse(sorted(dataset,key=lambda F:proj(F))[:int(R/2)])
+      _ = recurse(sorted(dataset,key=lambda F:proj(F))[int(R/2):])
+
+  recurse(data)
+  return clusters
+
+def _test(dir='../Data/Jureczko/ant/'):
+  files=[]
+  for (dirpath, _, filename) in walk(dir):
+    for f in filename:
+      df=pd.read_csv(dirpath+f)
+      headers = [h for h in df.columns if '?' not in h]
+      files.append(df[headers])
+
+  "For N files in a project, use 1 to N-1 as train."
+  train = pd.concat(files[:-1])
+  clusters = where(train)
+  # ----- ::DEBUG:: -----
+  set_trace()
+
+if __name__=='__main__':
+  _test()

### 2017-02-09 src/Planners/XTREE/Planner/CROSSTREES.py
Lab Machine Changes

@@ -21,21 +21,10 @@ from pdb import set_trace
 from random import uniform, randint, shuffle
 import csv
 
-from sklearn.ensemble import AdaBoostClassifier
-from sklearn.ensemble import RandomForestClassifier
-from sklearn.neighbors import KNeighborsClassifier
-from sklearn.tree import DecisionTreeClassifier
-
-from collections import Counter
-
 from Planners.XTREE.lib import *
-from tools.axe.abcd import _Abcd
 from smote import *
-import Planners.XTREE.lib.makeAmodel as mam
 from methods1 import *
 import numpy as np
-import pandas as pd
-import tools.sk
 
 
 def genTable(tbl, rows):
@@ -250,8 +239,6 @@ class xtrees():
     if not len(best) > 0:
       best = vals
 
-    # Get a list of DoCs (DoC -> (D)epth (o)f (C)orrespondence, btw..)
-    # set_trace()
     attr = {}
     bests = {}
     unq = sorted(list(set([v.DoC for v in best])))  # A list of all DoCs..

### 2017-03-12 doc/Submission rev. 2/response.tex
Autocommit

\documentclass[twocolumn,5p]{elsarticle}
\pdfoutput=1
\usepackage{hyperref}
\usepackage{tikz}
\def\firstcircle{(90:1.75cm) circle (2.5cm)}
\def\secondcircle{(210:1.75cm) circle (2.5cm)}
\def\thirdcircle{(330:1.75cm) circle (2.5cm)}
\usepackage{comment}
\usepackage{framed,graphicx}
\usepackage{multirow}
\usepackage{rotating}
\usepackage{amsmath}
\usepackage{bigstrut}
\usepackage{color}
\usepackage{graphics}
\usepackage{eqparbox}
\usepackage{graphics}
\usepackage{colortbl}
%\usepackage{times}
\usepackage{mathptmx} \usepackage[scaled=.90]{helvet} \usepackage{courier}
\usepackage{balance}
\usepackage{picture}
\usepackage{algorithm}
\usepackage{algorithmicx}
\usepackage{algpseudocode}
\usepackage[export]{adjustbox}
\renewcommand{\footnotesize}{\scriptsize}
\definecolor{lightgray}{gray}{0.8}
\definecolor{darkgray}{gray}{0.6}
\definecolor{lavenderpink}{rgb}{0.98, 0.68, 0.82}
\definecolor{celadon}{rgb}{0.67, 0.88, 0.69}
\renewcommand{\algorithmicrequire}{\textbf{Input:}}
\renewcommand{\algorithmicensure}{\textbf{Output:}}
%%% graph
\newcommand{\crule}[3][darkgray]{\textcolor{#1}{\rule{#2}{#3}}}

\newcommand{\quart}[4]{\begin{picture}(80,4)%1
	{\color{black}\put(#3,2){\circle*{4}}\put(#1,2){\line(1,0){#2}}}\end{picture}}

\definecolor{Gray}{gray}{0.95}
\definecolor{LightGray}{gray}{0.975}

\newcommand{\rahul}[1]{{\color{steel}{#1}}}
\newcommand{\menzies}[1]{{\color{magenta}{#1}}}
\newcommand{\lucas}[1]{{\color{red}{#1}}}

%% timm tricks
\newcommand{\bi}{\begin{itemize}[leftmargin=0.4cm]}
	\newcommand{\ei}{\end{itemize}}
\newcommand{\be}{\begin{enumerate}}
	\newcommand{\ee}{\end{enumerate}}
\newcommand{\tion}[1]{\S#1}
\newcommand{\fig}[1]{Figure~#1}
\newcommand{\tab}[1]{Table~\ref{tab:#1}}
\newcommand{\eq}[1]{Equation~\ref{eq:#1}}
\newcommand{\review}[1]{\noindent\textit{#1\\}}

\usepackage[shortlabels]{enumitem}
\usepackage{url}

\definecolor{steel}{rgb}{.11, .11, .7}
\definecolor{Gray}{rgb}{0.88,1,1}
\definecolor{Gray}{gray}{0.85}
% \usepackage[svgnames]{xcolor}
\usepackage[framed]{ntheorem}
\usepackage{framed}
\usepackage{tikz}
\usetikzlibrary{shadows}
%\newtheorem{Lesson}{Lesson}
\theoremclass{Lesson}
\theoremstyle{break}

% inner sep=10pt,
\tikzstyle{thmbox} = [rectangle, rounded corners, draw=black,
fill=Gray!40,  drop shadow={fill=black, opacity=1}]
\newcommand\thmbox[1]{%
	\noindent\begin{tikzpicture}%
	\node [thmbox] (box){%
		\begin{minipage}{.94\textwidth}%
		\vspace{-2mm}#1\vspace{-3mm}%
		\end{minipage}%
	};%
	\end{tikzpicture}}

\let\theoremframecommand\thmbox
\newshadedtheorem{lesson}{Result}

\begin{document}
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% RESPONSE TO REVIEWERS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\pagebreak
\newpage
\appendix
\renewcommand*{\thesection}{\Alph{section}}
\nobalance
\section*{RESPONSE TO REVIEWERS}
\section*{Comments from the editor}
\review{The reviewers have finished to  evaluate your work. 
	As you 
	can observe, they raised some concerns that deserve your attention~$\ldots$}

\noindent Thank you very much indeed for your comments.\\

\review{ $\ldots$  It is important that you take into account their 
	comments and 
	evolve the paper accordingly. Please,  evolve the paper to make clear the 
	defect model, hypothesis, limitations and readability}

We offer clarifications to all the issues highlighted by the reviewers. In 
addition to these, we have made several key modifications to our paper. We 
have changed the title of our paper to reflect the changes we have made. In 
order to assist reviewers in tracking our changes, we have ensured all 
new additions are {\color{steel} highlighted in blue}. 
A brief summary of our changes are listed below:
\be
\item At the suggestion of Reviewers 1 and 2, we have included a section on 
the choice of datasets. Additionally, we have greatly expanded the section 
on defect prediction to highlight its importance and its relevance to our 
work.
\item To address comments by Reviewer~\#1 on how this work fits in with the 
body of knowledge, we have compiled a new section (see~\tion{2.1}) on the 
previous attempts to address similar issues. 
\item Further, at the suggestion of Reviewer~\#1, we have included a 
section remarking on the key limitations of our work. It now appears as a 
new section (see \tion{7}).
\item Also, as a response to Reviewer~\#1's comments, we have modified the 
future work section to reflect the implications of our findings on 
\textit{technical debt}. 
\item We acknowledge Reviewer~\#2's comment that our initial submission 
lacks a formal introduction of software ``defects" and its relevance to 
code reorganization. In order to address this, we have attempted to 
clarify 
the interpretation of defects in our work. As for other issues related to 
defects, we have added a new section on the choice of datasets 
(see~\tion{3}).
\item Also, keeping in mind the suggestions of Reviewer~\#2, we have 
rewritten the research questions (especially, RQ1 and RQ5).
\item Additionally, at the suggestion of Reviewer~\#2, we clarify our 
descriptions of several figures included in this paper. Specifically, we 
expand on the importance of tuning which relates to \fig{5} (previously 
Figure 4). We also expand on the significance of \fig{9} 
(previously 
Figure 8).
\item Finally, we have evolved our paper in the most appropriate areas in 
response to all the major and minor issues raised by both Reviewer~\#1 and 
Reviewer~\#2.
\ee

\section*{Response to Reviewer~\#1}

Thank you for your detailed comments. Our new draft contains many 
corrections, clarifications, and extensions as directed by your feedback.
All our changes are marked in the body and appears in {\color{steel} 
	blue}.\\

\review{I missed a section discussing possible implications for 
	researchers 
	and practitioners. How the results of this work contribute to future 
	research activities in the area? How practitioners can benefit from the 
	results achieved in the paper?}

You're quite correct, there was no future work section in the paper. The
following text
has been included in the revised submission and appears in~\tion{7} 
(see {\color{steel} Reviewer 1a}).

\begin{quote}``Our research shows that it is potentially na\"{\i}ve to explore 
	thresholds in static code attributes in isolation to each other. 
	This work clearly demonstrates how changing one necessitates changing 
	other associated metrics. So, for future work, we recommend that 
	researchers and practitioners look for tools that recommend changes to sets 
	of code changes. When exploring candidate technologies, apart from XTREE, 
	researchers may potentially use: (1) Association rule learning; (2) 
	Thresholds generated across synthetic dimensions (eg. PCA); and (3) 
	Techniques that cluster data and look for deltas between them. (Note: we 
	offer XTREE as a possible example of this point).''

	``Additionally, we plan on extending our work by exploring scalable 
	solutions 
	to achieve similar results in much larger datasets. After this, we shall 
	look at applications beyond that of measuring static 
	code attributes. For example, as an initial attempt, we have been looking 
	at sentiment analysis in stack overflow exchanges to learn dialog pattern 
	that most select for relevant entries.''
\end{quote}

\review{I also missed a section presenting the main limitations of 
	the 
	work. Although some words have been said about it, I believe it is 
	important to have a more structured discussion on a specific section.}

You are quite correct that we have missed a section highlighting the key 
limitations of our work. In the revised paper, we have dedicated a section 
to discussing the 
limitations and future work (see {\color{steel} Reviewer1b} in 
~\tion{7}).\\

\review{It would be interesting to have further discussion at the 
	end 
	indicating how this work complements the body of knowledge about code 
	smells. Do 
	reached results indicate a similar direction? contradictory? Does This work 
	somehow confirms the results of other studies or points to new 
	directions?}

Thank you for your comment, we admit the last version of the paper has 
an inadequate discussion on this matter. This revised version now includes an 
expanded prior work section which places greater emphasis on these issues 
(see {\color{steel} Reviewer1c} in 
\tion{2.1}).

As to your specific comment that this be included in the 
end, we feel our response to this recommendation is an important note on 
the state-of-the-art in this area. We have therefore added it towards the 
beginning of the paper instead, so it may premise the rest of our work.\\

\review{$\ldots$ this work evaluated XTREE, a framework to 
	evaluate whether a code reorganization is likely to have a perceivable 
	benefit in terms of defect-proneness. It is fine to have this scope 
	(defect-proneness) in terms of evaluation. However, it would be nice to 
	have a discussion on why this characteristic (defect-proneness) is good to 
	support the decision on code reorganization and/or how it could complement 
	other characteristics.}

You are quite right in pointing out that we need a better description of 
defect proneness. We have now added a section on defect-proneness and its 
relevance to our paper (please see content marked with {\color{steel} 
	Reviewer1d} in~\tion{3}).\\

\review{$\ldots$ nowadays we are seeing a growing discussion on 
	technical debt, 
	that brings financial aspects (interest, principal, debt…) to the 
	decision-making process on development activities. Could we use XTREE as a 
	strategy to prioritize the payment of technical debt items?}

Thank you for that suggestion. We do think XTREE can be used as a 
recommendation system to prioritize technical debt. In our revised paper, 
we expanded the introduction to highlight this possibility (see 
content prefixed with {\color{steel}Reviewer1e} in \tion{7}).\\

\review{Finally, I have one last question: is there any reason for 
	do not 
	use the GQM template to state the goal of the study and also to define null 
	and alternative hypotheses for the research questions?}

We can certainly do that if you wish. As to why we {\em didn't} do it,
this paper is clearly MSR-conference-style and not
ESEM-conference-style (GQM is less uses at MSR than ESEM).

To whether or not that is a ``good thing'' or not, we cannot say. What
we would say is that we think our use of stand-out boxes for research
findings makes our results easy to access within this paper.

That said, if the reviewer thinks this paper needs further structuring
to clarify our message then, of course, we would follow that direction.

%	\texttt{XXX}

\section*{Response to Reviewer~\#2}

Thank you for your detailed review. We have made several 
corrections, clarifications, and revisions as directed by your comments, 
this new draft is significantly improved thanks to your feedback.

\noindent All our 
changes are marked in the body and appears in 
{\color{steel} blue}.\\

\review{The introduction talks about Fowler’s bad smells and 
	refers to 
	literature on the (often contradictory) effects of such smells. And Figure 
	1 shows a list of bad smells. However, without making it clear, the paper 
	continues to talk about smells but the real topic is not the smells but the 
	metrics that are used to identify various smells. What’s the connection 
	between whether a smell is bad or not and the threshold values of the 
	various code metrics?}

Thank you for this comment. At your suggestion, we have significantly 
expanded \tion{3} in order to discuss the use of static code metrics 
with regards to code smells.\\

\review{I also find it very difficult to understand the conceptual model of 
	defects in this paper~\ldots}

We do apologize for the inconvenience.
Your remark clearly indicates that we need to further clarify our use
of the term.
So at your suggestion, we have 
dedicated a section to discussing the choice of dataset in \tion{3} 
(please see content marked with 
{\color{steel} Reviewer2a}).\\

\review{\ldots~The concept of “number of defects (defect counts)” 
	is fully mixed with the concept of “percent of classes with 
	defects/defective modules/ presence or absence of defects”. What does it 
	then mean to “reduce defects in our data sets”? Is it the total number of 
	defects in the data set (system?) or the number of “infected modules” in 
	the data set?}

We have clarified this in \tion{3}. Briefly, with respect to the 
datasets used in this study, when we say, ``reduce defects in our data 
sets,'' we refer to 
reorganizing code such that our secondary oracle reports
that the number of infected modules (i.e., classes with 
$\texttt{nDefects}>0$) is reduced to having \textit{no defects}.
For notes on our {\em primary} and {\em secondary} oracle, see page2, 
column1, of this paper.

In response to your  comment, we have expanded \tion{3}, to 
better explain this in much greater detail (please see content marked with 
{\color{steel}Reviewer2b} in \tion{3}). \\

\review{ Section 2 discusses the idea of why not just ask developers
	about the effect of code smells when the research literature is
	contradictory. The authors argue that practitioners
	should not be expected resolve contradictions. My point is that it is
	so obvious that most of Section 2 should be deleted. Figure 1 as part
	of a related work section may remain.}

This is an interesting comment since it is the {\em opposite} of the feedback 
we got on a earlier draft of this paper. In fact, we had
a certain senior SE person (who the reviewer might actually know....) demanding 
``why not just use best practices from the literature?''.
That comment lead to the Fig1 survey.

That said, we quite take your point that our current 
section~\tion{2.3} is far 
too long. For this draft, prompted by
your comment, we have cut its length in half.\\

\review{\ldots~How does a log of defects look 
	like? What kind of information is recorded? ...  In case 
	four new modules are developed, is there then also a log 
	history that shows how the total number of modules in the system correlates 
	with the total number of defects? Are we talking about total number of 
	defects or only the number of “infected modules”?}

To answer these issues, we have provided a sample defect data set in 
\fig{3}. The example shows a few rows of data from Ant 1.3 
containing: (1) Module 
name; (2) 20 CK-Metrics; and (3) Defects (as a count of raw defects and a 
boolean variable). Note that \fig{5} lists all the remaining datasets and 
they all have been formated in the same way. \\

\review{From RQ1: ``This code reorganization will start with some initial 
	code base that is changed to a new code base. For example, if the bad smell 
	is loc $>$ 100 and a code module has 500 lines of code, we reason 
	optimistically that we can change that code metric to 100. Using the 
	secondary verification oracle, we then predict the number of defects in 
	new.'' What is the idea here?}

Thank you for the question. Your observation regarding this --- \emph{Is 
	the point that a log 
	history of defects has shown that modules 
	with more than 100 loc have more defects (per lines of code?) than smaller 
	modules, and then the action is to reduce the size of that module?} --- is 
accurate.  We have now modified the content in corresponding section to 
further explain this in \textbf{RQ1} (please see content marked with 
{\color{steel} Reviewer2c} in \tion{5}).\\

\review{RQ1 is  ``which of the methods is most accurate?'' without 
	presenting 
	the methods. They are just referred to in three other papers that probably 
	describe them. What are your selection criteria for comparing the tool (or 
	framework or system as you also call it) XTREE with exactly these methods?}

Thank you for your comment. We have fixed the description of \textbf{RQ1} 
to be more specific (please see content marked with 
{\color{steel} Reviewer2d} in \tion{1.1}). As to selecting primary change 
oracles, we undertook a survey of literature to identify commonly used 
methods to do this. We found three other techniques: CD from a previous 
work, VARL based thresholds~\cite{Shatnawi10}, and Statistical 
thresholding~\cite{Alves2010}.
\\

\review{It is stated that this paper reports a case study. I know that within 
the SW community is its common to use the term case study to denote just a 
demonstration of an example performed by the researchers. But in more mature 
disciplines, which we should aim to become a member of, “case study” has a 
certain meaning (e.g. Yin 2003). It would mean an evaluation in a real software 
development context. This is note the case here. See also the work by Runeson 
and Host 2009 on case studies in software engineering.}

Thank you for that comment. We can show that our definition of
``case study'' is aligned with how Per Runeson uses the term.
In 2013, we were  working on revising a data mining paper for TSE paper
where Runeson was the associate editor. He pushed us hard for better 
terminilogy and definitions, including our term ``case study''. To address his 
concerns, we wrote the following
notes about ``case studies'' and data mining papers. Note that
he accepted the point offered below and accepted the paper.

\begin{quote}

	As we read standard texts on empirical software engineering
	(e.g. Runeson \& Host\footnote{P. Runeson and M. Host, ``Guidelines for 
	conducting and reporting
		case study research in software engineering,'' Empirical Software
		Engineering, vol. 14, pp. 131–164, 2009} ) the term ``case study'' 
		often 
	refers to some act which includes observing or changing
	the conditions under which humans perform some software
	engineering action.

	In the age of data mining and modelbased
	optimization this definition should be further extended
	to include case studies exploring how data collected from
	different projects can be generalized across multiple projects.
	As Cruzes et al. comment:
	\begin{quote}
		``Choosing a suitable method for synthesizing evidence
		across a set of case studies is not straightforward...
		limited access to raw data may limit the ability
		to fully understand and synthesize studies.\footnote{P. R. M. H. 
		Daniela Cruzes, Tore Dyba, ``Case studies synthesis:
			Brief experience and challenges for the future,'' in ESEM’11: the
			International Symposium on Empirical Software Engineering and 
			Measurement,
			2011.}''
	\end{quote}
\end{quote}
Note that the above quote from Cruzes et al. is almost a summary of the
specific goals of this paper: given limited amounts of software
project data, how can we rank bad smells such as to avoid making unecessary, or 
bad, changes.
\\
%\clearpage

\review{Regarding case study, what kind of work remains before the proposed 
tool could be used by practitioners?}

We need to address a scale-up problem (which is the current focus of Mr. 
Krishna's Ph.D. work) and once that is done,
we will make this a Python package freely available to the world on Windows,
Linux, and Mac machines via the simple command `\texttt{pip install xtree}'.
After that is installed, the code would search a directory of project data to 
automatically generate the figures of this paper.\\

\review{What’s the difference between tool, framework, and method in this 
	paper?}

Thank you for pointing that out. We offer the following definitions: (1) 
Framework: A basic structure underlying recommending reorganization. It 
comprises of a primary change oracle and a secondary verification oracle; 
(2) Method: Refers to how the primary change oracle offers these 
recommendation. 
In this work it may be based on Cluster Deltas (XTREE) or threshold based 
(Shatnawi and Alves); and (3) Tool: Comprises of any one primary change 
oracle (XTREE) and a secondary verification oracle (Tuned Random Forest).

We may have used these interchangeably in the first draft of our paper. 
This has been fixed in this revision.\\

\review{How does this work related to the work by Arcelli Fontana, in 
	particular: Arcelli Fontana, F., Mantyla, M.V., Zanoni, M. et al. Comparing 
	and experimenting machine learning techniques for code smell detection, 
	Empir Software Eng (2016) 21: 1143. doi:10.1007/s10664-015-9378-4?}

Thank you for the reference. Our work differs from this specific paper in 
one 
key aspect --- we attempt to assist reorganization of code and prevent 
needless reorganization while they focus on 
detecting code smells using machine learning techniques. Our work is much 
closer to other work by Arcelli Fontana~\cite{font1}. We discuss this 
in~\tion{2.1}. \\

\review{Improving on one metric may cause degradation 
	on another one. This issue could have been much more spelt out with good 
	examples in the paper. It's stated that XTREE “recommends” 
	(or “suggests”) increasing coupling while reducing LOC of a module. Sure, 
	if you split a module into several smaller modules, or move code from one 
	large module to other, smaller modules, usually the overall coupling will 
	increase.  But isn't that an avoidable consequence that will occur 
	implicitly in the process of module splitting or moving code between 
	modules? The way it’s formulated now gives the impression that the 
	programmers should follow the recommendation of increasing the coupling, 
	that is, as if it’s a conscious action. Or am I missing the point?}

You are quite right, we have now rewritten associated text with 
\textbf{RQ5} in \tion{6.5} to better explain 
the underlying connectedness of the metrics ({\color{steel} Reviewer2e} in 
\tion{6.5}).

To summarize, we were trying to convey the following information with this 
specific example:

\be

\item
Attempting to reduce certain code metrics (like LOC) necessitates 
increasing other metrics. Any recommendation that fails to respect these 
``co-changes'' may not the practical to follow.
\item  XTREE is aware of 
the relationship between metrics and always recommends changes to 
conjunctions of metrics. These changes are pragmatic in that XTREE 
sometimes suggests the same metric be either increased or decreased based 
on the dataset. As an example, consider \fig{8} in Ant coupling 
between objects (CBO) has to be reduced while in Lucene CBO has to be 
increased.
\ee

Developers are now aware of these interconnected changes. They can proceed 
to make these changes because of the historical evidence of its 
effectiveness.\\

\review{In Section 4: ``It can be difficult to judge the effects of 
	removing 
	bad smells. Code that is reorganized cannot be assessed just by a rerun of 
	the test suite since such reorganizations may not change the system 
	behavior (e.g., refactorings).'' Isn't the point about removing bad smells 
	to improve the code without changing the behavior (refactorings)? Why 
	cannot a test suite be run before and after if the behavior is not changed?}

It is true that refactoring improves the code by performing behavior 
preserving modifications. Evaluating this code with test suites that are 
designed to 
identify faults would not work for three reasons: (1) Test suites may not 
be 
designed to identify code smells, they only report pass/fail based on 
whether or not a specific module runs. It is entirely possible that a test 
case may pass for code that contains one or more code smells; (2) While 
smells are certainly symptomatic of design flaws, not all smells cause the 
system to fail in manner suitable for identification by test cases; and (3) 
It make take a significant amount of effort to write new test cases that 
identify bad smells, especially for stable software.

Finally, in our work we tackle reorganization which subsumes refactoring. 
Since not all reorganization efforts comprise of refactoring, that makes it 
difficult to assert when test case will pass or fail. Thus, using test 
suites is not a reliable option.

At your suggestion, we have now added this in \tion{5.2} (please see text 
marked {\color{steel} Reviewer2f}).\\

\balance

\review{Figure 4 shows the effect of tuning, and the authors write: ``The 
	rows marked with a * in Figure 4 show data sets whose performance was 
	improved remarkably  by  these  techniques. For example, in poi, the recall 
	increased by 4\% while the false alarm rate dropped by 21\%.'' This is a 
	good example of researcher bias. Your example is the most favorable example 
	from your point of view. It is one of only two of the eight data sets that 
	improved on both pd and pf.}

You are right \ldots ~there are only a few cases where we see an 
improvement 
in both recall and false alarm at the same time (poi, synapse and log4j). 
But, we don't think is due to a researcher bias. Instead, this due to the 
specifics of tuning and the goals used for this. We would like to draw your 
attention to two other kinds of improvements as 
a result of tuning:

\be

\item Cases where there is a significant 
improvement in one measure (recall or false alarm) with no deterioration in 
the other measure (Ivy, Jedit, Lucene, and Xalan); and

\item Cases where there is a significantly large improvement in one measure 
with acceptable deterioration in the other metric (Poi and Ant).

\ee

\noindent We attribute these to the nature of multiobjective search 
performed by 
differential evolution. As highlighted by Fu et 
al.~\cite{fu:ase15} (page 2, \S2.2), defining objectives for tuning is a 
notoriously 
difficult task. They find that tuning for recall or false alarms 
independently can lead to some undesirable results. Tuning on recall yields 
oracles that have near 100\% recall but with almost 100\% false alarm. 
Similarly, tuning for only false alarm results in oracles that have 0\% 
false alarm with 0\% recall. We take their advice and tune on metrics that 
combine both precision and recall, thereby turning this into a 
multiobjective search. Results in \fig{5} (previously Figure 4) show recall 
and false alarms have reached a ``trade-off'' with maximum improvement, 
such 
is the nature of multiobjective differential evolution.

Thank you for your comments, we ought to have had a formal discussion of 
these in the paper. At your suggestion, these observations and reasons for 
the same have now been dealt with in much greater detail in the current 
version on the paper (see text marked with {\color{steel} Reviewer2g} in 
\tion{5.2.1})
\\

\review{The authors state that if there are no historical records of 
	defects, the results of this paper can be used as a guide (which results?). 
	It is referred to Table 8 in the abstract but there is no Table 8. Is it 
	meant to be Figure 8? In case, it’s very hard to understand how that figure 
	could be used.}

A good catch ... there seems to be a typo, Table 8 has now 
been replaced by \fig{9} in the abstract. Regarding the 
understandability 
of~\fig{9}, you are quite right in that we haven't provided 
sufficient information explaining this. As per your suggestion, we have now 
expanded the section that refers to this 
figure (see text prefixed with {\color{steel} Reviewer2h} in 
\tion{6.5}) to better explain how the 
conclusions 
from this figure may be used when historical records are absent.
	\balance
\bibliographystyle{unsrt}
\bibliography{References}

\end{document}

### 2017-03-12 doc/Submission rev. 2/sample_data.tex
Autocommit

\begin{figure}[tp!]
\centering
\resizebox{\linewidth}{!}{
\label{my-label}
\begin{tabular}{c|l|l|l|c|l|c}
& & \multicolumn{3}{c|}{Metrics} & \multicolumn{2}{c}{Class} \\ \hline
Version                & \multicolumn{1}{c|}{Module Name}                             & wmc                    & dit                    & \ldots & nDefects & isDefective \\ \hline
1.3                    & org.apache.tools.ant.taskdefs.ExecuteOn & 11                     & 4                      & \ldots & 0        & FALSE       \\ \hline
1.3                    & org.apache.tools.ant.DefaultLogger      & 14                     & 1                      & \ldots & 2        & TRUE        \\ \hline
\multicolumn{1}{c|}{\ldots} & \multicolumn{1}{c|}{\ldots}                  & \multicolumn{1}{c|}{\ldots} & \multicolumn{1}{c|}{\ldots} & \ldots & 0        & FALSE       \\ \hline
1.3                    & org.apache.tools.ant.taskdefs.Cvs       & 12                     & 3                      & \ldots & 0        & FALSE       \\ \hline
1.3                    & org.apache.tools.ant.taskdefs.Copyfile  & 6                      & 3                      & \ldots & 1        & TRUE       
\end{tabular}}
\caption{A sample of ant 1.3}
\label{fig:example}
\end{figure}

### 2017-04-03 doc/Submission rev. 1/refactor.tex

\def\checkmark{\tikz\fill[scale=0.4](0,.35) -- (.25,0) -- (1,.7) -- (.25,.15) -- cycle;} 
\begin{figure}[!t] 
\scriptsize
\centering
\begin{tabular}{r|c|c|c|c}

\begin{turn}{75}Fowler'99~\cite{fowler99} and~\cite{Kerievsky2005}\end{turn} &\begin{turn}{75} Lanza'06~\cite{Lanza2006}\end{turn} & \begin{turn}{75}SonarQube~\cite{sq15} \end{turn} &  \begin{turn}{75}Yamashita'13\cite{Yamashita2013} \end{turn}& \begin{turn}{75} Developer Survey 2015\end{turn}\\\hline
  Alt. Classes with Diff. Interfaces & & & & \\
  Combinatorial Explosion~\cite{Kerievsky2005} & & &  & \\
  Comments & & & 11 & VL\\
  Conditional Complexity~\cite{Kerievsky2005} & & & 14  & ?\\
  Data Class & \checkmark & &  &\\
  Data Clumps &  &  &  &\\
  Divergent Change & & &  & \\
  Duplicated Code & \checkmark & \checkmark & 1  & VH\\
  Feature Envy & \checkmark & & 8  &\\

  Inappropriate Intimacy & & \checkmark &  & L\\
  Indecent Exposure~\cite{Kerievsky2005} & & &  & ?\\
  Incomplete Library Class & & &  &\\
  Large Class & \checkmark & \checkmark & 4  & VH\\
  Lazy Class/Freeloader & & \checkmark & 7  &\\
  Long Method & \checkmark& \checkmark & 2  & VH\\
  Long Parameter List &  & \checkmark & 9  & L \\

  Message Chains & & &  & H\\
  Middle Man & &  &  &\\
  Oddball Solution~\cite{Kerievsky2005} & & &  & \\
  Parallel Inheritance Hierarchies & & &  &\\
  Primitive Obsession &  & &  &\\

  Refused Bequest & \checkmark & \checkmark &  & \\ 
  Shotgun Surgery & \checkmark& &  & \\
  Solution Sprawl~\cite{Kerievsky2005} & & &  &\\
  Speculative Generality & & &  & L\\
  Switch Statements &  & &  & L\\
  Temporary Field & & \checkmark &  & ?\\
  \end{tabular}
%   \multicolumn{5}{l}{} \\
%   \multicolumn{5}{l}{\textsuperscript{\textdagger} + Exact rule, - Possibly related rule} \\
%     \multicolumn{5}{l}{\textsuperscript{\textdaggerdbl} + is included in list} \\
%     \multicolumn{5}{l}{\textsuperscript{\textexclamdown} VH: Very High, H: High, L: Low, VL: Very Low, ?: Still investigating} \\
%   \multicolumn{5}{l}{\textsuperscript{*} Computation is based on more than simple metrics.} \\

\caption{Bad   smells from different sources.  Check marks (\protect\checkmark) denote   a bad smell was mentioned.
Numbers or symbolic labels (e.g. "VH") denote  a priorization comment (and
``?'' indicates lack of consensus). Empty cells
denote some bad smell listed in column one that was not found relevant
in other studies.
Note: there are many blank cells.}
\label{fig:smells}
\end{figure}

### 2017-04-03 doc/Submission rev. 2/Manuscript.tex

--- 2017-02-07 doc/IST/Manuscript.tex
@@
 \definecolor{steel}{rgb}{0,0,0}
+\definecolor{steel2}{rgb}{.11, .11, .7}
 \definecolor{Gray}{rgb}{0.88,1,1}
@@
 			recommendations from previous studies. Further, XTREE endorses 
-			changes to very few code metrics, so XTREE requires programmers to do less
-                        work. Further, XTREE's recommendations are more 
-                        responsive to the
-                        particulars of different data sets.
+			changes to very few code metrics, so XTREE requires programmers to 
+			do less work. Further, XTREE's recommendations are more 
+            responsive to the particulars of different data sets. Finally 
+            XTREE's recommendations may be generalized to identify the most 
+            crucial factors affecting multiple datasets (see the last figure in 
+            paper).
 
@@
 			historical record  that it is useful to make that change. Note 
-			that 
-			this use case applies to both manual code reorganizations proposed 
-			by developers as well as those conducted by automatic methods. 
-			This 
-			recommendation assumes that there is an historical record. If none 
-			exists, then the results of this paper could be used as a guide 
-			(see the last figure of this paper).
+			that this use case applies to both manual code reorganizations 
+			proposed by developers as well as those conducted by automatic 
+			methods.
 
@@
 
-	{\color{steel}In terms of concrete recommendations for
+	In terms of concrete recommendations for
 		practitioners, we say {\em look before you leap}:
@@
 		methods~\cite{mkaouer2015many}. That is, XTREE could optimize automatic
-		code reorganization by discouraging reorganizations for useless goals.}
+		code reorganization by discouraging reorganizations for useless goals.
+
+	{\color{steel2} (Reviewer1a)
+	Beside this introduction, the rest of this paper is formatted as follows. 
+	\tion{prior0} relates the current work to the prior literature on bad 
+	smells and code reorganization efforts. In \tion{dataset}, we 
+	discuss the choice 
+	of our datasets and briefly describe it's structure. \tion{bst} details the 
+	frequently used techniques on leaning bad smell thresholds to assist 
+	reorganization. Specifically, 
+	\tion{xtreextree} and \tion{xtreextree2} describe our preferred method for 
+	performing code reorganizations. Our experimental setup and evaluation 
+	strategies are presented in \tion{setup}. The results and corresponding 
+	descriptions are available in \tion{results}. The future work and the 
+	reliability of our finding are available in \tion{future} and \tion{valid} 
+	respectively. Finally, the conclusions are presented in \tion{conclusions}. 
+}
 
 	\section{Relationship to Prior Work }
+	\label{sect:prior0}
 	{\color{steel}	
@@
 	\subsubsection{XTREE: Recommending Code Reorganizations}
-
+		\label{sect:xtreextree2}
 	Using the training data construct a decision tree as suggested above.
@@
 	\textit{Ant} there was a significantly large improvement in one metric with 
-	a very small deterioration in the other.
-
-	However, as expected, we could not salvage all the data 
-	sets. Therefore, we eliminated the data sets for which we could not build 
+	a very small deterioration in the other. }
+
+	{\color{steel2} (Reviewer2a) However, as expected, we found that some 
+	datasets (xerces, 
+	xalan, log4j, 
+	...) were not responsive to our tuning efforts. Since, we could not salvage 
+	all the data 
+	sets, we eliminated these data sets for which we could not build 
 	an adequately performing Random Forest classifier with $\mathit{pd}\ge 60 
@@
 	\section{Results}
+	\label{sect:results}
 
@@
 
-	This is quite significant for practitioners 
+	{\color{steel2} (Reviewer2b) This is quite significant for practitioners 
 	attempting to perform code reorganization to similar projects without a 
@@
 	reducing values all the metrics because an increase can sometimes be more 
-	beneficial.
+	beneficial.}
 
@@
         that make it harder, in the long-term, to maintain the software.
-        A recent study by 
+        A study by 
         Ernst et al.~\cite{ernst15} showed that practitioners agree on the 
@@
         al.~\cite{li15td} report that dedicated technical debt management (TDM) 
-        tools are needed for managing various types of technical debts. XTREE 
-        could be adapted for this purpose-- providing that there existed
+        tools are needed for managing various types of technical debts. 
+        {\color{steel2} (Reviewer1b) Recently Alves et al.~\cite{alves2016} 
+        conducted an 
+        extensive mapping study on the identification and management of 
+        technical debt. They identified several types of debts over the past 
+        decade and found that bad smells of the sort discussed in this paper 
+        are very well known indicators of design debt. In fact, they happen to 
+        be few of most 
+        frequently referenced kinds of debts. 
+        XTREE 
+        could be adapted for this purpose by supporting decisions if and when a 
+        technical debt item should be paid off -- providing that there existed
         a working ``secondary oracle'' (of the kind we define in our introduction)
-        that can recognize quick-and-dirty sections of code.
+        that can recognize quick-and-dirty sections of code.}
 
@@
 	\section{Conclusions}
+	\label{sect:conclusions}
 	How to discourage useless code reorganizations?
@@
 
-%	
-%	
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%	%%% RESPONSE TO REVIEWERS
-%	
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%	\pagebreak
-%	\newpage
-%	\appendix
-%	\renewcommand*{\thesection}{\Alph{section}}
-%	\nobalance
-%	\section*{RESPONSE TO REVIEWERS}
-%	\section*{Comments from the editor}
-%	\review{The reviewers have finished to  evaluate your work. 
-%	As you 
-%	can observe, they raised some concerns that deserve your attention~$\ldots$}
-%	
-%	\noindent Thank you very much indeed for your comments.\\
-%	
-%	
-%	\review{ $\ldots$  It is important that you take into account their 
-%	comments and 
-%	evolve the paper accordingly. Please,  evolve the paper to make clear the 
-%	defect model, hypothesis, limitations and readability}
-%	
-%	We offer clarifications to all the issues highlighted by the reviewers. In 
-%	addition to these, we have made several key modifications to our paper. We 
-%	have changed the title of our paper to reflect the changes we have made. In 
-%	order to assist reviewers in tracking our changes, we have ensured all 
-%	new additions are {\color{steel} highlighted in blue}. 
-%	A brief summary of our changes are listed below:
-%	\be
-%	\item At the suggestion of Reviewers 1 and 2, we have included a section on 
-%	the choice of datasets. Additionally, we have greatly expanded the section 
-%	on defect prediction to highlight its importance and its relevance to our 
-%	work.
-%	\item To address comments by Reviewer~\#1 on how this work fits in with the 
-%	body of knowledge, we have compiled a new section (see~\tion{prior}) on the 
-%	previous attempts to address similar issues. 
-%	\item Further, at the suggestion of Reviewer~\#1, we have included a 
-%	section remarking on the key limitations of our work. It now appears as a 
-%	new section (see \tion{future}).
-%	\item Also, as a response to Reviewer~\#1's comments, we have modified the 
-%	future work section to reflect the implications of our findings on 
-%	\textit{technical debt}. 
-%	\item We acknowledge Reviewer~\#2's comment that our initial submission 
-%	lacks a formal introduction of software ``defects" and its relevance to 
-%	code reorganization. In order to address this, we have attempted to 
-%	clarify 
-%	the interpretation of defects in our work. As for other issues related to 
-%	defects, we have added a new section on the choice of datasets 
-%	(see~\tion{dataset}).
-%	\item Also, keeping in mind the suggestions of Reviewer~\#2, we have 
-%	rewritten the research questions (especially, RQ1 and RQ5).
-%	\item Additionally, at the suggestion of Reviewer~\#2, we clarify our 
-%	descriptions of several figures included in this paper. Specifically, we 
-%	expand on the importance of tuning which relates to \fig{j} (previously 
-%	Figure 4). We also expand on the significance of \fig{multcomp} 
-%	(previously 
-%	Figure 8).
-%	\item Finally, we have evolved our paper in the most appropriate areas in 
-%	response to all the major and minor issues raised by both Reviewer~\#1 and 
-%	Reviewer~\#2.
-%	\ee
-%	
-%	\section*{Response to Reviewer~\#1}
-%	
-%	Thank you for your detailed comments. Our new draft contains many 
-%	corrections, clarifications, and extensions as directed by your feedback.
-%	All our changes are marked in the body and appears in {\color{steel} 
-%	blue}.\\
-%	
-%	\review{I missed a section discussing possible implications for 
-%	researchers 
-%	and practitioners. How the results of this work contribute to future 
-%	research activities in the area? How practitioners can benefit from the 
-%	results achieved in the paper?}
-%	
-%	
-%	You're quite correct, there was no future work section in the paper. The
-%        following text
-%	has been included in the revised submission and appears in~\tion{future} 
-%	(see {\color{steel} Reviewer 1a}). 
-%	
-%	
-%	\begin{quote}``Our research shows that it is potentially na\"{\i}ve to 
-%explore 
-%	thresholds in static code attributes in isolation to each other. 
-%	This work clearly demonstrates how changing one necessitates changing 
-%	other associated metrics. So, for future work, we recommend that 
-%	researchers and practitioners look for tools that recommend changes to sets 
-%	of code changes. When exploring candidate technologies, apart from XTREE, 
-%	researchers may potentially use: (1) Association rule learning; (2) 
-%	Thresholds generated across synthetic dimensions (eg. PCA); and (3) 
-%	Techniques that cluster data and look for deltas between them. (Note: we 
-%	offer XTREE as a possible example of this point).''
-%	
-%	``Additionally, we plan on extending our work by exploring scalable 
-%solutions 
-%	to achieve similar results in much larger datasets. After this, we shall 
-%	look at applications beyond that of measuring static 
-%	code attributes. For example, as an initial attempt, we have been looking 
-%	at sentiment analysis in stack overflow exchanges to learn dialog pattern 
-%	that most select for relevant entries.''
-%        \end{quote}
-%	
-%	
-%	\review{I also missed a section presenting the main limitations of 
-%	the 
-%	work. Although some words have been said about it, I believe it is 
-%	important to have a more structured discussion on a specific section.}
-%
-%	You are quite correct that we have missed a section highlighting the key 
-%	limitations of our work. In the revised paper, we have dedicated a section 
-%	to discussing the 
-%	limitations and future work (see {\color{steel} Reviewer1b} in 
-%	~\tion{future}).\\
-%	
-%	\review{It would be interesting to have further discussion at the 
-%	end 
-%	indicating how this work complements the body of knowledge about code 
-%	smells. Do 
-%	reached results indicate a similar direction? contradictory? Does This work 
-%	somehow confirms the results of other studies or points to new 
-%	directions?}
-%
-%	Thank you for your comment, we admit the last version of the paper has 
-%	an inadequate discussion on this matter. This revised version now includes 
-%an 
-%	expanded prior work section which places greater emphasis on these issues 
-%	(see {\color{steel} Reviewer1c} in 
-%	\tion{prior}). 
-%	
-%	As to your specific comment that this be included in the 
-%	end, we feel our response to this recommendation is an important note on 
-%	the state-of-the-art in this area. We have therefore added it towards the 
-%	beginning of the paper instead, so it may premise the rest of our work.\\
-%		
-%	\review{$\ldots$ this work evaluated XTREE, a framework to 
-%	evaluate whether a code reorganization is likely to have a perceivable 
-%	benefit in terms of defect-proneness. It is fine to have this scope 
-%	(defect-proneness) in terms of evaluation. However, it would be nice to 
-%	have a discussion on why this characteristic (defect-proneness) is good to 
-%	support the decision on code reorganization and/or how it could complement 
-%	other characteristics.}
-%	
-%	You are quite right in pointing out that we need a better description of 
-%	defect proneness. We have now added a section on defect-proneness and its 
-%	relevance to our paper (please see content marked with {\color{steel} 
-%	Reviewer1d} in~\tion{dataset}).\\
-%
-%	\review{$\ldots$ nowadays we are seeing a growing discussion on 
-%	technical debt, 
-%	that brings financial aspects (interest, principal, debt…) to the 
-%	decision-making process on development activities. Could we use XTREE as a 
-%	strategy to prioritize the payment of technical debt items?}
-%	
-%	Thank you for that suggestion. We do think XTREE can be used as a 
-%	recommendation system to prioritize technical debt. In our revised paper, 
-%	we expanded the introduction to highlight this possibility (see 
-%	content prefixed with {\color{steel}Reviewer1e} in \tion{future}).\\
-%	
-%	\review{Finally, I have one last question: is there any reason for 
-%	do not 
-%	use the GQM template to state the goal of the study and also to define null 
-%	and alternative hypotheses for the research questions?}
-%
-%        We can certainly do that if you wish. As to why we {\em didn't} do it,
-%        this paper is clearly MSR-conference-style and not
-%        ESEM-conference-style (GQM is less uses at MSR than ESEM).
-%
-%        To whether or not that is a ``good thing'' or not, we cannot say. What
-%        we would say is that we think our use of stand-out boxes for research
-%        findings makes our results easy to access within this paper.
-%
-%        That said, if the reviewer thinks this paper needs further structuring
-%        to clarify our message then, of course, we would follow that direction.
-%        
-%%	\texttt{XXX}
-%	
-%	\section*{Response to Reviewer~\#2}
-%	
-%	Thank you for your detailed review. We have made several 
-%	corrections, clarifications, and revisions as directed by your comments, 
-%	this new draft is significantly improved thanks to your feedback. 
-%	
-%	\noindent All our 
-%	changes are marked in the body and appears in 
-%	{\color{steel} blue}.\\
-%	
-%	\review{The introduction talks about Fowler’s bad smells and 
-%	refers to 
-%	literature on the (often contradictory) effects of such smells. And Figure 
-%	1 shows a list of bad smells. However, without making it clear, the paper 
-%	continues to talk about smells but the real topic is not the smells but the 
-%	metrics that are used to identify various smells. What’s the connection 
-%	between whether a smell is bad or not and the threshold values of the 
-%	various code metrics?}
-%
-%	Thank you for this comment. At your suggestion, we have significantly 
-%	expanded \tion{dataset} in order to discuss the use of static code metrics 
-%	with regards to code smells.\\
-%	
-%	\review{I also find it very difficult to understand the conceptual model of 
-%	defects in this paper~\ldots}
-%	
-%	We do apologize for the inconvenience.
-%Your remark clearly indicates that we need to further clarify our use
-%        of the term.
-%        So at your suggestion, we have 
-%	dedicated a section to discussing the choice of dataset in \tion{dataset} 
-%	(please see content marked with 
-%	{\color{steel} Reviewer2a}).\\
-%	
-%	\review{\ldots~The concept of “number of defects (defect counts)” 
-%	is fully mixed with the concept of “percent of classes with 
-%	defects/defective modules/ presence or absence of defects”. What does it 
-%	then mean to “reduce defects in our data sets”? Is it the total number of 
-%	defects in the data set (system?) or the number of “infected modules” in 
-%	the data set?}
-%	
-%	We have clarified this in \tion{dataset}. Briefly, with respect to the 
-%	datasets used in this study, when we say, ``reduce defects in our data 
-%	sets,'' we refer to 
-%	reorganizing code such that our secondary oracle reports
-%    that the number of infected modules (i.e., classes with 
-%	$\texttt{nDefects}>0$) is reduced to having \textit{no defects}.
-%    For notes on our {\em primary} and {\em secondary} oracle, see page2, 
-%    column1, of this paper.
-%	
-%	In response to your  comment, we have expanded \tion{dataset}, to 
-%	better explain this in much greater detail (please see content marked with 
-%	{\color{steel}Reviewer2b} in \tion{dataset}). \\
-%
-%   \review{ Section 2 discusses the idea of why not just ask developers
-%     about the effect of code smells when the research literature is
-%     contradictory. The authors argue that practitioners
-%     should not be expected resolve contradictions. My point is that it is
-%     so obvious that most of Section 2 should be deleted. Figure 1 as part
-%     of a related work section may remain.}
-%
-%       This is an interesting comment since it is the {\em opposite} of the 
-%feedback we got on a earlier draft of this paper. In fact, we had
-%       a certain senior SE person (who the reviewer might actually know....) 
-%demanding ``why not just use best practices from the literature?''.
-%       That comment lead to the Fig1 survey.
-%
-%
-%       That said, we quite take your point that our current 
-%       section~\tion{prelim} is far 
-%       too long. For this draft, prompted by
-%       your comment, we have cut its length in half.\\
-%	
-%	\review{\ldots~How does a log of defects look 
-%	like? What kind of information is recorded? ...  In case 
-%	four new modules are developed, is there then also a log 
-%	history that shows how the total number of modules in the system correlates 
-%	with the total number of defects? Are we talking about total number of 
-%	defects or only the number of “infected modules”?}
-%
-%	
-%	To answer these issues, we have provided a sample defect data set in 
-%	\fig{example}. The example shows a few rows of data from Ant 1.3 
-%	containing: (1) Module 
-%	name; (2) 20 CK-Metrics; and (3) Defects (as a count of raw defects and a 
-%	boolean variable). Note that \fig{j} lists all the remaining datasets and 
-%	they all have been formated in the same way. \\
-%	
-%	\review{From RQ1: ``This code reorganization will start with some initial 
-%	code base that is changed to a new code base. For example, if the bad smell 
-%	is loc $>$ 100 and a code module has 500 lines of code, we reason 
-%	optimistically that we can change that code metric to 100. Using the 
-%	secondary verification oracle, we then predict the number of defects in 
-%	new.'' What is the idea here?}
-%	
-%	Thank you for the question. Your observation regarding this --- \emph{Is 
-%	the point that a log 
-%	history of defects has shown that modules 
-%	with more than 100 loc have more defects (per lines of code?) than smaller 
-%	modules, and then the action is to reduce the size of that module?} --- is 
-%	accurate.  We have now modified the content in corresponding section to 
-%	further explain this in \textbf{RQ1} (please see content marked with 
-%	{\color{steel} Reviewer2c} in \tion{setup}).\\	
-%	
-%	
-%	\review{RQ1 is  ``which of the methods is most accurate?'' without 
-%	presenting 
-%	the methods. They are just referred to in three other papers that probably 
-%	describe them. What are your selection criteria for comparing the tool (or 
-%	framework or system as you also call it) XTREE with exactly these methods?}
-%	
-%	Thank you for your comment. We have fixed the description of \textbf{RQ1} 
-%	to be more specific (please see content marked with 
-%	{\color{steel} Reviewer2d} in \tion{rqs}). As to selecting primary change 
-%	oracles, we undertook a survey of literature to identify commonly used 
-%	methods to do this. We found three other techniques: CD from a previous 
-%	work, VARL based thresholds~\cite{Shatnawi10}, and Statistical 
-%	thresholding~\cite{Alves2010}.
-%	\\
-%
-%        \review{It is stated that this paper reports a case study. I know that 
-%within the SW community is its common to use the term case study to denote 
-%just 
-%a demonstration of an example performed by the researchers. But in more mature 
-%disciplines, which we should aim to become a member of, “case study” has a 
-%certain meaning (e.g. Yin 2003). It would mean an evaluation in a real 
-%software 
-%development context. This is note the case here. See also the work by Runeson 
-%and Host 2009 on case studies in software engineering.}
-%
-%        Thank you for that comment. We can show that our definition of
-%        ``case study'' is aligned with how Per Runeson uses the term.
-%        In 2013, we were  working on revising a data mining paper for TSE paper
-%        where Runeson was the associate editor. He pushed us hard for better 
-%terminilogy and definitions, including our term ``case study''. To address his 
-%concerns, we wrote the following
-%        notes about ``case studies'' and data mining papers. Note that
-%        he accepted the point offered below and accepted the paper.
-%
-%
-%        \begin{quote}
-%
-%As we read standard texts on empirical software engineering
-%(e.g. Runeson \& Host\footnote{P. Runeson and M. Host, ``Guidelines for 
-%conducting and reporting
-%case study research in software engineering,'' Empirical Software
-%Engineering, vol. 14, pp. 131–164, 2009} ) the term ``case study'' often 
-%refers to some act which includes observing or changing
-%the conditions under which humans perform some software
-%engineering action.
-%
-%In the age of data mining and modelbased
-%optimization this definition should be further extended
-%to include case studies exploring how data collected from
-%different projects can be generalized across multiple projects.
-%As Cruzes et al. comment:
-%\begin{quote}
-%``Choosing a suitable method for synthesizing evidence
-%across a set of case studies is not straightforward...
-%limited access to raw data may limit the ability
-%to fully understand and synthesize studies.\footnote{P. R. M. H. Daniela 
-%Cruzes, Tore Dyba, ``Case studies synthesis:
-%Brief experience and challenges for the future,'' in ESEM’11: the
-%International Symposium on Empirical Software Engineering and Measurement,
-%2011.}''
-%\end{quote}
-%        \end{quote}
-%        Note that the above quote from Cruzes et al. is almost a summary of the
-%specific goals of this paper: given limited amounts of software
-%project data, how can we rank bad smells such as to avoid making unecessary, 
-%or bad, changes.
-%\\
-%%\clearpage
-%
-%\review{Regarding case study, what kind of work remains before the proposed 
-%tool could be used by practitioners?}
-%
-%We need to address a scale-up problem (which is the current focus of Mr. 
-%Krishna's Ph.D. work) and once that is done,
-%we will make this a Python package freely available to the world on Windows,
-%Linux, and Mac machines via the simple command `\texttt{pip install xtree}'.
-%After that is installed, the code would search a directory of project data to 
-%automatically generate the figures of this paper.\\
-%        
-%	\review{What’s the difference between tool, framework, and method in this 
-%	paper?}
-%		
-%	Thank you for pointing that out. We offer the following definitions: (1) 
-%	Framework: A basic structure underlying recommending reorganization. It 
-%	comprises of a primary change oracle and a secondary verification oracle; 
-%	(2) Method: Refers to how the primary change oracle offers these 
-%	recommendation. 
-%	In this work it may be based on Cluster Deltas (XTREE) or threshold based 
-%	(Shatnawi and Alves); and (3) Tool: Comprises of any one primary change 
-%	oracle (XTREE) and a secondary verification oracle (Tuned Random Forest). 
-%	
-%	We may have used these interchangeably in the first draft of our paper. 
-%	This has been fixed in this revision.\\
-%	
-%	\review{How does this work related to the work by Arcelli Fontana, in 
-%	particular: Arcelli Fontana, F., Mantyla, M.V., Zanoni, M. et al. Comparing 
-%	and experimenting machine learning techniques for code smell detection, 
-%	Empir Software Eng (2016) 21: 1143. doi:10.1007/s10664-015-9378-4?}	
-%	
-%	Thank you for the reference. Our work differs from this specific paper in 
-%	one 
-%	key aspect --- we attempt to assist reorganization of code and prevent 
-%	needless reorganization while they focus on 
-%	detecting code smells using machine learning techniques. Our work is much 
-%	closer to other work by Arcelli Fontana~\cite{font1}. We discuss this 
-%	in~\tion{prior}. \\
-%	
-%	
-%	\review{Improving on one metric may cause degradation 
-%	on another one. This issue could have been much more spelt out with good 
-%	examples in the paper. It's stated that XTREE “recommends” 
-%	(or “suggests”) increasing coupling while reducing LOC of a module. Sure, 
-%	if you split a module into several smaller modules, or move code from one 
-%	large module to other, smaller modules, usually the overall coupling will 
-%	increase.  But isn't that an avoidable consequence that will occur 
-%	implicitly in the process of module splitting or moving code between 
-%	modules? The way it’s formulated now gives the impression that the 
-%	programmers should follow the recommendation of increasing the coupling, 
-%	that is, as if it’s a conscious action. Or am I missing the point?}
-%	
-%	You are quite right, we have now rewritten associated text with 
-%	\textbf{RQ5} in \tion{conjunct} to better explain 
-%	the underlying connectedness of the metrics ({\color{steel} Reviewer2e} in 
-%	\tion{conjunct}). 
-%	
-%	To summarize, we were trying to convey the following information with this 
-%	specific example:
-%	
-%	\be
-%	
-%	\item
-%	Attempting to reduce certain code metrics (like LOC) necessitates 
-%	increasing other metrics. Any recommendation that fails to respect these 
-%	``co-changes'' may not the practical to follow.
-%	\item  XTREE is aware of 
-%	the relationship between metrics and always recommends changes to 
-%	conjunctions of metrics. These changes are pragmatic in that XTREE 
-%	sometimes suggests the same metric be either increased or decreased based 
-%	on the dataset. As an example, consider \fig{changes} in Ant coupling 
-%	between objects (CBO) has to be reduced while in Lucene CBO has to be 
-%	increased.
-%	\ee
-%	
-%	Developers are now aware of these interconnected changes. They can proceed 
-%	to make these changes because of the historical evidence of its 
-%	effectiveness.\\
-%	
-%	
-%	\review{In Section 4: ``It can be difficult to judge the effects of 
-%	removing 
-%	bad smells. Code that is reorganized cannot be assessed just by a rerun of 
-%	the test suite since such reorganizations may not change the system 
-%	behavior (e.g., refactorings).'' Isn't the point about removing bad smells 
-%	to improve the code without changing the behavior (refactorings)? Why 
-%	cannot a test suite be run before and after if the behavior is not changed?}
-%	
-%	It is true that refactoring improves the code by performing behavior 
-%	preserving modifications. Evaluating this code with test suites that are 
-%	designed to 
-%	identify faults would not work for three reasons: (1) Test suites may not 
-%	be 
-%	designed to identify code smells, they only report pass/fail based on 
-%	whether or not a specific module runs. It is entirely possible that a test 
-%	case may pass for code that contains one or more code smells; (2) While 
-%	smells are certainly symptomatic of design flaws, not all smells cause the 
-%	system to fail in manner suitable for identification by test cases; and (3) 
-%	It make take a significant amount of effort to write new test cases that 
-%	identify bad smells, especially for stable software.
-%	
-%	Finally, in our work we tackle reorganization which subsumes refactoring. 
-%	Since not all reorganization efforts comprise of refactoring, that makes it 
-%	difficult to assert when test case will pass or fail. Thus, using test 
-%	suites is not a reliable option. 
-%	
-%	At your suggestion, we have now added this in \tion{eval} (please see text 
-%	marked {\color{steel} Reviewer2f}).\\
-%	
-%	\balance	
-%	
-%	\review{Figure 4 shows the effect of tuning, and the authors write: ``The 
-%	rows marked with a * in Figure 4 show data sets whose performance was 
-%	improved remarkably  by  these  techniques. For example, in poi, the recall 
-%	increased by 4\% while the false alarm rate dropped by 21\%.'' This is a 
-%	good example of researcher bias. Your example is the most favorable example 
-%	from your point of view. It is one of only two of the eight data sets that 
-%	improved on both pd and pf.}
-%	
-%	You are right \ldots ~there are only a few cases where we see an 
-%	improvement 
-%	in both recall and false alarm at the same time (poi, synapse and log4j). 
-%	But, we don't think is due to a researcher bias. Instead, this due to the 
-%	specifics of tuning and the goals used for this. We would like to draw your 
-%	attention to two other kinds of improvements as 
-%	a result of tuning: 
-%	
-%	\be 
-%	
-%	\item Cases where there is a significant 
-%	improvement in one measure (recall or false alarm) with no deterioration in 
-%	the other measure (Ivy, Jedit, Lucene, and Xalan); and 
-%	
-%	\item Cases where there is a significantly large improvement in one measure 
-%	with acceptable deterioration in the other metric (Poi and Ant).
-%	
-%	\ee
-%	
-%	\noindent We attribute these to the nature of multiobjective search 
-%	performed by 
-%	differential evolution. As highlighted by Fu et 
-%	al.~\cite{fu:ase15} (page 2, \S2.2), defining objectives for tuning is a 
-%	notoriously 
-%	difficult task. They find that tuning for recall or false alarms 
-%	independently can lead to some undesirable results. Tuning on recall yields 
-%	oracles that have near 100\% recall but with almost 100\% false alarm. 
-%	Similarly, tuning for only false alarm results in oracles that have 0\% 
-%	false alarm with 0\% recall. We take their advice and tune on metrics that 
-%	combine both precision and recall, thereby turning this into a 
-%	multiobjective search. Results in \fig{j} (previously Figure 4) show recall 
-%	and false alarms have reached a ``trade-off'' with maximum improvement, 
-%	such 
-%	is the nature of multiobjective differential evolution.
-%	
-%	
-%	Thank you for your comments, we ought to have had a formal discussion of 
-%	these in the paper. At your suggestion, these observations and reasons for 
-%	the same have now been dealt with in much greater detail in the current 
-%	version on the paper (see text marked with {\color{steel} Reviewer2g} in 
-%	\tion{tune})
-%	\\
-%	
-%		
-%	\review{The authors state that if there are no historical records of 
-%	defects, the results of this paper can be used as a guide (which results?). 
-%	It is referred to Table 8 in the abstract but there is no Table 8. Is it 
-%	meant to be Figure 8? In case, it’s very hard to understand how that figure 
-%	could be used.}
-%	
-%	A good catch ... there seems to be a typo, Table 8 has now 
-%	been replaced by \fig{multcomp} in the abstract. Regarding the 
-%	understandability 
-%	of~\fig{multcomp}, you are quite right in that we haven't provided 
-%	sufficient information explaining this. As per your suggestion, we have now 
-%	expanded the section that refers to this 
-%	figure (see text prefixed with {\color{steel} Reviewer2h} in 
-%	\tion{conjunct}) to better explain how the 
-%	conclusions 
-%	from this figure may be used when historical records are absent.
-
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+	%%% RESPONSE TO REVIEWERS
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+	\pagebreak
+	\newpage
+	\appendix
+	\renewcommand*{\thesection}{\Alph{section}}
+	\nobalance
+	\section*{RESPONSE TO REVIEWERS}
+	\section*{Comments from the editor}
+	\review{The reviewers recognized the improvements at the same time they 
+	raised some minor concerns regarding the content of the paper. Please, 
+	prepare an evolved version for a next verification. Use the reviewers' 
+	suggestions to make all changes needed.$\ldots$}
+
+	Thanks again for your comments. We have addressed all the concerns raised 
+	by the reviewers.
+
+	\review{Reviewer 1 suggested an additional reference that you have the 
+	freedom to 
+	consider it or not, depending on your interest on it. All other suggestions 
+	deserve your attention. }
+
+	We have taken into account the paper suggested by the reviewer. We found it 
+	very relevant to our work and have added it to our review in \S7.
+
+	\section*{Response to Reviewer \#1}
+
+	\review{Initially, I´d like to thank the authors for having appropriately 
+	addressed the comments from the first review. Now I have just minor 
+	comments on the paper:}
+
+	Thank you for your comments. We have taken your remarks into account and 
+	have made appropriate changes to the paper.\\
+
+	\review{I missed a last paragraph on the introduction presenting the 
+	structure of the paper (for example, ``Besides this introduction, Section 2 
+	presents\ldots. Next, Section 3 discusses…'').}
+
+	Thank you highlighting that. We have now added a paragraph toward the end 
+	of \S1
+	presenting the structure of the paper. Kindly see content marked 
+	{\color{steel2} Reviewer1a}.\\
+
+	\review{On Section 7, when you relate your approach with technical debt, 
+	I´d like to suggest you to also consider the mapping study cited below 
+	\ldots}
+
+	Thank you for recommending this paper. We have used this citation to expand 
+	our \S7 accordingly. Please see content marked 
+	{\color{steel2} Reviewer1b} in \S7.
+	\newpage
+	\section*{Response to Reviewer \#2}
+
+	\review{I’m happy with the great job the authors have done with the 
+	responses.}
+
+	Thank you very much for your comments. We have now addressed the comments 
+	in this 
+	revised version.\\
+
+	\review{I believe you missed my point, ``Your example is the most favorable 
+	example from your point of view. It is one of only two of the eight data 
+	sets that improved on both pd and pf.'' }
+
+	Thank you for that clarification. We see the issue. We have now added text 
+	to section \S5.2.1 providing example of failed cases in addition to 
+	positive sample. Kindly see content marked {\color{steel2}Reviewer 2a} in 
+	\S5.2.1.\\
+
+	\review{I still find the last two sentences in the abstract odd: ``This 
+	recommendation assumes that there is a historical record. If none exists, 
+	then the results of this paper could be used as a guide.''}
+
+	Thank you pointing that out. \textit{We have now removed these lines from 
+	the abstract} 
+	and have added it to relevant section in the body of paper. Briefly, we 
+	intended to 
+	convey the following with figure 9:
+	\bi
+	\item Some metrics (like loc) are best minimized as much as practically 
+	possible;
+	\item Developer need not hesitate leaving some metrics (like certain types 
+	of coupling) 
+	untouched or even maximize them when that's an option.
+	\ei
+
+	Please see content marked {\color{steel2} Reviewer2b} in \S6.5.
 \end{document}

### 2017-04-03 src/tools/oracle.py
Lab Machine Changes

@@ -6,7 +6,7 @@ from random import choice, seed as rseed, uniform as rand
 import pandas as pd
 import numpy as np
 from texttable import Texttable
-from stats import ABCD
+from stats import abcd
 from misc import *
 from pdb import set_trace
 from sklearn.neighbors import NearestNeighbors, BallTree, KDTree

### 2017-04-03 src/XTREE/XTREE.py
Lab Machine Changes

@@ -139,7 +139,6 @@ class patches:
             if i.testDF.iloc[n][-1] > 0 or i.testDF.iloc[n][-1] == True:
                 newRows.append(i.patchIt(i.testDF.iloc[n]))
             else:
-                set_trace()
                 newRows.append(i.testDF.iloc[n].tolist())
         return pd.DataFrame(newRows, columns=i.testDF.columns)
 

### 2017-04-03 src/run.py

@@ -8,6 +8,7 @@ root = os.path.join(os.getcwd().split('src')[0], 'src')
 if root not in sys.path:
     sys.path.append(root)
 
+from pdb import set_trace
 from oracle.model import rforest
 from Data.handler import get_train_test
 from XTREE.XTREE import execute
@@ -36,6 +37,9 @@ def change_efficacy(n_reps=1):
             seed(itr)
             patched = execute(train, test)
             before, after, __ = secondary_verification(train, test, patched)
+            if impact(before, after):
+                set_trace()
+
             res.append(impact(before, after))
         out.append(res)
 
